### 2018-06-06 index.Rmd
minimal template

--- 
title: "Oral Manuscript"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [lib.bib, packages.bib]
biblio-style: apalike
colorlinks: yes
lot: yes
lof: yes
fontsize: 12pt
link-citations: yes
#url: 'https://mgallow.github.io/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
---

# Prerequisites

Blah...

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

### 2018-06-06 _build.sh

@@ -1,3 +1,5 @@
 #!/bin/sh
 
 Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::gitbook')"
+
+Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::pdf_book')"

### 2018-06-06 _deploy.sh

@@ -5,12 +5,9 @@ set -e
 [ -z "${GITHUB_PAT}" ] && exit 0
 [ "${TRAVIS_BRANCH}" != "master" ] && exit 0
 
-git config --global user.email "xie@yihui.name"
-git config --global user.name "Yihui Xie"
+git config --global user.email "mgalloway42024@gmail.com"
+git config --global user.name "Matt Galloway"
 
-git clone -b gh-pages https://${GITHUB_PAT}@github.com/${TRAVIS_REPO_SLUG}.git book-output
-cd book-output
-cp -r ../_book/* ./
-git add --all *
-git commit -m"Update the book" || true
-git push -q origin gh-pages
+git add .
+git commit -m "Update the book" || true
+git push -q origin master

### 2018-06-06 _build.sh
bug fix

@@ -1,5 +1,0 @@
-#!/bin/sh
-
-Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::gitbook')"
-
-Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::pdf_book')"

### 2018-06-06 _deploy.sh

@@ -1,13 +1,0 @@
-#!/bin/sh
-
-set -e
-
-[ -z "${GITHUB_PAT}" ] && exit 0
-[ "${TRAVIS_BRANCH}" != "master" ] && exit 0
-
-git config --global user.email "mgalloway42024@gmail.com"
-git config --global user.name "Matt Galloway"
-
-git add .
-git commit -m "Update the book" || true
-git push -q origin master

### 2018-06-06 01-intro.Rmd
adjusted travis, fixed bug in report

# Introduction {#intro}

This is the introduction for Matt's oral manuscript.

### 2018-06-06 03-Details.Rmd
adjusted travis, fixed bug in report

# Details

Suppose we want to solve the following optimization problem:

\begin{align*}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{align*}

where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, and $c \in \mathbb{R}^{p}$. Following @boyd2011distributed, the optimization problem will be introduced in vector form though we will later consider cases where $x$ and $z$ are matrices. We will also assume $f$ and $g$ are convex functions. Optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods. For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem.

The *augmented lagrangian* is constructed as follows:

\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]

where $y \in \mathbb{R}^{p}$ is the lagrange multiplier and $\rho > 0$ is a scalar. Clearly any minimizer, $p^{*}$, under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point $(x, z)$ satisfies the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.

\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]

The alternating direction method of multipliers (ADMM) algorithm consists of the following repeated iterations:

\begin{align}
  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
\end{align}

A more complete introduction to the algorithm -- specifically how it arose out of *dual ascent* and *method of multipliers* -- can be found in @boyd2011distributed.

<br>\vspace{1cm}

## ADMM Algorithm

Now consider the case where $X_{1}, ..., X_{n}$ are iid $N_{p}(\mu, \Sigma)$ random variables and we are tasked with estimating the precision matrix, denoted $\Omega \equiv \Sigma^{-1}$. The maximum likelihood estimator for $\Omega$ is

\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]

where $S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n$ and $\bar{X}$ is the sample mean. By setting the gradient equal to zero, we can show that when the solution exists, $\hat{\Omega}_{MLE} = S^{-1}$.

As in regression settings, we can construct a *penalized* likelihood estimator by adding a penalty term, $P\left( \Omega \right)$, to the likelihood:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]

$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$. These penalties are the ridge and lasso, respectively. We will, instead, take $P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]$ so that the full penalized likelihood is

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]

where $0 \leq \alpha \leq 1$. This *elastic-net* penalty was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`. Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty.

By letting $f$ be equal to the non-penalized likelihood and $g$ equal to $P\left( \Omega \right)$, our goal is to minimize the full augmented lagrangian where the constraint is that $\Omega - Z$ is equal to zero:

\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]

The ADMM algorithm for estimating the penalized precision matrix in this problem is

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{align}

<br>\vspace{1cm}

## Scaled-Form ADMM

An alternate form of the ADMM algorithm can constructed by scaling the dual variable ($\Lambda^{k}$). Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.

\begin{align*}
  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
\end{align*}

Therefore, the condensed-form ADMM algorithm can now be written as

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
\end{align}

And more generally (in vector form),

\begin{align}
  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
\end{align}

Note that there are limitations to using this method. Because the dual variable is scaled by $\rho$ (the step size), this form limits one to using a constant step size without making further adjustments to $U^{k}$. It has been shown in the literature that a dynamic step size can significantly reduce the number of iterations required for convergence.

<br>\vspace{1cm}

## Algorithm

\begin{align*}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{align*}

<br>\vspace{1cm}

Initialize $Z^{0}, \Lambda^{0}$, and $\rho$. Iterate the following three steps until convergence:

1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ via spectral decomposition.

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]

2. Elementwise soft-thresholding for all $i = 1,..., p$ and $j = 1,..., p$.

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

3. Update $\Lambda^{k + 1}$.

\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]

<br>\vspace{1cm}

### Proof of (1):

\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]

\begin{align*}
  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\end{align*}

Set the gradient equal to zero and decompose $\Omega = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega$ and $V$ is the matrix with corresponding eigen vectors as columns.

\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{align*}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{align*}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]

<br>\vspace{1cm}

### Proof of (2)

\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]

\begin{align*}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
\end{align*}

where $Sign(Z)$ is the elementwise Sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij} > 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]

- If $Z_{ij} < 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that $Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

where $Soft$ is the soft-thresholding function.

<br><br>\newpage

<!-- \begin{thebibliography}{9} -->

<!-- \bibitem{1} -->
<!--   Boyd, Stephen, et al. "Distributed optimization and statistical learning via the alternating direction method of multipliers." Foundations and Trends® in Machine Learning 3.1 (2011): 1-122. -->

<!-- \bibitem{2} -->
<!--   Polson, Nicholas G., James G. Scott, and Brandon T. Willard. "Proximal algorithms in statistics and machine learning." Statistical Science 30.4 (2015): 559-581. -->

<!-- \bibitem{3} -->
<!--   Marjanovic, Goran, and Victor Solo. "On $ l_q $ optimization and matrix completion." IEEE Transactions on signal processing 60.11 (2012): 5714-5724. -->

<!-- \bibitem{4} -->
<!--   Zou, Hui, and Trevor Hastie. "Regularization and variable selection via the elastic net." Journal of the Royal Statistical Society: Series B (Statistical Methodology) 67.2 (2005): 301-320. -->

<!-- \end{thebibliography} -->

## References

### 2018-06-06 index.Rmd
bug fix
adjusted travis, fixed bug in report

@@
 documentclass: book
-bibliography: [lib.bib, packages.bib]
+#bibliography: [lib.bib, packages.bib]
+bibliography: lib.bib
 biblio-style: apalike
@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)
+
+# ```{r include=FALSE}
+# # automatically create a bib database for R packages
+# knitr::write_bib(c(
+#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
+# ), 'packages.bib')
+# ```
+
+```
+
 # Prerequisites
-
-Blah...
-
-```{r include=FALSE}
-# automatically create a bib database for R packages
-knitr::write_bib(c(
-  .packages(), 'bookdown', 'knitr', 'rmarkdown'
-), 'packages.bib')
-```

### 2018-06-06 _build.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+
+Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::gitbook')"
+
+Rscript -e "bookdown::render_book('index.Rmd', 'bookdown::pdf_book')"

### 2018-06-06 index.Rmd
added caching

@@
 colorlinks: yes
-lot: yes
-lof: yes
+lot: no
+lof: no
 fontsize: 12pt

### 2018-06-06 05-Benchmark.Rmd
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:master

# Benchmark

Below we benchmark the various functions contained in `ADMMsigma`. We can see that `ADMMsigma` (at the default tolerance) offers comparable computation time to the popular `glasso` R package.

### Computer Specs:

 - MacBook Pro (Late 2016)
 - Processor: 2.9 GHz Intel Core i5
 - Memory: 8GB 2133 MHz
 - Graphics: Intel Iris Graphics 550

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(ADMMsigma)
library(microbenchmark)

#  generate data from tri-diagonal (sparse) matrix
# compute covariance matrix (can confirm inverse is tri-diagonal)
S = matrix(0, nrow = 100, ncol = 100)

for (i in 1:100){
  for (j in 1:100){
    S[i, j] = 0.7^(abs(i - j))
  }
}

# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(1000*100), nrow = 1000, ncol = 100)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

# glasso (for comparison)
microbenchmark(glasso::glasso(s = S, rho = 0.1))

# benchmark ADMMsigma - default tolerance
microbenchmark(ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-4, tol.rel = 1e-4, trace = "none"))

# benchmark ADMMsigma - tolerance 1e-8
microbenchmark(ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-8, tol.rel = 1e-8, trace = "none"))

# benchmark ADMMsigma CV - default parameter grid
microbenchmark(ADMMsigma(X, trace = "none"), times = 5)

# benchmark ADMMsigma parallel CV
microbenchmark(ADMMsigma(X, cores = 3, trace = "none"), times = 5)

# benchmark ADMMsigma CV - likelihood convergence criteria
microbenchmark(ADMMsigma(X, crit = "loglik", trace = "none"), times = 5)

# benchmark RIDGEsigma CV
microbenchmark(RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none"), times = 5)

```

### 2018-06-06 _deploy.sh

@@ -1,0 +1,13 @@
+#!/bin/sh
+
+set -e
+
+[ -z "${GITHUB_PAT}" ] && exit 0
+[ "${TRAVIS_BRANCH}" != "master" ] && exit 0
+
+git config --global user.email "mgalloway42024@gmail.com"
+git config --global user.name "Matt Galloway"
+
+git add .
+git commit -m "Update the book" || true
+git push -q origin master

### 2018-06-06 02-Tutorial.Rmd
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:master

# Tutorial

<br>\vspace{0.5cm}
```{r, eval = FALSE, echo = TRUE}
# The easiest way to install is from CRAN
install.packages("ADMMsigma")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/ADMMsigma")
```
<br>\vspace{0.5cm}

If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/ADMMsigma/issues). You can also contact me via my [website](https://mgallow.github.io/). Pull requests are welcome!

<br>\vspace{0.5cm}

A (possibly incomplete) list of functions contained in the package can be found below:

* `ADMMsigma()` computes the estimated precision matrix (ridge, lasso, and elastic-net type regularization optional)

* `RIDGEsigma()` computes the estimated ridge penalized precision matrix via closed-form solution

* `plot.ADMMsigma()` produces a heat map or line graph for cross validation errors

* `plot.RIDGEsigma()` produces a heat map or line graph for cross validation errors

<br>\vspace{1cm}

## Usage

We will first generate data from a sparse, tri-diagonal precision matrix and denote it as Omega.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(ADMMsigma)

#  generate data from a sparse matrix
# first compute covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# print oracle precision matrix (shrinkage might be useful)
(Omega = round(qr.solve(S), 3))

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

# snap shot of data
head(X)

```
<br>\vspace{0.5cm}

As described earlier in the report, the maximum likelihood estimator (MLE) for Omega is the inverse of the sample precision matrix $S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}$:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print inverse of sample precision matrix (perhaps a bad estimate)
round(qr.solve(cov(X)*(nrow(X) - 1)/nrow(X)), 5)

```
<br>\vspace{0.5cm}

However, because Omega (known as the *oracle*) is sparse, a shrinkage estimator will perhaps perform better than the sample estimator. Below we construct various penalized estimators:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# elastic-net type penalty (set tolerance to 1e-8)
ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)

```
<br>\vspace{0.5cm}

**LASSO:**

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty (default tolerance)
ADMMsigma(X, alpha = 1)

```
<br>\vspace{0.5cm}

**ELASTIC-NET:**

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# elastic-net penalty (alpha = 0.5)
ADMMsigma(X, alpha = 0.5)

```
<br>\newpage

**RIDGE:**

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# ridge penalty
ADMMsigma(X, alpha = 0)

# ridge penalty no ADMM
RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01))

```
<br>\newpage

This package also has the capability to provide heat maps for the cross validation errors. The more bright (white) areas of the heat map pertain to more optimal tuning parameters.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# produce CV heat map for ADMMsigma
ADMM = ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)
plot(ADMM, type = "heatmap")

```
<br>\newpage

```{r, message = FALSE, echo = TRUE}

# produce line graph for CV errors for ADMMsigma
plot(ADMM, type = "line")

```
<br>\newpage

```{r, message = FALSE, echo = TRUE}

# produce CV heat map for RIDGEsigma
RIDGE = RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01))
plot(RIDGE, type = "heatmap")

```

<br>\newpage
```{r, message = FALSE, echo = TRUE}

# produce line graph for CV errors for RIDGEsigma
plot(RIDGE, type = "line")

```

### 2018-06-06 04-Simulations.Rmd
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:master

# Simulations

In the simulations below we generated data from a number of oracle precision matrices with various structures. For each data-generating procedure, the `ADMMsigma()` function was run using 5-fold cross validation. After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results in the top figure). These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure). We can see below that our cross validation procedure choosing tuning parameters close to the optimal parameters.

<br>\newpage

### Compound Symmetric: P = 100, N = 50

![](images/compound_N50_P100.png)

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# oracle precision matrix
Omega = matrix(0.9, ncol = 100, nrow = 100)
diag(Omega = 1)

# generate covariance matrix
S = qr.solve(Omega)

# generate data
Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

<br>\newpage

### Compound Symmetric: P = 10, N = 1000

![](images/compound_N1000_P10.png)

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# oracle precision matrix
Omega = matrix(0.9, ncol = 10, nrow = 10)
diag(Omega = 1)

# generate covariance matrix
S = qr.solve(Omega)

# generate data
Z = matrix(rnorm(10*1000), nrow = 1000, ncol = 10)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

<br>\newpage

### Dense: P = 100, N = 50

![](images/repsKLdenseQR_N50_P100.png)

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}

# generate eigen values
eigen = c(rep(1000, 5, rep(1, 100 - 5)))

# randomly generate orthogonal basis (via QR)
Q = matrix(rnorm(100*100), nrow = 100, ncol = 100) %>% qr %>% qr.Q

# generate covariance matrix
S = Q %*% diag(eigen) %*% t(Q)

# generate data
Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

<br>\newpage

### Dense: P = 10, N = 50

![](images/repsKLdense_N50_P10.png)

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}

# generate eigen values
eigen = c(rep(1000, 5, rep(1, 10 - 5)))

# randomly generate orthogonal basis (via QR)
Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q

# generate covariance matrix
S = Q %*% diag(eigen) %*% t(Q)

# generate data
Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

<br>\newpage

### Tridiagonal: P = 100, N = 50

![](images/repsKLtridiag_N50_P100.png)

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}

# generate covariance matrix
# (can confirm inverse is tri-diagonal)
S = matrix(0, nrow = 100, ncol = 100)
for (i in 1:100){
  for (j in 1:100){
    S[i, j] = 0.7^abs(i - j)
  }
}

# generate data
Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

### 2018-06-07 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[12pt,]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Oral Manuscript},
            pdfauthor={Matt Galloway},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{amsthm}
\makeatletter
\def\thm@space@setup{%
  \thm@preskip=8pt plus 2pt minus 4pt
  \thm@postskip=\thm@preskip
}
\makeatother
\usepackage[]{natbib}
\bibliographystyle{apalike}

\title{Oral Manuscript}
\author{Matt Galloway}
\date{2018-06-07}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\theoremstyle{definition}
\newtheorem{example}{Example}[chapter]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[chapter]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{prerequisites}{%
\chapter{Prerequisites}\label{prerequisites}}

\hypertarget{intro}{%
\chapter{Introduction}\label{intro}}

This is the introduction for Matt's oral manuscript. (UPDATED 8)

\hypertarget{tutorial}{%
\chapter{Tutorial}\label{tutorial}}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# The easiest way to install is from CRAN}
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"ADMMsigma"}\NormalTok{)}

\CommentTok{# You can also install the development version from GitHub:}
\CommentTok{# install.packages('devtools')}
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/ADMMsigma"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\vspace{0.5cm}

If there are any issues/bugs, please let me know:
\href{https://github.com/MGallow/ADMMsigma/issues}{github}. You can also
contact me via my \href{https://mgallow.github.io/}{website}. Pull
requests are welcome!

\vspace{0.5cm}

A (possibly incomplete) list of functions contained in the package can
be found below:

\begin{itemize}
\item
  \texttt{ADMMsigma()} computes the estimated precision matrix (ridge,
  lasso, and elastic-net type regularization optional)
\item
  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision
  matrix via closed-form solution
\item
  \texttt{plot.ADMMsigma()} produces a heat map or line graph for cross
  validation errors
\item
  \texttt{plot.RIDGEsigma()} produces a heat map or line graph for cross
  validation errors
\end{itemize}

\vspace{1cm}

\hypertarget{usage}{%
\section{Usage}\label{usage}}

We will first generate data from a sparse, tri-diagonal precision matrix
and denote it as Omega.

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(ADMMsigma)}

\CommentTok{# generate data from a sparse matrix first compute covariance matrix}
\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{5}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
\NormalTok{        S[i, j] =}\StringTok{ }\NormalTok{S[i, j]}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
\NormalTok{    \}}
\NormalTok{\}}

\CommentTok{# print oracle precision matrix (shrinkage might be useful)}
\NormalTok{(}\DataTypeTok{Omega =} \KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(S), }\DecValTok{3}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##        [,1]   [,2]   [,3]   [,4]   [,5]
## [1,]  1.961 -1.373  0.000  0.000  0.000
## [2,] -1.373  2.922 -1.373  0.000  0.000
## [3,]  0.000 -1.373  2.922 -1.373  0.000
## [4,]  0.000  0.000 -1.373  2.922 -1.373
## [5,]  0.000  0.000  0.000 -1.373  1.961
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{5}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}

\CommentTok{# snap shot of data}
\KeywordTok{head}\NormalTok{(X)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##            [,1]         [,2]         [,3]       [,4]        [,5]
## [1,] -0.4311177 -0.217744186  1.276826576 -0.1061308 -0.02363953
## [2,] -0.0418538  0.304253474  0.688201742 -0.5976510 -1.06758924
## [3,]  1.1344174  0.004493877 -0.440059159 -0.9793198 -0.86953222
## [4,] -0.0738241 -0.286438212  0.009577281 -0.7850619 -0.32351261
## [5,] -0.2905499 -0.906939891 -0.656034183 -0.4324413  0.28516534
## [6,]  1.3761967  0.276942730 -0.297518545 -0.2634814 -1.35944340
\end{verbatim}

\vspace{0.5cm}

As described earlier in the report, the maximum likelihood estimator
(MLE) for Omega is the inverse of the sample precision matrix
\(S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}\):

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# print inverse of sample precision matrix (perhaps a bad estimate)}
\KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(}\KeywordTok{cov}\NormalTok{(X) }\OperatorTok{*}\StringTok{ }\NormalTok{(}\KeywordTok{nrow}\NormalTok{(X) }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)}\OperatorTok{/}\KeywordTok{nrow}\NormalTok{(X)), }\DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.32976 -1.55033  0.22105 -0.08607  0.24309
## [2,] -1.55033  3.27561 -1.68026 -0.14277  0.18949
## [3,]  0.22105 -1.68026  3.19897 -1.25158 -0.11016
## [4,] -0.08607 -0.14277 -1.25158  2.76790 -1.37226
## [5,]  0.24309  0.18949 -0.11016 -1.37226  2.05377
\end{verbatim}

\vspace{0.5cm}

However, because Omega (known as the \emph{oracle}) is sparse, a
shrinkage estimator will perhaps perform better than the sample
estimator. Below we construct various penalized estimators:

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# elastic-net type penalty (set tolerance to 1e-8)}
\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call: ADMMsigma(X = X, tol.abs = 1e-08, tol.rel = 1e-08)
## 
## Iterations: 162
## 
## Tuning parameters:
##       log10(lam)  alpha
## [1,]      -1.599      1
## 
## Log-likelihood: -108.41003
## 
## Omega:
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.15283 -1.26902  0.00000  0.00000  0.19765
## [2,] -1.26902  2.79032 -1.32206 -0.08056  0.00925
## [3,]  0.00000 -1.32206  2.85470 -1.17072 -0.00865
## [4,]  0.00000 -0.08056 -1.17072  2.49554 -1.18959
## [5,]  0.19765  0.00925 -0.00865 -1.18959  1.88121
\end{verbatim}

\vspace{0.5cm}

\textbf{LASSO:}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# lasso penalty (default tolerance)}
\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call: ADMMsigma(X = X, alpha = 1)
## 
## Iterations: 66
## 
## Tuning parameters:
##       log10(lam)  alpha
## [1,]      -1.599      1
## 
## Log-likelihood: -108.41022
## 
## Omega:
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.15228 -1.26841  0.00000  0.00000  0.19744
## [2,] -1.26841  2.78830 -1.31943 -0.08246  0.01018
## [3,]  0.00000 -1.31943  2.84979 -1.16708 -0.01015
## [4,]  0.00000 -0.08246 -1.16708  2.49277 -1.18844
## [5,]  0.19744  0.01018 -0.01015 -1.18844  1.88069
\end{verbatim}

\vspace{0.5cm}

\textbf{ELASTIC-NET:}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# elastic-net penalty (alpha = 0.5)}
\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call: ADMMsigma(X = X, alpha = 0.5)
## 
## Iterations: 67
## 
## Tuning parameters:
##       log10(lam)  alpha
## [1,]      -1.821    0.5
## 
## Log-likelihood: -101.13595
## 
## Omega:
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.20031 -1.32471  0.01656 -0.00334  0.21798
## [2,] -1.32471  2.90659 -1.37599 -0.19084  0.13651
## [3,]  0.01656 -1.37599  2.92489 -1.12859 -0.12033
## [4,] -0.00334 -0.19084 -1.12859  2.56559 -1.23472
## [5,]  0.21798  0.13651 -0.12033 -1.23472  1.94528
\end{verbatim}

\newpage

\textbf{RIDGE:}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# ridge penalty}
\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{0}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call: ADMMsigma(X = X, alpha = 0)
## 
## Iterations: 65
## 
## Tuning parameters:
##       log10(lam)  alpha
## [1,]      -1.821      0
## 
## Log-likelihood: -99.19746
## 
## Omega:
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.18979 -1.31533  0.04515 -0.04090  0.23511
## [2,] -1.31533  2.90019 -1.37049 -0.22633  0.17808
## [3,]  0.04515 -1.37049  2.89435 -1.07647 -0.17369
## [4,] -0.04090 -0.22633 -1.07647  2.55026 -1.22786
## [5,]  0.23511  0.17808 -0.17369 -1.22786  1.95495
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# ridge penalty no ADMM}
\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Call: RIDGEsigma(X = X, lam = 10^seq(-8, 8, 0.01))
## 
## Tuning parameter:
##       log10(lam)    lam
## [1,]       -2.17  0.007
## 
## Log-likelihood: -109.18156
## 
## Omega:
##          [,1]     [,2]     [,3]     [,4]     [,5]
## [1,]  2.15416 -1.31185  0.08499 -0.05571  0.22862
## [2,] -1.31185  2.85605 -1.36677 -0.19650  0.16880
## [3,]  0.08499 -1.36677  2.82606 -1.06325 -0.14946
## [4,] -0.05571 -0.19650 -1.06325  2.50721 -1.21935
## [5,]  0.22862  0.16880 -0.14946 -1.21935  1.92871
\end{verbatim}

\newpage

This package also has the capability to provide heat maps for the cross
validation errors. The more bright (white) areas of the heat map pertain
to more optimal tuning parameters.

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# produce CV heat map for ADMMsigma}
\NormalTok{ADMM =}\StringTok{ }\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# produce line graph for CV errors for ADMMsigma}
\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# produce CV heat map for RIDGEsigma}
\NormalTok{RIDGE =}\StringTok{ }\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}

\newpage

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# produce line graph for CV errors for RIDGEsigma}
\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}

\hypertarget{details}{%
\chapter{Details}\label{details}}

Suppose we want to solve the following optimization problem:

\begin{align*}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{align*}

where
\(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\),
and \(c \in \mathbb{R}^{p}\). Following \citet{boyd2011distributed}, the
optimization problem will be introduced in vector form though we will
later consider cases where \(x\) and \(z\) are matrices. We will also
assume \(f\) and \(g\) are convex functions. Optimization problems like
this arise naturally in several statistics and machine learning
applications -- particularly regularization methods. For instance, we
could take \(f\) to be the squared error loss, \(g\) to be the
\(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be
identity matrices to solve the ridge regression optimization problem.

The \emph{augmented lagrangian} is constructed as follows:

\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]

where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and
\(\rho > 0\) is a scalar. Clearly any minimizer, \(p^{*}\), under the
augmented lagrangian is equivalent to that of the lagrangian since any
feasible point \((x, z)\) satisfies the constraint
\(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).

\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]

The alternating direction method of multipliers (ADMM) algorithm
consists of the following repeated iterations:

\begin{align}
  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
\end{align}

A more complete introduction to the algorithm -- specifically how it
arose out of \emph{dual ascent} and \emph{method of multipliers} -- can
be found in \citet{boyd2011distributed}.

\vspace{1cm}

\hypertarget{admm-algorithm}{%
\section{ADMM Algorithm}\label{admm-algorithm}}

Now consider the case where \(X_{1}, ..., X_{n}\) are iid
\(N_{p}(\mu, \Sigma)\) random variables and we are tasked with
estimating the precision matrix, denoted \(\Omega \equiv \Sigma^{-1}\).
The maximum likelihood estimator for \(\Omega\) is

\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]

where \(S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n\)
and \(\bar{X}\) is the sample mean. By setting the gradient equal to
zero, we can show that when the solution exists,
\(\hat{\Omega}_{MLE} = S^{-1}\).

As in regression settings, we can construct a \emph{penalized}
likelihood estimator by adding a penalty term,
\(P\left( \Omega \right)\), to the likelihood:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]

\(P\left( \Omega \right)\) is often of the form
\(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}\) or
\(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\),
\(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define
\(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\). These
penalties are the ridge and lasso, respectively. We will, instead, take
\(P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]\)
so that the full penalized likelihood is

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]

where \(0 \leq \alpha \leq 1\). This \emph{elastic-net} penalty was
explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and
is identical to the penalty used in the popular penalized regression
package \texttt{glmnet}. Clearly, when \(\alpha = 0\) the elastic-net
reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a
lasso-type penalty.

By letting \(f\) be equal to the non-penalized likelihood and \(g\)
equal to \(P\left( \Omega \right)\), our goal is to minimize the full
augmented lagrangian where the constraint is that \(\Omega - Z\) is
equal to zero:

\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]

The ADMM algorithm for estimating the penalized precision matrix in this
problem is

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{align}

\vspace{1cm}

\hypertarget{scaled-form-admm}{%
\section{Scaled-Form ADMM}\label{scaled-form-admm}}

An alternate form of the ADMM algorithm can constructed by scaling the
dual variable (\(\Lambda^{k}\)). Let us define
\(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).

\begin{align*}
  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
\end{align*}

Therefore, the condensed-form ADMM algorithm can now be written as

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
\end{align}

And more generally (in vector form),

\begin{align}
  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
\end{align}

Note that there are limitations to using this method. Because the dual
variable is scaled by \(\rho\) (the step size), this form limits one to
using a constant step size without making further adjustments to
\(U^{k}\). It has been shown in the literature that a dynamic step size
can significantly reduce the number of iterations required for
convergence.

\vspace{1cm}

\hypertarget{algorithm}{%
\section{Algorithm}\label{algorithm}}

\begin{align*}
  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{align*}

\vspace{1cm}

Initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Iterate the following
three steps until convergence:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) via spectral
  decomposition.
\end{enumerate}

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Elementwise soft-thresholding for all \(i = 1,..., p\) and
  \(j = 1,..., p\).
\end{enumerate}

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Update \(\Lambda^{k + 1}\).
\end{enumerate}

\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]

\vspace{1cm}

\hypertarget{proof-of-1}{%
\subsection{Proof of (1):}\label{proof-of-1}}

\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]

\begin{align*}
  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\end{align*}

Set the gradient equal to zero and decompose \(\Omega = VDV^{T}\) where
\(D\) is a diagonal matrix with diagonal elements equal to the eigen
values of \(\Omega\) and \(V\) is the matrix with corresponding eigen
vectors as columns.

\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]

where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.

\begin{align*}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{align*}

In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\)
then

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]

\vspace{1cm}

\hypertarget{proof-of-2}{%
\subsection{Proof of (2)}\label{proof-of-2}}

\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]

\begin{align*}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
\end{align*}

where \(Sign(Z)\) is the elementwise Sign operator. By setting the
gradient/sub-differential equal to zero, we arrive at the following
equivalence:

\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]

for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:

\begin{itemize}
\tightlist
\item
  If \(Z_{ij} > 0\) then
\end{itemize}

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]

\begin{itemize}
\tightlist
\item
  If \(Z_{ij} < 0\) then
\end{itemize}

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that
\(Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\).
Putting all the pieces together, we arrive at

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

where \(Soft\) is the soft-thresholding function.

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{simulations}{%
\chapter{Simulations}\label{simulations}}

In the simulations below we generated data from a number of oracle
precision matrices with various structures. For each data-generating
procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross
validation. After 20 replications, the cross validation errors were
totalled and the optimal tuning parameters were selected (results in the
top figure). These results are compared with the Kullback Leibler (KL)
losses between the estimates and the oracle precision matrix (bottom
figure). We can see below that our cross validation procedure choosing
tuning parameters close to the optimal parameters.

\newpage

\hypertarget{compound-symmetric-p-100-n-50}{%
\subsection{Compound Symmetric: P = 100, N =
50}\label{compound-symmetric-p-100-n-50}}

\includegraphics{images/compound_N50_P100.png}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# oracle precision matrix}
\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{)}
\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}

\CommentTok{# generate covariance matrix}
\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}

\CommentTok{# generate data}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
\end{Highlighting}
\end{Shaded}

\newpage

\hypertarget{compound-symmetric-p-10-n-1000}{%
\subsection{Compound Symmetric: P = 10, N =
1000}\label{compound-symmetric-p-10-n-1000}}

\includegraphics{images/compound_N1000_P10.png}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# oracle precision matrix}
\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{)}
\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}

\CommentTok{# generate covariance matrix}
\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}

\CommentTok{# generate data}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{1000}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
\end{Highlighting}
\end{Shaded}

\newpage

\hypertarget{dense-p-100-n-50}{%
\subsection{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}

\includegraphics{images/repsKLdenseQR_N50_P100.png}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# generate eigen values}
\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{100} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}

\CommentTok{# randomly generate orthogonal basis (via QR)}
\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}

\CommentTok{# generate covariance matrix}
\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}

\CommentTok{# generate data}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
\end{Highlighting}
\end{Shaded}

\newpage

\hypertarget{dense-p-10-n-50}{%
\subsection{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}

\includegraphics{images/repsKLdense_N50_P10.png}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# generate eigen values}
\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}

\CommentTok{# randomly generate orthogonal basis (via QR)}
\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{10}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}

\CommentTok{# generate covariance matrix}
\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}

\CommentTok{# generate data}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
\end{Highlighting}
\end{Shaded}

\newpage

\hypertarget{tridiagonal-p-100-n-50}{%
\subsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}

\includegraphics{images/repsKLtridiag_N50_P100.png}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# generate covariance matrix}
\CommentTok{# (can confirm inverse is tri-diagonal)}
\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
\NormalTok{    S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
\NormalTok{  \}}
\NormalTok{\}}

\CommentTok{# generate data}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
\end{Highlighting}
\end{Shaded}

\hypertarget{benchmark}{%
\chapter{Benchmark}\label{benchmark}}

Below we benchmark the various functions contained in
\texttt{ADMMsigma}. We can see that \texttt{ADMMsigma} (at the default
tolerance) offers comparable computation time to the popular
\texttt{glasso} R package.

\hypertarget{computer-specs}{%
\subsection{Computer Specs:}\label{computer-specs}}

\begin{itemize}
\tightlist
\item
  MacBook Pro (Late 2016)
\item
  Processor: 2.9 GHz Intel Core i5
\item
  Memory: 8GB 2133 MHz
\item
  Graphics: Intel Iris Graphics 550
\end{itemize}

\vspace{0.5cm}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(ADMMsigma)}
\KeywordTok{library}\NormalTok{(microbenchmark)}

\CommentTok{# generate data from tri-diagonal (sparse) matrix compute covariance matrix}
\CommentTok{# (can confirm inverse is tri-diagonal)}
\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}

\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
\NormalTok{        S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\NormalTok{(}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j))}
\NormalTok{    \}}
\NormalTok{\}}

\CommentTok{# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)}
\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{1000} \OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}

\CommentTok{# glasso (for comparison)}
\KeywordTok{microbenchmark}\NormalTok{(glasso}\OperatorTok{::}\KeywordTok{glasso}\NormalTok{(}\DataTypeTok{s =}\NormalTok{ S, }\DataTypeTok{rho =} \FloatTok{0.1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: milliseconds
##                              expr      min       lq     mean   median
##  glasso::glasso(s = S, rho = 0.1) 49.46673 53.37757 58.35196 55.90935
##        uq      max neval
##  60.77517 92.68082   100
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark ADMMsigma - default tolerance}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-04}\NormalTok{, }
    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: milliseconds
##                                                                                           expr
##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-04, tol.rel = 1e-04,      trace = "none")
##      min       lq     mean   median       uq      max neval
##  77.2134 83.51351 89.71565 85.37738 94.37814 126.0049   100
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark ADMMsigma - tolerance 1e-8}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{, }
    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: milliseconds
##                                                                                           expr
##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-08, tol.rel = 1e-08,      trace = "none")
##       min       lq     mean   median       uq      max neval
##  258.5389 261.5402 272.3741 267.8829 274.7276 353.4726   100
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark ADMMsigma CV - default parameter grid}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: seconds
##                          expr      min       lq     mean   median       uq
##  ADMMsigma(X, trace = "none") 8.338241 8.341611 8.536446 8.472933 8.515822
##       max neval
##  9.013621     5
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark ADMMsigma parallel CV}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{cores =} \DecValTok{3}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: seconds
##                                     expr      min       lq     mean
##  ADMMsigma(X, cores = 3, trace = "none") 9.285137 9.315978 9.470666
##   median       uq      max neval
##  9.40943 9.426579 9.916207     5
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark ADMMsigma CV - likelihood convergence criteria}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{crit =} \StringTok{"loglik"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: seconds
##                                           expr      min       lq     mean
##  ADMMsigma(X, crit = "loglik", trace = "none") 7.028816 7.121599 7.185927
##    median       uq      max neval
##  7.181803 7.277249 7.320166     5
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# benchmark RIDGEsigma CV}
\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{), }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Unit: seconds
##                                                      expr      min
##  RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none") 12.22374
##        lq     mean   median       uq      max neval
##  12.37326 12.93705 13.01892 13.04356 14.02577     5
\end{verbatim}

\bibliography{lib.bib}

\end{document}

### 2018-06-12 index.Rmd
reduced font

@@
 lof: no
-fontsize: 12pt
+fontsize: 11pt
 link-citations: yes

### 2018-06-20 03-Details.Rmd
test

@@
 
-\begin{align*}
+$$ \begin{align*}
   \mbox{minimize } f(x) + g(z) \\
   \mbox{subject to } Ax + Bz = c
-\end{align*}
+\end{align*} $$
 
@@
 where $Soft$ is the soft-thresholding function.
-
-<br><br>\newpage
-
-<!-- \begin{thebibliography}{9} -->
-
-<!-- \bibitem{1} -->
-<!--   Boyd, Stephen, et al. "Distributed optimization and statistical learning via the alternating direction method of multipliers." Foundations and Trends® in Machine Learning 3.1 (2011): 1-122. -->
-
-<!-- \bibitem{2} -->
-<!--   Polson, Nicholas G., James G. Scott, and Brandon T. Willard. "Proximal algorithms in statistics and machine learning." Statistical Science 30.4 (2015): 559-581. -->
-
-<!-- \bibitem{3} -->
-<!--   Marjanovic, Goran, and Victor Solo. "On $ l_q $ optimization and matrix completion." IEEE Transactions on signal processing 60.11 (2012): 5714-5724. -->
-
-<!-- \bibitem{4} -->
-<!--   Zou, Hui, and Trevor Hastie. "Regularization and variable selection via the elastic net." Journal of the Royal Statistical Society: Series B (Statistical Methodology) 67.2 (2005): 301-320. -->
-
-<!-- \end{thebibliography} -->
-
-## References

### 2018-06-20 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

@@
 %
-\documentclass[12pt,]{book}
+\documentclass[11pt,]{book}
 \usepackage{lmodern}
@@
 \author{Matt Galloway}
-\date{2018-06-07}
+\date{2018-06-20}
 
@@
 
-\begin{align*}
+\[
+\begin{aligned}
   \mbox{minimize } f(x) + g(z) \\
   \mbox{subject to } Ax + Bz = c
-\end{align*}
+\end{aligned}
+\]
 
@@
 
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
 \hypertarget{simulations}{%
@@
 
-\newpage
-
 \hypertarget{compound-symmetric-p-100-n-50}{%
-\subsection{Compound Symmetric: P = 100, N =
+\section{Compound Symmetric: P = 100, N =
 50}\label{compound-symmetric-p-100-n-50}}
@@
 
-\newpage
-
 \hypertarget{compound-symmetric-p-10-n-1000}{%
-\subsection{Compound Symmetric: P = 10, N =
+\section{Compound Symmetric: P = 10, N =
 1000}\label{compound-symmetric-p-10-n-1000}}
@@
 
-\newpage
-
 \hypertarget{dense-p-100-n-50}{%
-\subsection{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
+\section{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
 
@@
 
-\newpage
-
 \hypertarget{dense-p-10-n-50}{%
-\subsection{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
+\section{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
 
@@
 
-\newpage
-
 \hypertarget{tridiagonal-p-100-n-50}{%
-\subsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
+\section{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
 
@@
 
+\hypertarget{penalized-regression-estimators}{%
+\chapter{Penalized Regression
+Estimators}\label{penalized-regression-estimators}}
+
+This document explores a number of regression estimators subject to
+various assumptions. We will assume \(n\) samples of
+
+\[ Y_{i} = \mu_{y} + \beta^{T}(X_{i} - \mu_{x}) + \epsilon_{i} \]
+
+where \(\epsilon_{i} \sim N_{r}\left(0, \Sigma_{y | x} \right)\) and
+\(X_{i} \sim N_{p}\left(0, \Sigma_{x}\right)\) so that by taking
+\(\theta = \left( \mu_{y}, \mu_{x}, vec\left( \beta \right), vec\left( \Sigma_{y | x}^{-1} \right), vec\left( \Sigma_{xx}^{-1} \right) \right)^{T}\)
+the joint log-likelihood is of the following form:
+
+\begin{align*}
+  l(\theta) &= \frac{nr}{2}log(2\pi) - \frac{n}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left( X_{i} - \mu_{x} \right) \right)^{T}\Sigma_{y | x}^{-1}\left( Y_{i} - \mu_{y} - \beta^{T}\left( X_{i} - \mu_{x} \right) \right) \\
+  &+ \frac{np}{2}log(2\pi) - \frac{n}{2}log\left| \Sigma_{xx}^{-1} \right| + \frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)^{T}\Sigma_{xx}^{1}\left( X_{i} - \mu_{x} \right) \\
+\end{align*}
+
+For convenience, we will later denote \(\mathbb{X}\) as the
+\(n \times p\) matrix with rows \(X_{i} - \bar{X}\) where
+\(\bar{X} = \sum_{i = 1}^{n}X_{i}/n\) and \(\mathbb{Y}\) as the
+\(n \times r\) matrix with rows \(Y_{i} - \bar{Y}\) and \(\bar{Y}\)
+defined similarly. Note that \(\bar{X}\) and \(\bar{Y}\) are the maximum
+likelihood esitmators of \(\mu_{x}\) and \(\mu_{y}\), respectively.
+
+\hypertarget{formulas}{%
+\section{Formulas}\label{formulas}}
+
+Below we outline a few important formulas that will be used throughout
+this report:
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Forward regression coefficient:
+  \(\beta = \Sigma_{xx}^{-1}\Sigma_{xy} = \Sigma_{x | y}^{-1}\alpha^{T}\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Inverse regression coefficient:
+  \(\alpha = \Sigma_{yy}^{-1}\Sigma_{xy}^{T}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  \(\Sigma_{y | x} = \Sigma_{yy} - \beta^{T}\Sigma_{xx}\beta = \Sigma_{yy} - \Sigma_{xy}^{T}\Sigma_{xx}^{-1}\Sigma_{xy}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  \(\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{yy} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  \(\Sigma_{x | y} = \Sigma_{xx} - \alpha^{T}\Sigma_{yy}\alpha = \Sigma_{xx} - \Sigma_{xy}\Sigma_{yy}^{-1}\Sigma_{xy}^{T}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{5}
+\tightlist
+\item
+  \(\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{6}
+\tightlist
+\item
+  \(\Sigma_{yy}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{xx} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}\)
+\end{enumerate}
+
+\vspace{0.5cm}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{7}
+\tightlist
+\item
+  \(\Sigma_{xx}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}\)
+\end{enumerate}
+
+\newpage
+
+\hypertarget{estimators}{%
+\section{Estimators}\label{estimators}}
+
+\hypertarget{assume-ridge-beta-optimize-in-sample-prediction-error}{%
+\subsection{\texorpdfstring{Assume ridge \(\beta\), optimize in-sample
+prediction
+error}{Assume ridge \textbackslash{}beta, optimize in-sample prediction error}}\label{assume-ridge-beta-optimize-in-sample-prediction-error}}
+
+\[ \hat{\beta} = \arg\min_{\beta}\left\{\frac{1}{2} \left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \beta \right\|_{F}^{2}\right\} \]
+
+\begin{align*}
+  &\Rightarrow -\mathbb{X}^{T}\left( \mathbb{Y} - \mathbb{X}\hat{\beta} \right) + \lambda\hat{\beta} = 0 \\
+  & \\
+  &\Rightarrow \hat{\beta} = \left( \mathbb{X}^{T}\mathbb{X} + \lambda I_{p} \right)^{-1}\mathbb{X}^{T}\mathbb{Y} = \mathbb{X}^{T}\left( \mathbb{X}\mathbb{X}^{T} + \lambda I_{n} \right)^{-1}\mathbb{Y}
+\end{align*}
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-beta-optimize-the-likelihood-for-beta}{%
+\subsection{\texorpdfstring{Assume ridge \(\beta\), optimize the
+likelihood for
+\(\beta\)}{Assume ridge \textbackslash{}beta, optimize the likelihood for \textbackslash{}beta}}\label{assume-ridge-beta-optimize-the-likelihood-for-beta}}
+
+\[ \hat{\beta} = \arg\min_{\beta}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{Y} - \mathbb{X}\beta \right)^{T}\left( \mathbb{Y} - \mathbb{X}\beta \right)\Sigma_{y | x}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{\lambda}{n}\left\| \beta \right\|_{F}^{2} \right\} \]
+
+\begin{align*}
+  &\Rightarrow -\frac{2}{n}\mathbb{X}^{T}\left( \mathbb{Y} - \mathbb{X}\hat{\beta} \right)\hat{\Sigma}_{y | x}^{-1} + \frac{2}{n}\lambda\hat{\beta} = 0 \Rightarrow \left( \hat{\Sigma}_{y | x}^{-1} \otimes \mathbb{X}^{T}\mathbb{X} \right)vec\left( \hat{\beta} \right) + \lambda vec\left( \hat{\beta} \right) = vec\left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1} \right) \\
+  & \\
+  &\Rightarrow vec\left( \hat{\beta} \right) = \left( \hat{\Sigma}_{y | x}^{-1} \otimes \mathbb{X}^{T}\mathbb{X} + \lambda I_{pr} \right)^{-1}vec\left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1} \right) \\
+\end{align*}
+
+where
+\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\).
+In order to solve for \(\hat{\beta}\), we need to iterate between
+\(\hat{\beta}\) and \(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+
+Note that if \(r = 1\) then \(\sigma_{y}^{2}\) can be absorbed into
+\(\tilde{\lambda}\) and
+
+\[ \hat{\beta} = \left( \mathbb{X}^{T}\mathbb{X} + \tilde{\lambda}I_{p} \right)^{-1}\mathbb{X}^{T}\mathbb{Y} = \mathbb{X}^{T}\left( \mathbb{X}\mathbb{X}^{T} + \tilde{\lambda}_{n}I_{n} \right)^{-1}\mathbb{Y} \]
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_xx-1-optimize-in-sample-prediction-error}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
+in-sample prediction
+error}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize in-sample prediction error}}\label{assume-ridge-sigma_xx-1-optimize-in-sample-prediction-error}}
+
+\begin{align*}
+  \hat{\Sigma}_{xx}^{-1} &= \arg\min_{\Sigma_{xx}^{-1}}\left\{ \frac{1}{2}\left\| \mathbb{Y} - \mathbb{X}\mathbb{\beta} \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} \\
+  & \\
+  &= \arg\min_{\Sigma_{xx}^{-1}}\left\{ \frac{1}{2}\left\| \mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} \\
+\end{align*}
+
+\begin{align*}
+  \nabla_{\Sigma_{xx}^{-1}}&\left\{ \frac{1}{2}Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right) \right] + \frac{\lambda}{2}Tr\left[ \Sigma_{xx}^{-1}\Sigma_{xx}^{-1} \right] \right\} \\
+  & \\
+  &= -\mathbb{X}^{T}\mathbb{Y}\Sigma_{xy}^{T} + \mathbb{X}^{T}\mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy}\Sigma_{xy}^{T} + \lambda\Sigma_{xx}^{-1} \\
+  & \\
+  &\Rightarrow vec\left( \hat{\Sigma}_{xx}^{-1} \right) = \left(\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} \otimes \mathbb{X}^{T}\mathbb{X} + \lambda I_{pp} \right)^{-1}vec\left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy}^{T} \right) \\
+\end{align*}
+
+If we use the sample estimate
+\(\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n\) then
+
+\[ vec\left( \hat{\Sigma}_{xx}^{-1} \right) = \left( \mathbb{X}^{T}\mathbb{Y}\mathbb{Y}^{T}\mathbb{X} \otimes \frac{1}{n}\mathbb{X}^{T}\mathbb{X} + \tilde{\lambda}I_{pp} \right)^{-1}vec\left( \mathbb{X}^{T}\mathbb{Y}\mathbb{Y}^{T}\mathbb{X} \right) \]
+
+so that
+\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\).
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_xx-1-optimize-likelihood-for-beta}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
+likelihood for
+\(\beta\)}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize likelihood for \textbackslash{}beta}}\label{assume-ridge-sigma_xx-1-optimize-likelihood-for-beta}}
+
+\begin{align*}
+  \hat{\Sigma}_{xx}^{-1} &= \arg\min_{\Sigma_{xx}^{-1}}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{Y} - \mathbb{X}\beta \right)^{T}\left( \mathbb{Y} - \mathbb{X}\beta \right)\Sigma_{y | x}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{\lambda}{n}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} \\
+  & \\
+  &= \arg\min_{\Sigma_{xx}^{-1}}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)\Sigma_{y | x}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{\lambda}{n}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} \\
+\end{align*}
+
+\begin{align*}
+  \nabla_{\Sigma_{xx}^{-1}}&\left\{ \frac{1}{n}Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)\Sigma_{y | x}^{-1} \right] + \frac{\lambda}{n}Tr\left[ \Sigma_{xx}^{-1}\Sigma_{xx}^{-1} \right] \right\} \\
+  & \\
+  &= -\frac{2}{n}\mathbb{X}^{T}\mathbb{Y}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} + \frac{2}{n}\mathbb{X}^{T}\mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} + \frac{2\lambda}{n}\Sigma_{xx}^{-1} \\
+  & \\
+  &\Rightarrow vec\left( \hat{\Sigma}_{xx}^{-1} \right) = \left(\hat{\Sigma}_{xy}\hat{\Sigma}_{y | x}^{-1}\hat{\Sigma}_{xy}^{T} \otimes \mathbb{X}^{T}\mathbb{X} + \lambda I_{pp} \right)^{-1}vec\left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1}\hat{\Sigma}_{xy}^{T} \right) \\
+\end{align*}
+
+If we use the sample estimate
+\(\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n\) then
+
+\[ vec\left( \hat{\Sigma}_{xx}^{-1} \right) = \left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1}\mathbb{Y}^{T}\mathbb{X} \otimes \frac{1}{n}\mathbb{X}^{T}\mathbb{X} + \tilde{\lambda}I_{pp} \right)^{-1}vec\left( \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1}\mathbb{Y}^{T}\mathbb{X} \right) \]
+
+where
+\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\)
+so that in order to solve for
+\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\),
+we need to iterate between \(\hat{\beta}\) and
+\(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_xx-1-optimize-likelihood-for-sigma_xx-1}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
+likelihood for
+\(\Sigma_{xx}^{-1}\)}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize likelihood for \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}}}\label{assume-ridge-sigma_xx-1-optimize-likelihood-for-sigma_xx-1}}
+
+\[ \hat{\Sigma}_{xx}^{-1} = \arg\min_{\Sigma_{xx}^{-1}}\left\{ Tr\left( S_{xx}\Sigma_{xx}^{-1} \right) - log\left| \Sigma_{xx}^{-1} \right| + \frac{\lambda}{2}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} \]
+
+\begin{align*}
+  \nabla_{\Sigma_{xx}^{-1}}&\left\{ Tr\left( S_{xx}\Sigma_{xx}^{-1} \right) - \log\det\left( \Sigma_{xx}^{-1} \right) + \frac{\lambda}{2}\left\| \Sigma_{xx}^{-1} \right\|_{F}^{2} \right\} = S_{xx} - \Sigma_{xx} + \lambda\Sigma_{xx}^{-1} \\
+\end{align*}
+
+where \(S_{xx} = \mathbb{X}^{T}\mathbb{X}/n\). Set the gradient equal to
+zero and decompose \(\Sigma_{xx}^{-1} = VDV^{T}\) where \(D\) is a
+diagonal matrix with diagonal elements equal to the eigen values of
+\(\Sigma_{xx}^{-1}\) and \(V\) is the matrix with corresponding eigen
+vectors as columns.
+
+\[ S_{xx} = \Sigma_{xx} - \lambda\Sigma_{xx}^{-1} = VD^{-1}V^{T} - \lambda VDV^{T} = V\left(D^{-1} - \lambda D \right)V{^T} \]
+
+This equivalence implies that
+
+\[ \phi_{j}\left( S_{xx} \right) = \frac{1}{\phi_{j}(\Sigma_{xx}^{-1})} - \lambda\phi_{j}\left( \Sigma_{xx}^{-1} \right) \]
+
+where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
+
+\begin{align*}
+  &\Rightarrow \lambda\phi_{j}^{2}\left( \Sigma_{xx}^{-1} \right) + \phi_{j}\left( S_{xx} \right)\phi_{j}\left( \Sigma_{xx}^{-1} \right) - 1 = 0 \\
+  & \\
+  &\Rightarrow \phi_{j}\left( \Sigma_{xx}^{-1} \right) = \frac{-\phi_{j}\left( S_{xx} \right) \pm \sqrt{\phi_{j}^{2}\left( S_{xx} \right) + 4\lambda}}{2\lambda}
+\end{align*}
+
+In summary, if we decompose \(S_{xx} = VQV^{T}\) then
+
+\[ \hat{\Sigma}_{xx}^{-1} = \frac{1}{2\lambda}V\left[ -Q + \left( Q^{2} + 4\lambda I_{p} \right)^{1/2} \right]V^{T} \]
+
+so that
+\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\Sigma_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\).
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_xy-optimize-in-sample-prediction-error}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xy}\), optimize
+in-sample prediction
+error}{Assume ridge \textbackslash{}Sigma\_\{xy\}, optimize in-sample prediction error}}\label{assume-ridge-sigma_xy-optimize-in-sample-prediction-error}}
+
+\begin{align*}
+  \hat{\Sigma}_{xy} &= \arg\min_{\Sigma_{xy}}\left\{ \frac{1}{2}\left\| \mathbb{Y} - \mathbb{X}\mathbb{\beta} \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \Sigma_{xy} \right\|_{F}^{2} \right\} \\
+  & \\
+  &= \arg\min_{\Sigma_{xy}}\left\{ \frac{1}{2}\left\| \mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \Sigma_{xy} \right\|_{F}^{2} \right\} \\
+\end{align*}
+
+\begin{align*}
+  \nabla_{\Sigma_{xy}}&\left\{ \frac{1}{2}Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right) \right] + \frac{\lambda}{2}Tr\left[ \Sigma_{xy}\Sigma_{xy} \right] \right\} \\
+  & \\
+  &= -\Sigma_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y} + \Sigma_{xx}^{-1}\mathbb{X}^{T}\mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} + \lambda\Sigma_{xy} \\
+  & \\
+  &\Rightarrow \hat{\Sigma}_{xy} = \left(\hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{X}\hat{\Sigma}_{xx}^{-1} + \lambda I_{p} \right)^{-1}\hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y} \\
+\end{align*}
+
+If we use the sample estimate
+\(\hat{\Sigma}_{xx} = \mathbb{X}^{T}\mathbb{X}/n\) (assuming
+\(\mathbb{X}^{T}\mathbb{X}\) is positive definite) then
+
+\[ \hat{\Sigma}_{xy} = \left[\left(\mathbb{X}^{T}\mathbb{X} \right)^{-1} + \tilde{\lambda}I_{p} \right]^{-1}\left(\mathbb{X}^{T}\mathbb{X} \right)^{-1}\mathbb{X}^{T}\mathbb{Y}/n = \left( I_{p} + \tilde{\lambda}\mathbb{X}^{T}\mathbb{X} \right)^{-1}\mathbb{X}^{T}\mathbb{Y}/n \]
+
+so that
+
+\begin{align*}
+  \hat{\beta} &= \left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\left[ \left( \mathbb{X}^{T}\mathbb{X} \right)^{-1} + \tilde{\lambda}I_{p} \right]^{-1}\left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\mathbb{X}^{T}\mathbb{Y} \\
+  & \\
+  &= \left[ \mathbb{X}^{T}\mathbb{X}\left( I_{p} + \tilde{\lambda}\mathbb{X}^{T}\mathbb{X} \right) \right]^{-1}\mathbb{X}^{T}\mathbb{X} = \left( \mathbb{X}^{T}\mathbb{X} + \tilde{\lambda}\mathbb{X}^{T}\mathbb{X}\mathbb{X}^{T}\mathbb{X} \right)^{-1}\mathbb{X}^{T}\mathbb{Y}
+\end{align*}
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_xy-optimize-likelihood-for-beta}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xy}\), optimize
+likelihood for
+\(\beta\)}{Assume ridge \textbackslash{}Sigma\_\{xy\}, optimize likelihood for \textbackslash{}beta}}\label{assume-ridge-sigma_xy-optimize-likelihood-for-beta}}
+
+\begin{align*}
+  \hat{\Sigma}_{xy} &= \arg\min_{\Sigma_{xy}}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{Y} - \mathbb{X}\beta \right)^{T}\left( \mathbb{Y} - \mathbb{X}\beta \right)\Sigma_{y | x}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{\lambda}{n}\left\| \Sigma_{xy} \right\|_{F}^{2} \right\} \\
+  & \\
+  &= \arg\min_{\Sigma_{xy}}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)\Sigma_{y | x}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{y | x}^{-1} \right| + \frac{\lambda}{n}\left\| \Sigma_{xy} \right\|_{F}^{2} \right\} \\
+\end{align*}
+
+\begin{align*}
+  \nabla_{\Sigma_{xy}}&\left\{ \frac{1}{n}Tr\left[ \left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)^{T}\left(\mathbb{Y} - \mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy} \right)\Sigma_{y | x}^{-1} \right] + \frac{\lambda}{n}Tr\left[ \Sigma_{xy}^{T}\Sigma_{xy} \right] \right\} \\
+  & \\
+  &= -\frac{2}{n}\Sigma_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}\Sigma_{y | x}^{-1} + \frac{2}{n}\Sigma_{xx}^{-1}\mathbb{X}^{T}\mathbb{X}\Sigma_{xx}^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} + \frac{2\lambda}{n}\Sigma_{xy} \\
+\end{align*}
+
+If we use the sample estimate
+\(\hat{\Sigma}_{xx} = \mathbb{X}^{T}\mathbb{X}/n\) (assuming
+\(\mathbb{X}^{T}\mathbb{X}\) is positive definite) then
+
+\begin{align*}
+  vec\left( \hat{\Sigma}_{xy} \right) &= \left[\hat{\Sigma}_{y | x}^{-1} \otimes n\left( \mathbb{X}^{T}\mathbb{X} \right)^{-1} + \tilde{\lambda} I_{rp} \right]^{-1}vec\left[ \left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{y | x}^{-1} \right] \\
+  & \\
+  &= \left[ \Sigma_{y | x}^{-1} \otimes \left( \tilde{\lambda}\mathbb{X}^{T}\mathbb{X} + I_{p} \right) \right]^{-1}vec\left[ \mathbb{X}^{T}\mathbb{Y}\Sigma_{y | x}^{-1} \right]
+\end{align*}
+
+where
+\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\)
+so that in order to solve for
+\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = n\left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\hat{\Sigma}_{xy}\),
+we need to iterate between \(\hat{\beta}\) and
+\(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-sigma_x-y-1-optimize-likelihood-for-sigma_x-y-1}{%
+\subsection{\texorpdfstring{Assume ridge \(\Sigma_{x | y}^{-1}\),
+optimize likelihood for
+\(\Sigma_{x | y}^{-1}\)}{Assume ridge \textbackslash{}Sigma\_\{x \textbar{} y\}\^{}\{-1\}, optimize likelihood for \textbackslash{}Sigma\_\{x \textbar{} y\}\^{}\{-1\}}}\label{assume-ridge-sigma_x-y-1-optimize-likelihood-for-sigma_x-y-1}}
+
+\[ \hat{\Sigma}_{x | y}^{-1} = \arg\min_{\Sigma_{x | y}^{-1}}\left\{ Tr\left( S_{x | y}\Sigma_{x | y}^{-1} \right) - log\left| \Sigma_{x | y}^{-1} \right| + \frac{\lambda}{2}\left\| \Sigma_{x | y}^{-1} \right\|_{F}^{2} \right\} \]
+
+\begin{align*}
+  \nabla_{\Sigma_{x | y}^{-1}}&\left\{ Tr\left( S_{x | y}\Sigma_{x | y}^{-1} \right) - \log\det\left( \Sigma_{x | y}^{-1} \right) + \frac{\lambda}{2}\left\| \Sigma_{x | y}^{-1} \right\|_{F}^{2} \right\} = S_{x | y} - \Sigma_{x | y} + \lambda\Sigma_{x | y}^{-1} \\
+\end{align*}
+
+where
+\(S_{x | y} = \left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)^{T}\left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)/n\)
+and
+\(\hat{\alpha} = \left( \mathbb{Y}^{T}\mathbb{Y} \right)^{-1}\mathbb{Y}^{T}\mathbb{X}\).
+Following the derivations in section (3.5), if we decompose
+\(S_{x | y} = VQV^{T}\) then
+
+\[ \hat{\Sigma}_{x | y}^{-1} = \frac{1}{2\lambda}V\left[ -Q + \left( Q^{2} + 4\lambda I_{p} \right)^{1/2} \right]V^{T} \]
+
+Using the Woodbury Identity, we find that
+
+\[ \hat{\beta} = \hat{\Sigma}_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\hat{\Sigma}_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{yy} = \hat{\Sigma}_{x | y}^{-1}\hat{\alpha}^{T}\left( \Sigma_{yy}^{-1} + \hat{\alpha}\hat{\Sigma}_{x | y}^{-1}\hat{\alpha} \right)^{-1} \]
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-alpha-optimize-in-sample-prediction-error-for-alpha}{%
+\subsection{\texorpdfstring{Assume ridge \(\alpha\), optimize in-sample
+prediction error for
+\(\alpha\)}{Assume ridge \textbackslash{}alpha, optimize in-sample prediction error for \textbackslash{}alpha}}\label{assume-ridge-alpha-optimize-in-sample-prediction-error-for-alpha}}
+
+\[ \hat{\alpha} = \arg\min_{\alpha}\left\{\frac{1}{2} \left\| \mathbb{X} - \mathbb{Y}\alpha \right\|_{F}^{2} + \frac{\lambda}{2}\left\| \alpha \right\|_{F}^{2}\right\} \]
+
+\begin{align*}
+  &\Rightarrow -\mathbb{Y}^{T}\left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right) + \lambda\hat{\alpha} = 0 \\
+  & \\
+  &\Rightarrow \hat{\alpha} = \left( \mathbb{Y}^{T}\mathbb{Y} + \lambda I_{r} \right)^{-1}\mathbb{Y}^{T}\mathbb{X} = \mathbb{Y}^{T}\left( \mathbb{Y}\mathbb{Y}^{T} + \lambda I_{n} \right)^{-1}\mathbb{X}
+\end{align*}
+
+Using the Woodbury Identity, we find that
+
+\[ \hat{\beta} = \Sigma_{x | y}^{-1}\hat{\alpha}^{T}\left( \Sigma_{yy}^{-1} + \hat{\alpha}\Sigma_{x | y}^{-1}\hat{\alpha}^{T} \right)^{-1} \]
+
+\vspace{0.5cm}
+
+\hypertarget{assume-ridge-alpha-optimize-likelihood-for-alpha}{%
+\subsection{\texorpdfstring{Assume ridge \(\alpha\), optimize likelihood
+for
+\(\alpha\)}{Assume ridge \textbackslash{}alpha, optimize likelihood for \textbackslash{}alpha}}\label{assume-ridge-alpha-optimize-likelihood-for-alpha}}
+
+\[ \hat{\alpha} = \arg\min_{\alpha}\left\{ \frac{1}{n} Tr\left[ \left(\mathbb{X} - \mathbb{Y}\alpha \right)^{T}\left( \mathbb{X} - \mathbb{Y}\alpha \right)\Sigma_{x | y}^{-1} \right] - \frac{1}{2}log\left| \Sigma_{x | y}^{-1} \right| + \frac{\lambda}{n}\left\| \alpha \right\|_{F}^{2} \right\} \]
+
+\begin{align*}
+  &\Rightarrow -\frac{2}{n}\mathbb{Y}^{T}\left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)\hat{\Sigma}_{x | y}^{-1} + \frac{2}{n}\lambda\hat{\alpha} = 0 \Rightarrow \left( \hat{\Sigma}_{x | y}^{-1} \otimes \mathbb{Y}^{T}\mathbb{Y} \right)vec\left( \hat{\alpha} \right) + \lambda vec\left( \hat{\alpha} \right) = vec\left( \mathbb{Y}^{T}\mathbb{X}\hat{\Sigma}_{x | y}^{-1} \right) \\
+  & \\
+  &\Rightarrow vec\left( \hat{\alpha} \right) = \left( \hat{\Sigma}_{x | y}^{-1} \otimes \mathbb{Y}^{T}\mathbb{Y} + \lambda I_{pr} \right)^{-1}vec\left( \mathbb{Y}^{T}\mathbb{X}\hat{\Sigma}_{x | y}^{-1} \right) \\
+\end{align*}
+
+where
+\(\hat{\Sigma}_{x | y} = (\mathbb{X} - \mathbb{Y}\hat{\alpha} )^{T}(\mathbb{X} - \mathbb{Y}\hat{\alpha})/n\).
+In order to solve for \(\hat{\alpha}\), we need to iterate between
+\(\hat{\alpha}\) and \(\hat{\Sigma}_{x | y}^{-1}\) until convergence.
+Again, using the Woodbury Identity, we find that
+
+\[ \hat{\beta} = \hat{\Sigma}_{x | y}^{-1}\hat{\alpha}^{T}\left( \Sigma_{yy}^{-1} + \hat{\alpha}\hat{\Sigma}_{x | y}^{-1}\hat{\alpha}^{T} \right)^{-1} \]
+
 \bibliography{lib.bib}

### 2018-07-17 02-ADMM-Details.Rmd
added SCPME materials

# `ADMMsigma` Details

Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Sigma$. That is, $X_{i} \sim N_{p}\left( \mu, \Sigma \right)$.

Because we assume independence, we know that the probability of observing these specific observations $X_{1}, ..., X_{n}$ is equal to

\begin{align*}
  f(X | \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
  &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
\end{align*}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Sigma$ is equal to the following:

\[ l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \]

If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$. However, in addition to $\mu$, many practical applications require the estimation of $\Sigma$ as well. Like $\mu$, we can find a maximum likelihood estimator:

\begin{align*}
  &\hat{\Sigma} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \right\} \\
  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} - \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
  \Rightarrow &\hat{\Sigma} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
\end{align*}

by setting the gradient equal to zero and plugging in the MLE for $\mu$. This implies that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$. We could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]

so that $\hat{\Omega} = S^{-1}$. Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate. Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instad of $\Sigma$.

As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the likelihood:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\} \]

$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$. These penalties are the ridge and lasso, respectively. In the `ADMMsigma` package, we instead take $P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]$ so that solving the full penalized log-likelihood for $\Omega$ results in solving

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]

where $0 \leq \alpha \leq 1$. This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`. Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty. Having this flexibility or generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.

We will explore how to solve for $\hat{\Omega}$ in the next section.

<br>\vspace{1cm}

## ADMM Algorithm

Many efficient methods have been proposed in order to solve for $\hat{\Omega}$ when $\alpha = 1$. The most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse. However, no methods (to the best of my knowledge) have estimated $\Omega$ when $\alpha \in (0, 1)$. We will use the alternating direction method of multipliers (ADMM) algorithm to do so.

As the authors state in @boyd2011distributed, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers." For our purposes, we will only focus on the ADMM algorithm but it is encouraged to read the original text from Boyd and others for a complete introduction to the other two methods.

In general, suppose we want to solve an optimization problem of the following form:

\begin{align*}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{align*}

where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are assumed to be convex functions. Our goal is to find $x^{*} \in \mathbb{R}^{n}$ and $z^{*} \in \mathbb{R}^{m}$ that results in the infimum $p^{*}$:

\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]

Honoring the constraint $Ax + Bz = c$, the lagrangian will be of the form

\[ L(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) \]

where $y \in \mathbb{R}^{p}$ is the lagrange multiplier. Following @boyd2011distributed, the estimation procedure will be introduced in vector form though we will later consider the case where $x$ and $z$ are matrices.

In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods. For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem.

The ADMM algorithm, however, uses the *augmented lagrangian*

\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]

in which case $\rho > 0$ is a scalar. Clearly any minimizer, $p^{*}$, under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point $(x, z)$ satisfies the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$. The ADMM algorithm consists of the following repeated iterations:

\begin{align}
  x^{k + 1} &:= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
  z^{k + 1} &:= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
\end{align}

In the context of precision matrix estimation, we can let $f$ be equal to the non-penalized likelihood, $g$ be equal to $P\left( \Omega \right)$, and use the constraint $\Omega$ equal to some $Z$ so that the lagrangian is

\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] \]

Augmented lagrangian:

\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]

The ADMM algorithm is now the following:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
\end{align}

<br>\vspace{1cm}

### Algorithm

Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}$, and $\rho$. Repeat steps 1-3 until convergence:

1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ via spectral decomposition.

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]

2. Elementwise soft-thresholding for all $i = 1,..., p$ and $j = 1,..., p$.

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

3. Update $\Lambda^{k + 1}$.

\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]

where $Soft(a, b) = Sign(a)(\left| a \right| - b)_{+}$.

<br>\vspace{1cm}

### Proof of (1):

\[ \Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]

\vspace{1cm}

\begin{align*}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\end{align*}

Note that because all of the variables are symmetric, we can essentially ignore the constraint when deriving the gradient.
Set the gradient equal to zero and decompose $\Omega = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega$ and $V$ is the matrix with corresponding eigen vectors as columns.

\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{align*}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{align*}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]

<br>\vspace{1cm}

### Proof of (2)

\[ Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]

\vspace{1cm}

\begin{align*}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
\end{align*}

where $Sign(Z)$ is the elementwise Sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij} > 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]

- If $Z_{ij} < 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that $Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
\end{align*}

where $Soft$ is the soft-thresholding function.

<br>\vspace{1cm}

## Scaled-Form ADMM

There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable ($\Lambda^{k}$).

Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.

\begin{align*}
  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
\end{align*}

Therefore, a scaled-form can now be written as

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
\end{align}

And more generally (in vector form),

\begin{align}
  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
\end{align}

Note that there are limitations to using this method. Because the dual variable is scaled by $\rho$ (the step size), this form limits one to using a constant step size without making further adjustments to $U^{k}$. It has been shown in the literature that a dynamic step size (like the one used in `ADMMsigma`) can significantly reduce the number of iterations required for convergence.

<br>\vspace{1cm}

## Stopping Criterion

In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to precision matrix estimation.

Below we have three optimality conditions:

1. Primal:

\[ \Omega^{k + 1} - Z^{k + 1} = 0 \]

2. Dual:

\[ 0 \in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \]

\[ 0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \]

We will define the left-hand side of the first condition as the primal residual: $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$. At convergence, optimality conditions require that $r^{k + 1} \approx 0$. The second residual we will define is the dual residual: $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$. This residual is defined from the following:

Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,

\begin{align*}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
\end{align*}

Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied:

\begin{align*}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
\end{align*}

One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where

\begin{align*}
  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
\end{align*}

### 2018-07-17 06-SCPME-Details.Rmd
added SCPME materials

# `SCPME` Details

Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Sigma$. That is, $X_{i} \sim N_{p}\left( \mu, \Sigma \right)$.

Because we assume independence, we know that the probability of observing these specific observations $X_{1}, ..., X_{n}$ is equal to

\begin{align*}
  f(X | \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
  &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
\end{align*}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Sigma$ is equal to the following:

\[ l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \]

If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$. However, in addition to $\mu$, many practical applications require the estimation of $\Sigma$ as well. Like $\mu$, we can find a maximum likelihood estimator:

\begin{align*}
  &\hat{\Sigma} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \right\} \\
  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} - \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
  \Rightarrow &\hat{\Sigma} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
\end{align*}

by setting the gradient equal to zero and plugging in the MLE for $\mu$. This implies that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$. We could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| \right\} \]

so that $\hat{\Omega} = S^{-1}$. Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate. Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instad of $\Sigma$.

As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the likelihood:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\} \]

$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$. These penalties are the ridge and lasso, respectively. The penalty proposed by @molstad2017shrinking is one of the following form:

\[ P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1} \]

so that solving the full penalized log-likelihood for $\Omega$ results in solving

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\} \]

where $A \in \mathbb{R}^{n \times p}, B \in \mathbb{R}^{p \times r}, \mbox{ and } C \in \mathbb{R}^{n \times r}$ are matrices assumed to be known and specified by the user. As discussed [here](https://mgallow.github.io/SCPME/articles/Jointloglik.html), this type of penalty leads to many new, interesting, and novel estimators for $\Omega$. An example of one such estimator would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ so that we assume sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.

We will explore how to solve for $\hat{\Omega}$ in the next section.

<br>\vspace{1cm}

## Augmented ADMM Algorithm

This section requires general knowledge of the ADMM algorithm. I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.

The ADMM algorithm within the context of this problem consists of the following repeated iterations:

\begin{align}
  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  Z^{k + 1} &:= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
  \Lambda^{k + 1} &:= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{align}

where $L_{p}(\cdot)$ is the *augmented lagrangian* defined as

\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \]

with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$.

We instead replace with

\begin{align*}
  tr\left(S\Omega\right) &- \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] \\
  &+ \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \\
  &= tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C)\right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2} \\
  &+ \frac{\rho}{2}tr\left[A^{T}A(\Omega - \Omega^{k})BB^{T}(\Omega - \Omega^{k})\right] + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2}
\end{align*}

**Note:**

\begin{align*}
  vec\left(\Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) &= vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}(\Omega - \Omega^{k})A^{T}A\right) \\
  &= tr\left[A^{T}A\left(\Omega - \Omega^{k}\right)BB^{T}\left(\Omega - \Omega^{k}\right)\right]
\end{align*}

Suppose we define $G^{k} := A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho$. Then

\begin{align*}
  &\nabla_{\Omega}\left\{tr\left[\left(S + \rho A^{T}G^{k}B^{T}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
\end{align*}

Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to

\begin{align*}
  0 &= S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - (\Omega^{k + 1})^{-1} + \rho\tau\left(\Omega^{k + 1} - \Omega^{k}\right) \\
  \Rightarrow &S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1}
\end{align*}

Consider

\begin{align*}
  &\nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A \\
  &\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
\end{align*}

\begin{align*}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
\end{align*}

Consider $\rho vec\left(\Omega - \Omega^{k}\right)^{T}Q vec\left(\Omega - \Omega^{k} \right)/2$ where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite.

Note that if $Q$ is positive definite (p.d.), then

\[ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)Q\left(\Omega - \Omega^{k} \right) > 0 \]

since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.

This implies the following fact:

\[ \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \leq \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q vec\left(\Omega - \Omega^{k} \right) \]

Further,

\begin{align*}
  \nabla_{\Omega}&\left\{const. + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k} \right\|_{F}^{2} + \rho tr\left[\Omega^{T}\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \right] \right\} \\
  &= \rho\tau\left(\Omega - \Omega^{k}\right) + \rho BB^{T}\Omega A^{T}A - \rho B(Z^{k})^{T}A - \rho BC^{T}A
\end{align*}

This implies a majorizing function!

<br>\vspace{1cm}

### Algorithm

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$

2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z_{k + 1} = \mbox{soft}\left( A\Omega_{k + 1}B - C + \rho^{-1}Y_{k}, \rho^{-1}\lambda \right)$

5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

where $Soft(a, b) = Sign(a)(\left| a \right| - b)_{+}$.

<br>\vspace{1cm}

### Proof of (2-3):

\[ \Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]

\vspace{1cm}

\begin{align*}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
\end{align*}

Note that because all of the variables are symmetric, we can essentially ignore the constraint when deriving the gradient.
Set the gradient equal to zero and decompose $\Omega = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega$ and $V$ is the matrix with corresponding eigen vectors as columns.

\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{align*}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{align*}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]

<br>\vspace{1cm}

### Proof of (4)

\[ Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \]

\vspace{1cm}

\begin{align*}
  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= Sign(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
\end{align*}

where $Sign(Z)$ is the elementwise Sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\[ Z_{ij} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda \right) \]

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij} > 0$ then

\[ \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \]

- If $Z_{ij} < 0$ then

\[ \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that $Sign(Z_{ij}) = Sign\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at

\begin{align*}
Z_{ij}^{k + 1} &= \frac{1}{\rho}Sign\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
&= \frac{1}{\rho}Soft\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
\end{align*}

where $Soft$ is the soft-thresholding function.

<br>\vspace{1cm}

## Stopping Criterion

In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to the SCPME method.

Below we have three optimality conditions:

1. Primal:

\[ A\Omega^{k + 1}B - Z^{k + 1} - C = 0 \]

2. Dual:

\begin{align*}
  0 &\in \partial f\left(\Omega^{k + 1}\right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) \\
  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
\end{align*}

The first dual optimality condition is a result of taking the sub-differential of $L_{\rho}\left( \Omega^{k + 1}, Z^{k + 1}, \Lambda^{k + 1} \right)$ with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$).

We will define the left-hand side of the primal optimality condition as the primal residual: $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$. At convergence, the optimality conditions require that $r^{k + 1} \approx 0$. The second residual we will define is the dual residual:

\[ s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \]

This residual is defined from the following:

Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,

\begin{align*}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
\end{align*}

Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied:

\begin{align*}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
\end{align*}

One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where

\begin{align*}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
\end{align*}

### 2018-07-17 07-SCPME-Connection.Rmd
added SCPME materials

# `SCPME` Connection to Joint Log-likelihood

The general optimization problem outlined in @molstad2017shrinking is to estimate $\hat{\Omega}$ such that

\begin{align}
  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
\end{align}

where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm. In addition, $A \in \mathbb{R}^{n \times p}, B \in \mathbb{R}^{p \times r}, \mbox{ and } C \in \mathbb{R}^{n \times r}$ are matrices assumed to be known and specified by the user. This objective function is the log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$, plus a penalty term.

\[ \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\} \]

where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$. Under this particular likelihood, it is assumed that each observation of $X$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- though Dennis Cook and others have shown this objective function to work well as a generic loss even when the assumptions are not met.

This type of formulation leads to many new, interesting, and novel estimators for $\Omega$. For instance, we might set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0,$ in which case

\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]

That is, this objective function estimates an $\Omega$ with respect to the marginal likelihood of $X$ under the assumption that $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.

\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]

In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$. Further, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that

\begin{align}
  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\} \nonumber
\end{align}

This estimator encourages the predicted values $\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}$ to be exactly equal to the observed responses $\mathbb{Y}$. We will name this estimator the *lasso SCPME estimator*. Note that in practice - for any of these estimators - we do not know the true covariance $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$.

All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) framework outlined in the paper. The augmented ADMM algorithm is the following:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$

2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z_{k + 1} = \mbox{soft}\left( A\Omega_{k + 1}B - C + \rho^{-1}Y_{k}, \rho^{-1}\lambda \right)$

5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

<br>
\vspace{1cm}

## Connection to joint log-likelihood

The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ when we consider its analogous *ridge* version - the *ridge SCPME estimator*:

\begin{align}
  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
\end{align}

To see this, let us suppose that we have $n$ independent copies of $(Y_{i}, X_{i})$ where $Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}X_{i}, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$. That is,

\[ Y_{i} = \mu_{y} + \beta^{T}X_{i} + E_{i} \]

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$. Similar to before, take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$.

Below we derive the joint likelihood:

\begin{align*}
  L\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) &\propto f\left(Y | X, \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X | \Omega, \mu_{x} \right) \\
  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right) \right] \\
  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)^{T}\Omega_{y | x} \right] \\
  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
\end{align*}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:

\begin{align*}
  l\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
\end{align*}

**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.

\begin{align*}
 \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left( -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right) \right\} \\
 &= -\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
 \Rightarrow \hat{\mu_{x}} &= \bar{X} \\ \\
 \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left( -n\mu_{y}(\bar{Y} - \beta^{T}\bar{X})\Omega_{y | x} - n(\bar{Y} - \beta^{T}\bar{X})\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right) \right\} \\
 &= -\frac{1}{2}\left( -n\Omega_{y | x}(\bar{Y} - \beta^{T}\bar{X}) - n\Omega_{y | x}(\bar{Y} - \beta^{T}\bar{X}) + 2n\Omega_{y | x}\mu_{y} \right) \\
 \Rightarrow \hat{\mu_{y}} &= \bar{Y} - \beta^{T}\bar{X}
\end{align*}

Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$. This can be achieved by simply centering the data by the sample averages.

Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:

\begin{align*}
  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
\end{align*}

where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:

\begin{align*}
  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
\end{align*}

where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm. Let us assume that $\Omega_{y | x}^{1/2} = I_{r}$ and let $\lambda = 2/n$. Then

\begin{align}
  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
\end{align}

Notice that this is exactly the ridge SCPME estimator. This tells us that with just a few assumptions, the ridge SCPME estimator with $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ is equivalent to maximizing the joint log-likelihood of $X$ and $Y$ with respect to $\Omega$. Specifically, if we assume that, given $X$, each response is independent of one another and has equal variance (denoted as $\sigma_{y | x}^{2}$) then letting $\lambda = 2/(n\sigma_{y | x}^{2})$ and solving for the ridge SCPME estimator is equivalent to solving for the optimal $\hat{\Omega}$ under the joint log-likelihood of $X$ and $Y$.

In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$

2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z_{k + 1} = \left[ \rho\left( A\Omega_{k + 1} B - C \right) + Y_{k} \right]/(\lambda + \rho)$

5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

The only difference is in step 4.

There are a few takeaways we can make after revealing this connection. The first is that the estimator constructed in this section is not complete nonsense. We are, in fact, solving a very similar problem to that of optimizing the joint likelihood. The second takeaway is that the SCPME estimator offers a very efficient method of computing this joint likelihood estimator. To the best of my knowledge, no closed-form solution to the ridge SCPME estimator exists and so we must resort to some iterative algorithm like this one in order to solve it.

<br>
\vspace{1cm}

## Exploratory simulations

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with probability 0.5 being equal to 1. The $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse). Then for $n$ independent, identically distributed samples:

\[ X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right) \]

\[ Y_{i}| X_{i} \sim N_{r}\left( \beta^{T}X_{i}, \Sigma_{y | x} \right) \]

We will take $(n = 100, p = 10, r = 5)$ for this short study and use the `data_gen` function I already have built in R.

<br>\vspace{1cm}
```{r, tidy = TRUE}

# load libraries
library(statr)
library(SCPME)
set.seed(1234)

# randomly generate the data
data = data_gen(n = 100, p = 10, r = 5)

# print Omega
Omega = qr.solve(data$SigmaX)
round(Omega, 5)

# print sample precision matrix (perhaps bad estimate)
sample = qr.solve((nrow(data$X) - 1)/nrow(data$X)*cov(data$X))
round(sample, 5)

```

### 2018-07-17 08-SCPME-Simulations.Rmd
added SCPME materials

# `SCPME` Simulations

We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.

<br>\vspace{1cm}

### Models

In the following estimators, let the superscript * denote the oracle estimator:

 - `OLS` = ordinary least squares estimator in *low* dimensional setting and Moore-Penrose estimator in a *high* ($p >> n$) dimensional setting

 - `ridge` = ridge regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `lasso` = lasso regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `oracleB` = oracle estimator with the true $\beta^{*}$ known ($\left\| Y - X\beta^{*} \right\|_{F}^{2}$)

 - `oracleO` = oracle estimator with the true $\Omega^{*}$ known ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$)

 - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)

 - `shrinkBS` = shrinking characteristics regression estimator with oracle cross-covariance where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$)

 - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)

 - `shrinkXY` = shrinking characteristics regression estimator with A = X, B = cov(X, Y), and C = Y (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$)

 - `shrinkXYO` = shrinking characteristics regression estimator meant to emulate the "likelihood" for $\beta$ (using oracle $\Omega_{y | x}^{*}$) (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$)

 - `glasso` = lasso penalized precision matrix where optimal tuning parameter is chosen to maximize log-likelihood via 3-fold CV.

<br>\vspace{1cm}

### Data Generation

Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that

\[ \mathbb{Y} = \mathbb{X}\beta + \mathbb{E} \]

These values are generated in the following way:

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1. In effect, each $\beta$ entry is turned off with equal probability.

Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse).

Then for $n$ independent, identically distributed samples:

\[ X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right) \]

\[ E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right) \]

If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.

An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$). For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).

Possible parameters in simulation:

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150)
 - `r` = c(1, 5)
 - `sparse` = 0.5
 - `sigma` = "tridiag"

Note that prior to estimation, the intercept is removed by centering the data.

<br>\vspace{1cm}

## Plots

```{r, eval = T, echo = F}

# load data
load("images/sim5.Rdata")

# set P to numeric 
data$P %<>% as.character %>% as.numeric

# MSPE by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 500, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r, eval = T, echo = F}

# MSPE by P (N = 100, R = 1, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, R == 1, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 1, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 100, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**

```{r, eval = T, echo = F}

# MSPE table (N = 100, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

```

<br>\vspace{1cm}

```{r, eval = T, echo = F}

# MSPE by P (N = 100, R = 5, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 100, R == 5, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 5, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 100, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**

```{r, eval = T, echo = F}

# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

```

<br>\vspace{1cm}

```{r, eval = T, echo = F}

# MSPE by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 5000, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r, eval = T, echo = F}

# MSPE by P (N = 1000, R = 1, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, R == 1, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 1, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 1000, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**

```{r, eval = T, echo = F}

# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 1)
data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

```

<br>\vspace{1cm}

```{r, eval = T, echo = F}

# MSPE by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 5, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 1000, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**

```{r, eval = T, echo = F}

# MSPE table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)

```

<br>\vspace{1cm}

## Takeaways

1. `shrinkBO` (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$. I don't think it's surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.

2. It's interesting to see that in all cases `shrinkBS` (penalty: $\lambda\left\| \Omega\Sigma_{xy}^{*} \right\|_{1}$) performed worse than `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$). So the takeaway is that for these two very similar estimators, the estimator with the oracle $\Sigma_{xy}$ cross-covariance matrix performs much worse than using the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$. Is this due to an error? Could the root cause be because I centered the data?

3. `OracleO` ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$) performed awful in all simulations as well... possibly link to the Abundant paper?

4. `shrinkXY` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$) and `shrinkXYO` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$) did not perform well relative to the others in the high-dimensional setting. In the low-dimensional setting, they performed better but worse than `lasso` and `ridge`. But what is an appropriate data generating model for these estimators? A model that can perfectly fit the observed values? And would MSPE be the most appropriate criteria for these estimators?

<br>\vspace{1cm}

## Questions

1. Is MSPE the best criteria? Or would model error be a better metric?

### 2018-07-17 09-betas.Rmd
added SCPME materials

--- 2018-06-20 Manuscript.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[11pt,]{book}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{xcolor}
-\usepackage{hyperref}
-\hypersetup{
-            pdftitle={Oral Manuscript},
-            pdfauthor={Matt Galloway},
-            colorlinks=true,
-            linkcolor=Maroon,
-            citecolor=Blue,
-            urlcolor=Blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+# Penalized Regression Estimators
 
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-\usepackage{booktabs}
-\usepackage{amsthm}
-\makeatletter
-\def\thm@space@setup{%
-  \thm@preskip=8pt plus 2pt minus 4pt
-  \thm@postskip=\thm@preskip
-}
-\makeatother
-\usepackage[]{natbib}
-\bibliographystyle{apalike}
-
-\title{Oral Manuscript}
-\author{Matt Galloway}
-\date{2018-06-20}
-
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
-\newtheorem{proposition}{Proposition}[chapter]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[chapter]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[chapter]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
-\begin{document}
-\maketitle
-
-{
-\hypersetup{linkcolor=}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\hypertarget{prerequisites}{%
-\chapter{Prerequisites}\label{prerequisites}}
-
-\hypertarget{intro}{%
-\chapter{Introduction}\label{intro}}
-
-This is the introduction for Matt's oral manuscript. (UPDATED 8)
-
-\hypertarget{tutorial}{%
-\chapter{Tutorial}\label{tutorial}}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# The easiest way to install is from CRAN}
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"ADMMsigma"}\NormalTok{)}
-
-\CommentTok{# You can also install the development version from GitHub:}
-\CommentTok{# install.packages('devtools')}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/ADMMsigma"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\vspace{0.5cm}
-
-If there are any issues/bugs, please let me know:
-\href{https://github.com/MGallow/ADMMsigma/issues}{github}. You can also
-contact me via my \href{https://mgallow.github.io/}{website}. Pull
-requests are welcome!
-
-\vspace{0.5cm}
-
-A (possibly incomplete) list of functions contained in the package can
-be found below:
-
-\begin{itemize}
-\item
-  \texttt{ADMMsigma()} computes the estimated precision matrix (ridge,
-  lasso, and elastic-net type regularization optional)
-\item
-  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision
-  matrix via closed-form solution
-\item
-  \texttt{plot.ADMMsigma()} produces a heat map or line graph for cross
-  validation errors
-\item
-  \texttt{plot.RIDGEsigma()} produces a heat map or line graph for cross
-  validation errors
-\end{itemize}
-
-\vspace{1cm}
-
-\hypertarget{usage}{%
-\section{Usage}\label{usage}}
-
-We will first generate data from a sparse, tri-diagonal precision matrix
-and denote it as Omega.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-
-\CommentTok{# generate data from a sparse matrix first compute covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{5}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\NormalTok{S[i, j]}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# print oracle precision matrix (shrinkage might be useful)}
-\NormalTok{(}\DataTypeTok{Omega =} \KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(S), }\DecValTok{3}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##        [,1]   [,2]   [,3]   [,4]   [,5]
-## [1,]  1.961 -1.373  0.000  0.000  0.000
-## [2,] -1.373  2.922 -1.373  0.000  0.000
-## [3,]  0.000 -1.373  2.922 -1.373  0.000
-## [4,]  0.000  0.000 -1.373  2.922 -1.373
-## [5,]  0.000  0.000  0.000 -1.373  1.961
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{5}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# snap shot of data}
-\KeywordTok{head}\NormalTok{(X)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##            [,1]         [,2]         [,3]       [,4]        [,5]
-## [1,] -0.4311177 -0.217744186  1.276826576 -0.1061308 -0.02363953
-## [2,] -0.0418538  0.304253474  0.688201742 -0.5976510 -1.06758924
-## [3,]  1.1344174  0.004493877 -0.440059159 -0.9793198 -0.86953222
-## [4,] -0.0738241 -0.286438212  0.009577281 -0.7850619 -0.32351261
-## [5,] -0.2905499 -0.906939891 -0.656034183 -0.4324413  0.28516534
-## [6,]  1.3761967  0.276942730 -0.297518545 -0.2634814 -1.35944340
-\end{verbatim}
-
-\vspace{0.5cm}
-
-As described earlier in the report, the maximum likelihood estimator
-(MLE) for Omega is the inverse of the sample precision matrix
-\(S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}\):
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# print inverse of sample precision matrix (perhaps a bad estimate)}
-\KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(}\KeywordTok{cov}\NormalTok{(X) }\OperatorTok{*}\StringTok{ }\NormalTok{(}\KeywordTok{nrow}\NormalTok{(X) }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)}\OperatorTok{/}\KeywordTok{nrow}\NormalTok{(X)), }\DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.32976 -1.55033  0.22105 -0.08607  0.24309
-## [2,] -1.55033  3.27561 -1.68026 -0.14277  0.18949
-## [3,]  0.22105 -1.68026  3.19897 -1.25158 -0.11016
-## [4,] -0.08607 -0.14277 -1.25158  2.76790 -1.37226
-## [5,]  0.24309  0.18949 -0.11016 -1.37226  2.05377
-\end{verbatim}
-
-\vspace{0.5cm}
-
-However, because Omega (known as the \emph{oracle}) is sparse, a
-shrinkage estimator will perhaps perform better than the sample
-estimator. Below we construct various penalized estimators:
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net type penalty (set tolerance to 1e-8)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, tol.abs = 1e-08, tol.rel = 1e-08)
-## 
-## Iterations: 162
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41003
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15283 -1.26902  0.00000  0.00000  0.19765
-## [2,] -1.26902  2.79032 -1.32206 -0.08056  0.00925
-## [3,]  0.00000 -1.32206  2.85470 -1.17072 -0.00865
-## [4,]  0.00000 -0.08056 -1.17072  2.49554 -1.18959
-## [5,]  0.19765  0.00925 -0.00865 -1.18959  1.88121
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{LASSO:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# lasso penalty (default tolerance)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 1)
-## 
-## Iterations: 66
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41022
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15228 -1.26841  0.00000  0.00000  0.19744
-## [2,] -1.26841  2.78830 -1.31943 -0.08246  0.01018
-## [3,]  0.00000 -1.31943  2.84979 -1.16708 -0.01015
-## [4,]  0.00000 -0.08246 -1.16708  2.49277 -1.18844
-## [5,]  0.19744  0.01018 -0.01015 -1.18844  1.88069
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{ELASTIC-NET:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net penalty (alpha = 0.5)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0.5)
-## 
-## Iterations: 67
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821    0.5
-## 
-## Log-likelihood: -101.13595
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.20031 -1.32471  0.01656 -0.00334  0.21798
-## [2,] -1.32471  2.90659 -1.37599 -0.19084  0.13651
-## [3,]  0.01656 -1.37599  2.92489 -1.12859 -0.12033
-## [4,] -0.00334 -0.19084 -1.12859  2.56559 -1.23472
-## [5,]  0.21798  0.13651 -0.12033 -1.23472  1.94528
-\end{verbatim}
-
-\newpage
-
-\textbf{RIDGE:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{0}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0)
-## 
-## Iterations: 65
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821      0
-## 
-## Log-likelihood: -99.19746
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.18979 -1.31533  0.04515 -0.04090  0.23511
-## [2,] -1.31533  2.90019 -1.37049 -0.22633  0.17808
-## [3,]  0.04515 -1.37049  2.89435 -1.07647 -0.17369
-## [4,] -0.04090 -0.22633 -1.07647  2.55026 -1.22786
-## [5,]  0.23511  0.17808 -0.17369 -1.22786  1.95495
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty no ADMM}
-\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: RIDGEsigma(X = X, lam = 10^seq(-8, 8, 0.01))
-## 
-## Tuning parameter:
-##       log10(lam)    lam
-## [1,]       -2.17  0.007
-## 
-## Log-likelihood: -109.18156
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15416 -1.31185  0.08499 -0.05571  0.22862
-## [2,] -1.31185  2.85605 -1.36677 -0.19650  0.16880
-## [3,]  0.08499 -1.36677  2.82606 -1.06325 -0.14946
-## [4,] -0.05571 -0.19650 -1.06325  2.50721 -1.21935
-## [5,]  0.22862  0.16880 -0.14946 -1.21935  1.92871
-\end{verbatim}
-
-\newpage
-
-This package also has the capability to provide heat maps for the cross
-validation errors. The more bright (white) areas of the heat map pertain
-to more optimal tuning parameters.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for ADMMsigma}
-\NormalTok{ADMM =}\StringTok{ }\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for ADMMsigma}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for RIDGEsigma}
-\NormalTok{RIDGE =}\StringTok{ }\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for RIDGEsigma}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-
-\hypertarget{details}{%
-\chapter{Details}\label{details}}
-
-Suppose we want to solve the following optimization problem:
-
-\[
-\begin{aligned}
-  \mbox{minimize } f(x) + g(z) \\
-  \mbox{subject to } Ax + Bz = c
-\end{aligned}
-\]
-
-where
-\(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\),
-and \(c \in \mathbb{R}^{p}\). Following \citet{boyd2011distributed}, the
-optimization problem will be introduced in vector form though we will
-later consider cases where \(x\) and \(z\) are matrices. We will also
-assume \(f\) and \(g\) are convex functions. Optimization problems like
-this arise naturally in several statistics and machine learning
-applications -- particularly regularization methods. For instance, we
-could take \(f\) to be the squared error loss, \(g\) to be the
-\(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be
-identity matrices to solve the ridge regression optimization problem.
-
-The \emph{augmented lagrangian} is constructed as follows:
-
-\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]
-
-where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and
-\(\rho > 0\) is a scalar. Clearly any minimizer, \(p^{*}\), under the
-augmented lagrangian is equivalent to that of the lagrangian since any
-feasible point \((x, z)\) satisfies the constraint
-\(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
-
-\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]
-
-The alternating direction method of multipliers (ADMM) algorithm
-consists of the following repeated iterations:
-
-\begin{align}
-  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
-\end{align}
-
-A more complete introduction to the algorithm -- specifically how it
-arose out of \emph{dual ascent} and \emph{method of multipliers} -- can
-be found in \citet{boyd2011distributed}.
-
-\vspace{1cm}
-
-\hypertarget{admm-algorithm}{%
-\section{ADMM Algorithm}\label{admm-algorithm}}
-
-Now consider the case where \(X_{1}, ..., X_{n}\) are iid
-\(N_{p}(\mu, \Sigma)\) random variables and we are tasked with
-estimating the precision matrix, denoted \(\Omega \equiv \Sigma^{-1}\).
-The maximum likelihood estimator for \(\Omega\) is
-
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]
-
-where \(S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n\)
-and \(\bar{X}\) is the sample mean. By setting the gradient equal to
-zero, we can show that when the solution exists,
-\(\hat{\Omega}_{MLE} = S^{-1}\).
-
-As in regression settings, we can construct a \emph{penalized}
-likelihood estimator by adding a penalty term,
-\(P\left( \Omega \right)\), to the likelihood:
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]
-
-\(P\left( \Omega \right)\) is often of the form
-\(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}\) or
-\(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\),
-\(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define
-\(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\). These
-penalties are the ridge and lasso, respectively. We will, instead, take
-\(P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]\)
-so that the full penalized likelihood is
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]
-
-where \(0 \leq \alpha \leq 1\). This \emph{elastic-net} penalty was
-explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and
-is identical to the penalty used in the popular penalized regression
-package \texttt{glmnet}. Clearly, when \(\alpha = 0\) the elastic-net
-reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a
-lasso-type penalty.
-
-By letting \(f\) be equal to the non-penalized likelihood and \(g\)
-equal to \(P\left( \Omega \right)\), our goal is to minimize the full
-augmented lagrangian where the constraint is that \(\Omega - Z\) is
-equal to zero:
-
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]
-
-The ADMM algorithm for estimating the penalized precision matrix in this
-problem is
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align}
-
-\vspace{1cm}
-
-\hypertarget{scaled-form-admm}{%
-\section{Scaled-Form ADMM}\label{scaled-form-admm}}
-
-An alternate form of the ADMM algorithm can constructed by scaling the
-dual variable (\(\Lambda^{k}\)). Let us define
-\(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).
-
-\begin{align*}
-  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-\end{align*}
-
-Therefore, the condensed-form ADMM algorithm can now be written as
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
-\end{align}
-
-And more generally (in vector form),
-
-\begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
-\end{align}
-
-Note that there are limitations to using this method. Because the dual
-variable is scaled by \(\rho\) (the step size), this form limits one to
-using a constant step size without making further adjustments to
-\(U^{k}\). It has been shown in the literature that a dynamic step size
-can significantly reduce the number of iterations required for
-convergence.
-
-\vspace{1cm}
-
-\hypertarget{algorithm}{%
-\section{Algorithm}\label{algorithm}}
-
-\begin{align*}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align*}
-
-\vspace{1cm}
-
-Initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Iterate the following
-three steps until convergence:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) via spectral
-  decomposition.
-\end{enumerate}
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Elementwise soft-thresholding for all \(i = 1,..., p\) and
-  \(j = 1,..., p\).
-\end{enumerate}
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Update \(\Lambda^{k + 1}\).
-\end{enumerate}
-
-\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-1}{%
-\subsection{Proof of (1):}\label{proof-of-1}}
-
-\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
-\end{align*}
-
-Set the gradient equal to zero and decompose \(\Omega = VDV^{T}\) where
-\(D\) is a diagonal matrix with diagonal elements equal to the eigen
-values of \(\Omega\) and \(V\) is the matrix with corresponding eigen
-vectors as columns.
-
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
-
-This equivalence implies that
-
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
-
-where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
-
-\begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
-\end{align*}
-
-In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\)
-then
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-2}{%
-\subsection{Proof of (2)}\label{proof-of-2}}
-
-\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
-\end{align*}
-
-where \(Sign(Z)\) is the elementwise Sign operator. By setting the
-gradient/sub-differential equal to zero, we arrive at the following
-equivalence:
-
-\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]
-
-for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} > 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} < 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]
-
-This implies that
-\(Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\).
-Putting all the pieces together, we arrive at
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-where \(Soft\) is the soft-thresholding function.
-
-\hypertarget{simulations}{%
-\chapter{Simulations}\label{simulations}}
-
-In the simulations below we generated data from a number of oracle
-precision matrices with various structures. For each data-generating
-procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross
-validation. After 20 replications, the cross validation errors were
-totalled and the optimal tuning parameters were selected (results in the
-top figure). These results are compared with the Kullback Leibler (KL)
-losses between the estimates and the oracle precision matrix (bottom
-figure). We can see below that our cross validation procedure choosing
-tuning parameters close to the optimal parameters.
-
-\hypertarget{compound-symmetric-p-100-n-50}{%
-\section{Compound Symmetric: P = 100, N =
-50}\label{compound-symmetric-p-100-n-50}}
-
-\includegraphics{images/compound_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{compound-symmetric-p-10-n-1000}{%
-\section{Compound Symmetric: P = 10, N =
-1000}\label{compound-symmetric-p-10-n-1000}}
-
-\includegraphics{images/compound_N1000_P10.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{1000}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{dense-p-100-n-50}{%
-\section{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
-
-\includegraphics{images/repsKLdenseQR_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{100} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{dense-p-10-n-50}{%
-\section{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
-
-\includegraphics{images/repsKLdense_N50_P10.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{10}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{tridiagonal-p-100-n-50}{%
-\section{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
-
-\includegraphics{images/repsKLtridiag_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-\NormalTok{    S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{  \}}
-\NormalTok{\}}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{benchmark}{%
-\chapter{Benchmark}\label{benchmark}}
-
-Below we benchmark the various functions contained in
-\texttt{ADMMsigma}. We can see that \texttt{ADMMsigma} (at the default
-tolerance) offers comparable computation time to the popular
-\texttt{glasso} R package.
-
-\hypertarget{computer-specs}{%
-\subsection{Computer Specs:}\label{computer-specs}}
-
-\begin{itemize}
-\tightlist
-\item
-  MacBook Pro (Late 2016)
-\item
-  Processor: 2.9 GHz Intel Core i5
-\item
-  Memory: 8GB 2133 MHz
-\item
-  Graphics: Intel Iris Graphics 550
-\end{itemize}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-\KeywordTok{library}\NormalTok{(microbenchmark)}
-
-\CommentTok{# generate data from tri-diagonal (sparse) matrix compute covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\NormalTok{(}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j))}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{1000} \OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# glasso (for comparison)}
-\KeywordTok{microbenchmark}\NormalTok{(glasso}\OperatorTok{::}\KeywordTok{glasso}\NormalTok{(}\DataTypeTok{s =}\NormalTok{ S, }\DataTypeTok{rho =} \FloatTok{0.1}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                              expr      min       lq     mean   median
-##  glasso::glasso(s = S, rho = 0.1) 49.46673 53.37757 58.35196 55.90935
-##        uq      max neval
-##  60.77517 92.68082   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - default tolerance}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-04}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-04, tol.rel = 1e-04,      trace = "none")
-##      min       lq     mean   median       uq      max neval
-##  77.2134 83.51351 89.71565 85.37738 94.37814 126.0049   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - tolerance 1e-8}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-08, tol.rel = 1e-08,      trace = "none")
-##       min       lq     mean   median       uq      max neval
-##  258.5389 261.5402 272.3741 267.8829 274.7276 353.4726   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - default parameter grid}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                          expr      min       lq     mean   median       uq
-##  ADMMsigma(X, trace = "none") 8.338241 8.341611 8.536446 8.472933 8.515822
-##       max neval
-##  9.013621     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma parallel CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{cores =} \DecValTok{3}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                     expr      min       lq     mean
-##  ADMMsigma(X, cores = 3, trace = "none") 9.285137 9.315978 9.470666
-##   median       uq      max neval
-##  9.40943 9.426579 9.916207     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - likelihood convergence criteria}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{crit =} \StringTok{"loglik"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                           expr      min       lq     mean
-##  ADMMsigma(X, crit = "loglik", trace = "none") 7.028816 7.121599 7.185927
-##    median       uq      max neval
-##  7.181803 7.277249 7.320166     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark RIDGEsigma CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{), }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                                      expr      min
-##  RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none") 12.22374
-##        lq     mean   median       uq      max neval
-##  12.37326 12.93705 13.01892 13.04356 14.02577     5
-\end{verbatim}
-
-\hypertarget{penalized-regression-estimators}{%
-\chapter{Penalized Regression
-Estimators}\label{penalized-regression-estimators}}
-
-This document explores a number of regression estimators subject to
-various assumptions. We will assume \(n\) samples of
+This document explores a number of regression estimators subject to various assumptions. We will assume $n$ samples of
 
@@
 
-where \(\epsilon_{i} \sim N_{r}\left(0, \Sigma_{y | x} \right)\) and
-\(X_{i} \sim N_{p}\left(0, \Sigma_{x}\right)\) so that by taking
-\(\theta = \left( \mu_{y}, \mu_{x}, vec\left( \beta \right), vec\left( \Sigma_{y | x}^{-1} \right), vec\left( \Sigma_{xx}^{-1} \right) \right)^{T}\)
-the joint log-likelihood is of the following form:
+where $\epsilon_{i} \sim N_{r}\left(0, \Sigma_{y | x} \right)$ and $X_{i} \sim N_{p}\left(0, \Sigma_{x}\right)$ so that by taking $\theta = \left( \mu_{y}, \mu_{x}, vec\left( \beta \right), vec\left( \Sigma_{y | x}^{-1} \right), vec\left( \Sigma_{xx}^{-1} \right) \right)^{T}$ the joint log-likelihood is of the following form:
 
@@
 
-For convenience, we will later denote \(\mathbb{X}\) as the
-\(n \times p\) matrix with rows \(X_{i} - \bar{X}\) where
-\(\bar{X} = \sum_{i = 1}^{n}X_{i}/n\) and \(\mathbb{Y}\) as the
-\(n \times r\) matrix with rows \(Y_{i} - \bar{Y}\) and \(\bar{Y}\)
-defined similarly. Note that \(\bar{X}\) and \(\bar{Y}\) are the maximum
-likelihood esitmators of \(\mu_{x}\) and \(\mu_{y}\), respectively.
+For convenience, we will later denote $\mathbb{X}$ as the $n \times p$ matrix with rows $X_{i} - \bar{X}$ where $\bar{X} = \sum_{i = 1}^{n}X_{i}/n$ and $\mathbb{Y}$ as the $n \times r$ matrix with rows $Y_{i} - \bar{Y}$ and $\bar{Y}$ defined similarly.
+Note that $\bar{X}$ and $\bar{Y}$ are the maximum likelihood esitmators of $\mu_{x}$ and $\mu_{y}$, respectively.
 
-\hypertarget{formulas}{%
-\section{Formulas}\label{formulas}}
+## Formulas
 
-Below we outline a few important formulas that will be used throughout
-this report:
+Below we outline a few important formulas that will be used throughout this report:
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Forward regression coefficient:
-  \(\beta = \Sigma_{xx}^{-1}\Sigma_{xy} = \Sigma_{x | y}^{-1}\alpha^{T}\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\)
-\end{enumerate}
+1. Forward regression coefficient: $\beta = \Sigma_{xx}^{-1}\Sigma_{xy} = \Sigma_{x | y}^{-1}\alpha^{T}\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Inverse regression coefficient:
-  \(\alpha = \Sigma_{yy}^{-1}\Sigma_{xy}^{T}\)
-\end{enumerate}
+2. Inverse regression coefficient: $\alpha = \Sigma_{yy}^{-1}\Sigma_{xy}^{T}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  \(\Sigma_{y | x} = \Sigma_{yy} - \beta^{T}\Sigma_{xx}\beta = \Sigma_{yy} - \Sigma_{xy}^{T}\Sigma_{xx}^{-1}\Sigma_{xy}\)
-\end{enumerate}
+3. $\Sigma_{y | x} = \Sigma_{yy} - \beta^{T}\Sigma_{xx}\beta = \Sigma_{yy} - \Sigma_{xy}^{T}\Sigma_{xx}^{-1}\Sigma_{xy}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{3}
-\tightlist
-\item
-  \(\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{yy} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}\)
-\end{enumerate}
+4.
+$\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{yy} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{yy}^{-1} + \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{4}
-\tightlist
-\item
-  \(\Sigma_{x | y} = \Sigma_{xx} - \alpha^{T}\Sigma_{yy}\alpha = \Sigma_{xx} - \Sigma_{xy}\Sigma_{yy}^{-1}\Sigma_{xy}^{T}\)
-\end{enumerate}
+5. $\Sigma_{x | y} = \Sigma_{xx} - \alpha^{T}\Sigma_{yy}\alpha = \Sigma_{xx} - \Sigma_{xy}\Sigma_{yy}^{-1}\Sigma_{xy}^{T}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{5}
-\tightlist
-\item
-  \(\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}\)
-\end{enumerate}
+6.
+$\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{xx}^{-1} + \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{6}
-\tightlist
-\item
-  \(\Sigma_{yy}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{xx} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}\)
-\end{enumerate}
+7.
+$\Sigma_{yy}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\Sigma_{xy}^{T}\left( \Sigma_{xx} + \Sigma_{xy}\Sigma_{y | x}^{-1}\Sigma_{xy}^{T} \right)^{-1}\Sigma_{xy}\Sigma_{y | x}^{-1} = \Sigma_{y | x}^{-1} - \Sigma_{y | x}^{-1}\beta\left( \Sigma_{xx}^{-1} + \beta\Sigma_{y | x}^{-1}\beta^{T} \right)^{-1}\beta\Sigma_{y | x}^{-1}$
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{7}
-\tightlist
-\item
-  \(\Sigma_{xx}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}\)
-\end{enumerate}
+8.
+$\Sigma_{xx}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\Sigma_{xy}\left( \Sigma_{yy} + \Sigma_{xy}^{T}\Sigma_{x | y}^{-1}\Sigma_{xy} \right)^{-1}\Sigma_{xy}^{T}\Sigma_{x | y}^{-1} = \Sigma_{x | y}^{-1} - \Sigma_{x | y}^{-1}\alpha\left( \Sigma_{yy}^{-1} + \alpha\Sigma_{x | y}^{-1}\alpha^{T} \right)^{-1}\alpha\Sigma_{x | y}^{-1}$
 
@@
 
-\hypertarget{estimators}{%
-\section{Estimators}\label{estimators}}
+## Estimators
 
-\hypertarget{assume-ridge-beta-optimize-in-sample-prediction-error}{%
-\subsection{\texorpdfstring{Assume ridge \(\beta\), optimize in-sample
-prediction
-error}{Assume ridge \textbackslash{}beta, optimize in-sample prediction error}}\label{assume-ridge-beta-optimize-in-sample-prediction-error}}
+### Assume ridge $\beta$, optimize in-sample prediction error
 
@@
 
-\hypertarget{assume-ridge-beta-optimize-the-likelihood-for-beta}{%
-\subsection{\texorpdfstring{Assume ridge \(\beta\), optimize the
-likelihood for
-\(\beta\)}{Assume ridge \textbackslash{}beta, optimize the likelihood for \textbackslash{}beta}}\label{assume-ridge-beta-optimize-the-likelihood-for-beta}}
+### Assume ridge $\beta$, optimize the likelihood for $\beta$
 
@@
 
-where
-\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\).
-In order to solve for \(\hat{\beta}\), we need to iterate between
-\(\hat{\beta}\) and \(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+where $\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n$.
+In order to solve for $\hat{\beta}$, we need to iterate between $\hat{\beta}$ and $\hat{\Sigma}_{y | x}^{-1}$ until convergence.
 
-Note that if \(r = 1\) then \(\sigma_{y}^{2}\) can be absorbed into
-\(\tilde{\lambda}\) and
+Note that if $r = 1$ then $\sigma_{y}^{2}$ can be absorbed into $\tilde{\lambda}$ and
 
@@
 
-\hypertarget{assume-ridge-sigma_xx-1-optimize-in-sample-prediction-error}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
-in-sample prediction
-error}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize in-sample prediction error}}\label{assume-ridge-sigma_xx-1-optimize-in-sample-prediction-error}}
+### Assume ridge $\Sigma_{xx}^{-1}$, optimize in-sample prediction error
 
@@
 
-If we use the sample estimate
-\(\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n\) then
+If we use the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ then
 
@@
 
-so that
-\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\).
+so that $\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n$.
 
@@
 
-\hypertarget{assume-ridge-sigma_xx-1-optimize-likelihood-for-beta}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
-likelihood for
-\(\beta\)}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize likelihood for \textbackslash{}beta}}\label{assume-ridge-sigma_xx-1-optimize-likelihood-for-beta}}
+### Assume ridge $\Sigma_{xx}^{-1}$, optimize likelihood for $\beta$
 
@@
 
-where
-\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\)
-so that in order to solve for
-\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\),
-we need to iterate between \(\hat{\beta}\) and
-\(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+where $\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n$ so that in order to solve for $\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n$, we need to iterate between $\hat{\beta}$ and $\hat{\Sigma}_{y | x}^{-1}$ until convergence.
 
@@
 
-\hypertarget{assume-ridge-sigma_xx-1-optimize-likelihood-for-sigma_xx-1}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xx}^{-1}\), optimize
-likelihood for
-\(\Sigma_{xx}^{-1}\)}{Assume ridge \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}, optimize likelihood for \textbackslash{}Sigma\_\{xx\}\^{}\{-1\}}}\label{assume-ridge-sigma_xx-1-optimize-likelihood-for-sigma_xx-1}}
+### Assume ridge $\Sigma_{xx}^{-1}$, optimize likelihood for $\Sigma_{xx}^{-1}$
 
@@
 
-where \(S_{xx} = \mathbb{X}^{T}\mathbb{X}/n\). Set the gradient equal to
-zero and decompose \(\Sigma_{xx}^{-1} = VDV^{T}\) where \(D\) is a
-diagonal matrix with diagonal elements equal to the eigen values of
-\(\Sigma_{xx}^{-1}\) and \(V\) is the matrix with corresponding eigen
-vectors as columns.
+where $S_{xx} = \mathbb{X}^{T}\mathbb{X}/n$.
+Set the gradient equal to zero and decompose $\Sigma_{xx}^{-1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Sigma_{xx}^{-1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
 
@@
 
-where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
+where $\phi_{j}(\cdot)$ is the $j$th eigen value.
 
@@
 
-In summary, if we decompose \(S_{xx} = VQV^{T}\) then
+In summary, if we decompose $S_{xx} = VQV^{T}$ then
 
@@
 
-so that
-\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\Sigma_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n\).
+so that $\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\Sigma_{xy} = \hat{\Sigma}_{xx}^{-1}\mathbb{X}^{T}\mathbb{Y}/n$.
 
@@
 
-\hypertarget{assume-ridge-sigma_xy-optimize-in-sample-prediction-error}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xy}\), optimize
-in-sample prediction
-error}{Assume ridge \textbackslash{}Sigma\_\{xy\}, optimize in-sample prediction error}}\label{assume-ridge-sigma_xy-optimize-in-sample-prediction-error}}
+### Assume ridge $\Sigma_{xy}$, optimize in-sample prediction error
 
@@
 
-If we use the sample estimate
-\(\hat{\Sigma}_{xx} = \mathbb{X}^{T}\mathbb{X}/n\) (assuming
-\(\mathbb{X}^{T}\mathbb{X}\) is positive definite) then
+If we use the sample estimate $\hat{\Sigma}_{xx} = \mathbb{X}^{T}\mathbb{X}/n$ (assuming $\mathbb{X}^{T}\mathbb{X}$ is positive definite) then
 
@@
 
-\hypertarget{assume-ridge-sigma_xy-optimize-likelihood-for-beta}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{xy}\), optimize
-likelihood for
-\(\beta\)}{Assume ridge \textbackslash{}Sigma\_\{xy\}, optimize likelihood for \textbackslash{}beta}}\label{assume-ridge-sigma_xy-optimize-likelihood-for-beta}}
+### Assume ridge $\Sigma_{xy}$, optimize likelihood for $\beta$
 
@@
 
-where
-\(\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n\)
-so that in order to solve for
-\(\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = n\left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\hat{\Sigma}_{xy}\),
-we need to iterate between \(\hat{\beta}\) and
-\(\hat{\Sigma}_{y | x}^{-1}\) until convergence.
+where $\hat{\Sigma}_{y | x} = (\mathbb{Y} - \mathbb{X}\hat{\beta} )^{T}(\mathbb{Y} - \mathbb{X}\hat{\beta})/n$ so that in order to solve for $\hat{\beta} = \hat{\Sigma}_{xx}^{-1}\hat{\Sigma}_{xy} = n\left( \mathbb{X}^{T}\mathbb{X} \right)^{-1}\hat{\Sigma}_{xy}$, we need to iterate between $\hat{\beta}$ and $\hat{\Sigma}_{y | x}^{-1}$ until convergence.
 
@@
 
-\hypertarget{assume-ridge-sigma_x-y-1-optimize-likelihood-for-sigma_x-y-1}{%
-\subsection{\texorpdfstring{Assume ridge \(\Sigma_{x | y}^{-1}\),
-optimize likelihood for
-\(\Sigma_{x | y}^{-1}\)}{Assume ridge \textbackslash{}Sigma\_\{x \textbar{} y\}\^{}\{-1\}, optimize likelihood for \textbackslash{}Sigma\_\{x \textbar{} y\}\^{}\{-1\}}}\label{assume-ridge-sigma_x-y-1-optimize-likelihood-for-sigma_x-y-1}}
+### Assume ridge $\Sigma_{x | y}^{-1}$, optimize likelihood for $\Sigma_{x | y}^{-1}$
 
@@
 
-where
-\(S_{x | y} = \left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)^{T}\left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)/n\)
-and
-\(\hat{\alpha} = \left( \mathbb{Y}^{T}\mathbb{Y} \right)^{-1}\mathbb{Y}^{T}\mathbb{X}\).
-Following the derivations in section (3.5), if we decompose
-\(S_{x | y} = VQV^{T}\) then
+where $S_{x | y} = \left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)^{T}\left( \mathbb{X} - \mathbb{Y}\hat{\alpha} \right)/n$ and $\hat{\alpha} = \left( \mathbb{Y}^{T}\mathbb{Y} \right)^{-1}\mathbb{Y}^{T}\mathbb{X}$.
+Following the derivations in section (3.5), if we decompose $S_{x | y} = VQV^{T}$ then
 
@@
 
-\hypertarget{assume-ridge-alpha-optimize-in-sample-prediction-error-for-alpha}{%
-\subsection{\texorpdfstring{Assume ridge \(\alpha\), optimize in-sample
-prediction error for
-\(\alpha\)}{Assume ridge \textbackslash{}alpha, optimize in-sample prediction error for \textbackslash{}alpha}}\label{assume-ridge-alpha-optimize-in-sample-prediction-error-for-alpha}}
+### Assume ridge $\alpha$, optimize in-sample prediction error for $\alpha$
 
@@
 
-\hypertarget{assume-ridge-alpha-optimize-likelihood-for-alpha}{%
-\subsection{\texorpdfstring{Assume ridge \(\alpha\), optimize likelihood
-for
-\(\alpha\)}{Assume ridge \textbackslash{}alpha, optimize likelihood for \textbackslash{}alpha}}\label{assume-ridge-alpha-optimize-likelihood-for-alpha}}
+### Assume ridge $\alpha$, optimize likelihood for $\alpha$
 
@@
 
-where
-\(\hat{\Sigma}_{x | y} = (\mathbb{X} - \mathbb{Y}\hat{\alpha} )^{T}(\mathbb{X} - \mathbb{Y}\hat{\alpha})/n\).
-In order to solve for \(\hat{\alpha}\), we need to iterate between
-\(\hat{\alpha}\) and \(\hat{\Sigma}_{x | y}^{-1}\) until convergence.
+where $\hat{\Sigma}_{x | y} = (\mathbb{X} - \mathbb{Y}\hat{\alpha} )^{T}(\mathbb{X} - \mathbb{Y}\hat{\alpha})/n$.
+In order to solve for $\hat{\alpha}$, we need to iterate between $\hat{\alpha}$ and $\hat{\Sigma}_{x | y}^{-1}$ until convergence.
 Again, using the Woodbury Identity, we find that
@@
 \[ \hat{\beta} = \hat{\Sigma}_{x | y}^{-1}\hat{\alpha}^{T}\left( \Sigma_{yy}^{-1} + \hat{\alpha}\hat{\Sigma}_{x | y}^{-1}\hat{\alpha}^{T} \right)^{-1} \]
-
-\bibliography{lib.bib}
-
-\end{document}

### 2018-08-03 02-ADMM-Details.Rmd
updated material with new vignettes

@@
 \begin{align*}
-  f(X | \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
+  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
   &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
@@
 
-If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$.
-However, in addition to $\mu$, many practical applications require the estimation of $\Sigma$ as well.
-Like $\mu$, we can find a maximum likelihood estimator:
+If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}_{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$.
+However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well.
+We can also find a maximum likelihood estimator:
 
 \begin{align*}
-  &\hat{\Sigma} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
+  &\hat{\Sigma}_{MLE} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
 - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \right\} \\
-  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} - \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
-  \Rightarrow &\hat{\Sigma} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
+  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} + \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
+  \Rightarrow &\hat{\Sigma}_{MLE} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
 \end{align*}
 
-by setting the gradient equal to zero and plugging in the MLE for $\mu$.
-This implies that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$.
-We could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$:
+By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$.
+It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:
 
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
+\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
 
-so that $\hat{\Omega} = S^{-1}$.
-Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
-Both procedures will result in the same estimate.
-Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instad of $\Sigma$.
+so that $\hat{\Omega}_{MLE} = S^{-1}$.
+Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$.
 
-As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the likelihood:
+Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate.
+
+As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
 
@@
 
-$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
+$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
 These penalties are the ridge and lasso, respectively.
-In the `ADMMsigma` package, we instead take $P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]$ so that solving the full penalized log-likelihood for $\Omega$ results in solving
+In the `ADMMsigma` package, we instead take
+
+\[ P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \]
+
+so that solving the full penalized log-likelihood for $\Omega$ results in solving
 
@@
 Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty.
-Having this flexibility or generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.
+Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.
 
@@
 
-Many efficient methods have been proposed in order to solve for $\hat{\Omega}$ when $\alpha = 1$.
+Many efficient methods have been proposed to solve for $\hat{\Omega}$ when $\alpha = 1$.
 The most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse.
@@
 
-where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are assumed to be convex functions.
-Our goal is to find $x^{*} \in \mathbb{R}^{n}$ and $z^{*} \in \mathbb{R}^{m}$ that results in the infimum $p^{*}$:
+where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are assumed to be convex functions (following @boyd2011distributed, the estimation procedure will be introduced in vector form though we could just as easily take $x$ and $z$ to be matrices).
+In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods.
+For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem.
+In all cases, our goal is to find $x^{*} \in \mathbb{R}^{n}$ and $z^{*} \in \mathbb{R}^{m}$ that achieves the infimum $p^{*}$:
 
@@
 
-Honoring the constraint $Ax + Bz = c$, the lagrangian will be of the form
-
-\[ L(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) \]
-
-where $y \in \mathbb{R}^{p}$ is the lagrange multiplier.
-Following @boyd2011distributed, the estimation procedure will be introduced in vector form though we will later consider the case where $x$ and $z$ are matrices.
-
-In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods.
-For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem.
-
-The ADMM algorithm, however, uses the *augmented lagrangian*
+To do so, the ADMM algorithm uses the *augmented lagrangian*
 
@@
 
-in which case $\rho > 0$ is a scalar.
+where $y \in \mathbb{R}^{p}$ is the lagrange multiplier and $\rho > 0$ is a scalar.
 Clearly any minimizer, $p^{*}$, under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point $(x, z)$ satisfies the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.
-The ADMM algorithm consists of the following repeated iterations:
+
+The algorithm consists of the following repeated iterations:
 
 \begin{align}
-  x^{k + 1} &:= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &:= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
+  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
+  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
 \end{align}
@@
 
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] \]
+\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] \]
 
-Augmented lagrangian:
+and the augmented lagrangian is
 
@@
 \begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
 \end{align*}
@@
 
-where $Soft(a, b) = Sign(a)(\left| a \right| - b)_{+}$.
+where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
 
@@
 
-Note that because all of the variables are symmetric, we can essentially ignore the constraint when deriving the gradient.
-Set the gradient equal to zero and decompose $\Omega = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega$ and $V$ is the matrix with corresponding eigen vectors as columns.
+Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
+First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:
 
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
+\[ S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
 
@@
   &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
+  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
 \end{align*}
 
-where $Sign(Z)$ is the elementwise Sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
 
-\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]
+\[ Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right) \]
 
@@
 
-- If $Z_{ij} > 0$ then
+- If $Z_{ij}^{k + 1} > 0$ then
 
@@
 
-- If $Z_{ij} < 0$ then
+- If $Z_{ij}^{k + 1} < 0$ then
 
@@
 
-This implies that $Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at
+This implies that $\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at
 
 \begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
 \end{align*}
 
-where $Soft$ is the soft-thresholding function.
+where soft is the soft-thresholding function.
 
@@
 
-There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable ($\Lambda^{k}$).
-
-Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.
+There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable ($\Lambda^{k}$). Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.
 
@@
 
-We will define the left-hand side of the first condition as the primal residual: $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$.
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).
+
+We will define the left-hand side of the first condition as the primal residual $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$.
 At convergence, optimality conditions require that $r^{k + 1} \approx 0$.
-The second residual we will define is the dual residual: $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$.
-This residual is defined from the following:
+The second residual we will define is the dual residual $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$.
+This residual is derived from the following:
 
@@
   &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
-  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
   &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\

### 2018-08-03 03-ADMM-Tutorial.Rmd
added SCPME materials
updated material with new vignettes

--- 2018-06-06 02-Tutorial.Rmd
@@
-# Tutorial
+# `ADMMsigma` Tutorial
 
-<br>\vspace{0.5cm}
-```{r, eval = FALSE, echo = TRUE}
-# The easiest way to install is from CRAN
-install.packages("ADMMsigma")
+In many statistical applications, estimating the covariance for a set of random variables is a critical task.
+The covariance is useful because it characterizes the *relationship* between variables.
+For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form
 
-# You can also install the development version from GitHub:
-# install.packages("devtools")
-devtools::install_github("MGallow/ADMMsigma")
-```
-<br>\vspace{0.5cm}
+\[ \Sigma_{xyz} = \begin{pmatrix}
+1 & 0 & 0.5 \\ 
+0 & 1 & 0 \\ 
+0.5 & 0 & 1
+\end{pmatrix} \]
 
-If there are any issues/bugs, please let me know: [github](https://github.com/MGallow/ADMMsigma/issues).
-You can also contact me via my [website](https://mgallow.github.io/).
-Pull requests are welcome!
+We can gather valuable information from this matrix.
+First of all, we know that each of the variables has an equal variance of 1.
+Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0.
+This implies that any information in $X$ is useless in trying to gather information about $Y$.
+Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.
+
+Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging.
+For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
+
+`ADMMsigma` is designed to estimate a robust $\Omega$ efficiently while also allowing for flexibility and rapid experimentation for the end user.
+
+We will illustrate this with a short simulation.
 
@@
 
-A (possibly incomplete) list of functions contained in the package can be found below:
+## Simulation
 
-* `ADMMsigma()` computes the estimated precision matrix (ridge, lasso, and elastic-net type regularization optional)
-
-* `RIDGEsigma()` computes the estimated ridge penalized precision matrix via closed-form solution
-
-* `plot.ADMMsigma()` produces a heat map or line graph for cross validation errors
-
-* `plot.RIDGEsigma()` produces a heat map or line graph for cross validation errors
-
-<br>\vspace{1cm}
-
-## Usage
-
-We will first generate data from a sparse, tri-diagonal precision matrix and denote it as Omega.
+Let us generate some data.
 
@@
 
-# print oracle precision matrix (shrinkage might be useful)
-(Omega = round(qr.solve(S), 3))
-
 # generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
@@
 
-As described earlier in the report, the maximum likelihood estimator (MLE) for Omega is the inverse of the sample precision matrix $S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}$:
+We have generated 100 samples (5 variables) from a normal distribution with mean equal to zero and an oracle covariance matrix $S$.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE}
+
+# print oracle covariance matrix
+S
+
+# print inverse covariance matrix (omega)
+round(qr.solve(S), 5)
+
+```
+<br>\vspace{0.5cm}
+
+It turns out that this particular oracle covariance matrix (tapered matrix) has an inverse - or precision matrix - that is sparse (tri-diagonal). That is, the precision matrix has many zeros.
+
+In this particular setting, we could estimate $\Omega$ by taking the inverse of the sample covariance matrix $\hat{S} = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n$:
 
@@
 
-However, because Omega (known as the *oracle*) is sparse, a shrinkage estimator will perhaps perform better than the sample estimator. Below we construct various penalized estimators:
+However, because $\Omega$ is sparse, this estimator will likely perform very poorly.
+Notice the number of zeros in our oracle precision matrix compared to the inverse of the sample covariance matrix.
+Instead, we will use `ADMMsigma` to estimate $\Omega$.
+
+By default, `ADMMsigma` will construct $\Omega$ using an elastic-net penalty and choose the optimal `lam` and `alpha` tuning parameters.
 
@@
 
-**LASSO:**
+We can see that the optimal `alpha` value selected was 1.
+This selection corresponds with a lasso penalty -- a special case of the elastic-net penalty.
+Further, a lasso penalty embeds an assumption in the estimate (call it $\hat{\Omega}$) that the true $\Omega$ is sparse.
+Thus the package has automatically selected the penalty that most-appropriately matches the *true* data-generating precision matrix.
+
+We can also explicitly assume sparsity in our estimate by restricting the class of penalties to the lasso. We do this by setting `alpha = 1` in our function:
 
@@
 
-**ELASTIC-NET:**
+We might also want to restrict `alpha = 0.5`:
 
@@
 
-**RIDGE:**
+Or maybe we want to assume that $\Omega$ is *not* sparse but has entries close to zero.
+In this case, a ridge penalty would be most appropriate.
+We can estimate an $\Omega$ of this form by setting `alpha = 0` in the `ADMMsigma` function or using the `RIDGEsigma` function.
+`RIDGEsigma` uses a closed-form solution rather than an algorithm to compute its estimate -- and for this reason should be preferred in most cases (less computationally intensive).
 
@@
 
-# ridge penalty no ADMM
+# ridge penalty (using closed-form solution)
 RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01))
@@
 
-This package also has the capability to provide heat maps for the cross validation errors. The more bright (white) areas of the heat map pertain to more optimal tuning parameters.
+`ADMMsigma` also has the capability to provide plots for the cross validation errors. This allows the user to analyze and select the appropriate tuning parameters.
+
+In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection.
 
@@
 ```
-<br>\newpage
+<br>\vspace{0.5cm}
 
+We can also produce a line graph of the cross validation errors:
+
+<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE}
@@
 ```
-<br>\newpage
+<br>\vspace{0.5cm}
 
+And similarly for `RIDGEsigma`:
+
+<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE}
@@
 
-```
-
-<br>\newpage
-```{r, message = FALSE, echo = TRUE}
-
 # produce line graph for CV errors for RIDGEsigma
@@
 ```
+<br>\vspace{0.5cm}
+
+## More advanced options
+
+`ADMMsigma` contains a number of different criteria for selecting the optimal tuning parameters during cross validation.
+The package default is to choose the tuning parameters that maximize the log-likelihood (`crit.cv = loglik`).
+Other options include `AIC` and `BIC`.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE}
+
+# AIC
+plot(ADMMsigma(X, crit.cv = "AIC"))
+
+# BIC
+plot(ADMMsigma(X, crit.cv = "BIC"))
+
+```
+<br>\vspace{0.5cm}
+
+This allows the user to select appropriate tuning parameters under various decision criteria.
+We also have the option to print *all* of the estimated precision matrices for each tuning parameter combination using the `path` option.
+This option should be used with *extreme* care when the dimension and sample size is large -- you may run into memory issues.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE}
+
+# keep all estimates using path
+ADMM = ADMMsigma(X, path = TRUE)
+
+# print only first three objects
+ADMM$Path[,,1:3]
+
+```
+<br>\vspace{0.5cm}
+
+A huge issue in precision matrix estimation is the computational complexity when the sample size and dimension of our data is particularly large.
+There are a number of built-in options in `ADMMsigma` that can be used to improve computation speed:
+
+ - Reduce the number of `lam` values during cross validation. The default number is 10.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# reduce number of lam to 5
+ADMM = ADMMsigma(X, nlam = 5)
+
+```
+<br>\vspace{0.5cm}
+
+ - Reduce the number of `K` folds during cross validation. The default number is 5.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# reduce number of folds to 3
+ADMM = ADMMsigma(X, K = 3)
+
+```
+<br>\vspace{0.5cm}
+
+ - Relax the convergence critera for the ADMM algorithm using the `tol.abs` and `tol.rel` options. The default for each is 1e-4.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# relax convergence criteria
+ADMM = ADMMsigma(X, tol.abs = 1e-3, tol.rel = 1e-3)
+
+```
+<br>\vspace{0.5cm}
+
+ - Adjust the maximum number of iterations. The default is 1e4.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# adjust maximum number of iterations
+ADMM = ADMMsigma(X, maxit = 1e3)
+
+```
+<br>\vspace{0.5cm}
+
+ - Adjust `adjmaxit`.
+This allows the user to adjust the maximum number of iterations *after* the first `lam` tuning parameter has fully converged during cross validation.
+This allows for *one-step estimators* and can greatly reduce the time required for the cross validation procedure while still choosing near-optimal tuning parameters.
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# adjust adjmaxit
+ADMM = ADMMsigma(X, maxit = 1e4, adjmaxit = 2)
+
+```
+<br>\vspace{0.5cm}
+
+ - We can also opt to run our cross validation procedure in parallel. The user should check how many cores are on their system before using this option
+
+<br>\vspace{0.5cm}
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# parallel CV
+ADMM = ADMMsigma(X, cores = 3)
+
+```
+<br>\vspace{0.5cm}

### 2018-08-03 04-ADMM-Simulations.Rmd
added SCPME materials
updated material with new vignettes

--- 2018-06-06 04-Simulations.Rmd
@@
-# Simulations
+# `ADMMsigma` Simulations
 
-In the simulations below we generated data from a number of oracle precision matrices with various structures.
+In the simulations below, we generate data from a number of different oracle precision matrices with various structures.
 For each data-generating procedure, the `ADMMsigma()` function was run using 5-fold cross validation.
-After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results in the top figure).
+After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results below the top figure).
 These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure).
-We can see below that our cross validation procedure choosing tuning parameters close to the optimal parameters.
 
-<br>\newpage
+We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.
+
+<br>\vspace{1cm}
+
+## Plots
 
@@
 
-![](images/compound_N50_P100.png)
-
-<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE, eval = FALSE}
@@
 ```
+<br>\vspace{0.5cm}
+
+![](images/compound_N50_P100.png)
 
@@
 
-![](images/compound_N1000_P10.png)
-
-<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE, eval = FALSE}
@@
 ```
+<br>\vspace{0.5cm}
+
+![](images/compound_N1000_P10.png)
 
@@
 
-![](images/repsKLdenseQR_N50_P100.png)
-
-<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
@@
 ```
+<br>\vspace{0.5cm}
+
+![](images/repsKLdenseQR_N50_P100.png)
 
@@
 
-![](images/repsKLdense_N50_P10.png)
-
-<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
@@
 ```
+<br>\vspace{0.5cm}
+
+![](images/repsKLdense_N50_P10.png)
 
@@
 
-![](images/repsKLtridiag_N50_P100.png)
-
-<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
@@
 ```
+<br>\vspace{0.5cm}
+
+![](images/repsKLtridiag_N50_P100.png)

### 2018-08-03 06-SCPME-Details.Rmd
updated material with new vignettes

@@
 
-If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$.
-However, in addition to $\mu$, many practical applications require the estimation of $\Sigma$ as well.
-Like $\mu$, we can find a maximum likelihood estimator:
+If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}_{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$.
+However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well.
+We can also find a maximum likelihood estimator:
 
 \begin{align*}
-  &\hat{\Sigma} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
+  &\hat{\Sigma}_{MLE} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
 - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \right\} \\
-  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} - \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
-  \Rightarrow &\hat{\Sigma} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
+  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} + \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
+  \Rightarrow &\hat{\Sigma}_{MLE} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
 \end{align*}
 
-by setting the gradient equal to zero and plugging in the MLE for $\mu$.
-This implies that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$.
-We could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$:
+By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$.
+It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:
 
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| \right\} \]
+\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
 
-so that $\hat{\Omega} = S^{-1}$.
-Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
-Both procedures will result in the same estimate.
-Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instad of $\Sigma$.
+so that $\hat{\Omega}_{MLE} = S^{-1}$.
+Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$.
 
@@
 
-$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
+$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
 These penalties are the ridge and lasso, respectively.
@@
 
-so that solving the full penalized log-likelihood for $\Omega$ results in solving
+where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
+Solving the full penalized log-likelihood for $\Omega$ results in solving
 
@@
 
-where $A \in \mathbb{R}^{n \times p}, B \in \mathbb{R}^{p \times r}, \mbox{ and } C \in \mathbb{R}^{n \times r}$ are matrices assumed to be known and specified by the user.
-As discussed [here](https://mgallow.github.io/SCPME/articles/Jointloglik.html), this type of penalty leads to many new, interesting, and novel estimators for $\Omega$.
-An example of one such estimator would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ so that we assume sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.
+This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$.
+This type of penalty leads to many new, interesting, and novel estimators for $\Omega$.
+An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$.
+This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$
 
@@
 
-This section requires general knowledge of the ADMM algorithm.
-I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.
+*This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm.
+I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.*
 
-The ADMM algorithm within the context of this problem consists of the following repeated iterations:
+The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.
+Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:
 
 \begin{align}
-  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
-  Z^{k + 1} &:= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
-  \Lambda^{k + 1} &:= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
 \end{align}
@@
 with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$.
+However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.
 
-We instead replace with
+The approximating function is defined as
 
 \begin{align*}
-  tr\left(S\Omega\right) &- \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] \\
-  &+ \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \\
-  &= tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C)\right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}tr\left[A^{T}A(\Omega - \Omega^{k})BB^{T}(\Omega - \Omega^{k})\right] + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2}
+  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
+\end{align*}
+
+where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$, $\otimes$ is the Kronecker product, and $\tau$ is chosen such that $Q$ is positive definite.
+Note that if $Q$ is positive definite (p.d.), then
+
+\[ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0 \]
+
+since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.
+Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function.
+
+To see why this particular function was used, consider the Taylor's expansion of $\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2$:
+
+\begin{align*}
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
 \end{align*}
@@
 **Note:**
-
-\begin{align*}
-  vec\left(\Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) &= vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}(\Omega - \Omega^{k})A^{T}A\right) \\
-  &= tr\left[A^{T}A\left(\Omega - \Omega^{k}\right)BB^{T}\left(\Omega - \Omega^{k}\right)\right]
-\end{align*}
-
-Suppose we define $G^{k} := A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho$. Then
-
-\begin{align*}
-  &\nabla_{\Omega}\left\{tr\left[\left(S + \rho A^{T}G^{k}B^{T}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
-  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
-  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
-\end{align*}
-
-Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to
-
-\begin{align*}
-  0 &= S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - (\Omega^{k + 1})^{-1} + \rho\tau\left(\Omega^{k + 1} - \Omega^{k}\right) \\
-  \Rightarrow &S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1}
-\end{align*}
-
-Consider
 
@@
 
+This implies that
+
 \begin{align*}
-  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
+  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
   &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
-  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
+  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
+  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
 \end{align*}
 
-Consider $\rho vec\left(\Omega - \Omega^{k}\right)^{T}Q vec\left(\Omega - \Omega^{k} \right)/2$ where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite.
-
-Note that if $Q$ is positive definite (p.d.), then
-
-\[ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)Q\left(\Omega - \Omega^{k} \right) > 0 \]
-
-since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.
-
-This implies the following fact:
-
-\[ \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \leq \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q vec\left(\Omega - \Omega^{k} \right) \]
-
-Further,
+Let us now plug in this equality into our optimization problem in step one:
 
 \begin{align*}
-  \nabla_{\Omega}&\left\{const.
-+ \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k} \right\|_{F}^{2} + \rho tr\left[\Omega^{T}\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \right] \right\} \\
-  &= \rho\tau\left(\Omega - \Omega^{k}\right) + \rho BB^{T}\Omega A^{T}A - \rho B(Z^{k})^{T}A - \rho BC^{T}A
+  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
+  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
+ tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
 \end{align*}
 
-This implies a majorizing function!
+where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.
+
+<br>\vspace{1cm}
+
+The *augmented ADMM* algorithm is the following:
+
+\begin{align}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+\end{align}
 
@@
 
-1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$
+1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}$
 
-2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).
+2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
 
-3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
+3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
 
-4. Set $Z_{k + 1} = \mbox{soft}\left( A\Omega_{k + 1}B - C + \rho^{-1}Y_{k}, \rho^{-1}\lambda \right)$
+4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)$
 
-5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$
+5. Set $Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
 
@@
 
-\[ \Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\vspace{1cm}
+\[ \Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \]
 
 \begin{align*}
-  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
+  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
+  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
 \end{align*}
 
-Note that because all of the variables are symmetric, we can essentially ignore the constraint when deriving the gradient.
-Set the gradient equal to zero and decompose $\Omega = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega$ and $V$ is the matrix with corresponding eigen vectors as columns.
+Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to
 
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
+\[ S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \]
+
+We can then decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
+
+\[ S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \]
 
@@
 
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
+\[ \phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \]
 
-where $\phi_{j}(\cdot)$ is the $j$th eigen value.
+where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}$. Therefore
 
 \begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
+  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
+  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
 \end{align*}
 
-In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then
+In summary, if we decompose $S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ then
 
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
+\[ \Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T} \]
 
@@
   &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
-  &= Sign(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
+  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
 \end{align*}
 
-where $Sign(Z)$ is the elementwise Sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+where $\mbox{sign(Z)}$ is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
 
-\[ Z_{ij} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda \right) \]
+\[ Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right) \]
 
@@
 
-This implies that $Sign(Z_{ij}) = Sign\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at
+This implies that $\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at
 
 \begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\rho}Sign\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
-&= \frac{1}{\rho}Soft\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
+Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
+&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
 \end{align*}
 
-where $Soft$ is the soft-thresholding function.
+where soft is the soft-thresholding function.
 
@@
 
-The first dual optimality condition is a result of taking the sub-differential of $L_{\rho}\left( \Omega^{k + 1}, Z^{k + 1}, \Lambda^{k + 1} \right)$ with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$).
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).
 
-We will define the left-hand side of the primal optimality condition as the primal residual: $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$.
+We will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$.
 At convergence, the optimality conditions require that $r^{k + 1} \approx 0$.
@@
 
-This residual is defined from the following:
+This residual is derived from the following:
 

### 2018-08-03 07-SCPME-Connection.Rmd
updated material with new vignettes

@@
 where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm.
-In addition, $A \in \mathbb{R}^{n \times p}, B \in \mathbb{R}^{p \times r}, \mbox{ and } C \in \mathbb{R}^{n \times r}$ are matrices assumed to be known and specified by the user.
-This objective function is the log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$, plus a penalty term.
+In addition, $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
+This objective function is a penalized log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$.
 
-\[ \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\} \]
+\[ \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\} \]
 
 where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$.
-Under this particular likelihood, it is assumed that each observation of $X$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- though Dennis Cook and others have shown this objective function to work well as a generic loss even when the assumptions are not met.
+Under this particular likelihood, it is assumed that each observation of $X_{i}$ in a sample size of size $n$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.
 
-This type of formulation leads to many new, interesting, and novel estimators for $\Omega$. For instance, we might set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0,$ in which case
+This particular formulation for the penalty leads to many new, interesting, and novel estimators for $\Omega$.
+For instance, if in addition to $X$ we also observe $n$ copies of the random variable $Y$, we might set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$.
+In which case
 
@@
 
-That is, this objective function estimates an $\Omega$ with respect to the marginal likelihood of $X$ under the assumption that $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$).
+This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$).
 We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.
@@
 In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
-Further, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that
+Furthermore, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that
 
@@
 We will name this estimator the *lasso SCPME estimator*.
-Note that in practice - for any of these estimators - we do not know the true covariance $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$.
+Note that in practice - for any of these estimators - we do not know the true covariance matrix $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ in its place.
 
-All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) framework outlined in the paper. The augmented ADMM algorithm is the following:
+All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper.
+The augmented ADMM algorithm (details [here](https://mgallow.github.io/SCPME/articles/Details.html#augmented-admm-algorithm)) is the following:
 
@@
 
-1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$
+1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}$
 
-2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).
+2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
 
-3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
+3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
 
-4. Set $Z_{k + 1} = \mbox{soft}\left( A\Omega_{k + 1}B - C + \rho^{-1}Y_{k}, \rho^{-1}\lambda \right)$
+4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)$
 
-5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$
+5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
 
@@
 
-The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
+The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
 
@@
 
-To see this, let us suppose that we have $n$ independent copies of $(Y_{i}, X_{i})$ where $Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}X_{i}, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-That is,
+To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:
 
-\[ Y_{i} = \mu_{y} + \beta^{T}X_{i} + E_{i} \]
+\[ Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i} \]
 
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$.
-Similar to before, take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$.
+where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
+These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form
 
-Below we derive the joint likelihood:
+\[ Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right) \]
+
+We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$.
+Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience.
+We will also let $f$ denote the probability distribution function for each respective variable.
 
 \begin{align*}
-  L\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) &\propto f\left(Y | X, \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X | \Omega, \mu_{x} \right) \\
-  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right) \right] \\
+  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
+  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
   &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
-  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)^{T}\Omega_{y | x} \right] \\
+  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
   &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
@@
 \begin{align*}
-  l\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\left( Y_{i} - \mu_{y} - \beta^{T}X_{i} \right)\Omega_{y | x} \right] \\
-  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
+  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const.
++ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
+  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
 \end{align*}
@@
 \begin{align*}
- \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left( -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right) \right\} \\
- &= -\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
- \Rightarrow \hat{\mu_{x}} &= \bar{X} \\ \\
- \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left( -n\mu_{y}(\bar{Y} - \beta^{T}\bar{X})\Omega_{y | x} - n(\bar{Y} - \beta^{T}\bar{X})\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right) \right\} \\
- &= -\frac{1}{2}\left( -n\Omega_{y | x}(\bar{Y} - \beta^{T}\bar{X}) - n\Omega_{y | x}(\bar{Y} - \beta^{T}\bar{X}) + 2n\Omega_{y | x}\mu_{y} \right) \\
- \Rightarrow \hat{\mu_{y}} &= \bar{Y} - \beta^{T}\bar{X}
+ \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
+ &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
+ \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right) \\ \\
+ \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
+ &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
+ &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
+ &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
+ \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
+ \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
+ \Rightarrow \hat{\mu}_{x} &= \bar{X}
 \end{align*}
 
-Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$. This can be achieved by simply centering the data by the sample averages.
+Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.
 
+Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$.
+This can be achieved by simply centering the data by the sample averages.
 Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:
@@
   l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\Omega_{y | x} \right] \\
++ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
   &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
@@
 
-where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm. Let us assume that $\Omega_{y | x}^{1/2} = I_{r}$ and let $\lambda = 2/n$. Then
+where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm.
+Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$.
+Therefore, we have that
 
@@
 
-Notice that this is exactly the ridge SCPME estimator.
-This tells us that with just a few assumptions, the ridge SCPME estimator with $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ is equivalent to maximizing the joint log-likelihood of $X$ and $Y$ with respect to $\Omega$.
-Specifically, if we assume that, given $X$, each response is independent of one another and has equal variance (denoted as $\sigma_{y | x}^{2}$) then letting $\lambda = 2/(n\sigma_{y | x}^{2})$ and solving for the ridge SCPME estimator is equivalent to solving for the optimal $\hat{\Omega}$ under the joint log-likelihood of $X$ and $Y$.
+Notice that this is exactly the ridge SCPME estimator!
+
+<br>
+\vspace{1cm}
+
+## Takeaways
+
+We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:
+
+1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that
+
+\[ Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i} \]
+
+where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
+
+2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.
+
+3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.
 
@@
 
-1. Compute $G_{k} = \rho A^{T}\left( A\Omega_{k} B - Z_{k} - C + \rho^{-1}Y_{k} \right)$
+1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$
 
-2. Decompose $S + \left( G_{k} + G_{k}^{T} \right)/2 - \rho\tau\Omega_{k} = VQV^{T}$ (via the spectral decomposition).
+2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
 
-3. Set $\Omega_{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
+3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
 
-4. Set $Z_{k + 1} = \left[ \rho\left( A\Omega_{k + 1} B - C \right) + Y_{k} \right]/(\lambda + \rho)$
+4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$
 
-5. Set $Y_{k + 1} = \rho\left( A\Omega_{k + 1} B - Z_{k + 1} - C \right)$
+5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
 
@@
 
-The only difference is in step 4.
+Note that the only difference is in step 4.
 
 There are a few takeaways we can make after revealing this connection.
-The first is that the estimator constructed in this section is not complete nonsense.
-We are, in fact, solving a very similar problem to that of optimizing the joint likelihood.
-The second takeaway is that the SCPME estimator offers a very efficient method of computing this joint likelihood estimator.
-To the best of my knowledge, no closed-form solution to the ridge SCPME estimator exists and so we must resort to some iterative algorithm like this one in order to solve it.
+The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$.
+The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator.
+No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it.
+We show this below:
+
+<br>\vspace{1cm}
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \]
+
+\begin{align*}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
+  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
+  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
+  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
+\end{align*}
+
+by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.
 
@@
 ## Exploratory simulations
+
+Under the assumptions discussed previously, let us first show that the MLE for $\Omega$ is *not*, in fact, the sample estimator $\hat{\Omega} = \left(\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right)^{-1}$.
+We can prove this by showing that the ridge MSCPME estimator achieves a larger log-likelihood value.
+
+Below we will randomly generate some data from a diagonal oracle precision matrix and compute our estimators:
+
+<br>\vspace{1cm}
+```{r, tidy = TRUE}
+
+# load libraries
+library(SCPME)
+set.seed(1234)
+
+# randomly generate the data
+data = data_gen(n = 100, p = 10, r = 5)
+
+# print Omega
+Omega = qr.solve(data$SigmaX)
+round(Omega, 5)
+
+# print sample precision matrix (perhaps bad estimate)
+sample = qr.solve((nrow(data$X) - 1)/nrow(data$X)*cov(data$X))
+round(sample, 5)
+
+SCPME = shrink(data$X, data$Y, A = data$X, B = cov(data$X, data$Y), C = data$Y, lam = 2/100, alpha = 0)
+
+```
+<br>\vspace{1cm}
+
+Note that we use the oracle covariance $\Sigma_{xy}$ in our calculation. We can also substitute for it using the sample estimate:
 
@@
 
-# load libraries
-library(statr)
-library(SCPME)
-set.seed(1234)
-
 # randomly generate the data
@@
 ```
+<br>\vspace{1cm}
+
+### Calculate the *lasso SCPME estimator* using 5-fold CV to choose the $\lambda$ that minimizes in-sample MSPE:
+
+<br>\vspace{1cm}
+```{r, tidy = TRUE}
+
+# lasso SCPME
+(lasso = shrink(data$X, data$Y, A = data$X, B = cov(data$X, data$Y), C = data$Y, lam.max = 10, lam.min.ratio = 1e-4, nlam = 20))
+
+```
+<br>\vspace{1cm}
+
+### Calculate the *ridge SCPME estimator* by first setting $\lambda = 2/100$:
+
+<br>\vspace{1cm}
+```{r, tidy = TRUE}
+
+# ridge SCPME
+(lasso = shrink(data$X, data$Y, A = data$X, B = cov(data$X, data$Y), C = data$Y, lam = 2/100, alpha = 0))
+
+```
+<br>\vspace{1cm}
+
+### Now calculate the *ridge SCPME estimator* using 5-fold CV to choose the $\lambda$ that minimizes in-sample MSPE:
+
+<br>\vspace{1cm}
+```{r, tidy = TRUE}
+
+# lasso SCPME
+(lasso = shrink(data$X, data$Y, A = data$X, B = cov(data$X, data$Y), C = data$Y, lam.max = 10, lam.min.ratio = 1e-4, nlam = 20, alpha = 0))
+
+# plot CV errors
+plot(lasso)
+
+```
+<br>\vspace{1cm}
+
+We can see that optimal tuning parameter selected is on the edge of the candidate set.
+This will be true even if you allow `lam.max = 100`.
+This is due to the fact that the cross validation criteria is the in-sample prediction error and the penalty term is the prediction error across all samples -- so weighting, or putting more emphasis, on the prediction error in the objective function will always be favored.
+One can overcome this by changing the cross validation criteria.
+
+### Calculate the *ridge SCPME estimator* using 5-fold CV to choose the $\lambda$ that maximizes the penalized log-likelihood:
+
+<br>\vspace{1cm}
+```{r, tidy = TRUE}
+
+# lasso SCPME
+(lasso = shrink(data$X, data$Y, A = data$X, B = cov(data$X, data$Y), C = data$Y, lam.max = 10, lam.min.ratio = 1e-4, nlam = 20, alpha = 0, crit.cv = "penloglik"))
+
+```
+<br>\vspace{1cm}

### 2018-08-03 08-SCPME-Simulations.Rmd
updated material with new vignettes

@@
 # `SCPME` Simulations
+
+## Estimator Comparison
 
@@
 
+ - `oracleS` = oracle estimator with the true $\Sigma_{xy}^{*}$ known and sample estimator for $\Omega$ ($\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}$)
+
  - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)
@@
  - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)
-
- - `shrinkXY` = shrinking characteristics regression estimator with A = X, B = cov(X, Y), and C = Y (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$)
-
- - `shrinkXYO` = shrinking characteristics regression estimator meant to emulate the "likelihood" for $\beta$ (using oracle $\Omega_{y | x}^{*}$) (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$)
 
@@
  - `p` = (10, 50, 100, 150)
- - `r` = c(1, 5)
- - `sparse` = 0.5
- - `sigma` = "tridiag"
+ - `r` = c(1, 5, 10)
+ - `sparse` = c(0.5)
+ - `sigma` = c("tridiag")
 
@@
 
-## Plots
+### Plots
+
+#### High Dimension
+
+Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE).
+Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.
 
@@
 # load data
-load("images/sim5.Rdata")
+load("images/sim6.Rdata")
 
@@
 
-# MSPE by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 500, sparse = 0.5, sigma = tridiag)")
+# ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
+data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")
 
@@
 
-# MSPE by P (N = 100, R = 1, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 100, R == 1, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 1, sparse = 0.5, sigma = tridiag)")
+# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
+data %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
 
@@
 
-**Notable: N = 100, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**
+**Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = "tridiag"**
 
@@
 
-# MSPE table (N = 100, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
-data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
+# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
+data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
+
+```
+
+<br>\vspace{1cm}
+
+#### Low Dimension
+
+```{r, eval = T, echo = F}
+
+# ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
+data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")
 
@@
 
-# MSPE by P (N = 100, R = 5, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 100, R == 5, sparse == 0.5, sigma == "tridiag", model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 500, R = 5, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-**Notable: N = 100, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**
-
-```{r, eval = T, echo = F}
-
-# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
-data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
-
-```
-
-<br>\vspace{1cm}
-
-```{r, eval = T, echo = F}
-
-# MSPE by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P and R (N = 5000, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-```{r, eval = T, echo = F}
-
-# MSPE by P (N = 1000, R = 1, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 1000, R == 1, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 1, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-**Notable: N = 1000, P = 150, R = 1, sparse = 0.5, sigma = "tridiag"**
-
-```{r, eval = T, echo = F}
-
-# MSPE table (N = 500, sparse = 0.5, sigma = "tridiag", P = 100, R = 1)
-data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 1) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
-
-```
-
-<br>\vspace{1cm}
-
-```{r, eval = T, echo = F}
-
-# MSPE by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("MSPE") + ggtitle("MSPE by P (N = 5000, R = 5, sparse = 0.5, sigma = tridiag)")
+# ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
+data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")
 
@@
 
-# MSPE table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 100, R = 5)
+# ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
 data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
@@
 
-## Takeaways
+### Takeaways
 
 1.
-`shrinkBO` (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$.
-I don't think it's surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.
+In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$.
+It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.
 
 2.
-It's interesting to see that in all cases `shrinkBS` (penalty: $\lambda\left\| \Omega\Sigma_{xy}^{*} \right\|_{1}$) performed worse than `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$).
-So the takeaway is that for these two very similar estimators, the estimator with the oracle $\Sigma_{xy}$ cross-covariance matrix performs much worse than using the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$.
-Is this due to an error?
-Could the root cause be because I centered the data?
+In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS.
+The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.
 
-3. `OracleO` ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$) performed awful in all simulations as well... possibly link to the Abundant paper?
+3. When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.
 
 4.
-`shrinkXY` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy} - Y \right\|_{1}$) and `shrinkXYO` (penalty: $\lambda\left\| X\Omega\hat{\Sigma}_{xy}\Omega_{y | x}^{1/2} - Y\Omega_{y | x}^{1/2} \right\|_{1}$) did not perform well relative to the others in the high-dimensional setting.
-In the low-dimensional setting, they performed better but worse than `lasso` and `ridge`.
-But what is an appropriate data generating model for these estimators?
-A model that can perfectly fit the observed values?
-And would MSPE be the most appropriate criteria for these estimators?
+It is interesting that `oracleO` performed worse than `oracleS` in the final table.
+It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
 
@@
 
-## Questions
+## Shrinking Covariance
 
-1. Is MSPE the best criteria? Or would model error be a better metric?
+We compare the performance of the `shrinkB` and `shrinkBO` estimators when manually shrinking the sample covariance matrix of $X$ and $Y$ (denoted $\Sigma_{xy}$).
+Each data scenario was replicated a total of 20 times.
+
+<br>\vspace{1cm}
+
+### Models
+
+In the following estimators, let the superscript * denote the oracle estimator:
+
+ - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)
+
+ - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)
+
+For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$.
+We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.
+
+<br>\vspace{1cm}
+
+### Data Generation
+
+Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that
+
+\[ \mathbb{Y} = \mathbb{X}\beta + \mathbb{E} \]
+
+These values are generated in the following way:
+
+Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1.
+In effect, each $\beta$ entry is turned off with equal probability.
+
+Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
+This ensures that the inverses will be tridiagonal (sparse).
+
+Then for $n$ independent, identically distributed samples:
+
+\[ X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right) \]
+
+\[ E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right) \]
+
+If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.
+
+An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$).
+For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).
+
+Possible parameters in simulation:
+
+ - `reps` = 20
+ - `n` = (100, 1000)
+ - `p` = (10, 50, 100, 150, 200)
+ - `r` = c(1, 5, 10)
+ - `sparse` = c(0.5)
+ - `sigma` = c("tridiag", "compound")
+
+Note that prior to estimation, the intercept is removed by centering the data.
+
+<br>\vspace{1cm}
+
+### Plots
+
+```{r, eval = T, echo = F}
+
+# load data
+load("images/sigma.Rdata")
+
+# design color palette
+bluetowhite <- c("#000E29", "white")
+
+# change to numeric
+data$lam %<>% as.character %>% as.numeric
+data$const %<>% as.character %>% as.numeric
+
+```
+
+#### High Dimension
+
+##### `shrinkB`
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
+d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
+d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+##### `shrinkBO`
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
+d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
+d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+#### Low Dimension
+
+##### `shrinkB`
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
+d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
+d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+#### `shrinkBO`
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
+d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+```{r, eval = T, echo = F}
+
+# shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
+d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+
+<br>\vspace{1cm}
+
+### Takeaways
+
+1.
+In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE.
+This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.
+
+2. In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.
+
+3. The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.
+
+4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)

### 2018-08-03 index.Rmd
updated material with new vignettes

@@
 site: bookdown::bookdown_site
-output: bookdown::gitbook
+output:
+  bookdown::pdf_book:
+    toc_depth: 2
+  bookdown::gitbook:
+    fig_caption: false
 documentclass: book
-#bibliography: [lib.bib, packages.bib]
-bibliography: lib.bib
+bibliography: [lib.bib, packages.bib]
+#bibliography: lib.bib
 biblio-style: apalike
@@
 
-# ```{r include=FALSE}
-# # automatically create a bib database for R packages
-# knitr::write_bib(c(
-#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
-# ), 'packages.bib')
-# ```
+```
+
+```{r include=FALSE}
+# automatically create a bib database for R packages
+knitr::write_bib(c(.packages(), "glasso", "ADMMsigma"), 'packages.bib')
 

### 2018-08-06 02-ADMM-Details.Rmd
updated format of document

@@
 
-\begin{align*}
-  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
+\begin{align}
+  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \notag \\
   &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
-\end{align*}
+\end{align}
 
@@
 
-\[ l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \]
+\begin{equation}
+  l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
+(\#eq:loglik)
+\end{equation}
 
@@
 so that $\hat{\Omega}_{MLE} = S^{-1}$.
-Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$.
-
-Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate.
+Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$ ^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
+Both procedures will result in the same estimate.].
 

### 2018-08-06 08-SCPME-Simulations.Rmd
updated format of document

@@
 # set P to numeric 
-data$P %<>% as.character %>% as.numeric
+sim6$P %<>% as.character %>% as.numeric
 
 # ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")
 
@@
 
-```{r, eval = T, echo = F}
+```{r, eval = T, echo = F, fig.cap = "Figure caption here."}
 
 # ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
 
@@
 # ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
-data %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
+sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")
 
@@
 # ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")
 
@@
 # ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
-data %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")
 
@@
 # ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
-data %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean)
+sim6 %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")
 
@@
 # change to numeric
-data$lam %<>% as.character %>% as.numeric
-data$const %<>% as.character %>% as.numeric
+sigma$lam %<>% as.character %>% as.numeric
+sigma$const %<>% as.character %>% as.numeric
 
@@
 # shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
-d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
-d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
-d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
-d = data %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
-d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
-d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
-d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 
@@
 # shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
-d = data %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
 

### 2018-08-06 index.Rmd
updated format of document

@@
 --- 
-title: "Oral Manuscript"
+title: "Precision Matrix Estimation"
 author: "Matt Galloway"
@@
     toc_depth: 2
+    includes:
+      in_header: preamble.tex
   bookdown::gitbook:
-    fig_caption: false
-documentclass: book
+    toc_depth: 2
+documentclass: report
 bibliography: [lib.bib, packages.bib]
@@
 biblio-style: apalike
+#geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
+geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
 colorlinks: yes
@@
 lof: no
+toc_appendix: yes
 fontsize: 11pt
+linestretch: 1.5
 link-citations: yes
@@
 ```
-
-# Prerequisites

### 2018-08-06 preamble.tex
updated format of document

--- 2018-06-07 Manuscript.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
-%
-\documentclass[12pt,]{book}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{xcolor}
-\usepackage{hyperref}
-\hypersetup{
-            pdftitle={Oral Manuscript},
-            pdfauthor={Matt Galloway},
-            colorlinks=true,
-            linkcolor=Maroon,
-            citecolor=Blue,
-            urlcolor=Blue,
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
 \usepackage{booktabs}
 \usepackage{amsthm}
+\usepackage{fancyhdr} % Required for custom headers
+\usepackage{lastpage} % Required to determine the last page for the footer
+\usepackage{extramarks} % Required for headers and footers
 \makeatletter
@@
 \makeatother
-\usepackage[]{natbib}
-\bibliographystyle{apalike}
-
-\title{Oral Manuscript}
-\author{Matt Galloway}
-\date{2018-06-07}
-
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
-\newtheorem{proposition}{Proposition}[chapter]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[chapter]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[chapter]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
-\begin{document}
-\maketitle
-
-{
-\hypersetup{linkcolor=}
-\setcounter{tocdepth}{2}
-\tableofcontents
-}
-\hypertarget{prerequisites}{%
-\chapter{Prerequisites}\label{prerequisites}}
-
-\hypertarget{intro}{%
-\chapter{Introduction}\label{intro}}
-
-This is the introduction for Matt's oral manuscript. (UPDATED 8)
-
-\hypertarget{tutorial}{%
-\chapter{Tutorial}\label{tutorial}}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# The easiest way to install is from CRAN}
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"ADMMsigma"}\NormalTok{)}
-
-\CommentTok{# You can also install the development version from GitHub:}
-\CommentTok{# install.packages('devtools')}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/ADMMsigma"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\vspace{0.5cm}
-
-If there are any issues/bugs, please let me know:
-\href{https://github.com/MGallow/ADMMsigma/issues}{github}. You can also
-contact me via my \href{https://mgallow.github.io/}{website}. Pull
-requests are welcome!
-
-\vspace{0.5cm}
-
-A (possibly incomplete) list of functions contained in the package can
-be found below:
-
-\begin{itemize}
-\item
-  \texttt{ADMMsigma()} computes the estimated precision matrix (ridge,
-  lasso, and elastic-net type regularization optional)
-\item
-  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision
-  matrix via closed-form solution
-\item
-  \texttt{plot.ADMMsigma()} produces a heat map or line graph for cross
-  validation errors
-\item
-  \texttt{plot.RIDGEsigma()} produces a heat map or line graph for cross
-  validation errors
-\end{itemize}
-
-\vspace{1cm}
-
-\hypertarget{usage}{%
-\section{Usage}\label{usage}}
-
-We will first generate data from a sparse, tri-diagonal precision matrix
-and denote it as Omega.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-
-\CommentTok{# generate data from a sparse matrix first compute covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{5}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\NormalTok{S[i, j]}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# print oracle precision matrix (shrinkage might be useful)}
-\NormalTok{(}\DataTypeTok{Omega =} \KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(S), }\DecValTok{3}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##        [,1]   [,2]   [,3]   [,4]   [,5]
-## [1,]  1.961 -1.373  0.000  0.000  0.000
-## [2,] -1.373  2.922 -1.373  0.000  0.000
-## [3,]  0.000 -1.373  2.922 -1.373  0.000
-## [4,]  0.000  0.000 -1.373  2.922 -1.373
-## [5,]  0.000  0.000  0.000 -1.373  1.961
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{5}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# snap shot of data}
-\KeywordTok{head}\NormalTok{(X)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##            [,1]         [,2]         [,3]       [,4]        [,5]
-## [1,] -0.4311177 -0.217744186  1.276826576 -0.1061308 -0.02363953
-## [2,] -0.0418538  0.304253474  0.688201742 -0.5976510 -1.06758924
-## [3,]  1.1344174  0.004493877 -0.440059159 -0.9793198 -0.86953222
-## [4,] -0.0738241 -0.286438212  0.009577281 -0.7850619 -0.32351261
-## [5,] -0.2905499 -0.906939891 -0.656034183 -0.4324413  0.28516534
-## [6,]  1.3761967  0.276942730 -0.297518545 -0.2634814 -1.35944340
-\end{verbatim}
-
-\vspace{0.5cm}
-
-As described earlier in the report, the maximum likelihood estimator
-(MLE) for Omega is the inverse of the sample precision matrix
-\(S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}\):
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# print inverse of sample precision matrix (perhaps a bad estimate)}
-\KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(}\KeywordTok{cov}\NormalTok{(X) }\OperatorTok{*}\StringTok{ }\NormalTok{(}\KeywordTok{nrow}\NormalTok{(X) }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)}\OperatorTok{/}\KeywordTok{nrow}\NormalTok{(X)), }\DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.32976 -1.55033  0.22105 -0.08607  0.24309
-## [2,] -1.55033  3.27561 -1.68026 -0.14277  0.18949
-## [3,]  0.22105 -1.68026  3.19897 -1.25158 -0.11016
-## [4,] -0.08607 -0.14277 -1.25158  2.76790 -1.37226
-## [5,]  0.24309  0.18949 -0.11016 -1.37226  2.05377
-\end{verbatim}
-
-\vspace{0.5cm}
-
-However, because Omega (known as the \emph{oracle}) is sparse, a
-shrinkage estimator will perhaps perform better than the sample
-estimator. Below we construct various penalized estimators:
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net type penalty (set tolerance to 1e-8)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, tol.abs = 1e-08, tol.rel = 1e-08)
-## 
-## Iterations: 162
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41003
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15283 -1.26902  0.00000  0.00000  0.19765
-## [2,] -1.26902  2.79032 -1.32206 -0.08056  0.00925
-## [3,]  0.00000 -1.32206  2.85470 -1.17072 -0.00865
-## [4,]  0.00000 -0.08056 -1.17072  2.49554 -1.18959
-## [5,]  0.19765  0.00925 -0.00865 -1.18959  1.88121
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{LASSO:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# lasso penalty (default tolerance)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 1)
-## 
-## Iterations: 66
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41022
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15228 -1.26841  0.00000  0.00000  0.19744
-## [2,] -1.26841  2.78830 -1.31943 -0.08246  0.01018
-## [3,]  0.00000 -1.31943  2.84979 -1.16708 -0.01015
-## [4,]  0.00000 -0.08246 -1.16708  2.49277 -1.18844
-## [5,]  0.19744  0.01018 -0.01015 -1.18844  1.88069
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{ELASTIC-NET:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net penalty (alpha = 0.5)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0.5)
-## 
-## Iterations: 67
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821    0.5
-## 
-## Log-likelihood: -101.13595
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.20031 -1.32471  0.01656 -0.00334  0.21798
-## [2,] -1.32471  2.90659 -1.37599 -0.19084  0.13651
-## [3,]  0.01656 -1.37599  2.92489 -1.12859 -0.12033
-## [4,] -0.00334 -0.19084 -1.12859  2.56559 -1.23472
-## [5,]  0.21798  0.13651 -0.12033 -1.23472  1.94528
-\end{verbatim}
-
-\newpage
-
-\textbf{RIDGE:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{0}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0)
-## 
-## Iterations: 65
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821      0
-## 
-## Log-likelihood: -99.19746
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.18979 -1.31533  0.04515 -0.04090  0.23511
-## [2,] -1.31533  2.90019 -1.37049 -0.22633  0.17808
-## [3,]  0.04515 -1.37049  2.89435 -1.07647 -0.17369
-## [4,] -0.04090 -0.22633 -1.07647  2.55026 -1.22786
-## [5,]  0.23511  0.17808 -0.17369 -1.22786  1.95495
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty no ADMM}
-\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: RIDGEsigma(X = X, lam = 10^seq(-8, 8, 0.01))
-## 
-## Tuning parameter:
-##       log10(lam)    lam
-## [1,]       -2.17  0.007
-## 
-## Log-likelihood: -109.18156
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15416 -1.31185  0.08499 -0.05571  0.22862
-## [2,] -1.31185  2.85605 -1.36677 -0.19650  0.16880
-## [3,]  0.08499 -1.36677  2.82606 -1.06325 -0.14946
-## [4,] -0.05571 -0.19650 -1.06325  2.50721 -1.21935
-## [5,]  0.22862  0.16880 -0.14946 -1.21935  1.92871
-\end{verbatim}
-
-\newpage
-
-This package also has the capability to provide heat maps for the cross
-validation errors. The more bright (white) areas of the heat map pertain
-to more optimal tuning parameters.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for ADMMsigma}
-\NormalTok{ADMM =}\StringTok{ }\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for ADMMsigma}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for RIDGEsigma}
-\NormalTok{RIDGE =}\StringTok{ }\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for RIDGEsigma}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-
-\hypertarget{details}{%
-\chapter{Details}\label{details}}
-
-Suppose we want to solve the following optimization problem:
-
-\begin{align*}
-  \mbox{minimize } f(x) + g(z) \\
-  \mbox{subject to } Ax + Bz = c
-\end{align*}
-
-where
-\(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\),
-and \(c \in \mathbb{R}^{p}\). Following \citet{boyd2011distributed}, the
-optimization problem will be introduced in vector form though we will
-later consider cases where \(x\) and \(z\) are matrices. We will also
-assume \(f\) and \(g\) are convex functions. Optimization problems like
-this arise naturally in several statistics and machine learning
-applications -- particularly regularization methods. For instance, we
-could take \(f\) to be the squared error loss, \(g\) to be the
-\(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be
-identity matrices to solve the ridge regression optimization problem.
-
-The \emph{augmented lagrangian} is constructed as follows:
-
-\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]
-
-where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and
-\(\rho > 0\) is a scalar. Clearly any minimizer, \(p^{*}\), under the
-augmented lagrangian is equivalent to that of the lagrangian since any
-feasible point \((x, z)\) satisfies the constraint
-\(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
-
-\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]
-
-The alternating direction method of multipliers (ADMM) algorithm
-consists of the following repeated iterations:
-
-\begin{align}
-  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
-\end{align}
-
-A more complete introduction to the algorithm -- specifically how it
-arose out of \emph{dual ascent} and \emph{method of multipliers} -- can
-be found in \citet{boyd2011distributed}.
-
-\vspace{1cm}
-
-\hypertarget{admm-algorithm}{%
-\section{ADMM Algorithm}\label{admm-algorithm}}
-
-Now consider the case where \(X_{1}, ..., X_{n}\) are iid
-\(N_{p}(\mu, \Sigma)\) random variables and we are tasked with
-estimating the precision matrix, denoted \(\Omega \equiv \Sigma^{-1}\).
-The maximum likelihood estimator for \(\Omega\) is
-
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]
-
-where \(S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n\)
-and \(\bar{X}\) is the sample mean. By setting the gradient equal to
-zero, we can show that when the solution exists,
-\(\hat{\Omega}_{MLE} = S^{-1}\).
-
-As in regression settings, we can construct a \emph{penalized}
-likelihood estimator by adding a penalty term,
-\(P\left( \Omega \right)\), to the likelihood:
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]
-
-\(P\left( \Omega \right)\) is often of the form
-\(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}\) or
-\(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\),
-\(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define
-\(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\). These
-penalties are the ridge and lasso, respectively. We will, instead, take
-\(P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]\)
-so that the full penalized likelihood is
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]
-
-where \(0 \leq \alpha \leq 1\). This \emph{elastic-net} penalty was
-explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and
-is identical to the penalty used in the popular penalized regression
-package \texttt{glmnet}. Clearly, when \(\alpha = 0\) the elastic-net
-reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a
-lasso-type penalty.
-
-By letting \(f\) be equal to the non-penalized likelihood and \(g\)
-equal to \(P\left( \Omega \right)\), our goal is to minimize the full
-augmented lagrangian where the constraint is that \(\Omega - Z\) is
-equal to zero:
-
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]
-
-The ADMM algorithm for estimating the penalized precision matrix in this
-problem is
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align}
-
-\vspace{1cm}
-
-\hypertarget{scaled-form-admm}{%
-\section{Scaled-Form ADMM}\label{scaled-form-admm}}
-
-An alternate form of the ADMM algorithm can constructed by scaling the
-dual variable (\(\Lambda^{k}\)). Let us define
-\(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).
-
-\begin{align*}
-  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-\end{align*}
-
-Therefore, the condensed-form ADMM algorithm can now be written as
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
-\end{align}
-
-And more generally (in vector form),
-
-\begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
-\end{align}
-
-Note that there are limitations to using this method. Because the dual
-variable is scaled by \(\rho\) (the step size), this form limits one to
-using a constant step size without making further adjustments to
-\(U^{k}\). It has been shown in the literature that a dynamic step size
-can significantly reduce the number of iterations required for
-convergence.
-
-\vspace{1cm}
-
-\hypertarget{algorithm}{%
-\section{Algorithm}\label{algorithm}}
-
-\begin{align*}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align*}
-
-\vspace{1cm}
-
-Initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Iterate the following
-three steps until convergence:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) via spectral
-  decomposition.
-\end{enumerate}
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Elementwise soft-thresholding for all \(i = 1,..., p\) and
-  \(j = 1,..., p\).
-\end{enumerate}
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Update \(\Lambda^{k + 1}\).
-\end{enumerate}
-
-\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-1}{%
-\subsection{Proof of (1):}\label{proof-of-1}}
-
-\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
-\end{align*}
-
-Set the gradient equal to zero and decompose \(\Omega = VDV^{T}\) where
-\(D\) is a diagonal matrix with diagonal elements equal to the eigen
-values of \(\Omega\) and \(V\) is the matrix with corresponding eigen
-vectors as columns.
-
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
-
-This equivalence implies that
-
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
-
-where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
-
-\begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
-\end{align*}
-
-In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\)
-then
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-2}{%
-\subsection{Proof of (2)}\label{proof-of-2}}
-
-\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
-\end{align*}
-
-where \(Sign(Z)\) is the elementwise Sign operator. By setting the
-gradient/sub-differential equal to zero, we arrive at the following
-equivalence:
-
-\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]
-
-for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} > 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} < 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]
-
-This implies that
-\(Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\).
-Putting all the pieces together, we arrive at
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-where \(Soft\) is the soft-thresholding function.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{simulations}{%
-\chapter{Simulations}\label{simulations}}
-
-In the simulations below we generated data from a number of oracle
-precision matrices with various structures. For each data-generating
-procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross
-validation. After 20 replications, the cross validation errors were
-totalled and the optimal tuning parameters were selected (results in the
-top figure). These results are compared with the Kullback Leibler (KL)
-losses between the estimates and the oracle precision matrix (bottom
-figure). We can see below that our cross validation procedure choosing
-tuning parameters close to the optimal parameters.
-
-\newpage
-
-\hypertarget{compound-symmetric-p-100-n-50}{%
-\subsection{Compound Symmetric: P = 100, N =
-50}\label{compound-symmetric-p-100-n-50}}
-
-\includegraphics{images/compound_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
-
-\hypertarget{compound-symmetric-p-10-n-1000}{%
-\subsection{Compound Symmetric: P = 10, N =
-1000}\label{compound-symmetric-p-10-n-1000}}
-
-\includegraphics{images/compound_N1000_P10.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{1000}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
-
-\hypertarget{dense-p-100-n-50}{%
-\subsection{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
-
-\includegraphics{images/repsKLdenseQR_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{100} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
-
-\hypertarget{dense-p-10-n-50}{%
-\subsection{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
-
-\includegraphics{images/repsKLdense_N50_P10.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{10}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
-
-\hypertarget{tridiagonal-p-100-n-50}{%
-\subsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
-
-\includegraphics{images/repsKLtridiag_N50_P100.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-\NormalTok{    S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{  \}}
-\NormalTok{\}}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\hypertarget{benchmark}{%
-\chapter{Benchmark}\label{benchmark}}
-
-Below we benchmark the various functions contained in
-\texttt{ADMMsigma}. We can see that \texttt{ADMMsigma} (at the default
-tolerance) offers comparable computation time to the popular
-\texttt{glasso} R package.
-
-\hypertarget{computer-specs}{%
-\subsection{Computer Specs:}\label{computer-specs}}
-
-\begin{itemize}
-\tightlist
-\item
-  MacBook Pro (Late 2016)
-\item
-  Processor: 2.9 GHz Intel Core i5
-\item
-  Memory: 8GB 2133 MHz
-\item
-  Graphics: Intel Iris Graphics 550
-\end{itemize}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-\KeywordTok{library}\NormalTok{(microbenchmark)}
-
-\CommentTok{# generate data from tri-diagonal (sparse) matrix compute covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\NormalTok{(}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j))}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{1000} \OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# glasso (for comparison)}
-\KeywordTok{microbenchmark}\NormalTok{(glasso}\OperatorTok{::}\KeywordTok{glasso}\NormalTok{(}\DataTypeTok{s =}\NormalTok{ S, }\DataTypeTok{rho =} \FloatTok{0.1}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                              expr      min       lq     mean   median
-##  glasso::glasso(s = S, rho = 0.1) 49.46673 53.37757 58.35196 55.90935
-##        uq      max neval
-##  60.77517 92.68082   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - default tolerance}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-04}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-04, tol.rel = 1e-04,      trace = "none")
-##      min       lq     mean   median       uq      max neval
-##  77.2134 83.51351 89.71565 85.37738 94.37814 126.0049   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - tolerance 1e-8}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-08, tol.rel = 1e-08,      trace = "none")
-##       min       lq     mean   median       uq      max neval
-##  258.5389 261.5402 272.3741 267.8829 274.7276 353.4726   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - default parameter grid}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                          expr      min       lq     mean   median       uq
-##  ADMMsigma(X, trace = "none") 8.338241 8.341611 8.536446 8.472933 8.515822
-##       max neval
-##  9.013621     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma parallel CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{cores =} \DecValTok{3}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                     expr      min       lq     mean
-##  ADMMsigma(X, cores = 3, trace = "none") 9.285137 9.315978 9.470666
-##   median       uq      max neval
-##  9.40943 9.426579 9.916207     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - likelihood convergence criteria}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{crit =} \StringTok{"loglik"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                           expr      min       lq     mean
-##  ADMMsigma(X, crit = "loglik", trace = "none") 7.028816 7.121599 7.185927
-##    median       uq      max neval
-##  7.181803 7.277249 7.320166     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark RIDGEsigma CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{), }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                                      expr      min
-##  RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none") 12.22374
-##        lq     mean   median       uq      max neval
-##  12.37326 12.93705 13.01892 13.04356 14.02577     5
-\end{verbatim}
-
-\bibliography{lib.bib}
-
-\end{document}
+\pagestyle{fancy}
+% \pagestyle{empty}

### 2019-01-09 01-intro.Rmd
testing new travis
new travis 2
new travis 3
new travis 4
new travis 5
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:master
new travis 7, turned off keep-history
bug fix, changed allow empty commit
updated material with new vignettes
restructed manuscript

@@
 
-This is the introduction for Matt's oral manuscript.
+In many statistical applications, estimating the covariance for a set of random variables is a critical task.
+The covariance is useful because it characterizes the *relationship* between variables.
+For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form
+
+\[ \Sigma_{xyz} = \begin{pmatrix}
+1 & 0 & 0.5 \\ 
+0 & 1 & 0 \\ 
+0.5 & 0 & 1
+\end{pmatrix} \]
+
+We can gather valuable information from this matrix.
+First of all, we know that each of the variables has an equal variance of 1.
+Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0.
+This implies that any information in $X$ is useless in trying to gather information about $Y$.
+Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.
+
+Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging.
+For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
+
+- Why do we care?
+
+- What is SCPME?
+
+- Guide
+
+- Model and notation

### 2019-01-09 02-PME.Rmd
restructed manuscript

--- 2018-08-06 02-ADMM-Details.Rmd
@@
-# `ADMMsigma` Details
+# Precision Matrix Estimation
+
+## Background
 
@@
 
-\begin{align}
-  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)^{T}\Sigma^{-1}\left( X_{i} - \mu \right) \right] \notag \\
-  &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
-\end{align}
+\begin{equation} 
+\begin{split}
+  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
+  &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Sigma^{-1} \right]
+\end{split}
+(\#eq:lik)
+\end{equation}
 
@@
 \begin{equation}
-  l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right]
+  l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-1} \right]
 (\#eq:loglik)
@@
 
-\begin{align*}
-  &\hat{\Sigma}_{MLE} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
-- \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-1} \right] \right\} \\
-  &\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} + \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)^{T}\Sigma^{-2} \\
-  \Rightarrow &\hat{\Sigma}_{MLE} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T} \right]
-\end{align*}
+\begin{equation}
+\hat{\Sigma}^{mle} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
+- \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-1} \right] \right\}
+(\#eq:sigmaloglik)
+\end{equation}
+
+\begin{equation}
+\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} + \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-2}
+(\#eq:nablasigma)
+\end{equation}
+
+\begin{equation}
+\Rightarrow \hat{\Sigma}^{mle} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]
+(\#eq:sigmamle)
+\end{equation}
 
@@
 
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
+\begin{equation}
+\hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
+(\#eq:omegamle)
+\end{equation}
 
@@
 
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\} \]
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
+(\#eq:omegapen)
+\end{equation}
 
@@
 
-\[ P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \]
+\begin{equation}
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+(\#eq:pen)
+\end{equation}
 
@@
 
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
+(\#eq:omegaloglik)
+\end{equation}
 
@@
 
+The penalty proposed by @molstad2017shrinking is one of the following form:
+
+\begin{equation}
+P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
+(\#eq:pen2)
+\end{equation}
+
+where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
+Solving the full penalized log-likelihood for $\Omega$ results in solving
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+(\#eq:omegaloglik2)
+\end{equation}
+
+This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$.
+This type of penalty leads to many new, interesting, and novel estimators for $\Omega$.
+An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$.
+This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$
+
 We will explore how to solve for $\hat{\Omega}$ in the next section.
 
-<br>\vspace{1cm}
-
-## ADMM Algorithm
+## ADMM algorithm
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
   \mbox{minimize } f(x) + g(z) \\
   \mbox{subject to } Ax + Bz = c
-\end{align*}
+\end{split}
+\end{equation}
 
@@
 
-\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]
+\begin{equation}
+L_{\rho}(x, z, y) = f(x) + g(z) + y'(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2}
+(\#eq:auglagrange)
+\end{equation}
 
@@
 \begin{align}
-  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) (\#eq:xauglagrange) \\
+  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) (\#eq:zauglagrange) \\
+  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c) (\#eq:yauglagrange)
 \end{align}
@@
 
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] \]
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
+(\#eq:lagrange)
+\end{equation}
 
@@
 
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
+(\#eq:auglagrangian)
+\end{equation}
 
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} (\#eq:omegaauglagrange) \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} (\#eq:ZZauglagrange) \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) (\#eq:lamauglagrange)
 \end{align}
-
-<br>\vspace{1cm}
 
@@
 
-1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ via spectral decomposition.
+1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV'$ via spectral decomposition.
 
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V'
+(\#eq:omegaalgo)
+\end{equation}
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
 Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
 &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
+(\#eq:ZZalgo)
+\end{split}
+\end{equation}
 
@@
 
-\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]
+\begin{equation}
+\Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+(\#eq:lamalgo)
+\end{equation}
 
@@
 
-<br>\vspace{1cm}
-
-### Proof of (1):
-
-\[ \Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\vspace{1cm}
-
-\begin{align*}
-  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
-\end{align*}
-
-Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
-First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:
-
-\[ S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
-
-This equivalence implies that
-
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
-
-where $\phi_{j}(\cdot)$ is the $j$th eigen value.
-
-\begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
-\end{align*}
-
-In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
-
-<br>\vspace{1cm}
-
-### Proof of (2)
-
-\[ Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]
-
-\vspace{1cm}
-
-\begin{align*}
-  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
-\end{align*}
-
-where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
-
-\[ Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right) \]
-
-for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:
-
-- If $Z_{ij}^{k + 1} > 0$ then
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]
-
-- If $Z_{ij}^{k + 1} < 0$ then
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]
-
-This implies that $\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-where soft is the soft-thresholding function.
-
-<br>\vspace{1cm}
-
-## Scaled-Form ADMM
+### Scaled-Form ADMM
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
   tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
@@
   &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-\end{align*}
+(\#eq:scaled)
+\end{split}
+\end{equation}
 
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} (\#eq:omegascaled) \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} (\#eq:ZZscaled) \\
+  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} (\#eq:Uscaled)
 \end{align}
@@
 \begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
+  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:xscaled) \\
+  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:zscaled) \\
+  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c (\#eq:uscaled)
 \end{align}
@@
 
-<br>\vspace{1cm}
-
-## Stopping Criterion
+### Stopping Criterion
 
@@
 
-\[ \Omega^{k + 1} - Z^{k + 1} = 0 \]
+\begin{equation}
+\Omega^{k + 1} - Z^{k + 1} = 0
+(\#eq:admmprimal)
+\end{equation}
 
@@
 
-\[ 0 \in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \]
-
-\[ 0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \]
+\begin{equation}
+\begin{split}
+  0 &\in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \\
+  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
+(\#eq:admmdual)
+\end{split}
+\end{equation}
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
   0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
@@
   \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
-\end{align*}
+(\#eq:dualresidual)
+\end{split}
+\end{equation}
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
   0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
@@
   &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
-\end{align*}
+(\#eq:dualopt)
+\end{split}
+\end{equation}
 
@@
 
-\begin{align*}
+\begin{equation}
+\begin{split}
   \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
-\end{align*}
+(\#eq:admmstopping)
+\end{split}
+\end{equation}
+
+## Simulations
+
+In the simulations below, we generate data from a number of different oracle precision matrices with various structures.
+For each data-generating procedure, the `ADMMsigma()` function was run using 5-fold cross validation.
+After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results below the top figure).
+These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure).
+
+We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.
+
+### Plots
+
+#### Compound Symmetric: P = 100, N = 50
+
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# oracle precision matrix
+Omega = matrix(0.9, ncol = 100, nrow = 100)
+diag(Omega = 1)
+
+# generate covariance matrix
+S = qr.solve(Omega)
+
+# generate data
+Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
+out = eigen(S, symmetric = TRUE)
+S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
+X = Z %*% S.sqrt
+
+```
+<br>\vspace{0.5cm}
+
+<!-- <center> -->
+<!-- ![Figure caption here.](images/compound_N50_P100.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+
+```{r admmsim1, eval = T, echo = F, fig.cap = "Figure caption here."}
+
+knitr::include_graphics("images/compound_N50_P100.png")
+
+```
+
+#### Compound Symmetric: P = 10, N = 1000
+
+```{r, message = FALSE, echo = TRUE, eval = FALSE}
+
+# oracle precision matrix
+Omega = matrix(0.9, ncol = 10, nrow = 10)
+diag(Omega = 1)
+
+# generate covariance matrix
+S = qr.solve(Omega)
+
+# generate data
+Z = matrix(rnorm(10*1000), nrow = 1000, ncol = 10)
+out = eigen(S, symmetric = TRUE)
+S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
+X = Z %*% S.sqrt
+
+```
+<br>\vspace{0.5cm}
+
+<!-- <center> -->
+<!-- ![Figure caption here.](images/compound_N1000_P10.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+
+```{r admmsim2, eval = T, echo = F, fig.cap = "Figure caption here."}
+
+knitr::include_graphics("images/compound_N1000_P10.png")
+
+```
+
+#### Dense: P = 100, N = 50
+
+```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
+
+# generate eigen values
+eigen = c(rep(1000, 5, rep(1, 100 - 5)))
+
+# randomly generate orthogonal basis (via QR)
+Q = matrix(rnorm(100*100), nrow = 100, ncol = 100) %>% qr %>% qr.Q
+
+# generate covariance matrix
+S = Q %*% diag(eigen) %*% t(Q)
+
+# generate data
+Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
+out = eigen(S, symmetric = TRUE)
+S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
+X = Z %*% S.sqrt
+
+```
+<br>\vspace{0.5cm}
+
+<!-- <center> -->
+<!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+<!-- } -->
+
+```{r admmsim3, eval = T, echo = F, fig.cap = "Figure caption here."}
+
+knitr::include_graphics("images/repsKLdenseQR_N50_P100.png")
+
+```
+
+#### Dense: P = 10, N = 50
+
+```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
+
+# generate eigen values
+eigen = c(rep(1000, 5, rep(1, 10 - 5)))
+
+# randomly generate orthogonal basis (via QR)
+Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q
+
+# generate covariance matrix
+S = Q %*% diag(eigen) %*% t(Q)
+
+# generate data
+Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
+out = eigen(S, symmetric = TRUE)
+S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
+X = Z %*% S.sqrt
+
+```
+<br>\vspace{0.5cm}
+
+<!-- <center> -->
+<!-- ![Figure caption here.](images/repsKLdense_N50_P10.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+
+```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."}
+
+knitr::include_graphics("images/repsKLdense_N50_P10.png")
+
+```
+
+#### Tridiagonal: P = 100, N = 50
+
+```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
+
+# generate covariance matrix
+# (can confirm inverse is tri-diagonal)
+S = matrix(0, nrow = 100, ncol = 100)
+for (i in 1:100){
+  for (j in 1:100){
+    S[i, j] = 0.7^abs(i - j)
+  }
+}
+
+# generate data
+Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
+out = eigen(S, symmetric = TRUE)
+S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
+X = Z %*% S.sqrt
+
+```
+<br>\vspace{0.5cm}
+
+<!-- <center> -->
+<!-- ![Figure caption here.](images/repsKLtridiag_N50_P100.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+
+```{r admmsim5, eval = T, echo = F, fig.cap = "Figure caption here."}
+
+knitr::include_graphics("images/repsKLtridiag_N50_P100.png")
+
+```

### 2019-01-09 03-SCPME.Rmd
restructed manuscript

# SCPME

The penalty proposed by @molstad2017shrinking is one of the following form:

\begin{equation}
P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
(\#eq:pen2)
\end{equation}

where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user. Solving the full penalized log-likelihood for $\Omega$ results in solving

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
(\#eq:omegaloglik2)
\end{equation}

This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$. This type of penalty leads to many new, interesting, and novel estimators for $\Omega$. An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$. This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$. Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$

We will explore how to solve for $\hat{\Omega}$ in the next section.

## Augmented ADMM Algorithm

*This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm. I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.*

The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications. Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) (\#eq:omegaauglagrange2) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) (\#eq:ZZauglagrange2) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamauglagrange2)
\end{align}

where $L_{p}(\cdot)$ is the *augmented lagrangian* defined as

\begin{equation}
L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
(\#eq:auglagrange2)
\end{equation}

with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$. However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.

The approximating function is defined as

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
(\#eq:approx)
\end{split}
\end{equation}

where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$, $\otimes$ is the Kronecker product, and $\tau$ is chosen such that $Q$ is positive definite. Note that if $Q$ is positive definite (p.d.), then

\begin{equation}
\frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0
(\#eq:pd)
\end{equation}

since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$. Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function.

To see why this particular function was used, consider the Taylor's expansion of $\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2$:

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
(\#eq:taylors)
\end{split}
\end{equation}

**Note:**

\begin{equation}
  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
(\#eq:gradient)
\end{equation}

\begin{equation}
\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
(\#eq:hessian)
\end{equation}

This implies that

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
(\#eq:penapprox)
\end{split}
\end{equation}

Let us now plug in this equality into our optimization problem in step one:

\begin{equation}
\begin{split}
  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
 tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
(\#eq:omegaapprox)
\end{split}
\end{equation}

where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.

The *augmented ADMM* algorithm is the following:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} (\#eq:omegaaugadmm) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} (\#eq:ZZaugadmm) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamaugadmm)
\end{align}

### Algorithm

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)$

5. Set $Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.

### Stopping Criterion

In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to the SCPME method.

Below we have three optimality conditions:

1. Primal:

\begin{equation}
A\Omega^{k + 1}B - Z^{k + 1} - C = 0
(\#eq:scpmeprimal)
\end{equation}

2. Dual:

\begin{equation}
\begin{split}
  0 &\in \partial f\left(\Omega^{k + 1}\right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) \\
  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
(\#eq:scpmedual)
\end{split}
\end{equation}

The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).

We will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$. At convergence, the optimality conditions require that $r^{k + 1} \approx 0$. The second residual we will define is the dual residual:

\[ s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \]

This residual is derived from the fact. Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
(\#eq:stopproof)
\end{split}
\end{equation}

Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied:

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:dualopt2)
\end{split}
\end{equation}

One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
(\#eq:scpmestopping)
\end{split}
\end{equation}

## Illustration via Regression

## Simulations

We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.

### Models

In the following estimators, let the superscript * denote the oracle estimator:

 - `OLS` = ordinary least squares estimator in *low* dimensional setting and Moore-Penrose estimator in a *high* ($p >> n$) dimensional setting

 - `ridge` = ridge regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `lasso` = lasso regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `oracleB` = oracle estimator with the true $\beta^{*}$ known ($\left\| Y - X\beta^{*} \right\|_{F}^{2}$)

 - `oracleO` = oracle estimator with the true $\Omega^{*}$ known ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$)

 - `oracleS` = oracle estimator with the true $\Sigma_{xy}^{*}$ known and sample estimator for $\Omega$ ($\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}$)

 - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)

 - `shrinkBS` = shrinking characteristics regression estimator with oracle cross-covariance where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$)

 - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)

 - `glasso` = lasso penalized precision matrix where optimal tuning parameter is chosen to maximize log-likelihood via 3-fold CV.

### Data Generation

Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that

\begin{equation}
\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
(\#eq:datalinregression)
\end{equation}

These values are generated in the following way:

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1. In effect, each $\beta$ entry is turned off with equal probability.

Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse).

Then for $n$ independent, identically distributed samples:

\begin{equation}
X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)
(\#eq:xnormal)
\end{equation}

\begin{equation}
E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)
(\#eq:enormal)
\end{equation}

If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.

An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$). For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).

Possible parameters in simulation:

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag")

Note that prior to estimation, the intercept is removed by centering the data.

### Plots

#### High Dimension

Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE). Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.

```{r scpmesim1, eval = T, echo = F, fig.cap = "Figure caption here."}

# load data
load("images/sim6.Rdata")

# set P to numeric 
sim6$P %<>% as.character %>% as.numeric

# ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r scpmesim2, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = "tridiag"**

```{r scpmesim3, eval = T, echo = F}

# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")

```

<br>\vspace{1cm}

#### Low Dimension

```{r scpmesim4, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r scpmesim5, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 1000, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**

```{r scpmesim6, eval = T, echo = F}

# ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
sim6 %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")

```

### Takeaways

1. In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$. It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.

2. In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS. The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.

3. When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.

4. It is interesting that `oracleO` performed worse than `oracleS` in the final table. It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.

### Shrinking Covariance Models

In the following estimators, let the superscript * denote the oracle estimator:

 - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)

 - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)

For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$. We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.

### Data Generation

Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that

\begin{equation}
\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
(\#eq:datalinregression2)
\end{equation}

These values are generated in the following way:

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1. In effect, each $\beta$ entry is turned off with equal probability.

Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse).

Then for $n$ independent, identically distributed samples:

\begin{equation}
X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)
(\#eq:xnormal2)
\end{equation}

\begin{equation}
E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)
(\#eq:enormal2)
\end{equation}

If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.

An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$). For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).

Possible parameters in simulation:

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150, 200)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag", "compound")

Note that prior to estimation, the intercept is removed by centering the data.

### Plots

```{r, eval = T, echo = F}

# load data
load("images/sigma.Rdata")

# design color palette
bluetowhite <- c("#000E29", "white")

# change to numeric
sigma$lam %<>% as.character %>% as.numeric
sigma$const %<>% as.character %>% as.numeric

```

#### High Dimension

##### `shrinkB`

<br>\vspace{1cm}

```{r scpmesim7, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim8, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

##### `shrinkBO`

<br>\vspace{1cm}

```{r scpmesim9, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim10, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

#### Low Dimension

##### `shrinkB`

<br>\vspace{1cm}

```{r scpmesim11, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim12, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

#### `shrinkBO`

<br>\vspace{1cm}

```{r scpmesim13, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim14, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

### Takeaways

1. In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE. This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.

2. In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.

3. The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.

4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)

## Discussion

The general optimization problem outlined in @molstad2017shrinking is to estimate $\hat{\Omega}$ such that

\begin{equation}
  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
(\#eq:penloglik3)
\end{equation}

where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm. In addition, $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user. This objective function is a penalized log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$.

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\}
(\#eq:penloglik3)
\end{equation}

where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$. Under this particular likelihood, it is assumed that each observation of $X_{i}$ in a sample size of size $n$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.

This particular formulation for the penalty leads to many new, interesting, and novel estimators for $\Omega$. For instance, if in addition to $X$ we also observe $n$ copies of the random variable $Y$, we might set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$. In which case

\begin{equation}
P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1}
(\#eq:pen3)
\end{equation}

This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.

\begin{equation}
P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
(\#eq:pen4)
\end{equation}

In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$. Furthermore, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that

\begin{equation}
\begin{split}
\hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\}
(\#eq:penloglik4)
\end{split}
\end{equation}

This estimator encourages the predicted values $\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}$ to be exactly equal to the observed responses $\mathbb{Y}$. We will name this estimator the *lasso SCPME estimator*. Note that in practice - for any of these estimators - we do not know the true covariance matrix $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ in its place.

All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper. The augmented ADMM algorithm (details [here](https://mgallow.github.io/SCPME/articles/Details.html#augmented-admm-algorithm)) is the following:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)$

5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

### Connection to joint log-likelihood

The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:penregression)
\end{equation}

To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression)
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$. These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form

\begin{equation}
Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
(\#eq:linnormal)
\end{equation}

We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$. Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience. We will also let $f$ denote the probability distribution function for each respective variable.

\begin{equation}
\begin{split}
  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
(\#eq:jointlik)
\end{split}
\end{equation}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:

\begin{equation}
\begin{split}
  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const. + \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
(\#eq:jointloglik)
\end{split}
\end{equation}

**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.

\begin{equation}
\begin{split}
 \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
 &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
 \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
 (\#eq:gradient2)
\end{split}
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
 &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
 &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
 &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
 \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow \hat{\mu}_{x} &= \bar{X}
(\#eq:gradient3)
\end{split}
\end{equation}

Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.

Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$. This can be achieved by simply centering the data by the sample averages. Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
(\#eq:partialjointloglik)
\end{split}
\end{equation}

where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:

\begin{equation}
\begin{split}
  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
(\#eq:omegajointloglik)
\end{split}
\end{equation}

where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm. Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$. Therefore, we have that

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:omegajointmle)
\end{equation}

Notice that this is exactly the ridge SCPME estimator!

### Takeaways

We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:

1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression2)
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.

2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.

3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.

In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$

5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

Note that the only difference is in step 4.

There are a few takeaways we can make after revealing this connection. The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$. The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator. No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it. We show this below:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
(\#eq:penregression2)
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
  (\#eq:penregressionproof)
\end{split}
\end{equation}

by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.

### 2019-01-09 04-ADMMsigma-Package.Rmd
restructed manuscript

--- 2018-08-03 03-ADMM-Tutorial.Rmd
@@
-# `ADMMsigma` Tutorial
-
-In many statistical applications, estimating the covariance for a set of random variables is a critical task.
-The covariance is useful because it characterizes the *relationship* between variables.
-For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form
-
-\[ \Sigma_{xyz} = \begin{pmatrix}
-1 & 0 & 0.5 \\ 
-0 & 1 & 0 \\ 
-0.5 & 0 & 1
-\end{pmatrix} \]
-
-We can gather valuable information from this matrix.
-First of all, we know that each of the variables has an equal variance of 1.
-Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0.
-This implies that any information in $X$ is useless in trying to gather information about $Y$.
-Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.
-
-Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging.
-For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
+# `ADMMsigma` R Package
 

### 2019-01-09 05-SCPME-Package.Rmd
restructed manuscript

# `SCPME` R Package

`SCPME` is an implementation of the proposed augmented ADMM algorithm in @molstad2017shrinking for solving the previous optimization problem. In addition, this package places a big emphasis on flexibility that allows for rapid experimentation for the end user.

We will illustrate this with a short simulation and show some of the new and interesting estimators for $\Omega$ that are a result of this penalty.

<br>\vspace{0.5cm}

## Simulation

Let us generate some data. For this example, we will assume

\[ Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i} \]

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$, $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$ and we are interested in estimating the marginal precision matrix of $X$ (denoted $\Omega$).

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(SCPME)
set.seed(123)

# generate data from a sparse oracle precision matrix.
# we can use the built-in `data_gen` function

# generate 100 x 5 X data matrix and 100 x 1 Y data matrix
data = data_gen(p = 5, n = 100, r = 1)

# the default regression coefficients are sparse
data$betas

# default oracle precision matrix is also sparse
round(qr.solve(data$SigmaX), 5)

# snap shot of X data matrix
head(data$X)

# snap shot of Y data matrix
head(data$Y)

```
<br>\vspace{0.5cm}

We have generated 100 samples of the random variable $X \in \mathbb{R}^{5}$ and 100 samples of the random variable $Y \in \mathbb{R}$. It turns out that this particular oracle covariance matrix for $X$ (tapered matrix) has an inverse that is sparse (tri-diagonal). That is, the precision matrix has many zeros.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print oracle covariance matrix
data$SigmaX

# print inverse covariance matrix (omega)
round(qr.solve(data$SigmaX), 5)

```
<br>\vspace{0.5cm}

In this particular setting, we could estimate $\Omega$ by taking the inverse of the sample covariance matrix $\hat{S} = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n$:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print inverse of sample precision matrix (perhaps a bad estimate)
round(qr.solve(cov(data$X)*(nrow(data$X) - 1)/nrow(data$X)), 5)

```
<br>\vspace{0.5cm}

However, because $\Omega$ is sparse, this estimator will likely perform very poorly. Notice the number of zeros in our oracle precision matrix compared to the inverse of the sample covariance matrix. Instead, we will use `SCPME` to estimate $\Omega$.

By default, `SCPME` will estimate $\Omega$ using a lasso penalty ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$) and choose the optimal `lam` tuning parameter that minimizes the mean squared prediction error for the regression of the variable $Y$ on $X$.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty
shrink(X = data$X, Y = data$Y)

```
<br>\vspace{0.5cm}

However, we could also select the optimal tuning parameter based on other criteria, such as log-likelihood. Other options include: AIC, BIC, and penalized log-likelihood (`penloglik`).

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty with crit.cv = loglik
shrink(X = data$X, Y = data$Y, crit.cv = "loglik")

```
<br>\vspace{0.5cm}

`SCPME` also has the capability to provide plots for the cross validation errors. In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# produce CV heat map
shrink = shrink(X = data$X, nlam = 50, crit.cv = "BIC")
plot(shrink, type = "heatmap")

```
<br>\vspace{0.5cm}

Note that in the previous plot, it is not necessary to provide the $Y$ data matrix because neither the penalty nor the cross validation criteria depends on the values of $Y$.

We can also produce a line graph of the cross validation errors:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# produce line graph
plot(shrink, type = "line")

```
<br>\vspace{0.5cm}

We also have the option to print *all* of the estimated precision matrices for each tuning parameter using the `path` option. This option should be used with *extreme* care when the dimension and sample size is large -- you may run into memory issues.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# keep all estimates using path
shrink = shrink(X = data$X, crit.cv = "loglik", path = TRUE)

# print only first three objects
shrink$Path[,,1:3]

```
<br>\vspace{0.5cm}

Recall that all of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in $\Omega$. In effect, this penalty embeds an assumption in our estimate that the true $\Omega$ is sparse.

The flexibility of the penalty described in @molstad2017shrinking allows us to make other assumptions as well. For instance, in the penalty we could set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$. In which case

\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]

This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). Of course, we do not know the true covariance matrix $\Sigma_{xy}$ but we could use the sample estimate instead.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta
lam_max = max(abs(crossprod(data$X, data$Y)))
(shrink = shrink(X = data$X, Y = data$Y, B = cov(data$X, data$Y), lam.max = lam_max, nlam = 20))

# plot CV errors
plot(shrink)

```
<br>\vspace{0.5cm}

Note that we specified the maximum `lam` value in the previous function to expand the tuning parameter grid.

Conveniently, with these settings, the augmented ADMM algorithm also solves for the estimated $\beta$ coefficient matrix simultaneously:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print estimated beta matrix
shrink$Z

```
<br>\vspace{0.5cm}

Another possible penalty is to set $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.

\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]

In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta AND omega
(shrink = shrink(X = data$X, Y = data$Y, B = cbind(cov(data$X, data$Y), diag(ncol(data$X))), lam.max = 10, lam.min.ratio = 1e-4, nlam = 20))

# print estimated beta
shrink$Z[, 1, drop = FALSE]

# plot CV errors
plot(shrink)

```
<br>\vspace{0.5cm}

## More advanced options

A huge issue in precision matrix estimation is the computational complexity when the sample size and dimension of our data is particularly large. There are a number of built-in options in `SCPME` that can be used to improve computation speed:

 - Reduce the number of `lam` values during cross validation. The default number is 10.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# reduce number of lam to 5
shrink = shrink(X = data$X, Y = data$Y, nlam = 5)

```
<br>\vspace{0.5cm}

 - Reduce the number of `K` folds during cross validation. The default number is 5.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# reduce number of folds to 3
shrink = shrink(X = data$X, Y = data$Y, K = 3)

```
<br>\vspace{0.5cm}

 - Relax the convergence critera for the ADMM algorithm using the `tol.abs` and `tol.rel` options. The default for each is 1e-4.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# relax convergence criteria
shrink = shrink(X = data$X, Y = data$Y, tol.abs = 1e-3, tol.rel = 1e-3)

```
<br>\vspace{0.5cm}

 - Adjust the maximum number of iterations. The default is 1e4.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# adjust maximum number of iterations
shrink = shrink(X = data$X, Y = data$Y, maxit = 1e3)

```
<br>\vspace{0.5cm}

 - Adjust `adjmaxit`. This allows the user to adjust the maximum number of iterations *after* the first `lam` tuning parameter has fully converged during cross validation. This allows for *one-step estimators* and can greatly reduce the time required for the cross validation procedure while still choosing near-optimal tuning parameters.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# adjust adjmaxit
shrink = shrink(X = data$X, Y = data$Y, adjmaxit = 2)

```
<br>\vspace{0.5cm}

 - We can also opt to run our cross validation procedure in parallel. The user should check how many cores are on their system before using this option

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE, eval = FALSE}

# parallel CV
shrink = shrink(X = data$X, Y = data$Y, cores = 2)

```
<br>\vspace{0.5cm}

### 2019-01-09 98-appendix.Rmd
restructed manuscript

# Appendix

## Proof of (1):

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik)
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
(\#eq:appendixomegagradient)
\end{split}
\end{equation}

Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient. First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:

\[ S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{align*}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{align*}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof)
\end{equation}

## Proof of (2)

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik)
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
(\#eq:appendixZZgradient)
\end{split}
\end{equation}

where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right)
(\#eq:ZZsoftproof)
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]

- If $Z_{ij}^{k + 1} < 0$ then

\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that $\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
(\#eq:appendixZZproof)
\end{split}
\end{equation}

where soft is the soft-thresholding function.

## Proof of (2-3):

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik2)
\end{equation}

\begin{equation}
\begin{split}
  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
(\#eq:appendixomegagradient2)
\end{split}
\end{equation}

Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to

\[ S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \]

We can then decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.

\[ S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \]

This equivalence implies that

\[ \phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \]

where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}$. Therefore

\begin{align*}
  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
\end{align*}

In summary, if we decompose $S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof2)
\end{equation}

## Proof of (4)

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik2)
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
(\#eq:appendixZZgradient2)
\end{split}
\end{equation}

where $\mbox{sign(Z)}$ is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right)
(\#eq:ZZsoftproof2)
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\[ \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \]

- If $Z_{ij}^{k + 1} < 0$ then

\[ \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \]

This implies that $\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
(\#eq:appendixZZproof2)
\end{split}
\end{equation}

where soft is the soft-thresholding function.

### 2019-01-09 index.Rmd
restructed manuscript

--- 2018-06-12 index.Rmd
@@
 --- 
-title: "Oral Manuscript"
+title: "Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression"
 author: "Matt Galloway"
@@
 site: bookdown::bookdown_site
-output: bookdown::gitbook
-documentclass: book
-#bibliography: [lib.bib, packages.bib]
-bibliography: lib.bib
+output:
+  bookdown::pdf_book:
+    toc_depth: 2
+    fig_caption: yes
+    includes:
+      in_header: preamble.tex
+  bookdown::gitbook:
+    toc_depth: 2
+documentclass: report
+bibliography: [lib.bib, packages.bib]
+#bibliography: lib.bib
 biblio-style: apalike
+#geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
+#geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
+geometry: "left = 1in, right = 1in, top = 1in, bottom = 1in"
 colorlinks: yes
@@
 github-repo: MGallow/oral_manuscript
-description: "This is a working manuscript in preparation for Matt Galloway's doctoral oral examination."
+description: "This is a working manuscript in preparation for Matt Galloway's master's thesis defense."
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE)
-
-# ```{r include=FALSE}
-# # automatically create a bib database for R packages
-# knitr::write_bib(c(
-#   .packages(), 'bookdown', 'knitr', 'rmarkdown'
-# ), 'packages.bib')
-# ```
+knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE, out.width = "90%", fig.align = "center", out.extra = "")
 
@@
 
-# Prerequisites
+```{r include=FALSE}
+# automatically create a bib database for R packages
+knitr::write_bib(c(.packages(), "glasso", "ADMMsigma", "SCPME"), 'packages.bib')
+
+```

### 2019-01-14 01-intro.Rmd
finished modifying structure of appendix

@@
 
-In many statistical applications, estimating the covariance for a set of random variables is a critical task.
-The covariance is useful because it characterizes the *relationship* between variables.
+In many statistical applications, estimating the covariance matrix, $\Sigma$, for a set of random variables is a critical task.
+The covariance matrix is useful because it characterizes the *relationship* between variables.
 For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form
 
-\[ \Sigma_{xyz} = \begin{pmatrix}
+\begin{equation}
+\Sigma_{xyz} = \begin{pmatrix}
 1 & 0 & 0.5 \\ 
@@
 0.5 & 0 & 1
-\end{pmatrix} \]
+\end{pmatrix}
+(\#eq:ex)\notag
+\end{equation}
 
@@
 
+If we have data that is normally distributed with mean $\mu$ and variance $\Sigma$ (that is, $X_{i} \sim N_{p}\left(\mu, \Sigma \right)$), the optimal estimator for $\Omega$ with respect to the log-likelihood is of the form
+
+\begin{equation}
+\hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
+(\#eq:mleoptim)
+\end{equation}
+
+where $S$ denotes the usual sample estimator ($S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T})$).
+As in regression settings, we can construct *penalized* log-likelihood estimators by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
+(\#eq:penoptim)
+\end{equation}
+
+$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
+These penalties are the ridge and lasso, respectively.
+The penalty proposed in @molstad2017shrinking, however, is of the form $P\left(\Omega\right) = \left\|A\Omega B - C\right\|_{1}$ so that the general optimization problem is
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+(\#eq:molstadeq)
+\end{equation}
+
+`SCPME` is an implementation of the proposed augmented ADMM algorithm in @molstad2017shrinking for solving the previous optimization problem.
+In addition, this package places a big emphasis on flexibility that allows for rapid experimentation for the end user.
+
+We will illustrate this with a short simulation and show some of the new and interesting estimators for $\Omega$ that are a result of this penalty.
+
 - Why do we care?

### 2019-01-14 03-SCPME.Rmd
finished modifying structure of appendix

@@
 ## Illustration via Regression
+
+In many statistical applications, estimating the covariance for a set of random variables is a critical task.
+Unfortunately, estimating $\Sigma$ well is often expensive and, in a few settings, extremely challenging.
+For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
+
+If we have data that is normally distributed with mean $\mu$ and variance $\Sigma$ (that is, $X_{i} \sim N_{p}\left(\mu, \Sigma \right)$), the optimal estimator for $\Omega$ with respect to the log-likelihood is of the form
+
+\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
+
+where $S$ denotes the usual sample estimator ($S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T})$).
+As in regression settings, we can construct *penalized* log-likelihood estimators by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\} \]
+
+$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
+These penalties are the ridge and lasso, respectively.
+The penalty proposed in @molstad2017shrinking, however, is of the form $P\left(\Omega\right) = \left\|A\Omega B - C\right\|_{1}$ so that the general optimization problem is
+
+\begin{align}
+  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+\end{align}
+
+`SCPME` is an implementation of the proposed augmented ADMM algorithm in @molstad2017shrinking for solving the previous optimization problem.
+In addition, this package places a big emphasis on flexibility that allows for rapid experimentation for the end user.
+
+We will illustrate this with a short simulation and show some of the new and interesting estimators for $\Omega$ that are a result of this penalty.
 

### 2019-01-14 05-ADMMsigma-Package.Rmd
finished modifying structure of appendix

# `ADMMsigma` R Package

`ADMMsigma` is an R package that estimates a penalized precision matrix, often denoted $\Omega$, via the alternating direction method of multipliers (ADMM) algorithm. Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user -- the primary goal of this package.

The package currently supports a general elastic-net penalty that allows for both ridge and lasso-type penalties as special cases. In particular, the algorithm solves the following optimization problem:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{tr(S\Omega) - \log\det\left(\Omega\right) + \lambda\left[\frac{1 - \alpha}{2}\left\|\Omega\right\|_{F}^{2} + \alpha\left\|\Omega\right\|_{1} \right] \right\} \]

where $\lambda > 0$, $0 \leq \alpha \leq 1$ are tuning parameters, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.

A list of functions contained in the package can be found below:

* `ADMMsigma()` computes the estimated precision matrix (ridge, lasso, and elastic-net type regularization optional)

* `RIDGEsigma()` computes the estimated ridge penalized precision matrix via closed-form solution

* `plot.ADMMsigma()` produces a heat map or line graph for cross validation errors

* `plot.RIDGEsigma()` produces a heat map or line graph for cross validation errors

## Installation

<br>\vspace{0.5cm}
```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("ADMMsigma")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/ADMMsigma")
```
<br>\vspace{0.5cm}

This package is hosted on Github at [github.com/MGallow/ADMMsigma](https://github.com/MGallow/ADMMsigma).

## Tutorial

By default, `ADMMsigma` will estimate a penalized precision matrix, $\Omega$, using the elastic-net penalty and choose the optimal $\lambda$ and $\alpha$ tuning parameters. The primary function is simply `ADMMsigma()`. The input value $X$ is an $n \times p$ data matrix so that there are $n$ rows each representing an observation and $p$ columns each representing a unique feauture or variable.

Here, the data matrix is $100 \times 5$ and generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$. A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal. That is, the precision matrix is sparse and the shrinkage penalty used here should prove useful.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = FALSE}
library(ADMMsigma)

#  generate data from a sparse matrix
# first compute covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

```{r, message = FALSE, echo = TRUE}

# elastic-net type penalty (set tolerance to 1e-8)
ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)

```
<br>\vspace{0.5cm}

We can see that the optimal $\alpha$ value selected is one. This selection corresponds with a lasso penalty -- a special case of the elastic-net penalty.

We can also explicitly assume sparsity in our estimate - rather than let the package decide - by restricting the class of penalties to the lasso. We do this by simply setting `alpha = 1` in our function:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty (default tolerance)
ADMMsigma(X, alpha = 1)

```
<br>\vspace{0.5cm}

`ADMMsigma` also has the capability to provide plots for the cross validation errors. This allows the user to analyze and select the appropriate tuning parameters. In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection. In the line graph, each line corresponds to a different $\alpha$ tuning parameter.

<br>\vspace{0.5cm}
```{r ADMMsigmapackage1, message = FALSE, echo = TRUE, fig.cap = "CV heatmap for ADMMsigma tutorial.", out.width = "80%"}

# produce CV heat map for ADMMsigma
ADMM = ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)
plot(ADMM, type = "heatmap")

```

```{r ADMMsigmapackage2, message = FALSE, echo = TRUE, fig.cap = "CV line graph for ADMMsigma tutorial.", out.width = "80%"}

# produce line graph for CV errors for ADMMsigma
plot(ADMM, type = "line")

```
<br>\vspace{0.5cm}

`ADMMsigma` has a number of more advanced options such as cross validation criteria, regularization path, and parallel processing that are explained in detail on the project website at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).

### 2019-01-14 06-SCPME-Package.Rmd
finished modifying structure of appendix

# `SCPME` R Package

`SCPME` is an R package that estimates a penalized precision matrix via a modified alternating direction method of multipliers (ADMM) algorithm as described in @molstad2017shrinking. Specifically, the modified ADMM algorithm solves the following optimization problem:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S \Omega\right) - \log\det\left(\Omega\right) + \lambda\left\| A\Omega B - C \right\|_{1} \right\} \]

where $\lambda > 0$ is a tuning parameter, $A, B, \mbox{ and } C$ are known matrices specified by the user, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.

This form of penalty leads to many new, interesting, and novel estimators for the precision matrix $\Omega$. In short, users can construct matrices $A, B, \mbox{ and } C$ so that emphasis is place on the sum, absolute value of a *characteristic* of $\Omega$. We will explore a few of these in the tutorial section.

A list of functions contained in the package can be found below:

* `shrink()` computes the estimated precision matrix

* `data_gen()` data generation function (for convenience)

* `plot.shrink()` produces a heat map or line graph for cross validation errors

## Installation

<br>\vspace{0.5cm}
```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("SCPME")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/SCPME")
```
<br>\vspace{0.5cm}

This package is hosted on Github at [github.com/MGallow/SCPME](https://github.com/MGallow/SCPME).

## Tutorial

The primary function is the `SCPME` package is simply `shrink()`. The input values $X$ is an $n \times p$ data matrix so that there are $n$ rows each representing an observation and $p$ columns each representing a unique variable and $Y$ is an $n \times r$ response matrix where $r$ is the dimension of the response vector. By default, `SCPME` will estimate $\Omega$ using a lasso penalty ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$) and choose the optimal $\lambda$ tuning parameter that minimizes the mean squared prediction error for the regression of the variable $Y$ on $X$. If $Y$ is not provided (optional), then tuning parameter selection will be based on the validation likelihood. Note that $\Omega$ (perhaps better denoted here as $\Omega_{x}$) will only have meaningful shrinkage unless the data vector $X \in \mathbb{R^{p}}$ is multi-dimensional - that is, $p > 1$.

Here, in this example, the data matrix is $100 \times 5$ and the response is generated according to the following model:

\[ Y_{i} = \beta^{T}X_{i} + E_{i} \]

where $E_{i} \sim N\left( 0, 1 \right)$ and $X_{i}$ is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$. A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal. It is this oracle precision matrix that is our primary interest in estimating. In addition, $\beta$ is randomly generated and sparse. The data will be generated using the `data_gen()` function contained in the package.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(SCPME)
set.seed(123)

# generate data from a sparse oracle precision matrix.
# we can use the built-in `data_gen` function

# generate 100 x 5 X data matrix and 100 x 1 Y data matrix
data = data_gen(p = 5, n = 100, r = 1)

# the oracle regression coefficients are sparse
data$betas

```

```{r, message = FALSE, echo = TRUE}

# shrink sum absolute entries in omega
shrink(X = data$X, Y = data$Y)

```
<br>\vspace{0.5cm}

Notice here that the estimated precision matrix is *not* sparse. This is due to the fact that our cross validation criteria is the mean-squared prediction. We can estimate a new precision matrix using the validation likelihood as criteria with the following command:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# shrink sum absolute entries in omega
shrink(X = data$X, Y = data$Y, crit.cv = "loglik")

```
<br>\vspace{0.5cm}

Recall that all of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in $\Omega$ ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$). In effect, this penalty embeds an assumption in our estimate that the true $\Omega$ is sparse. The flexibility of the penalty described in @molstad2017shrinking allows us to make other assumptions as well. For instance, in the penalty we could set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$. In which case

\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]

This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). Of course, in practice, we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta
lam_max = max(abs(crossprod(data$X, data$Y)))
(shrink = shrink(X = data$X, Y = data$Y, B = cov(data$X, data$Y), lam.max = lam_max, nlam = 20))

```

Note that we specified the maximum `lam` value in the previous function to expand the tuning parameter grid. Conveniently, with these settings, the augmented ADMM algorithm also solves for the estimated $\beta$ coefficient matrix simultaneously:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print estimated beta matrix
shrink$Z

```
<br>\vspace{0.5cm}

Another possible penalty is to set $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$. That is, the penalty $P$, is constructed as follows:

\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]

In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta AND omega
(shrink = shrink(X = data$X, Y = data$Y, B = cbind(cov(data$X, data$Y), diag(ncol(data$X))), lam.max = 10, lam.min.ratio = 1e-4, nlam = 20))

# print estimated beta
shrink$Z[, 1, drop = FALSE]

```
<br>\vspace{0.5cm}

`SCPME` also has the capability to provide plots (heatmap and line graph) for the cross validation errors. In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection.

<br>\vspace{0.5cm}
```{r SCPMEpackage1, message = FALSE, echo = TRUE, fig.cap = "CV heatmap for SCPME tutorial", out.width = "80%"}

# produce CV heat map
plot(shrink, type = "heatmap")

```

```{r SCPMEpackage2, message = FALSE, echo = TRUE, fig.cap = "CV line graph for SCPME tutorial", out.width = "80%"}

# produce line graph
plot(shrink, type = "line")

```
<br>\vspace{0.5cm}

`SCPME` has a number of more advanced options such as various convergence criteria and parallel processing that are explained in detail on the project website at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).

### 2019-01-14 02-PME.Rmd
finished PME appendix

@@
 \end{split}
-(\#eq:lik)
+(\#eq:normallik)
 \end{equation}
@@
   l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-1} \right]
-(\#eq:loglik)
+(\#eq:normalloglik)
 \end{equation}
@@
 
-so that $\hat{\Omega}_{MLE} = S^{-1}$.
-Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$ ^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
+so that $\hat{\Omega}^{MLE} = S^{-1}$.
+Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
 Both procedures will result in the same estimate.].
@@
 P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
-(\#eq:pen)
+(\#eq:penelastic)
 \end{equation}
@@
 \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
-(\#eq:omegaloglik)
+(\#eq:optimelastic)
 \end{equation}
@@
 P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
-(\#eq:pen2)
+(\#eq:penmolstad)
 \end{equation}
@@
 \end{split}
+(\#eq:boyd)
 \end{equation}
@@
 
-\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]
+\begin{equation}
+p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\}
+(\#eq:infimum)
+\end{equation}
 
@@
 
-\begin{align}
-  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) (\#eq:xauglagrange) \\
-  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) (\#eq:zauglagrange) \\
-  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c) (\#eq:yauglagrange)
-\end{align}
+\begin{equation}
+\begin{split}
+  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
+  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
+  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+\end{split}  
+(\#eq:admmalgo)
+\end{equation}
 
@@
 L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
-(\#eq:lagrange)
+(\#eq:lagrange2)
 \end{equation}
@@
 L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
-(\#eq:auglagrangian)
+(\#eq:auglagrange2)
 \end{equation}
@@
 
-1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV'$ via spectral decomposition.
+1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV'$ via spectral decomposition^[Proof of \@ref(eq:omegaalgo) in section \@ref(proofomegaalgo).]. Then
 
@@
 
-2. Elementwise soft-thresholding for all $i = 1,..., p$ and $j = 1,..., p$.
+2. Elementwise soft-thresholding for all $i = 1,..., p$ and $j = 1,..., p$^[Proof of \@ref(eq:ZZalgo) in section \@ref(proofZZalgo).].
 
@@
 
-Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,
+Because $\Omega^{k + 1}$ is the minimizer of the augmented lagragian, this implies that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ which further implies that^[Proof in section \@ref(proofdualresidual).]
+
+\begin{equation}
+0 \in \rho\left( Z^{k + 1} - Z^{k} \right)
+(\#eq:dualresidual)
+\end{equation}
+
+Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$.
+Note that the second dual optimality condition is always satisfied^[Proof in section \@ref(proofdualopt).]:
 
@@
 \begin{split}
-  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
-  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
-  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
-  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
-  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
-(\#eq:dualresidual)
-\end{split}
-\end{equation}
-
-Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied:
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+  0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
 (\#eq:dualopt)
@@
 We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.
+
+HOW DID WE GENERATE THE DATA?
 

### 2019-03-09 01-intro.Rmd
finished PME appendix
begin writing stage

@@
 \begin{equation}
-\hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
-(\#eq:mleoptim)
+\hat{\Omega}^{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
+(\#eq:mleoptim)\notag
 \end{equation}
@@
 \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
-(\#eq:penoptim)
+(\#eq:penoptim)\notag
 \end{equation}
@@
 \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
-(\#eq:molstadeq)
+(\#eq:molstadeq)\notag
 \end{equation}
@@
 
+The reference we need here is @molstad2017shrinking!
+
+1.
+From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
+For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.
+Many authors have proposed methods that directly estimate this characteristic @cai2011direct; @fan2012road; @mai2012direct."
+
+2.
+From @molstad2017shrinking: "@chen2016regularized proposed a method for estimating the characteristic $\Omega_{*}\mu_{*}$ directly, but like the direct linear discriminant methods, this apporach does not lead to an estimate of $\Omega_{*}$."
+
+3.
+Discuss linear regression application....
+where $\beta = \Omega_{*}\Sigma_{*XY}$.
+Like @witten2009covariance, this approach estimates the regression coefficients "using shrinkage estimators of the marginal precision matrix for the predictors".
+
 - Guide
@@
 - Model and notation
+
+## Outline
+
+- Why do we care about covariance matrices? Covariance matrices are an object that summarizes the relationship between variables.
+
+- What is a precision matrix? Precision matrix is the inverse of a covariance matrix.
+
+- Precision matrices are powerful, essential in representing relationships in variables
+
+- In fact, required to be estimated to fit many statistical models.
+
+- That is, we must provide an object that accurately summarizes the relationship and interaction between variables in our model.
+
+- Many proposed shrinkage estimators when p is particularly large. Shrinkage.
+
+- However, to fit these models, Molstad and Rothman focused on the fact that onnly a "characteristic" of a precision matrix is required to fit these models.
+"We propose a framework to shrink a user-specified characteristic of a precision matrix estimator."
+
+- For instance, LDA, linear regression, ...
+
+- Their approach/methodology was published in BLAH. Shrinking characteristic of precision matrix estimators.
+
+- BREAK
+
+- We wanted to explore the regression application that was mentioned but not pursued/investigated
+
+- This document will outline the research and work leading up to that
+
+- The document is outlined as follows...
+
+- We will begin chapter 2 with a brief introduction to precision matrix estimation.
+This will include mentions of estimation methods/approaches and we will spend a particular amount of time elaborating on one approach which is estimation via the ADMM algorithm.
+This dicussion will be useful when we circle back to SCPME, the regression application, and the augmented ADMM algorithm developed in BLAH.
+
+- Lastly, the document will end with two brief tutorials for the R packages ADMMsigma and SCPME.
+These packages, developed by myself, will be mentioned throughout the document and were instrumental in this pursued line of research and facilitated many simulations and research direction explored throughout.
+Both packages have since been published on CRAN
+
+## Model and Notation

### 2019-03-09 02-PME.Rmd
begin writing stage

@@
 # Precision Matrix Estimation
+
+### Literature Review?
+
+- Articles that review covariance and precision matrix estimation in high dimensional settings are @pourahmadi2013high and @fan2016overview.
+
+- The person who initially proposed the lasso-penalized gaussian likelihood precision matrix estimation is @yuan2007model.
+
+- Other authors who have proposed methods with non-lasso penalizations are (Frobenius norms) @witten2009covariance, @rothman2014existence, (non-convex penalties) @lam2009sparsistency, and @fan2009network.
+
+- Standard alternating direction method of multipliers approaches are found in @boyd11distributed.
+
+- ADMM with modification based on majorize-minimize principle is found in @lange2016mm.
+
+- Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.
+
+- L1-penalized gaussian likelihood precision matrix estimator (@yuan2007model; @rothman2008sparse; @friedman2008sparse).
 
@@
 
-Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Sigma$.
-That is, $X_{i} \sim N_{p}\left( \mu, \Sigma \right)$.
+Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$.
+That is, $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.
 
@@
 \begin{split}
-  f(X_{1}, ..., X_{n}; \mu, \Sigma) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Sigma \right|^{-1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Sigma^{-1}\left( X_{i} - \mu \right) \right] \\
-  &= (2\pi)^{-nr/2}\left| \Sigma \right|^{-n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Sigma^{-1} \right]
+  f(X_{1}, ..., X_{n}; \mu, \Omega^{-1}) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
+  &= (2\pi)^{-np/2}\left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Omega \right]
 \end{split}
@@
 
-where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Sigma$ is equal to the following:
+where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Omega$ is equal to the following:
 
 \begin{equation}
-  l(\mu, \Sigma | X) = const. - \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-1} \right]
+  l(\mu, \Omega | X) = const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
 (\#eq:normalloglik)
@@
 
-If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}_{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$.
+If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$.
 However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well.
@@
 \begin{equation}
-\hat{\Sigma}^{mle} = \arg\max_{\Sigma \in \mathbb{S}_{+}^{p}}\left\{ const.
-- \frac{n}{2}\log\left| \Sigma \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-1} \right] \right\}
-(\#eq:sigmaloglik)
+\begin{split}
+\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ const.
++ \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right] \right\} \\
+  &= \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]^{-1}
+\end{split}
+(\#eq:omegamle)
 \end{equation}
 
-\begin{equation}
-\nabla_{\Sigma}l(\mu, \Sigma | X) = -\frac{n}{2}\Sigma^{-1} + \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Sigma^{-2}
-(\#eq:nablasigma)
-\end{equation}
-
-\begin{equation}
-\Rightarrow \hat{\Sigma}^{mle} = \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]
-(\#eq:sigmamle)
-\end{equation}
-
-By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Sigma$ is our usual sample estimator often denoted as $S$.
+By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Omega$ is the inverse our usual sample estimator for the covariance matrix, denoted here as $S^{-1}$.
 It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:

### 2019-03-09 03-SCPME.Rmd
begin writing stage

@@
 # SCPME
+
+- A similar estimator was proposed by @dalal2017sparse when $C = 0$.
+
+- - Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.
 
@@
 since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.
-Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function.
-
-To see why this particular function was used, consider the Taylor's expansion of $\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2$:
-
-\begin{equation}
-\begin{split}
-  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
-  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
-(\#eq:taylors)
-\end{split}
-\end{equation}
-
-**Note:**
-
-\begin{equation}
-  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
-(\#eq:gradient)
-\end{equation}
-
-\begin{equation}
-\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
-(\#eq:hessian)
-\end{equation}
-
-This implies that
-
-\begin{equation}
-\begin{split}
-  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
-  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
-  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
-  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
-  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
-  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
-(\#eq:penapprox)
-\end{split}
-\end{equation}
-
-Let us now plug in this equality into our optimization problem in step one:
-
-\begin{equation}
-\begin{split}
-  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
-  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
-  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
-  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
- tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
-(\#eq:omegaapprox)
-\end{split}
-\end{equation}
-
-where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.
+Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Proof of BLAH in section BLAHHH].
 
@@
 
-1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}$
+1. Compute $G^{k}$.
 
-2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
+\begin{equation}
+G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}
+(\#eq:Gk)
+\end{equation}
 
-3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
+2. Via spectral decomposition, decompose
 
-4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)$
+\begin{equation}
+S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}
+(\#eq:VQV)
+\end{equation}
 
-5. Set $Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
+3. Update^[Proof of \@ref(eq:Omegak) in section \@ref(proofOmegak)] $\Omega^{k + 1}$.
+
+\begin{equation}
+\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)
+(\#eq:Omegak)
+\end{equation}
+
+4. Update^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)] $Z^{k + 1}$.
+
+\begin{equation}
+Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)
+(\#eq:Zk)
+\end{equation}
+
+5. Update $Y^{k + 1}$.
+
+\begin{equation}
+Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+(\#eq:Yk)
+\end{equation}
 
@@
 
-where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
+The soft-thresholding function is defined as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
 
@@
 At convergence, the optimality conditions require that $r^{k + 1} \approx 0$.
-The second residual we will define is the dual residual:
+The second residual we will define is the dual residual^[Proof of \@ref(eq:stopproof) in section \@ref(proofstopproof).]:
 
-\[ s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \]
+\begin{equation}
+s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
+(\#eq:stopproof)
+\end{equation}
 
-This residual is derived from the fact. Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,
+Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$.
+Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt2) in section \@ref(proofdualopt2)].
 
@@
 \begin{split}
-  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
-  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
-  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
-  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
-  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
-  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
-(\#eq:stopproof)
-\end{split}
-\end{equation}
-
-Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied:
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
 (\#eq:dualopt2)
@@
 6. Replace $k$ with $k + 1$.
-
-### Connection to joint log-likelihood
-
-The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
-(\#eq:penregression)
-\end{equation}
-
-To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:
-
-\begin{equation}
-Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-(\#eq:linregression)
-\end{equation}
-
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form
-
-\begin{equation}
-Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
-(\#eq:linnormal)
-\end{equation}
-
-We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$.
-Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience.
-We will also let $f$ denote the probability distribution function for each respective variable.
-
-\begin{equation}
-\begin{split}
-  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
-  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
-  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
-  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
-  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
-(\#eq:jointlik)
-\end{split}
-\end{equation}
-
-where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:
-
-\begin{equation}
-\begin{split}
-  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const.
-+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
-  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
-(\#eq:jointloglik)
-\end{split}
-\end{equation}
-
-**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.
-
-\begin{equation}
-\begin{split}
- \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
- &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
- \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
- (\#eq:gradient2)
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
- &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
- &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
- &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
- \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
- \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
- \Rightarrow \hat{\mu}_{x} &= \bar{X}
-(\#eq:gradient3)
-\end{split}
-\end{equation}
-
-Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.
-
-Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$.
-This can be achieved by simply centering the data by the sample averages.
-Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:
-
-\begin{equation}
-\begin{split}
-  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
-  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
-  &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
-  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
-  &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
-  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
-(\#eq:partialjointloglik)
-\end{split}
-\end{equation}
-
-where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:
-
-\begin{equation}
-\begin{split}
-  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
-(\#eq:omegajointloglik)
-\end{split}
-\end{equation}
-
-where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm.
-Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$.
-Therefore, we have that
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
-(\#eq:omegajointmle)
-\end{equation}
-
-Notice that this is exactly the ridge SCPME estimator!
-
-### Takeaways
-
-We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:
-
-1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that
-
-\begin{equation}
-Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-(\#eq:linregression2)
-\end{equation}
-
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-
-2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.
-
-3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.
-
-In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:
-
-Set $k = 0$ and repeat steps 1-6 until convergence.
-
-1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$
-
-2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
-
-3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
-
-4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$
-
-5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
-
-6. Replace $k$ with $k + 1$.
-
-Note that the only difference is in step 4.
-
-There are a few takeaways we can make after revealing this connection.
-The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$.
-The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator.
-No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it.
-We show this below:
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
-(\#eq:penregression2)
-\end{equation}
-
-\begin{equation}
-\begin{split}
-  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
-  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
-  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
-  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
-  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
-  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
-  (\#eq:penregressionproof)
-\end{split}
-\end{equation}
-
-by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.

### 2019-03-10 01-intro.Rmd
added notations and restructured

@@
 
-If we have data that is normally distributed with mean $\mu$ and variance $\Sigma$ (that is, $X_{i} \sim N_{p}\left(\mu, \Sigma \right)$), the optimal estimator for $\Omega$ with respect to the log-likelihood is of the form
-
-\begin{equation}
-\hat{\Omega}^{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
-(\#eq:mleoptim)\notag
-\end{equation}
-
-where $S$ denotes the usual sample estimator ($S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T})$).
-As in regression settings, we can construct *penalized* log-likelihood estimators by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
-(\#eq:penoptim)\notag
-\end{equation}
-
-$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
-These penalties are the ridge and lasso, respectively.
-The penalty proposed in @molstad2017shrinking, however, is of the form $P\left(\Omega\right) = \left\|A\Omega B - C\right\|_{1}$ so that the general optimization problem is
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
-(\#eq:molstadeq)\notag
-\end{equation}
-
-`SCPME` is an implementation of the proposed augmented ADMM algorithm in @molstad2017shrinking for solving the previous optimization problem.
-In addition, this package places a big emphasis on flexibility that allows for rapid experimentation for the end user.
-
-We will illustrate this with a short simulation and show some of the new and interesting estimators for $\Omega$ that are a result of this penalty.
-
-- Why do we care?
-
-- What is SCPME?
+### references
 
@@
 
-## Model and Notation
+### Notation and Definitions
+
+For strictly positive integers $n$ and $p$, we will denote $\mathbb{R}^{n \times p}$ as the class of real matrices with dimenson $n \times p$.
+The class of real, symmetric matrices with dimension $p \times p$ will be denoted as $\mathbb{S}^{p}$ and $\mathbb{S}^{p}_{+}$ if we further require the object to be positive definite.
+The sample size in a given data set will most often correspond with $n$ and $p$ will correspond with the dimension of the prediction vector.
+If the dimension of the response vector exceeds one, we will denote it as $r$.
+
+Most matrices will take the form of either $\Sigma$, which should be taken to represent the population covariance matrix, or $\Omega$, which should be taken to represent the population *precision* matrix.
+Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$).
+We will sometimes add a subscript star if the object is oracle - or known- a priori ($\Omega_{*}$) and the population object's estimator that minimizes/maximizes a pre-specified objective function will have a hat attached to it ($\hat{\Omega}$).
+
+There will be significant matrix algebra notation throughout the document.
+The trace operator which sums the diagonal elements of a matrix will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$.
+The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$.
+The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$.
+Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

### 2019-03-10 02-PME.Rmd
added notations and restructured

@@
 \end{split}
-(\#eq:normallik)
+(\#eq:normallik)\notag
 \end{equation}
@@
   l(\mu, \Omega | X) = const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
-(\#eq:normalloglik)
+(\#eq:normalloglik)\notag
 \end{equation}
@@
 \end{split}
-(\#eq:omegamle)
+(\#eq:omegamle)\notag
 \end{equation}
@@
 \hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
-(\#eq:omegamle)
+(\#eq:omegamlesimple)
 \end{equation}
@@
 These penalties are the ridge and lasso, respectively.
-In the `ADMMsigma` package, we instead take
-
-\begin{equation}
-P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
-(\#eq:penelastic)
-\end{equation}
-
-so that solving the full penalized log-likelihood for $\Omega$ results in solving
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
-(\#eq:optimelastic)
-\end{equation}
-
-where $0 \leq \alpha \leq 1$.
-This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`.
-Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty.
-Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.
-
-The penalty proposed by @molstad2017shrinking is one of the following form:
-
-\begin{equation}
-P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
-(\#eq:penmolstad)
-\end{equation}
-
-where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
-Solving the full penalized log-likelihood for $\Omega$ results in solving
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
-(\#eq:omegaloglik2)
-\end{equation}
-
-This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$.
-This type of penalty leads to many new, interesting, and novel estimators for $\Omega$.
-An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$.
-This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.
-Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$
-
-We will explore how to solve for $\hat{\Omega}$ in the next section.
 
@@
 \end{split}
-(\#eq:boyd)
+(\#eq:boyd)\notag
 \end{equation}
@@
 p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\}
-(\#eq:infimum)
+(\#eq:infimum)\notag
 \end{equation}
@@
 L_{\rho}(x, z, y) = f(x) + g(z) + y'(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2}
-(\#eq:auglagrange)
+(\#eq:auglagrange)\notag
 \end{equation}
@@
 \end{split}  
-(\#eq:admmalgo)
+(\#eq:admmalgo)\notag
 \end{equation}
@@
 L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
-(\#eq:lagrange2)
+(\#eq:lagrange2)\notag
 \end{equation}
@@
 L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
-(\#eq:auglagrange2)
+(\#eq:auglagrange2)\notag
 \end{equation}
+
+\vspace{3cm}
+
+In the `ADMMsigma` package, we instead take
+
+\begin{equation}
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+(\#eq:penelastic)\notag
+\end{equation}
+
+so that solving the full penalized log-likelihood for $\Omega$ results in solving
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
+(\#eq:optimelastic)
+\end{equation}
+
+where $0 \leq \alpha \leq 1$.
+This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`.
+Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty.
+Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.
 
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} (\#eq:omegaauglagrange) \\
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} (#eq:omegaauglagrange) \\
   Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} (\#eq:ZZauglagrange) \\
@@
 \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-(\#eq:lamalgo)
+(\#eq:lamalgo)\notag
 \end{equation}
@@
   &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-(\#eq:scaled)
+(\#eq:scaled)\notag
 \end{split}
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} (\#eq:omegascaled) \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} (\#eq:ZZscaled) \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} (\#eq:Uscaled)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} (\#eq:omegascaled)\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} (\#eq:ZZscaled)\notag \\
+  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} (\#eq:Uscaled)\notag
 \end{align}
@@
 \begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:xscaled) \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:zscaled) \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c (\#eq:uscaled)
+  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:xscaled)\notag \\
+  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:zscaled)\notag \\
+  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c (\#eq:uscaled)\notag
 \end{align}
@@
 \Omega^{k + 1} - Z^{k + 1} = 0
-(\#eq:admmprimal)
+(\#eq:admmprimal)\notag
 \end{equation}
@@
   0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:admmdual)
+(\#eq:admmdual)\notag
 \end{split}
@@
 
-Because $\Omega^{k + 1}$ is the minimizer of the augmented lagragian, this implies that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ which further implies that^[Proof in section \@ref(proofdualresidual).]
+Because $\Omega^{k + 1}$ is the minimizer of the augmented lagragian^[Proof of \@ref(eq:dualresidual) in section \@ref(proofdualresidual).], this implies that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ which further implies that
 
@@
 Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$.
-Note that the second dual optimality condition is always satisfied^[Proof in section \@ref(proofdualopt).]:
+Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt) in section \@ref(proofdualopt).]:
 
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
-(\#eq:admmstopping)
+(\#eq:admmstopping)\notag
 \end{split}
@@
 
-#### Dense: P = 100, N = 50
+<!-- #### Dense: P = 100, N = 50 -->
 
-```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->
 
-# generate eigen values
-eigen = c(rep(1000, 5, rep(1, 100 - 5)))
+<!-- # generate eigen values -->
+<!-- eigen = c(rep(1000, 5, rep(1, 100 - 5))) -->
 
-# randomly generate orthogonal basis (via QR)
-Q = matrix(rnorm(100*100), nrow = 100, ncol = 100) %>% qr %>% qr.Q
+<!-- # randomly generate orthogonal basis (via QR) -->
+<!-- Q = matrix(rnorm(100*100), nrow = 100, ncol = 100) %>% qr %>% qr.Q -->
 
-# generate covariance matrix
-S = Q %*% diag(eigen) %*% t(Q)
+<!-- # generate covariance matrix -->
+<!-- S = Q %*% diag(eigen) %*% t(Q) -->
 
-# generate data
-Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
-out = eigen(S, symmetric = TRUE)
-S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
-X = Z %*% S.sqrt
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(100*50), nrow = 50, ncol = 100) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
 
-```
-<br>\vspace{0.5cm}
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
 
-<!-- <center> -->
-<!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ -->
-<!-- width=90% } -->
-<!-- </center> -->
-<!-- } -->
+<!-- <!-- <center> --> -->
+<!-- <!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ --> -->
+<!-- <!-- width=90% } --> -->
+<!-- <!-- </center> --> -->
+<!-- <!-- } --> -->
 
-```{r admmsim3, eval = T, echo = F, fig.cap = "Figure caption here."}
+<!-- ```{r admmsim3, eval = T, echo = F, fig.cap = "Figure caption here."} -->
 
-knitr::include_graphics("images/repsKLdenseQR_N50_P100.png")
+<!-- knitr::include_graphics("images/repsKLdenseQR_N50_P100.png") -->
 
-```
+<!-- ``` -->
 
-#### Dense: P = 10, N = 50
+<!-- #### Dense: P = 10, N = 50 -->
 
-```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->
 
-# generate eigen values
-eigen = c(rep(1000, 5, rep(1, 10 - 5)))
+<!-- # generate eigen values -->
+<!-- eigen = c(rep(1000, 5, rep(1, 10 - 5))) -->
 
-# randomly generate orthogonal basis (via QR)
-Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q
+<!-- # randomly generate orthogonal basis (via QR) -->
+<!-- Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q -->
 
-# generate covariance matrix
-S = Q %*% diag(eigen) %*% t(Q)
+<!-- # generate covariance matrix -->
+<!-- S = Q %*% diag(eigen) %*% t(Q) -->
 
-# generate data
-Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
-out = eigen(S, symmetric = TRUE)
-S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
-X = Z %*% S.sqrt
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(10*50), nrow = 50, ncol = 10) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
 
-```
-<br>\vspace{0.5cm}
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
 
-<!-- <center> -->
-<!-- ![Figure caption here.](images/repsKLdense_N50_P10.png){ -->
-<!-- width=90% } -->
-<!-- </center> -->
+<!-- <!-- <center> --> -->
+<!-- <!-- ![Figure caption here.](images/repsKLdense_N50_P10.png){ --> -->
+<!-- <!-- width=90% } --> -->
+<!-- <!-- </center> --> -->
 
-```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."}
+<!-- ```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."} -->
 
-knitr::include_graphics("images/repsKLdense_N50_P10.png")
+<!-- knitr::include_graphics("images/repsKLdense_N50_P10.png") -->
 
-```
+<!-- ``` -->
 

### 2019-03-10 03-SCPME.Rmd
added notations and restructured

@@
 # SCPME
+
+### literature review?
 
@@
 - - Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.
+
+###  other stuff
 
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) (\#eq:omegaauglagrange2) \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) (\#eq:ZZauglagrange2) \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamauglagrange2)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) (\#eq:omegaauglagrange2)\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) (\#eq:ZZauglagrange2)\notag \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamauglagrange2)\notag
 \end{align}
@@
   \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)\notag
 (\#eq:approx)
@@
 \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0
-(\#eq:pd)
+(\#eq:pd)\notag
 \end{equation}
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} (\#eq:omegaaugadmm) \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} (\#eq:ZZaugadmm) \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamaugadmm)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} (\#eq:omegaaugadmm)\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} (\#eq:ZZaugadmm)\notag \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamaugadmm)\notag
 \end{align}
@@
 G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}
-(\#eq:Gk)
+(\#eq:Gk)\notag
 \end{equation}
@@
 S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}
-(\#eq:VQV)
+(\#eq:VQV)\notag
 \end{equation}
 
-3. Update^[Proof of \@ref(eq:Omegak) in section \@ref(proofOmegak)] $\Omega^{k + 1}$.
+3. Update $\Omega^{k + 1}$.^[Proof of \@ref(eq:Omegak) in section \@ref(proofOmegak)]
 
@@
 
-4. Update^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)] $Z^{k + 1}$.
+4. Update $Z^{k + 1}$.^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)]
 
@@
 Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
-(\#eq:Yk)
+(\#eq:Yk)\notag
 \end{equation}
@@
 A\Omega^{k + 1}B - Z^{k + 1} - C = 0
-(\#eq:scpmeprimal)
+(\#eq:scpmeprimal)\notag
 \end{equation}
@@
   0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:scpmedual)
+(\#eq:scpmedual)\notag
 \end{split}
@@
 s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
-(\#eq:stopproof)
+(\#eq:stopproof)\notag
 \end{equation}
@@
   0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:dualopt2)
+(\#eq:dualopt2)\notag
 \end{split}
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
-(\#eq:scpmestopping)
+(\#eq:scpmestopping)\notag
 \end{split}
 \end{equation}
-
-## Illustration via Regression
-
-In many statistical applications, estimating the covariance for a set of random variables is a critical task.
-Unfortunately, estimating $\Sigma$ well is often expensive and, in a few settings, extremely challenging.
-For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
-
-If we have data that is normally distributed with mean $\mu$ and variance $\Sigma$ (that is, $X_{i} \sim N_{p}\left(\mu, \Sigma \right)$), the optimal estimator for $\Omega$ with respect to the log-likelihood is of the form
-
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \]
-
-where $S$ denotes the usual sample estimator ($S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)^{T})$).
-As in regression settings, we can construct *penalized* log-likelihood estimators by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\} \]
-
-$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
-These penalties are the ridge and lasso, respectively.
-The penalty proposed in @molstad2017shrinking, however, is of the form $P\left(\Omega\right) = \left\|A\Omega B - C\right\|_{1}$ so that the general optimization problem is
-
-\begin{align}
-  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
-\end{align}
-
-`SCPME` is an implementation of the proposed augmented ADMM algorithm in @molstad2017shrinking for solving the previous optimization problem.
-In addition, this package places a big emphasis on flexibility that allows for rapid experimentation for the end user.
-
-We will illustrate this with a short simulation and show some of the new and interesting estimators for $\Omega$ that are a result of this penalty.
-
-## Simulations
-
-We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.
-
-### Models
-
-In the following estimators, let the superscript * denote the oracle estimator:
-
- - `OLS` = ordinary least squares estimator in *low* dimensional setting and Moore-Penrose estimator in a *high* ($p >> n$) dimensional setting
-
- - `ridge` = ridge regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV
-
- - `lasso` = lasso regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV
-
- - `oracleB` = oracle estimator with the true $\beta^{*}$ known ($\left\| Y - X\beta^{*} \right\|_{F}^{2}$)
-
- - `oracleO` = oracle estimator with the true $\Omega^{*}$ known ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$)
-
- - `oracleS` = oracle estimator with the true $\Sigma_{xy}^{*}$ known and sample estimator for $\Omega$ ($\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}$)
-
- - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)
-
- - `shrinkBS` = shrinking characteristics regression estimator with oracle cross-covariance where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$)
-
- - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)
-
- - `glasso` = lasso penalized precision matrix where optimal tuning parameter is chosen to maximize log-likelihood via 3-fold CV.
-
-### Data Generation
-
-Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that
-
-\begin{equation}
-\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
-(\#eq:datalinregression)
-\end{equation}
-
-These values are generated in the following way:
-
-Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1.
-In effect, each $\beta$ entry is turned off with equal probability.
-
-Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
-This ensures that the inverses will be tridiagonal (sparse).
-
-Then for $n$ independent, identically distributed samples:
-
-\begin{equation}
-X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)
-(\#eq:xnormal)
-\end{equation}
-
-\begin{equation}
-E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)
-(\#eq:enormal)
-\end{equation}
-
-If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.
-
-An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$).
-For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).
-
-Possible parameters in simulation:
-
- - `reps` = 20
- - `n` = (100, 1000)
- - `p` = (10, 50, 100, 150)
- - `r` = c(1, 5, 10)
- - `sparse` = c(0.5)
- - `sigma` = c("tridiag")
-
-Note that prior to estimation, the intercept is removed by centering the data.
-
-### Plots
-
-#### High Dimension
-
-Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE).
-Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.
-
-```{r scpmesim1, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# load data
-load("images/sim6.Rdata")
-
-# set P to numeric 
-sim6$P %<>% as.character %>% as.numeric
-
-# ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
-sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim2, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
-sim6 %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-**Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = "tridiag"**
-
-```{r scpmesim3, eval = T, echo = F}
-
-# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
-sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")
-
-```
-
-<br>\vspace{1cm}
-
-#### Low Dimension
-
-```{r scpmesim4, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
-sim6 %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim5, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
-sim6 %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")
-
-```
-
-<br>\vspace{1cm}
-
-**Notable: N = 1000, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**
-
-```{r scpmesim6, eval = T, echo = F}
-
-# ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
-sim6 %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")
-
-```
-
-### Takeaways
-
-1.
-In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$.
-It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.
-
-2.
-In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS.
-The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.
-
-3. When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.
-
-4.
-It is interesting that `oracleO` performed worse than `oracleS` in the final table.
-It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
-
-### Shrinking Covariance Models
-
-In the following estimators, let the superscript * denote the oracle estimator:
-
- - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)
-
- - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)
-
-For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$.
-We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.
-
-### Data Generation
-
-Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that
-
-\begin{equation}
-\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
-(\#eq:datalinregression2)
-\end{equation}
-
-These values are generated in the following way:
-
-Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1.
-In effect, each $\beta$ entry is turned off with equal probability.
-
-Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
-This ensures that the inverses will be tridiagonal (sparse).
-
-Then for $n$ independent, identically distributed samples:
-
-\begin{equation}
-X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)
-(\#eq:xnormal2)
-\end{equation}
-
-\begin{equation}
-E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)
-(\#eq:enormal2)
-\end{equation}
-
-If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.
-
-An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$).
-For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).
-
-Possible parameters in simulation:
-
- - `reps` = 20
- - `n` = (100, 1000)
- - `p` = (10, 50, 100, 150, 200)
- - `r` = c(1, 5, 10)
- - `sparse` = c(0.5)
- - `sigma` = c("tridiag", "compound")
-
-Note that prior to estimation, the intercept is removed by centering the data.
-
-### Plots
-
-```{r, eval = T, echo = F}
-
-# load data
-load("images/sigma.Rdata")
-
-# design color palette
-bluetowhite <- c("#000E29", "white")
-
-# change to numeric
-sigma$lam %<>% as.character %>% as.numeric
-sigma$const %<>% as.character %>% as.numeric
-
-```
-
-#### High Dimension
-
-##### `shrinkB`
-
-<br>\vspace{1cm}
-
-```{r scpmesim7, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
-d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim8, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
-d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-##### `shrinkBO`
-
-<br>\vspace{1cm}
-
-```{r scpmesim9, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
-d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim10, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
-d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-#### Low Dimension
-
-##### `shrinkB`
-
-<br>\vspace{1cm}
-
-```{r scpmesim11, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
-d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim12, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
-d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-#### `shrinkBO`
-
-<br>\vspace{1cm}
-
-```{r scpmesim13, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
-d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-```{r scpmesim14, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-# shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
-d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
-
-min = d[d$mean == min(d$mean),]
-
-d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
-
-```
-
-<br>\vspace{1cm}
-
-### Takeaways
-
-1.
-In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE.
-This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.
-
-2. In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.
-
-3. The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.
-
-4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)
-
-## Discussion
-
-The general optimization problem outlined in @molstad2017shrinking is to estimate $\hat{\Omega}$ such that
-
-\begin{equation}
-  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
-(\#eq:penloglik3)
-\end{equation}
-
-where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm.
-In addition, $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
-This objective function is a penalized log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$.
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\}
-(\#eq:penloglik3)
-\end{equation}
-
-where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$.
-Under this particular likelihood, it is assumed that each observation of $X_{i}$ in a sample size of size $n$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.
-
-This particular formulation for the penalty leads to many new, interesting, and novel estimators for $\Omega$.
-For instance, if in addition to $X$ we also observe $n$ copies of the random variable $Y$, we might set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$.
-In which case
-
-\begin{equation}
-P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1}
-(\#eq:pen3)
-\end{equation}
-
-This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$).
-We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.
-
-\begin{equation}
-P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
-(\#eq:pen4)
-\end{equation}
-
-In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
-Furthermore, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that
-
-\begin{equation}
-\begin{split}
-\hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\}
-(\#eq:penloglik4)
-\end{split}
-\end{equation}
-
-This estimator encourages the predicted values $\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}$ to be exactly equal to the observed responses $\mathbb{Y}$.
-We will name this estimator the *lasso SCPME estimator*.
-Note that in practice - for any of these estimators - we do not know the true covariance matrix $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ in its place.
-
-All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper.
-The augmented ADMM algorithm (details [here](https://mgallow.github.io/SCPME/articles/Details.html#augmented-admm-algorithm)) is the following:
-
-Set $k = 0$ and repeat steps 1-6 until convergence.
-
-1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}$
-
-2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
-
-3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
-
-4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)$
-
-5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
-
-6. Replace $k$ with $k + 1$.

### 2019-03-10 04-REGRESS.Rmd
added notations and restructured

--- 2018-08-06 08-SCPME-Simulations.Rmd
@@
-# `SCPME` Simulations
+# Regression Illustration
 
-## Estimator Comparison
+Talk about regression problem...
+
+## Simulations
 
 We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.
-
-<br>\vspace{1cm}
 
@@
 
-<br>\vspace{1cm}
-
 ### Data Generation
@@
 
-\[ \mathbb{Y} = \mathbb{X}\beta + \mathbb{E} \]
+\begin{equation}
+\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
+(\#eq:datalinregression)\notag
+\end{equation}
 
@@
 
-Then for $n$ independent, identically distributed samples:
-
-\[ X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right) \]
-
-\[ E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right) \]
+Then for $n$ independent, identically distributed samples, we have that $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$.
 
@@
 
-<br>\vspace{1cm}
-
 ### Plots
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim1, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F, fig.cap = "Figure caption here."}
+```{r scpmesim2, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim3, eval = T, echo = F}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim4, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim5, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim6, eval = T, echo = F}
 
@@
 ```
-
-<br>\vspace{1cm}
 
@@
 
-<br>\vspace{1cm}
-
-## Shrinking Covariance
-
-We compare the performance of the `shrinkB` and `shrinkBO` estimators when manually shrinking the sample covariance matrix of $X$ and $Y$ (denoted $\Sigma_{xy}$).
-Each data scenario was replicated a total of 20 times.
-
-<br>\vspace{1cm}
-
-### Models
+### Shrinking Covariance Models
 
@@
 
-\[ \mathbb{Y} = \mathbb{X}\beta + \mathbb{E} \]
+\begin{equation}
+\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
+(\#eq:datalinregression2)\notag
+\end{equation}
 
@@
 Note that prior to estimation, the intercept is removed by centering the data.
-
-<br>\vspace{1cm}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim7, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim8, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim9, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim10, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim11, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim12, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim13, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 
-```{r, eval = T, echo = F}
+```{r scpmesim14, eval = T, echo = F, fig.cap = "Figure caption here."}
 
@@
 4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)
+
+## Discussion
+
+The general optimization problem outlined in @molstad2017shrinking is to estimate $\hat{\Omega}$ such that
+
+\begin{equation}
+  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+(\#eq:penloglik3)\notag
+\end{equation}
+
+where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm.
+In addition, $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
+This objective function is a penalized log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$.
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\}
+(\#eq:penloglik4)\notag
+\end{equation}
+
+where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$.
+Under this particular likelihood, it is assumed that each observation of $X_{i}$ in a sample size of size $n$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.
+
+This particular formulation for the penalty leads to many new, interesting, and novel estimators for $\Omega$.
+For instance, if in addition to $X$ we also observe $n$ copies of the random variable $Y$, we might set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$.
+In which case
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1}
+(\#eq:pen3)\notag
+\end{equation}
+
+This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$).
+We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
+(\#eq:pen4)\notag
+\end{equation}
+
+In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
+Furthermore, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that
+
+\begin{equation}
+\begin{split}
+\hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\}
+(\#eq:penloglik5)\notag
+\end{split}
+\end{equation}
+
+This estimator encourages the predicted values $\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}$ to be exactly equal to the observed responses $\mathbb{Y}$.
+We will name this estimator the *lasso SCPME estimator*.
+Note that in practice - for any of these estimators - we do not know the true covariance matrix $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ in its place.
+
+All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper.
+The augmented ADMM algorithm (details [here](https://mgallow.github.io/SCPME/articles/Details.html#augmented-admm-algorithm)) is the following:
+
+Set $k = 0$ and repeat steps 1-6 until convergence.
+
+1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}$
+
+2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
+
+3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
+
+4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)$
+
+5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
+
+6. Replace $k$ with $k + 1$.

### 2019-03-10 05-appendix.Rmd
added notations and restructured

# (APPENDIX) Appendix {-}

# Appendix

## Proofs

### Proof of \@ref(eq:omegaalgo) {#proofomegaalgo}

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik)\notag
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
(\#eq:appendixomegagradient)\notag
\end{split}
\end{equation}

Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient. First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:

\begin{equation}
S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T}\notag
\end{equation}

This equivalence implies that

\begin{equation}
\phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1})\notag
\end{equation}

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{equation}
\begin{split}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{split}
\notag
\end{equation}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof)\notag
\end{equation}

### Proof of \@ref(eq:ZZalgo) {#proofZZalgo}

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik)\notag
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
(\#eq:appendixZZgradient)\notag
\end{split}
\end{equation}

where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right)
(\#eq:ZZsoftproof)\notag
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\begin{equation}
\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \notag
\end{equation}

- If $Z_{ij}^{k + 1} < 0$ then

\begin{equation}
\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \notag
\end{equation}

This implies that $\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
(\#eq:appendixZZproof)\notag
\end{split}
\end{equation}

where soft is the soft-thresholding function.

### Proof of \@ref(eq:dualresidual) {#proofdualresidual}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
(\#eq:appendixdualresidual)\notag
\end{split}
\end{equation}

### Proof of \@ref(eq:dualopt) {#proofdualopt}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:appendixdualopt)\notag
\end{split}
\end{equation}

### Proof of BLAHHHH

To see why this particular function was used, consider the Taylor's expansion of $\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2$:

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
(\#eq:taylors)\notag
\end{split}
\end{equation}

**Note:**

\begin{equation}
  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
(\#eq:gradient)\notag
\end{equation}

\begin{equation}
\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
(\#eq:hessian)\notag
\end{equation}

This implies that

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
(\#eq:penapprox)\notag
\end{split}
\end{equation}

Let us now plug in this equality into our optimization problem in step one:

\begin{equation}
\begin{split}
  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
 tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
(\#eq:omegaapprox)\notag
\end{split}
\end{equation}

where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.

### Proof of \@ref(eq:Omegak) {#proofOmegak}

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik2)\notag
\end{equation}

\begin{equation}
\begin{split}
  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
(\#eq:appendixomegagradient2)\notag
\end{split}
\end{equation}

Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to

\begin{equation}
S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
\end{equation}

We can then decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.

\begin{equation}
S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \notag
\end{equation}

This equivalence implies that

\begin{equation}
\phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \notag
\end{equation}

where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}$. Therefore

\begin{equation}
\begin{split}
  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
\end{split}
\notag
\end{equation}

In summary, if we decompose $S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof2)\notag
\end{equation}

### Proof of \@ref(eq:Zk) {#proofZk}

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik2)\notag
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
(\#eq:appendixZZgradient2)\notag
\end{split}
\end{equation}

where $\mbox{sign(Z)}$ is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right)
(\#eq:ZZsoftproof2)\notag
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\begin{equation}
\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \notag
\end{equation}

- If $Z_{ij}^{k + 1} < 0$ then

\begin{equation}
\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \notag
\end{equation}

This implies that $\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
(\#eq:appendixZZproof2)\notag
\end{split}
\end{equation}

where soft is the soft-thresholding function.

### Proof of \@ref(eq:stopproof) {#proofstopproof}

This residual is derived from the fact. Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
(\#eq:appendixstopproof)\notag
\end{split}
\end{equation}

### Proof of \@ref(eq:dualopt2) {#proofdualopt2}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:appendixdualopt2)\notag
\end{split}
\end{equation}

### Connection to joint log-likelihood

The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:penregression)\notag
\end{equation}

To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression)\notag
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$. These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form

\begin{equation}
Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
(\#eq:linnormal)\notag
\end{equation}

We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$. Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience. We will also let $f$ denote the probability distribution function for each respective variable.

\begin{equation}
\begin{split}
  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
(\#eq:jointlik)\notag
\end{split}
\end{equation}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:

\begin{equation}
\begin{split}
  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const. + \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
(\#eq:jointloglik)\notag
\end{split}
\end{equation}

**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.

\begin{equation}
\begin{split}
 \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
 &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
 \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
 (\#eq:gradient2)\notag
\end{split}
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
 &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
 &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
 &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
 \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow \hat{\mu}_{x} &= \bar{X}
(\#eq:gradient3)\notag
\end{split}
\end{equation}

Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.

Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$. This can be achieved by simply centering the data by the sample averages. Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
(\#eq:partialjointloglik)\notag
\end{split}
\end{equation}

where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:

\begin{equation}
\begin{split}
  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
(\#eq:omegajointloglik)\notag
\end{split}
\end{equation}

where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm. Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$. Therefore, we have that

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:omegajointmle)\notag
\end{equation}

Notice that this is exactly the ridge SCPME estimator!

### Takeaways from connection to joint log-likelihood

We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:

1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression2)\notag
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.

2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.

3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.

In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$

5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

Note that the only difference is in step 4.

There are a few takeaways we can make after revealing this connection. The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$. The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator. No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it. We show this below:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
(\#eq:penregression2)\notag
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
(\#eq:penregressionproof)\notag
\end{split}
\end{equation}

by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.

### 2019-03-10 06-ADMMsigma-Package.Rmd
added notations and restructured

--- 2019-01-14 05-ADMMsigma-Package.Rmd
@@
 `ADMMsigma` is an R package that estimates a penalized precision matrix, often denoted $\Omega$, via the alternating direction method of multipliers (ADMM) algorithm.
-Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user -- the primary goal of this package.
+Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user, which is the primary goal of this package.
 
@@
 
-* `ADMMsigma()` computes the estimated precision matrix (ridge, lasso, and elastic-net type regularization optional)
+* `ADMMsigma()` computes the estimated precision matrix via the ADMM algorithm (ridge, lasso, and elastic-net regularization optional)
 
@@
 
-* `plot.ADMMsigma()` produces a heat map or line graph for cross validation errors
+* `plot.ADMMsigma()` produces a heat map or optional line graph for cross validation errors
 
-* `plot.RIDGEsigma()` produces a heat map or line graph for cross validation errors
+* `plot.RIDGEsigma()` produces a heat map or optional line graph for cross validation errors
 
@@
 
-<br>\vspace{0.5cm}
 ```{r, eval = FALSE}
@@
 This package is hosted on Github at [github.com/MGallow/ADMMsigma](https://github.com/MGallow/ADMMsigma).
+The project website is located at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).
 
@@
 
-Here, the data matrix is $100 \times 5$ and generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$.
-A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal.
-That is, the precision matrix is sparse and the shrinkage penalty used here should prove useful.
+Here, we will use a $100 \times 5$ data matrix that is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$.
+A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal, which is useful for illustration purposes because the object is sparse (many zero entries) and the shrinkage penalty should prove useful.
 
@@
 
-We can also explicitly assume sparsity in our estimate - rather than let the package decide - by restricting the class of penalties to the lasso.
-We do this by simply setting `alpha = 1` in our function:
+We can also explicitly assume sparsity in our estimate rather than let the package decide by restricting the class of penalties to the lasso. We do this by simply setting `alpha = 1` in our function:
 
@@
 `ADMMsigma` also has the capability to provide plots for the cross validation errors.
-This allows the user to analyze and select the appropriate tuning parameters.
-In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection.
+This allows the user to analyze and manually select the appropriate tuning parameters.
+In the heatmap plot below, the bright, white areas of the heat map correspond to a better tuning parameter selection (low validation error).
 In the line graph, each line corresponds to a different $\alpha$ tuning parameter.
@@
 
-`ADMMsigma` has a number of more advanced options such as cross validation criteria, regularization path, and parallel processing that are explained in detail on the project website at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).
+`ADMMsigma` has a number of more advanced options such as cross validation criteria, regularization path, and parallel CV that are explained in more detail on the project website at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).

### 2019-03-10 07-SCPME-Package.Rmd
added notations and restructured

--- 2019-01-14 06-SCPME-Package.Rmd
@@
 
-where $\lambda > 0$ is a tuning parameter, $A, B, \mbox{ and } C$ are known matrices specified by the user, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
+where $\lambda > 0$ is a tuning parameter, $A, B, \mbox{ and } C$ are known, user-specified matrices, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
 
 This form of penalty leads to many new, interesting, and novel estimators for the precision matrix $\Omega$.
-In short, users can construct matrices $A, B, \mbox{ and } C$ so that emphasis is place on the sum, absolute value of a *characteristic* of $\Omega$.
-We will explore a few of these in the tutorial section.
+Users can construct matrices $A, B, \mbox{ and } C$ so that emphasis is placed on the sum, absolute value of a *characteristic* of $\Omega$.
+We will explore a few of these estimators in the tutorial section.
 
@@
 
-* `plot.shrink()` produces a heat map or line graph for cross validation errors
+* `plot.shrink()` produces a heat map or optional line graph for the cross validation errors
 
@@
 
-This package is hosted on Github at [github.com/MGallow/SCPME](https://github.com/MGallow/SCPME).
+This package is hosted on Github at [github.com/MGallow/SCPME](https://github.com/MGallow/SCPME). The project website is located at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).
 
@@
 
-The primary function is the `SCPME` package is simply `shrink()`.
+The primary function in the `SCPME` package is `shrink()`.
 The input values $X$ is an $n \times p$ data matrix so that there are $n$ rows each representing an observation and $p$ columns each representing a unique variable and $Y$ is an $n \times r$ response matrix where $r$ is the dimension of the response vector.
-By default, `SCPME` will estimate $\Omega$ using a lasso penalty ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$) and choose the optimal $\lambda$ tuning parameter that minimizes the mean squared prediction error for the regression of the variable $Y$ on $X$.
-If $Y$ is not provided (optional), then tuning parameter selection will be based on the validation likelihood.
-Note that $\Omega$ (perhaps better denoted here as $\Omega_{x}$) will only have meaningful shrinkage unless the data vector $X \in \mathbb{R^{p}}$ is multi-dimensional - that is, $p > 1$.
+By default, `SCPME` will estimate $\Omega$ using a lasso penalty ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$) and choose the optimal $\lambda$ tuning parameter that minimizes the mean squared prediction error for the regression of the variable $Y$ on $X$ (here $I_{p}$ denotes a $p$-dimension identity matrix).
+If $Y$ is not provided, then tuning parameter selection will be based on the validation likelihood.
+Note that $\Omega$ (perhaps better denoted here as $\Omega_{x}$) will only have meaningful shrinkage unless the data vector $X \in \mathbb{R^{p}}$ is multi-dimensional ($p > 1$).
 
-Here, in this example, the data matrix is $100 \times 5$ and the response is generated according to the following model:
+In this example, the data matrix is $100 \times 5$ and the response is generated according to the following model:
 
@@
 where $E_{i} \sim N\left( 0, 1 \right)$ and $X_{i}$ is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$.
-A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal.
-It is this oracle precision matrix that is our primary interest in estimating.
+A tapered covariance matrix has the property that its inverse - the precision matrix - is tri-diagonal.
+Estimating this oracle precision matrix well and efficiently will be our primary interest.
 In addition, $\beta$ is randomly generated and sparse.
@@
 set.seed(123)
-
-# generate data from a sparse oracle precision matrix.
-# we can use the built-in `data_gen` function
 
@@
 
+<br>\vspace{0.5cm}
 ```{r, message = FALSE, echo = TRUE}
@@
 Notice here that the estimated precision matrix is *not* sparse.
-This is due to the fact that our cross validation criteria is the mean-squared prediction.
-We can estimate a new precision matrix using the validation likelihood as criteria with the following command:
+This is due to the fact that our cross validation criteria is the mean-squared prediction error.
+We can estimate a new precision matrix using the validation likelihood as the cross validation criteria with the following command:
 
@@
 
-Recall that all of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in $\Omega$ ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$).
-In effect, this penalty embeds an assumption in our estimate that the true $\Omega$ is sparse.
+All of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in $\Omega$ ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$).
+In effect, this penalty embeds an assumption in our estimate that the true population precision matrix, $\Omega$, is sparse.
 The flexibility of the penalty described in @molstad2017shrinking allows us to make other assumptions as well.
 For instance, in the penalty we could set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$.
-In which case
+In which case our penalty function
 
@@
 Note that we specified the maximum `lam` value in the previous function to expand the tuning parameter grid.
-Conveniently, with these settings, the augmented ADMM algorithm also solves for the estimated $\beta$ coefficient matrix simultaneously:
+With these settings, the augmented ADMM algorithm also solves for the estimated $\beta$ coefficient matrix simultaneously:
 
@@
 
-Another possible penalty is to set $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.
-That is, the penalty $P$, is constructed as follows:
+Another possible penalty is to set $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the covariance matrix of $X$ and $Y$. That is, the penalty $P$, is constructed as
 
@@
 
-In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
+In this case, we are equally penalizing the sum, absolute values of entries in $\beta$ *and* $\Omega$ which embeds an assumption that $\beta$ and $\Omega$ are both sparse.
 
@@
 
-`SCPME` also has the capability to provide plots (heatmap and line graph) for the cross validation errors.
-In the heatmap plot below, the more bright (white) areas of the heat map correspond to a better tuning parameter selection.
+`SCPME` also has the capability to provide plots (heatmaps and line graphs) for the cross validation errors.
+In the heatmap plot below, the more bright, white areas correspond to a better tuning parameter selection (lower cross validation error).
 
@@
 
-`SCPME` has a number of more advanced options such as various convergence criteria and parallel processing that are explained in detail on the project website at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).
+`SCPME` has a number of more advanced options including alternative convergence criteria and parallel CV that are explained in detail on the project website at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).

### 2019-03-10 Manuscript.Rmd
added notations and restructured

--- 
title: "Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression"
author: "Matt Galloway"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::pdf_book:
    toc_depth: 2
    fig_caption: yes
    includes:
      in_header: preamble.tex
  bookdown::gitbook:
    toc_depth: 2
documentclass: report
bibliography: [lib.bib, packages.bib]
#bibliography: lib.bib
biblio-style: apalike
#geometry: "left=4cm, right=3cm, top=2.5cm, bottom=2.5cm"
#geometry: "left = 1.5in, right = 1in, top = 1in, bottom = 1in"
geometry: "left = 1in, right = 1in, top = 1in, bottom = 1in"
colorlinks: yes
lot: no
lof: no
toc_appendix: yes
fontsize: 11pt
linestretch: 1.5
link-citations: yes
url: 'http://mattxgalloway.com/oral_manuscript/'
github-repo: MGallow/oral_manuscript
description: "Matt Galloway's Master's thesis."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE, out.width = "90%", fig.align = "center", out.extra = "")

```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), "glasso", "ADMMsigma", "SCPME"), 'packages.bib')

```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

In many statistical applications, estimating the covariance matrix, $\Sigma$, for a set of random variables is a critical task. The covariance matrix is useful because it characterizes the *relationship* between variables. For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form

\begin{equation}
\Sigma_{xyz} = \begin{pmatrix}
1 & 0 & 0.5 \\ 
0 & 1 & 0 \\ 
0.5 & 0 & 1
\end{pmatrix}
(\#eq:ex)\notag
\end{equation}

We can gather valuable information from this matrix. First of all, we know that each of the variables has an equal variance of 1. Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0. This implies that any information in $X$ is useless in trying to gather information about $Y$. Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.

Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging. For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.

### references

The reference we need here is @molstad2017shrinking!

1. From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated. For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors. Many authors have proposed methods that directly estimate this characteristic @cai2011direct; @fan2012road; @mai2012direct."

2. From @molstad2017shrinking: "@chen2016regularized proposed a method for estimating the characteristic $\Omega_{*}\mu_{*}$ directly, but like the direct linear discriminant methods, this apporach does not lead to an estimate of $\Omega_{*}$."

3. Discuss linear regression application.... where $\beta = \Omega_{*}\Sigma_{*XY}$. Like @witten2009covariance, this approach estimates the regression coefficients "using shrinkage estimators of the marginal precision matrix for the predictors".

- Guide

- Model and notation

## Outline

- Why do we care about covariance matrices? Covariance matrices are an object that summarizes the relationship between variables.

- What is a precision matrix? Precision matrix is the inverse of a covariance matrix.

- Precision matrices are powerful, essential in representing relationships in variables

- In fact, required to be estimated to fit many statistical models.

- That is, we must provide an object that accurately summarizes the relationship and interaction between variables in our model.

- Many proposed shrinkage estimators when p is particularly large. Shrinkage.

- However, to fit these models, Molstad and Rothman focused on the fact that onnly a "characteristic" of a precision matrix is required to fit these models. "We propose a framework to shrink a user-specified characteristic of a precision matrix estimator."

- For instance, LDA, linear regression, ...

- Their approach/methodology was published in BLAH. Shrinking characteristic of precision matrix estimators.

- BREAK

- We wanted to explore the regression application that was mentioned but not pursued/investigated

- This document will outline the research and work leading up to that

- The document is outlined as follows...

- We will begin chapter 2 with a brief introduction to precision matrix estimation. This will include mentions of estimation methods/approaches and we will spend a particular amount of time elaborating on one approach which is estimation via the ADMM algorithm. This dicussion will be useful when we circle back to SCPME, the regression application, and the augmented ADMM algorithm developed in BLAH.

- Lastly, the document will end with two brief tutorials for the R packages ADMMsigma and SCPME. These packages, developed by myself, will be mentioned throughout the document and were instrumental in this pursued line of research and facilitated many simulations and research direction explored throughout. Both packages have since been published on CRAN

### Notation and Definitions

For strictly positive integers $n$ and $p$, we will denote $\mathbb{R}^{n \times p}$ as the class of real matrices with dimenson $n \times p$. The class of real, symmetric matrices with dimension $p \times p$ will be denoted as $\mathbb{S}^{p}$ and $\mathbb{S}^{p}_{+}$ if we further require the object to be positive definite. The sample size in a given data set will most often correspond with $n$ and $p$ will correspond with the dimension of the prediction vector. If the dimension of the response vector exceeds one, we will denote it as $r$.

Most matrices will take the form of either $\Sigma$, which should be taken to represent the population covariance matrix, or $\Omega$, which should be taken to represent the population *precision* matrix. Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$). We will sometimes add a subscript star if the object is oracle - or known- a priori ($\Omega_{*}$) and the population object's estimator that minimizes/maximizes a pre-specified objective function will have a hat attached to it ($\hat{\Omega}$).

There will be significant matrix algebra notation throughout the document. The trace operator which sums the diagonal elements of a matrix will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$. The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$. The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$. Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

<!--chapter:end:01-intro.Rmd-->

# Precision Matrix Estimation

### Literature Review?

- Articles that review covariance and precision matrix estimation in high dimensional settings are @pourahmadi2013high and @fan2016overview.

- The person who initially proposed the lasso-penalized gaussian likelihood precision matrix estimation is @yuan2007model.

- Other authors who have proposed methods with non-lasso penalizations are (Frobenius norms) @witten2009covariance, @rothman2014existence, (non-convex penalties) @lam2009sparsistency, and @fan2009network.

- Standard alternating direction method of multipliers approaches are found in @boyd11distributed.

- ADMM with modification based on majorize-minimize principle is found in @lange2016mm.

- Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.

- L1-penalized gaussian likelihood precision matrix estimator (@yuan2007model; @rothman2008sparse; @friedman2008sparse).

## Background

Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$. That is, $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.

Because we assume independence, we know that the probability of observing these specific observations $X_{1}, ..., X_{n}$ is equal to

\begin{equation} 
\begin{split}
  f(X_{1}, ..., X_{n}; \mu, \Omega^{-1}) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
  &= (2\pi)^{-np/2}\left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Omega \right]
\end{split}
(\#eq:normallik)\notag
\end{equation}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Omega$ is equal to the following:

\begin{equation}
  l(\mu, \Omega | X) = const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
(\#eq:normalloglik)\notag
\end{equation}

If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$. However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well. We can also find a maximum likelihood estimator:

\begin{equation}
\begin{split}
\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right] \right\} \\
  &= \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]^{-1}
\end{split}
(\#eq:omegamle)\notag
\end{equation}

By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Omega$ is the inverse our usual sample estimator for the covariance matrix, denoted here as $S^{-1}$. It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:

\begin{equation}
\hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
(\#eq:omegamlesimple)
\end{equation}

so that $\hat{\Omega}^{MLE} = S^{-1}$. Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood. Both procedures will result in the same estimate.].

As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
(\#eq:omegapen)
\end{equation}

$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$. These penalties are the ridge and lasso, respectively.

## ADMM algorithm

Many efficient methods have been proposed to solve for $\hat{\Omega}$ when $\alpha = 1$. The most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse. However, no methods (to the best of my knowledge) have estimated $\Omega$ when $\alpha \in (0, 1)$. We will use the alternating direction method of multipliers (ADMM) algorithm to do so.

As the authors state in @boyd2011distributed, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers." For our purposes, we will only focus on the ADMM algorithm but it is encouraged to read the original text from Boyd and others for a complete introduction to the other two methods.

In general, suppose we want to solve an optimization problem of the following form:

\begin{equation}
\begin{split}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{split}
(\#eq:boyd)\notag
\end{equation}

where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are assumed to be convex functions (following @boyd2011distributed, the estimation procedure will be introduced in vector form though we could just as easily take $x$ and $z$ to be matrices). In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods. For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem. In all cases, our goal is to find $x^{*} \in \mathbb{R}^{n}$ and $z^{*} \in \mathbb{R}^{m}$ that achieves the infimum $p^{*}$:

\begin{equation}
p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\}
(\#eq:infimum)\notag
\end{equation}

To do so, the ADMM algorithm uses the *augmented lagrangian*

\begin{equation}
L_{\rho}(x, z, y) = f(x) + g(z) + y'(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2}
(\#eq:auglagrange)\notag
\end{equation}

where $y \in \mathbb{R}^{p}$ is the lagrange multiplier and $\rho > 0$ is a scalar. Clearly any minimizer, $p^{*}$, under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point $(x, z)$ satisfies the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.

The algorithm consists of the following repeated iterations:

\begin{equation}
\begin{split}
  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
\end{split}  
(\#eq:admmalgo)\notag
\end{equation}

In the context of precision matrix estimation, we can let $f$ be equal to the non-penalized likelihood, $g$ be equal to $P\left( \Omega \right)$, and use the constraint $\Omega$ equal to some $Z$ so that the lagrangian is

\begin{equation}
L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
(\#eq:lagrange2)\notag
\end{equation}

and the augmented lagrangian is

\begin{equation}
L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
(\#eq:auglagrange2)\notag
\end{equation}

\vspace{3cm}

In the `ADMMsigma` package, we instead take

\begin{equation}
P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
(\#eq:penelastic)\notag
\end{equation}

so that solving the full penalized log-likelihood for $\Omega$ results in solving

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
(\#eq:optimelastic)
\end{equation}

where $0 \leq \alpha \leq 1$. This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`. Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty. Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.

The ADMM algorithm is now the following:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} (\#eq:omegaauglagrangee) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} (\#eq:ZZauglagrange) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) (\#eq:lamauglagrange)
\end{align}

### Algorithm

Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}$, and $\rho$. Repeat steps 1-3 until convergence:

1. Decompose $S + \Lambda^{k} - \rho Z^{k} = VQV'$ via spectral decomposition^[Proof of \@ref(eq:omegaalgo) in section \@ref(proofomegaalgo).]. Then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V'
(\#eq:omegaalgo)
\end{equation}

2. Elementwise soft-thresholding for all $i = 1,..., p$ and $j = 1,..., p$^[Proof of \@ref(eq:ZZalgo) in section \@ref(proofZZalgo).].

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
(\#eq:ZZalgo)
\end{split}
\end{equation}

3. Update $\Lambda^{k + 1}$.

\begin{equation}
\Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
(\#eq:lamalgo)\notag
\end{equation}

where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.

### Scaled-Form ADMM

There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable ($\Lambda^{k}$). Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.

\begin{equation}
\begin{split}
  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
(\#eq:scaled)\notag
\end{split}
\end{equation}

Therefore, a scaled-form can now be written as

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} (\#eq:omegascaled)\notag \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} (\#eq:ZZscaled)\notag \\
  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} (\#eq:Uscaled)\notag
\end{align}

And more generally (in vector form),

\begin{align}
  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:xscaled)\notag \\
  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:zscaled)\notag \\
  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c (\#eq:uscaled)\notag
\end{align}

Note that there are limitations to using this method. Because the dual variable is scaled by $\rho$ (the step size), this form limits one to using a constant step size without making further adjustments to $U^{k}$. It has been shown in the literature that a dynamic step size (like the one used in `ADMMsigma`) can significantly reduce the number of iterations required for convergence.

### Stopping Criterion

In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to precision matrix estimation.

Below we have three optimality conditions:

1. Primal:

\begin{equation}
\Omega^{k + 1} - Z^{k + 1} = 0
(\#eq:admmprimal)\notag
\end{equation}

2. Dual:

\begin{equation}
\begin{split}
  0 &\in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \\
  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
(\#eq:admmdual)\notag
\end{split}
\end{equation}

The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).

We will define the left-hand side of the first condition as the primal residual $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$. At convergence, optimality conditions require that $r^{k + 1} \approx 0$. The second residual we will define is the dual residual $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$. This residual is derived from the following:

Because $\Omega^{k + 1}$ is the minimizer of the augmented lagragian^[Proof of \@ref(eq:dualresidual) in section \@ref(proofdualresidual).], this implies that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ which further implies that

\begin{equation}
0 \in \rho\left( Z^{k + 1} - Z^{k} \right)
(\#eq:dualresidual)
\end{equation}

Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt) in section \@ref(proofdualopt).]:

\begin{equation}
\begin{split}
  0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:dualopt)
\end{split}
\end{equation}

One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where

\begin{equation}
\begin{split}
  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
(\#eq:admmstopping)\notag
\end{split}
\end{equation}

## Simulations

In the simulations below, we generate data from a number of different oracle precision matrices with various structures. For each data-generating procedure, the `ADMMsigma()` function was run using 5-fold cross validation. After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results below the top figure). These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure).

We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.

HOW DID WE GENERATE THE DATA?

### Plots

#### Compound Symmetric: P = 100, N = 50

```{r, message = FALSE, echo = TRUE, eval = FALSE}

# oracle precision matrix
Omega = matrix(0.9, ncol = 100, nrow = 100)
diag(Omega = 1)

# generate covariance matrix
S = qr.solve(Omega)

# generate data
Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```
<br>\vspace{0.5cm}

<!-- <center> -->
<!-- ![Figure caption here.](images/compound_N50_P100.png){ -->
<!-- width=90% } -->
<!-- </center> -->

```{r admmsim1, eval = T, echo = F, fig.cap = "Figure caption here."}

knitr::include_graphics("images/compound_N50_P100.png")

```

#### Compound Symmetric: P = 10, N = 1000

```{r, message = FALSE, echo = TRUE, eval = FALSE}

# oracle precision matrix
Omega = matrix(0.9, ncol = 10, nrow = 10)
diag(Omega = 1)

# generate covariance matrix
S = qr.solve(Omega)

# generate data
Z = matrix(rnorm(10*1000), nrow = 1000, ncol = 10)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```
<br>\vspace{0.5cm}

<!-- <center> -->
<!-- ![Figure caption here.](images/compound_N1000_P10.png){ -->
<!-- width=90% } -->
<!-- </center> -->

```{r admmsim2, eval = T, echo = F, fig.cap = "Figure caption here."}

knitr::include_graphics("images/compound_N1000_P10.png")

```

<!-- #### Dense: P = 100, N = 50 -->

<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->

<!-- # generate eigen values -->
<!-- eigen = c(rep(1000, 5, rep(1, 100 - 5))) -->

<!-- # randomly generate orthogonal basis (via QR) -->
<!-- Q = matrix(rnorm(100*100), nrow = 100, ncol = 100) %>% qr %>% qr.Q -->

<!-- # generate covariance matrix -->
<!-- S = Q %*% diag(eigen) %*% t(Q) -->

<!-- # generate data -->
<!-- Z = matrix(rnorm(100*50), nrow = 50, ncol = 100) -->
<!-- out = eigen(S, symmetric = TRUE) -->
<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
<!-- X = Z %*% S.sqrt -->

<!-- ``` -->
<!-- <br>\vspace{0.5cm} -->

<!-- <!-- <center> --> -->
<!-- <!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ --> -->
<!-- <!-- width=90% } --> -->
<!-- <!-- </center> --> -->
<!-- <!-- } --> -->

<!-- ```{r admmsim3, eval = T, echo = F, fig.cap = "Figure caption here."} -->

<!-- knitr::include_graphics("images/repsKLdenseQR_N50_P100.png") -->

<!-- ``` -->

<!-- #### Dense: P = 10, N = 50 -->

<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->

<!-- # generate eigen values -->
<!-- eigen = c(rep(1000, 5, rep(1, 10 - 5))) -->

<!-- # randomly generate orthogonal basis (via QR) -->
<!-- Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q -->

<!-- # generate covariance matrix -->
<!-- S = Q %*% diag(eigen) %*% t(Q) -->

<!-- # generate data -->
<!-- Z = matrix(rnorm(10*50), nrow = 50, ncol = 10) -->
<!-- out = eigen(S, symmetric = TRUE) -->
<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
<!-- X = Z %*% S.sqrt -->

<!-- ``` -->
<!-- <br>\vspace{0.5cm} -->

<!-- <!-- <center> --> -->
<!-- <!-- ![Figure caption here.](images/repsKLdense_N50_P10.png){ --> -->
<!-- <!-- width=90% } --> -->
<!-- <!-- </center> --> -->

<!-- ```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."} -->

<!-- knitr::include_graphics("images/repsKLdense_N50_P10.png") -->

<!-- ``` -->

#### Tridiagonal: P = 100, N = 50

```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}

# generate covariance matrix
# (can confirm inverse is tri-diagonal)
S = matrix(0, nrow = 100, ncol = 100)
for (i in 1:100){
  for (j in 1:100){
    S[i, j] = 0.7^abs(i - j)
  }
}

# generate data
Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```
<br>\vspace{0.5cm}

<!-- <center> -->
<!-- ![Figure caption here.](images/repsKLtridiag_N50_P100.png){ -->
<!-- width=90% } -->
<!-- </center> -->

```{r admmsim5, eval = T, echo = F, fig.cap = "Figure caption here."}

knitr::include_graphics("images/repsKLtridiag_N50_P100.png")

```

<!--chapter:end:02-PME.Rmd-->

# SCPME

### literature review?

- A similar estimator was proposed by @dalal2017sparse when $C = 0$.

- - Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.

###  other stuff

The penalty proposed by @molstad2017shrinking is one of the following form:

\begin{equation}
P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
(\#eq:pen2)
\end{equation}

where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user. Solving the full penalized log-likelihood for $\Omega$ results in solving

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
(\#eq:omegaloglik2)
\end{equation}

This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$. This type of penalty leads to many new, interesting, and novel estimators for $\Omega$. An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$. This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$. Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$

We will explore how to solve for $\hat{\Omega}$ in the next section.

## Augmented ADMM Algorithm

*This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm. I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.*

The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications. Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) (\#eq:omegaauglagrange2)\notag \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) (\#eq:ZZauglagrange2)\notag \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamauglagrange2)\notag
\end{align}

where $L_{p}(\cdot)$ is the *augmented lagrangian* defined as

\begin{equation}
L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
(\#eq:auglagrange2)
\end{equation}

with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$. However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.

The approximating function is defined as

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)\notag
(\#eq:approx)
\end{split}
\end{equation}

where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$, $\otimes$ is the Kronecker product, and $\tau$ is chosen such that $Q$ is positive definite. Note that if $Q$ is positive definite (p.d.), then

\begin{equation}
\frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0
(\#eq:pd)\notag
\end{equation}

since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$. Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Proof of BLAH in section BLAHHH].

The *augmented ADMM* algorithm is the following:

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} (\#eq:omegaaugadmm)\notag \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} (\#eq:ZZaugadmm)\notag \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamaugadmm)\notag
\end{align}

### Algorithm

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k}$.

\begin{equation}
G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}
(\#eq:Gk)\notag
\end{equation}

2. Via spectral decomposition, decompose

\begin{equation}
S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}
(\#eq:VQV)\notag
\end{equation}

3. Update $\Omega^{k + 1}$.^[Proof of \@ref(eq:Omegak) in section \@ref(proofOmegak)]

\begin{equation}
\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)
(\#eq:Omegak)
\end{equation}

4. Update $Z^{k + 1}$.^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)]

\begin{equation}
Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)
(\#eq:Zk)
\end{equation}

5. Update $Y^{k + 1}$.

\begin{equation}
Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
(\#eq:Yk)\notag
\end{equation}

6. Replace $k$ with $k + 1$.

The soft-thresholding function is defined as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.

### Stopping Criterion

In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to the SCPME method.

Below we have three optimality conditions:

1. Primal:

\begin{equation}
A\Omega^{k + 1}B - Z^{k + 1} - C = 0
(\#eq:scpmeprimal)\notag
\end{equation}

2. Dual:

\begin{equation}
\begin{split}
  0 &\in \partial f\left(\Omega^{k + 1}\right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) \\
  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
(\#eq:scpmedual)\notag
\end{split}
\end{equation}

The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).

We will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$. At convergence, the optimality conditions require that $r^{k + 1} \approx 0$. The second residual we will define is the dual residual^[Proof of \@ref(eq:stopproof) in section \@ref(proofstopproof).]:

\begin{equation}
s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
(\#eq:stopproof)\notag
\end{equation}

Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$. Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt2) in section \@ref(proofdualopt2)].

\begin{equation}
\begin{split}
  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
(\#eq:dualopt2)\notag
\end{split}
\end{equation}

One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
(\#eq:scpmestopping)\notag
\end{split}
\end{equation}

<!--chapter:end:03-SCPME.Rmd-->

# Regression Illustration

Talk about regression problem...

## Simulations

We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.

### Models

In the following estimators, let the superscript * denote the oracle estimator:

 - `OLS` = ordinary least squares estimator in *low* dimensional setting and Moore-Penrose estimator in a *high* ($p >> n$) dimensional setting

 - `ridge` = ridge regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `lasso` = lasso regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV

 - `oracleB` = oracle estimator with the true $\beta^{*}$ known ($\left\| Y - X\beta^{*} \right\|_{F}^{2}$)

 - `oracleO` = oracle estimator with the true $\Omega^{*}$ known ($\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}$)

 - `oracleS` = oracle estimator with the true $\Sigma_{xy}^{*}$ known and sample estimator for $\Omega$ ($\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}$)

 - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)

 - `shrinkBS` = shrinking characteristics regression estimator with oracle cross-covariance where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$)

 - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)

 - `glasso` = lasso penalized precision matrix where optimal tuning parameter is chosen to maximize log-likelihood via 3-fold CV.

### Data Generation

Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that

\begin{equation}
\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
(\#eq:datalinregression)\notag
\end{equation}

These values are generated in the following way:

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1. In effect, each $\beta$ entry is turned off with equal probability.

Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse).

Then for $n$ independent, identically distributed samples, we have that $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$.

If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.

An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$). For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).

Possible parameters in simulation:

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag")

Note that prior to estimation, the intercept is removed by centering the data.

### Plots

#### High Dimension

Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE). Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.

```{r scpmesim1, eval = T, echo = F, fig.cap = "Figure caption here."}

# load data
load("images/sim6.Rdata")

# set P to numeric 
sim6$P %<>% as.character %>% as.numeric

# ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r scpmesim2, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = "tridiag"**

```{r scpmesim3, eval = T, echo = F}

# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")

```

<br>\vspace{1cm}

#### Low Dimension

```{r scpmesim4, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

```{r scpmesim5, eval = T, echo = F, fig.cap = "Figure caption here."}

# ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag")
sim6 %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)")

```

<br>\vspace{1cm}

**Notable: N = 1000, P = 150, R = 5, sparse = 0.5, sigma = "tridiag"**

```{r scpmesim6, eval = T, echo = F}

# ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5)
sim6 %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "Table caption here.")

```

### Takeaways

1. In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$. It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.

2. In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS. The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.

3. When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.

4. It is interesting that `oracleO` performed worse than `oracleS` in the final table. It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.

### Shrinking Covariance Models

In the following estimators, let the superscript * denote the oracle estimator:

 - `shrinkB` = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$)

 - `shrinkBO` = shrinking characteristics estimator that penalizes the sum of the absolute values of $\beta = \Omega\Sigma_{xy}$ *and* $\Omega$ (penalty: $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$)

For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$. We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.

### Data Generation

Let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that

\begin{equation}
\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
(\#eq:datalinregression2)\notag
\end{equation}

These values are generated in the following way:

Let $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $pr$ random bernoulli draws with `sparse` probability being equal to 1. In effect, each $\beta$ entry is turned off with equal probability.

Now, if `sigma = "tridiag"` then $\Sigma_{xx}$ and $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively. This ensures that the inverses will be tridiagonal (sparse).

Then for $n$ independent, identically distributed samples, we have that $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$.

If `sigma = "compound"` then the data is generated similarly but $\Omega_{xx} \equiv \Sigma_{xx}^{-1}$ and $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}$ both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.

An additional 1000 samples will be generated for the testing set -- regardless of the training set size ($n$). For instance, in the 3-fold cross validation procedure where `n = 100` and `p = 100`, 1000 samples would be set aside for later testing and $100*(2/3)$ samples would be used for training in each fold (ie: high dimensional setting).

Possible parameters in simulation:

 - `reps` = 20
 - `n` = (100, 1000)
 - `p` = (10, 50, 100, 150, 200)
 - `r` = c(1, 5, 10)
 - `sparse` = c(0.5)
 - `sigma` = c("tridiag", "compound")

Note that prior to estimation, the intercept is removed by centering the data.

### Plots

```{r, eval = T, echo = F}

# load data
load("images/sigma.Rdata")

# design color palette
bluetowhite <- c("#000E29", "white")

# change to numeric
sigma$lam %<>% as.character %>% as.numeric
sigma$const %<>% as.character %>% as.numeric

```

#### High Dimension

##### `shrinkB`

<br>\vspace{1cm}

```{r scpmesim7, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim8, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

##### `shrinkBO`

<br>\vspace{1cm}

```{r scpmesim9, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim10, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound")
d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

#### Low Dimension

##### `shrinkB`

<br>\vspace{1cm}

```{r scpmesim11, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim12, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

#### `shrinkBO`

<br>\vspace{1cm}

```{r scpmesim13, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

```{r scpmesim14, eval = T, echo = F, fig.cap = "Figure caption here."}

# shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound")
d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

min = d[d$mean == min(d$mean),]

d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))

```

<br>\vspace{1cm}

### Takeaways

1. In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE. This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.

2. In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.

3. The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.

4. The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)

## Discussion

The general optimization problem outlined in @molstad2017shrinking is to estimate $\hat{\Omega}$ such that

\begin{equation}
  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
(\#eq:penloglik3)\notag
\end{equation}

where $S$ is the sample covariance of $X \in \mathbb{R}^{p}$ (denominator $n$) and $\left\| \cdot \right\|_{1}$ denotes the $L_{1}$-norm. In addition, $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user. This objective function is a penalized log-likelihood for the marginal precision matrix of $X$, which we denote here as $\Omega \equiv \Sigma_{xx}^{-1}$.

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\}
(\#eq:penloglik4)\notag
\end{equation}

where $P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}$. Under this particular likelihood, it is assumed that each observation of $X_{i}$ in a sample size of size $n$ follows a $p$-variate normal distribution (ie: $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.

This particular formulation for the penalty leads to many new, interesting, and novel estimators for $\Omega$. For instance, if in addition to $X$ we also observe $n$ copies of the random variable $Y$, we might set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$. In which case

\begin{equation}
P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1}
(\#eq:pen3)\notag
\end{equation}

This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). We could also take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix (dimension $p$) is appended to the covariance matrix of $X$ and $Y$.

\begin{equation}
P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
(\#eq:pen4)\notag
\end{equation}

In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$. Furthermore, if we let $\mathbb{X} \in \mathbb{R}^{n \times p}$ be a matrix with rows $X_{i} - \bar{X}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ be a matrix with rows $Y_{i} - \bar{Y}$, we might also take $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$ so that

\begin{equation}
\begin{split}
\hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\}
(\#eq:penloglik5)\notag
\end{split}
\end{equation}

This estimator encourages the predicted values $\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}$ to be exactly equal to the observed responses $\mathbb{Y}$. We will name this estimator the *lasso SCPME estimator*. Note that in practice - for any of these estimators - we do not know the true covariance matrix $\Sigma_{xy}$ but we could provide the sample estimate $\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n$ in its place.

All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper. The augmented ADMM algorithm (details [here](https://mgallow.github.io/SCPME/articles/Details.html#augmented-admm-algorithm)) is the following:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)$

5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

<!--chapter:end:04-REGRESS.Rmd-->

# (APPENDIX) Appendix {-}

# Appendix

## Proofs

### Proof of \@ref(eq:omegaalgo) {#proofomegaalgo}

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik)\notag
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
(\#eq:appendixomegagradient)\notag
\end{split}
\end{equation}

Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient. First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:

\begin{equation}
S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T}\notag
\end{equation}

This equivalence implies that

\begin{equation}
\phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1})\notag
\end{equation}

where $\phi_{j}(\cdot)$ is the $j$th eigen value.

\begin{equation}
\begin{split}
  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
\end{split}
\notag
\end{equation}

In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof)\notag
\end{equation}

### Proof of \@ref(eq:ZZalgo) {#proofZZalgo}

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik)\notag
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
(\#eq:appendixZZgradient)\notag
\end{split}
\end{equation}

where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right)
(\#eq:ZZsoftproof)\notag
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\begin{equation}
\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \notag
\end{equation}

- If $Z_{ij}^{k + 1} < 0$ then

\begin{equation}
\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \notag
\end{equation}

This implies that $\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
(\#eq:appendixZZproof)\notag
\end{split}
\end{equation}

where soft is the soft-thresholding function.

### Proof of \@ref(eq:dualresidual) {#proofdualresidual}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
(\#eq:appendixdualresidual)\notag
\end{split}
\end{equation}

### Proof of \@ref(eq:dualopt) {#proofdualopt}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:appendixdualopt)\notag
\end{split}
\end{equation}

### Proof of BLAHHHH

To see why this particular function was used, consider the Taylor's expansion of $\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2$:

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
(\#eq:taylors)\notag
\end{split}
\end{equation}

**Note:**

\begin{equation}
  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
(\#eq:gradient)\notag
\end{equation}

\begin{equation}
\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
(\#eq:hessian)\notag
\end{equation}

This implies that

\begin{equation}
\begin{split}
  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
(\#eq:penapprox)\notag
\end{split}
\end{equation}

Let us now plug in this equality into our optimization problem in step one:

\begin{equation}
\begin{split}
  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
 tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
 tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
(\#eq:omegaapprox)\notag
\end{split}
\end{equation}

where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.

### Proof of \@ref(eq:Omegak) {#proofOmegak}

\begin{equation}
\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}
(\#eq:appendixomegaloglik2)\notag
\end{equation}

\begin{equation}
\begin{split}
  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
(\#eq:appendixomegagradient2)\notag
\end{split}
\end{equation}

Note that we need to honor the symmetric constraint given by $\Omega$. By setting the gradient equal to zero and multiplying all off-diagonal elements by $1/2$, this simplifies to

\begin{equation}
S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
\end{equation}

We can then decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.

\begin{equation}
S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \notag
\end{equation}

This equivalence implies that

\begin{equation}
\phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \notag
\end{equation}

where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}$. Therefore

\begin{equation}
\begin{split}
  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
\end{split}
\notag
\end{equation}

In summary, if we decompose $S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ then

\begin{equation}
\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T}
(\#eq:appendixomegaproof2)\notag
\end{equation}

### Proof of \@ref(eq:Zk) {#proofZk}

\begin{equation}
Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
(\#eq:appendixZZloglik2)\notag
\end{equation}

\begin{equation}
\begin{split}
  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
(\#eq:appendixZZgradient2)\notag
\end{split}
\end{equation}

where $\mbox{sign(Z)}$ is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:

\begin{equation}
Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right)
(\#eq:ZZsoftproof2)\notag
\end{equation}

for all $i = 1,..., p$ and $j = 1,..., p$. We observe two scenarios:

- If $Z_{ij}^{k + 1} > 0$ then

\begin{equation}
\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \notag
\end{equation}

- If $Z_{ij}^{k + 1} < 0$ then

\begin{equation}
\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \notag
\end{equation}

This implies that $\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at

\begin{equation}
\begin{split}
Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
(\#eq:appendixZZproof2)\notag
\end{split}
\end{equation}

where soft is the soft-thresholding function.

### Proof of \@ref(eq:stopproof) {#proofstopproof}

This residual is derived from the fact. Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
(\#eq:appendixstopproof)\notag
\end{split}
\end{equation}

### Proof of \@ref(eq:dualopt2) {#proofdualopt2}

\begin{equation}
\begin{split}
  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
(\#eq:appendixdualopt2)\notag
\end{split}
\end{equation}

### Connection to joint log-likelihood

The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:penregression)\notag
\end{equation}

To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression)\notag
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$. These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form

\begin{equation}
Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
(\#eq:linnormal)\notag
\end{equation}

We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$. Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience. We will also let $f$ denote the probability distribution function for each respective variable.

\begin{equation}
\begin{split}
  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
(\#eq:jointlik)\notag
\end{split}
\end{equation}

where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:

\begin{equation}
\begin{split}
  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const. + \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
(\#eq:jointloglik)\notag
\end{split}
\end{equation}

**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.

\begin{equation}
\begin{split}
 \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
 &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
 \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
 (\#eq:gradient2)\notag
\end{split}
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
 &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
 &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
 &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
 \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
 \Rightarrow \hat{\mu}_{x} &= \bar{X}
(\#eq:gradient3)\notag
\end{split}
\end{equation}

Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.

Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$. This can be achieved by simply centering the data by the sample averages. Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
  &= const. + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
(\#eq:partialjointloglik)\notag
\end{split}
\end{equation}

where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:

\begin{equation}
\begin{split}
  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
(\#eq:omegajointloglik)\notag
\end{split}
\end{equation}

where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm. Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$. Therefore, we have that

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
(\#eq:omegajointmle)\notag
\end{equation}

Notice that this is exactly the ridge SCPME estimator!

### Takeaways from connection to joint log-likelihood

We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:

1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that

\begin{equation}
Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
(\#eq:linregression2)\notag
\end{equation}

where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.

2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.

3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.

In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:

Set $k = 0$ and repeat steps 1-6 until convergence.

1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$

2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).

3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$

4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$

5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$

6. Replace $k$ with $k + 1$.

Note that the only difference is in step 4.

There are a few takeaways we can make after revealing this connection. The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$. The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator. No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it. We show this below:

\begin{equation}
\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
(\#eq:penregression2)\notag
\end{equation}

\begin{equation}
\begin{split}
  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
(\#eq:penregressionproof)\notag
\end{split}
\end{equation}

by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.

<!--chapter:end:05-appendix.Rmd-->

# `ADMMsigma` R Package

`ADMMsigma` is an R package that estimates a penalized precision matrix, often denoted $\Omega$, via the alternating direction method of multipliers (ADMM) algorithm. Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user, which is the primary goal of this package.

The package currently supports a general elastic-net penalty that allows for both ridge and lasso-type penalties as special cases. In particular, the algorithm solves the following optimization problem:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{tr(S\Omega) - \log\det\left(\Omega\right) + \lambda\left[\frac{1 - \alpha}{2}\left\|\Omega\right\|_{F}^{2} + \alpha\left\|\Omega\right\|_{1} \right] \right\} \]

where $\lambda > 0$, $0 \leq \alpha \leq 1$ are tuning parameters, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.

A list of functions contained in the package can be found below:

* `ADMMsigma()` computes the estimated precision matrix via the ADMM algorithm (ridge, lasso, and elastic-net regularization optional)

* `RIDGEsigma()` computes the estimated ridge penalized precision matrix via closed-form solution

* `plot.ADMMsigma()` produces a heat map or optional line graph for cross validation errors

* `plot.RIDGEsigma()` produces a heat map or optional line graph for cross validation errors

## Installation

```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("ADMMsigma")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/ADMMsigma")
```
<br>\vspace{0.5cm}

This package is hosted on Github at [github.com/MGallow/ADMMsigma](https://github.com/MGallow/ADMMsigma). The project website is located at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).

## Tutorial

By default, `ADMMsigma` will estimate a penalized precision matrix, $\Omega$, using the elastic-net penalty and choose the optimal $\lambda$ and $\alpha$ tuning parameters. The primary function is simply `ADMMsigma()`. The input value $X$ is an $n \times p$ data matrix so that there are $n$ rows each representing an observation and $p$ columns each representing a unique feauture or variable.

Here, we will use a $100 \times 5$ data matrix that is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$. A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal, which is useful for illustration purposes because the object is sparse (many zero entries) and the shrinkage penalty should prove useful.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = FALSE}
library(ADMMsigma)

#  generate data from a sparse matrix
# first compute covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

```

```{r, message = FALSE, echo = TRUE}

# elastic-net type penalty (set tolerance to 1e-8)
ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)

```
<br>\vspace{0.5cm}

We can see that the optimal $\alpha$ value selected is one. This selection corresponds with a lasso penalty -- a special case of the elastic-net penalty.

We can also explicitly assume sparsity in our estimate rather than let the package decide by restricting the class of penalties to the lasso. We do this by simply setting `alpha = 1` in our function:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty (default tolerance)
ADMMsigma(X, alpha = 1)

```
<br>\vspace{0.5cm}

`ADMMsigma` also has the capability to provide plots for the cross validation errors. This allows the user to analyze and manually select the appropriate tuning parameters. In the heatmap plot below, the bright, white areas of the heat map correspond to a better tuning parameter selection (low validation error). In the line graph, each line corresponds to a different $\alpha$ tuning parameter.

<br>\vspace{0.5cm}
```{r ADMMsigmapackage1, message = FALSE, echo = TRUE, fig.cap = "CV heatmap for ADMMsigma tutorial.", out.width = "80%"}

# produce CV heat map for ADMMsigma
ADMM = ADMMsigma(X, tol.abs = 1e-8, tol.rel = 1e-8)
plot(ADMM, type = "heatmap")

```

```{r ADMMsigmapackage2, message = FALSE, echo = TRUE, fig.cap = "CV line graph for ADMMsigma tutorial.", out.width = "80%"}

# produce line graph for CV errors for ADMMsigma
plot(ADMM, type = "line")

```
<br>\vspace{0.5cm}

`ADMMsigma` has a number of more advanced options such as cross validation criteria, regularization path, and parallel CV that are explained in more detail on the project website at [mattxgalloway.com/ADMMsigma](http://mattxgalloway.com/ADMMsigma/).

<!--chapter:end:06-ADMMsigma-Package.Rmd-->

# `SCPME` R Package

`SCPME` is an R package that estimates a penalized precision matrix via a modified alternating direction method of multipliers (ADMM) algorithm as described in @molstad2017shrinking. Specifically, the modified ADMM algorithm solves the following optimization problem:

\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S \Omega\right) - \log\det\left(\Omega\right) + \lambda\left\| A\Omega B - C \right\|_{1} \right\} \]

where $\lambda > 0$ is a tuning parameter, $A, B, \mbox{ and } C$ are known, user-specified matrices, and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.

This form of penalty leads to many new, interesting, and novel estimators for the precision matrix $\Omega$. Users can construct matrices $A, B, \mbox{ and } C$ so that emphasis is placed on the sum, absolute value of a *characteristic* of $\Omega$. We will explore a few of these estimators in the tutorial section.

A list of functions contained in the package can be found below:

* `shrink()` computes the estimated precision matrix

* `data_gen()` data generation function (for convenience)

* `plot.shrink()` produces a heat map or optional line graph for the cross validation errors

## Installation

```{r, eval = FALSE}
# The easiest way to install is from CRAN
install.packages("SCPME")

# You can also install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("MGallow/SCPME")
```
<br>\vspace{0.5cm}

This package is hosted on Github at [github.com/MGallow/SCPME](https://github.com/MGallow/SCPME). The project website is located at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).

## Tutorial

The primary function in the `SCPME` package is `shrink()`. The input values $X$ is an $n \times p$ data matrix so that there are $n$ rows each representing an observation and $p$ columns each representing a unique variable and $Y$ is an $n \times r$ response matrix where $r$ is the dimension of the response vector. By default, `SCPME` will estimate $\Omega$ using a lasso penalty ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$) and choose the optimal $\lambda$ tuning parameter that minimizes the mean squared prediction error for the regression of the variable $Y$ on $X$ (here $I_{p}$ denotes a $p$-dimension identity matrix). If $Y$ is not provided, then tuning parameter selection will be based on the validation likelihood. Note that $\Omega$ (perhaps better denoted here as $\Omega_{x}$) will only have meaningful shrinkage unless the data vector $X \in \mathbb{R^{p}}$ is multi-dimensional ($p > 1$).

In this example, the data matrix is $100 \times 5$ and the response is generated according to the following model:

\[ Y_{i} = \beta^{T}X_{i} + E_{i} \]

where $E_{i} \sim N\left( 0, 1 \right)$ and $X_{i}$ is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix $S$. A tapered covariance matrix has the property that its inverse - the precision matrix - is tri-diagonal. Estimating this oracle precision matrix well and efficiently will be our primary interest. In addition, $\beta$ is randomly generated and sparse. The data will be generated using the `data_gen()` function contained in the package.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(SCPME)
set.seed(123)

# generate 100 x 5 X data matrix and 100 x 1 Y data matrix
data = data_gen(p = 5, n = 100, r = 1)

# the oracle regression coefficients are sparse
data$betas

```

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# shrink sum absolute entries in omega
shrink(X = data$X, Y = data$Y)

```
<br>\vspace{0.5cm}

Notice here that the estimated precision matrix is *not* sparse. This is due to the fact that our cross validation criteria is the mean-squared prediction error. We can estimate a new precision matrix using the validation likelihood as the cross validation criteria with the following command:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# shrink sum absolute entries in omega
shrink(X = data$X, Y = data$Y, crit.cv = "loglik")

```
<br>\vspace{0.5cm}

All of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in $\Omega$ ($A = I_{p}, B = I_{p}, \mbox{ and } C = 0$). In effect, this penalty embeds an assumption in our estimate that the true population precision matrix, $\Omega$, is sparse. The flexibility of the penalty described in @molstad2017shrinking allows us to make other assumptions as well. For instance, in the penalty we could set $A = I_{p}, B = \Sigma_{xy}$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$, and $C = 0$. In which case our penalty function

\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]

This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$). Of course, in practice, we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta
lam_max = max(abs(crossprod(data$X, data$Y)))
(shrink = shrink(X = data$X, Y = data$Y, B = cov(data$X, data$Y), lam.max = lam_max, nlam = 20))

```

Note that we specified the maximum `lam` value in the previous function to expand the tuning parameter grid. With these settings, the augmented ADMM algorithm also solves for the estimated $\beta$ coefficient matrix simultaneously:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print estimated beta matrix
shrink$Z

```
<br>\vspace{0.5cm}

Another possible penalty is to set $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the covariance matrix of $X$ and $Y$. That is, the penalty $P$, is constructed as

\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]

In this case, we are equally penalizing the sum, absolute values of entries in $\beta$ *and* $\Omega$ which embeds an assumption that $\beta$ and $\Omega$ are both sparse.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# assume sparsity in beta AND omega
(shrink = shrink(X = data$X, Y = data$Y, B = cbind(cov(data$X, data$Y), diag(ncol(data$X))), lam.max = 10, lam.min.ratio = 1e-4, nlam = 20))

# print estimated beta
shrink$Z[, 1, drop = FALSE]

```
<br>\vspace{0.5cm}

`SCPME` also has the capability to provide plots (heatmaps and line graphs) for the cross validation errors. In the heatmap plot below, the more bright, white areas correspond to a better tuning parameter selection (lower cross validation error).

<br>\vspace{0.5cm}
```{r SCPMEpackage1, message = FALSE, echo = TRUE, fig.cap = "CV heatmap for SCPME tutorial", out.width = "80%"}

# produce CV heat map
plot(shrink, type = "heatmap")

```

```{r SCPMEpackage2, message = FALSE, echo = TRUE, fig.cap = "CV line graph for SCPME tutorial", out.width = "80%"}

# produce line graph
plot(shrink, type = "line")

```
<br>\vspace{0.5cm}

`SCPME` has a number of more advanced options including alternative convergence criteria and parallel CV that are explained in detail on the project website at [mattxgalloway.com/SCPME](http://mattxgalloway.com/SCPME/).

<!--chapter:end:07-SCPME-Package.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:99-references.Rmd-->

### 2019-03-10 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages
added notations and restructured

--- 2018-06-07 Manuscript.tex
@@
 %
-\documentclass[12pt,]{book}
+\documentclass[11pt,]{report}
 \usepackage{lmodern}
+\usepackage{setspace}
+\setstretch{1.5}
 \usepackage{amssymb,amsmath}
@@
 \hypersetup{
-            pdftitle={Oral Manuscript},
+            pdftitle={Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression},
             pdfauthor={Matt Galloway},
@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage[left = 1in, right = 1in, top = 1in, bottom = 1in]{geometry}
 \usepackage{color}
@@
 \IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 \usepackage{amsthm}
+\usepackage{fancyhdr} % Required for custom headers
+\usepackage{lastpage} % Required to determine the last page for the footer
+\usepackage{extramarks} % Required for headers and footers
 \makeatletter
@@
 \makeatother
+\pagestyle{fancy}
+% \pagestyle{empty}
+\usepackage[left]{lineno} % line number package
+\linenumbers % line number command
 \usepackage[]{natbib}
@@
 
-\title{Oral Manuscript}
+\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
 \author{Matt Galloway}
-\date{2018-06-07}
-
-\usepackage{amsthm}
-\newtheorem{theorem}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
-\newtheorem{proposition}{Proposition}[chapter]
-\theoremstyle{definition}
-\newtheorem{example}{Example}[chapter]
-\theoremstyle{definition}
-\newtheorem{exercise}{Exercise}[chapter]
-\theoremstyle{remark}
-\newtheorem*{remark}{Remark}
-\newtheorem*{solution}{Solution}
+\date{2019-03-09}
+
 \begin{document}
@@
 \hypersetup{linkcolor=}
-\setcounter{tocdepth}{2}
+\setcounter{tocdepth}{1}
 \tableofcontents
 }
-\hypertarget{prerequisites}{%
-\chapter{Prerequisites}\label{prerequisites}}
-
 \hypertarget{intro}{%
@@
 
-This is the introduction for Matt's oral manuscript. (UPDATED 8)
-
-\hypertarget{tutorial}{%
-\chapter{Tutorial}\label{tutorial}}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# The easiest way to install is from CRAN}
-\KeywordTok{install.packages}\NormalTok{(}\StringTok{"ADMMsigma"}\NormalTok{)}
-
-\CommentTok{# You can also install the development version from GitHub:}
-\CommentTok{# install.packages('devtools')}
-\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/ADMMsigma"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\vspace{0.5cm}
-
-If there are any issues/bugs, please let me know:
-\href{https://github.com/MGallow/ADMMsigma/issues}{github}. You can also
-contact me via my \href{https://mgallow.github.io/}{website}. Pull
-requests are welcome!
-
-\vspace{0.5cm}
-
-A (possibly incomplete) list of functions contained in the package can
-be found below:
+In many statistical applications, estimating the covariance matrix, \(\Sigma\), for a set of random variables is a critical task.
+The covariance matrix is useful because it characterizes the \emph{relationship} between variables.
+For instance, suppose we have three variables \(X, Y, \mbox{ and } Z\) and their covariance matrix is of the form
+
+\begin{equation}
+\Sigma_{xyz} = \begin{pmatrix}
+1 & 0 & 0.5 \\ 
+0 & 1 & 0 \\ 
+0.5 & 0 & 1
+\end{pmatrix}
+\label{eq:ex}\notag
+\end{equation}
+
+We can gather valuable information from this matrix.
+First of all, we know that each of the variables has an equal variance of 1.
+Second, we know that variables \(X\) and \(Y\) are likely independent because the covariance between the two is equal to 0.
+This implies that any information in \(X\) is useless in trying to gather information about \(Y\).
+Lastly, we know that variables \(X\) and \(Z\) are moderately, positively correlated because their covariance is 0.5.
+
+Unfortunately, estimating \(\Sigma\) well is often computationally expensive and, in a few settings, extremely challenging.
+For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of \(\Sigma\) which we like to denote as \(\Omega \equiv \Sigma^{-1}\).
+
+\hypertarget{references}{%
+\subsection{references}\label{references}}
+
+The reference we need here is \citet{molstad2017shrinking}!
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  From \citet{molstad2017shrinking}: ``To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
+For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.
+Many authors have proposed methods that directly estimate this characteristic \citet{cai2011direct}; \citet{fan2012road}; \citet{mai2012direct}.''
+\item
+  From \citet{molstad2017shrinking}: ``\citet{chen2016regularized} proposed a method for estimating the characteristic \(\Omega_{*}\mu_{*}\) directly, but like the direct linear discriminant methods, this apporach does not lead to an estimate of \(\Omega_{*}\).''
+\item
+  Discuss linear regression application\ldots{}.
+where \(\beta = \Omega_{*}\Sigma_{*XY}\).
+Like \citet{witten2009covariance}, this approach estimates the regression coefficients ``using shrinkage estimators of the marginal precision matrix for the predictors''.
+\end{enumerate}
 
@@
 \item
-  \texttt{ADMMsigma()} computes the estimated precision matrix (ridge,
-  lasso, and elastic-net type regularization optional)
-\item
-  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision
-  matrix via closed-form solution
-\item
-  \texttt{plot.ADMMsigma()} produces a heat map or line graph for cross
-  validation errors
-\item
-  \texttt{plot.RIDGEsigma()} produces a heat map or line graph for cross
-  validation errors
+  Guide
+\item
+  Model and notation
 \end{itemize}
 
-\vspace{1cm}
-
-\hypertarget{usage}{%
-\section{Usage}\label{usage}}
-
-We will first generate data from a sparse, tri-diagonal precision matrix
-and denote it as Omega.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-
-\CommentTok{# generate data from a sparse matrix first compute covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{5}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\NormalTok{S[i, j]}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# print oracle precision matrix (shrinkage might be useful)}
-\NormalTok{(}\DataTypeTok{Omega =} \KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(S), }\DecValTok{3}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##        [,1]   [,2]   [,3]   [,4]   [,5]
-## [1,]  1.961 -1.373  0.000  0.000  0.000
-## [2,] -1.373  2.922 -1.373  0.000  0.000
-## [3,]  0.000 -1.373  2.922 -1.373  0.000
-## [4,]  0.000  0.000 -1.373  2.922 -1.373
-## [5,]  0.000  0.000  0.000 -1.373  1.961
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{5}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# snap shot of data}
-\KeywordTok{head}\NormalTok{(X)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##            [,1]         [,2]         [,3]       [,4]        [,5]
-## [1,] -0.4311177 -0.217744186  1.276826576 -0.1061308 -0.02363953
-## [2,] -0.0418538  0.304253474  0.688201742 -0.5976510 -1.06758924
-## [3,]  1.1344174  0.004493877 -0.440059159 -0.9793198 -0.86953222
-## [4,] -0.0738241 -0.286438212  0.009577281 -0.7850619 -0.32351261
-## [5,] -0.2905499 -0.906939891 -0.656034183 -0.4324413  0.28516534
-## [6,]  1.3761967  0.276942730 -0.297518545 -0.2634814 -1.35944340
-\end{verbatim}
-
-\vspace{0.5cm}
-
-As described earlier in the report, the maximum likelihood estimator
-(MLE) for Omega is the inverse of the sample precision matrix
-\(S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}\):
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# print inverse of sample precision matrix (perhaps a bad estimate)}
-\KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(}\KeywordTok{cov}\NormalTok{(X) }\OperatorTok{*}\StringTok{ }\NormalTok{(}\KeywordTok{nrow}\NormalTok{(X) }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)}\OperatorTok{/}\KeywordTok{nrow}\NormalTok{(X)), }\DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.32976 -1.55033  0.22105 -0.08607  0.24309
-## [2,] -1.55033  3.27561 -1.68026 -0.14277  0.18949
-## [3,]  0.22105 -1.68026  3.19897 -1.25158 -0.11016
-## [4,] -0.08607 -0.14277 -1.25158  2.76790 -1.37226
-## [5,]  0.24309  0.18949 -0.11016 -1.37226  2.05377
-\end{verbatim}
-
-\vspace{0.5cm}
-
-However, because Omega (known as the \emph{oracle}) is sparse, a
-shrinkage estimator will perhaps perform better than the sample
-estimator. Below we construct various penalized estimators:
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net type penalty (set tolerance to 1e-8)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, tol.abs = 1e-08, tol.rel = 1e-08)
-## 
-## Iterations: 162
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41003
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15283 -1.26902  0.00000  0.00000  0.19765
-## [2,] -1.26902  2.79032 -1.32206 -0.08056  0.00925
-## [3,]  0.00000 -1.32206  2.85470 -1.17072 -0.00865
-## [4,]  0.00000 -0.08056 -1.17072  2.49554 -1.18959
-## [5,]  0.19765  0.00925 -0.00865 -1.18959  1.88121
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{LASSO:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# lasso penalty (default tolerance)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 1)
-## 
-## Iterations: 66
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.599      1
-## 
-## Log-likelihood: -108.41022
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15228 -1.26841  0.00000  0.00000  0.19744
-## [2,] -1.26841  2.78830 -1.31943 -0.08246  0.01018
-## [3,]  0.00000 -1.31943  2.84979 -1.16708 -0.01015
-## [4,]  0.00000 -0.08246 -1.16708  2.49277 -1.18844
-## [5,]  0.19744  0.01018 -0.01015 -1.18844  1.88069
-\end{verbatim}
-
-\vspace{0.5cm}
-
-\textbf{ELASTIC-NET:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net penalty (alpha = 0.5)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0.5)
-## 
-## Iterations: 67
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821    0.5
-## 
-## Log-likelihood: -101.13595
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.20031 -1.32471  0.01656 -0.00334  0.21798
-## [2,] -1.32471  2.90659 -1.37599 -0.19084  0.13651
-## [3,]  0.01656 -1.37599  2.92489 -1.12859 -0.12033
-## [4,] -0.00334 -0.19084 -1.12859  2.56559 -1.23472
-## [5,]  0.21798  0.13651 -0.12033 -1.23472  1.94528
-\end{verbatim}
-
-\newpage
-
-\textbf{RIDGE:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{0}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0)
-## 
-## Iterations: 65
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821      0
-## 
-## Log-likelihood: -99.19746
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.18979 -1.31533  0.04515 -0.04090  0.23511
-## [2,] -1.31533  2.90019 -1.37049 -0.22633  0.17808
-## [3,]  0.04515 -1.37049  2.89435 -1.07647 -0.17369
-## [4,] -0.04090 -0.22633 -1.07647  2.55026 -1.22786
-## [5,]  0.23511  0.17808 -0.17369 -1.22786  1.95495
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty no ADMM}
-\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: RIDGEsigma(X = X, lam = 10^seq(-8, 8, 0.01))
-## 
-## Tuning parameter:
-##       log10(lam)    lam
-## [1,]       -2.17  0.007
-## 
-## Log-likelihood: -109.18156
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15416 -1.31185  0.08499 -0.05571  0.22862
-## [2,] -1.31185  2.85605 -1.36677 -0.19650  0.16880
-## [3,]  0.08499 -1.36677  2.82606 -1.06325 -0.14946
-## [4,] -0.05571 -0.19650 -1.06325  2.50721 -1.21935
-## [5,]  0.22862  0.16880 -0.14946 -1.21935  1.92871
-\end{verbatim}
-
-\newpage
-
-This package also has the capability to provide heat maps for the cross
-validation errors. The more bright (white) areas of the heat map pertain
-to more optimal tuning parameters.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for ADMMsigma}
-\NormalTok{ADMM =}\StringTok{ }\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for ADMMsigma}
-\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce CV heat map for RIDGEsigma}
-\NormalTok{RIDGE =}\StringTok{ }\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-
-\newpage
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for RIDGEsigma}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-
-\hypertarget{details}{%
-\chapter{Details}\label{details}}
-
-Suppose we want to solve the following optimization problem:
-
-\begin{align*}
+\hypertarget{outline}{%
+\section{Outline}\label{outline}}
+
+\begin{itemize}
+\item
+  Why do we care about covariance matrices? Covariance matrices are an object that summarizes the relationship between variables.
+\item
+  What is a precision matrix? Precision matrix is the inverse of a covariance matrix.
+\item
+  Precision matrices are powerful, essential in representing relationships in variables
+\item
+  In fact, required to be estimated to fit many statistical models.
+\item
+  That is, we must provide an object that accurately summarizes the relationship and interaction between variables in our model.
+\item
+  Many proposed shrinkage estimators when p is particularly large. Shrinkage.
+\item
+  However, to fit these models, Molstad and Rothman focused on the fact that onnly a ``characteristic'' of a precision matrix is required to fit these models.
+``We propose a framework to shrink a user-specified characteristic of a precision matrix estimator.''
+\item
+  For instance, LDA, linear regression, \ldots{}
+\item
+  Their approach/methodology was published in BLAH. Shrinking characteristic of precision matrix estimators.
+\item
+  BREAK
+\item
+  We wanted to explore the regression application that was mentioned but not pursued/investigated
+\item
+  This document will outline the research and work leading up to that
+\item
+  The document is outlined as follows\ldots{}
+\item
+  We will begin chapter 2 with a brief introduction to precision matrix estimation.
+This will include mentions of estimation methods/approaches and we will spend a particular amount of time elaborating on one approach which is estimation via the ADMM algorithm.
+This dicussion will be useful when we circle back to SCPME, the regression application, and the augmented ADMM algorithm developed in BLAH.
+\item
+  Lastly, the document will end with two brief tutorials for the R packages ADMMsigma and SCPME.
+These packages, developed by myself, will be mentioned throughout the document and were instrumental in this pursued line of research and facilitated many simulations and research direction explored throughout.
+Both packages have since been published on CRAN
+\end{itemize}
+
+\hypertarget{notation-and-definitions}{%
+\subsection{Notation and Definitions}\label{notation-and-definitions}}
+
+For strictly positive integers \(n\) and \(p\), we will denote \(\mathbb{R}^{n \times p}\) as the class of real matrices with dimenson \(n \times p\).
+The class of real, symmetric matrices with dimension \(p \times p\) will be denoted as \(\mathbb{S}^{p}\) and \(\mathbb{S}^{p}_{+}\) if we further require the object to be positive definite.
+The sample size in a given data set will most often correspond with \(n\) and \(p\) will correspond with the dimension of the prediction vector.
+If the dimension of the response vector exceeds one, we will denote it as \(r\).
+
+Most matrices will take the form of either \(\Sigma\), which should be taken to represent the population covariance matrix, or \(\Omega\), which should be taken to represent the population \emph{precision} matrix.
+Note that the precision matrix is simply the inverse of the covariance matrix (\(\Omega \equiv \Sigma^{-1}\)).
+We will sometimes add a subscript star if the object is oracle - or known- a priori (\(\Omega_{*}\)) and the population object's estimator that minimizes/maximizes a pre-specified objective function will have a hat attached to it (\(\hat{\Omega}\)).
+
+There will be significant matrix algebra notation throughout the document.
+The trace operator which sums the diagonal elements of a matrix will take the form \(tr\left(\cdot\right)\) and the \emph{exponential} trace operator will be denoted similarly as \(etr\left(\cdot\right)\).
+The determinant of a matrix \(\mathbf{A}\) will be denoted as \(\left|\mathbf{A}\right|\) but may also take the form as simply \(det\left(\mathbf{A}\right)\).
+The kronecker product of two matrices \(\mathbf{A}\) and \(\mathbf{B}\) will be denoted as \(\mathbf{A} \otimes \mathbf{B}\).
+Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as \(\left\|\mathbf{A}\right\|_{F}\) and we will define \(\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|\) where the \(i\)-\(j\)th element in matrix \(\mathbf{A}\) is denoted as \(\left(\mathbf{A}\right)_{ij}\) or simply \(\mathbf{A}_{ij}\).
+
+\hypertarget{precision-matrix-estimation}{%
+\chapter{Precision Matrix Estimation}\label{precision-matrix-estimation}}
+
+\hypertarget{literature-review}{%
+\subsection{Literature Review?}\label{literature-review}}
+
+\begin{itemize}
+\item
+  Articles that review covariance and precision matrix estimation in high dimensional settings are \citet{pourahmadi2013high} and \citet{fan2016overview}.
+\item
+  The person who initially proposed the lasso-penalized gaussian likelihood precision matrix estimation is \citet{yuan2007model}.
+\item
+  Other authors who have proposed methods with non-lasso penalizations are (Frobenius norms) \citet{witten2009covariance}, \citet{rothman2014existence}, (non-convex penalties) \citet{lam2009sparsistency}, and \citet{fan2009network}.
+\item
+  Standard alternating direction method of multipliers approaches are found in \citet{boyd11distributed}.
+\item
+  ADMM with modification based on majorize-minimize principle is found in \citet{lange2016mm}.
+\item
+  Quadratic equation with ridge is solve in closed form using a similar approach to \citet{witten2009covariance}; \citet{price2015ridge}.
+\item
+  L1-penalized gaussian likelihood precision matrix estimator (\citet{yuan2007model}; \citet{rothman2008sparse}; \citet{friedman2008sparse}).
+\end{itemize}
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+Consider the case where we observe \(n\) independent, identically distributed copies of the random variable (\(X_{i}\)) where \(X_{i} \in \mathbb{R}^{p}\) is normally distributed with some mean, \(\mu\), and some variance, \(\Omega^{-1}\).
+That is, \(X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)\).
+
+Because we assume independence, we know that the probability of observing these specific observations \(X_{1}, ..., X_{n}\) is equal to
+
+\begin{equation} 
+\begin{split}
+  f(X_{1}, ..., X_{n}; \mu, \Omega^{-1}) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
+  &= (2\pi)^{-np/2}\left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Omega \right]
+\end{split}
+\label{eq:normallik}\notag
+\end{equation}
+
+where \(\mbox{etr}\left( \cdot \right)\) denotes the exponential trace operator. It follows that the log-likelihood for \(\mu\) and \(\Omega\) is equal to the following:
+
+\begin{equation}
+  l(\mu, \Omega | X) = const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
+\label{eq:normalloglik}\notag
+\end{equation}
+
+If we are interested in estimating \(\mu\), it is relatively straight forward to show that the maximum likelihood estimator (MLE) for \(\mu\) is \(\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n\) which we typically denote as \(\bar{X}\).
+However, in addition to \(\mu\), many applications require the estimation of \(\Sigma\) as well.
+We can also find a maximum likelihood estimator:
+
+\begin{equation}
+\begin{split}
+\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ const.
++ \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right] \right\} \\
+  &= \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]^{-1}
+\end{split}
+\label{eq:omegamle}\notag
+\end{equation}
+
+By setting the gradient equal to zero and plugging in the MLE for \(\mu\), we find that the MLE for \(\Omega\) is the inverse our usual sample estimator for the covariance matrix, denoted here as \(S^{-1}\).
+It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix \(\Omega \equiv \Sigma^{-1}\) and taken its inverse:
+
+\begin{equation}
+\hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
+\label{eq:omegamlesimple}
+\end{equation}
+
+so that \(\hat{\Omega}^{MLE} = S^{-1}\).
+Beyond the formatting convenience, computing estimates for \(\Omega\) as opposed to \(\Sigma\) often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for \(\Omega\) instead of \(\Sigma\)\footnote{Notice that here we are \emph{minimizing} the negative log-likelihood as opposed to maximizing the log-likelihood.
+Both procedures will result in the same estimate.}.
+
+As in regression settings, we can construct a \emph{penalized} log-likelihood estimator by adding a penalty term, \(P\left(\Omega\right)\), to the log-likelihood so that
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
+\label{eq:omegapen}
+\end{equation}
+
+\(P\left( \Omega \right)\) is often of the form \(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2\) or \(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\), \(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define \(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\).
+These penalties are the ridge and lasso, respectively.
+
+\hypertarget{admm-algorithm}{%
+\section{ADMM algorithm}\label{admm-algorithm}}
+
+Many efficient methods have been proposed to solve for \(\hat{\Omega}\) when \(\alpha = 1\).
+The most popular method is the graphical lasso algorithm (glasso) introduced by \citet{friedman2008sparse}.
+However, no methods (to the best of my knowledge) have estimated \(\Omega\) when \(\alpha \in (0, 1)\).
+We will use the alternating direction method of multipliers (ADMM) algorithm to do so.
+
+As the authors state in \citet{boyd2011distributed}, the ``ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers.'' For our purposes, we will only focus on the ADMM algorithm but it is encouraged to read the original text from Boyd and others for a complete introduction to the other two methods.
+
+In general, suppose we want to solve an optimization problem of the following form:
+
+\begin{equation}
+\begin{split}
   \mbox{minimize } f(x) + g(z) \\
   \mbox{subject to } Ax + Bz = c
-\end{align*}
-
-where
-\(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\),
-and \(c \in \mathbb{R}^{p}\). Following \citet{boyd2011distributed}, the
-optimization problem will be introduced in vector form though we will
-later consider cases where \(x\) and \(z\) are matrices. We will also
-assume \(f\) and \(g\) are convex functions. Optimization problems like
-this arise naturally in several statistics and machine learning
-applications -- particularly regularization methods. For instance, we
-could take \(f\) to be the squared error loss, \(g\) to be the
-\(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be
-identity matrices to solve the ridge regression optimization problem.
-
-The \emph{augmented lagrangian} is constructed as follows:
-
-\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]
-
-where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and
-\(\rho > 0\) is a scalar. Clearly any minimizer, \(p^{*}\), under the
-augmented lagrangian is equivalent to that of the lagrangian since any
-feasible point \((x, z)\) satisfies the constraint
-\(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
-
-\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]
-
-The alternating direction method of multipliers (ADMM) algorithm
-consists of the following repeated iterations:
+\end{split}
+\label{eq:boyd}\notag
+\end{equation}
+
+where \(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\), \(c \in \mathbb{R}^{p}\), and \(f\) and \(g\) are assumed to be convex functions (following \citet{boyd2011distributed}, the estimation procedure will be introduced in vector form though we could just as easily take \(x\) and \(z\) to be matrices).
+In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods.
+For instance, we could take \(f\) to be the squared error loss, \(g\) to be the \(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be identity matrices to solve the ridge regression optimization problem.
+In all cases, our goal is to find \(x^{*} \in \mathbb{R}^{n}\) and \(z^{*} \in \mathbb{R}^{m}\) that achieves the infimum \(p^{*}\):
+
+\begin{equation}
+p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\}
+\label{eq:infimum}\notag
+\end{equation}
+
+To do so, the ADMM algorithm uses the \emph{augmented lagrangian}
+
+\begin{equation}
+L_{\rho}(x, z, y) = f(x) + g(z) + y'(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2}
+\label{eq:auglagrange}\notag
+\end{equation}
+
+where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and \(\rho > 0\) is a scalar.
+Clearly any minimizer, \(p^{*}\), under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point \((x, z)\) satisfies the constraint \(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
+
+The algorithm consists of the following repeated iterations:
+
+\begin{equation}
+\begin{split}
+  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
+  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
+  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+\end{split}  
+\label{eq:admmalgo}\notag
+\end{equation}
+
+In the context of precision matrix estimation, we can let \(f\) be equal to the non-penalized likelihood, \(g\) be equal to \(P\left( \Omega \right)\), and use the constraint \(\Omega\) equal to some \(Z\) so that the lagrangian is
+
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
+\label{eq:lagrange2}\notag
+\end{equation}
+
+and the augmented lagrangian is
+
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
+\label{eq:auglagrange2}\notag
+\end{equation}
+
+\vspace{3cm}
+
+In the \texttt{ADMMsigma} package, we instead take
+
+\begin{equation}
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+\label{eq:penelastic}\notag
+\end{equation}
+
+so that solving the full penalized log-likelihood for \(\Omega\) results in solving
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
+\label{eq:optimelastic}
+\end{equation}
+
+where \(0 \leq \alpha \leq 1\).
+This penalty, know as the \emph{elastic-net} penalty, was explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and is identical to the penalty used in the popular penalized regression package \texttt{glmnet}.
+Clearly, when \(\alpha = 0\) the elastic-net reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a lasso-type penalty.
+Having this flexibility and generalization allows us to perform cross validation across proposed \(\alpha\) values in addition to proposed \(\lambda\) values.
+
+The ADMM algorithm is now the following:
 
 \begin{align}
-  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \label{eq:omegaauglagrangee} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \label{eq:ZZauglagrange} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \label{eq:lamauglagrange}
 \end{align}
 
-A more complete introduction to the algorithm -- specifically how it
-arose out of \emph{dual ascent} and \emph{method of multipliers} -- can
-be found in \citet{boyd2011distributed}.
-
-\vspace{1cm}
-
-\hypertarget{admm-algorithm}{%
-\section{ADMM Algorithm}\label{admm-algorithm}}
-
-Now consider the case where \(X_{1}, ..., X_{n}\) are iid
-\(N_{p}(\mu, \Sigma)\) random variables and we are tasked with
-estimating the precision matrix, denoted \(\Omega \equiv \Sigma^{-1}\).
-The maximum likelihood estimator for \(\Omega\) is
-
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]
-
-where \(S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n\)
-and \(\bar{X}\) is the sample mean. By setting the gradient equal to
-zero, we can show that when the solution exists,
-\(\hat{\Omega}_{MLE} = S^{-1}\).
-
-As in regression settings, we can construct a \emph{penalized}
-likelihood estimator by adding a penalty term,
-\(P\left( \Omega \right)\), to the likelihood:
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]
-
-\(P\left( \Omega \right)\) is often of the form
-\(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}\) or
-\(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\),
-\(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define
-\(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\). These
-penalties are the ridge and lasso, respectively. We will, instead, take
-\(P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]\)
-so that the full penalized likelihood is
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]
-
-where \(0 \leq \alpha \leq 1\). This \emph{elastic-net} penalty was
-explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and
-is identical to the penalty used in the popular penalized regression
-package \texttt{glmnet}. Clearly, when \(\alpha = 0\) the elastic-net
-reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a
-lasso-type penalty.
-
-By letting \(f\) be equal to the non-penalized likelihood and \(g\)
-equal to \(P\left( \Omega \right)\), our goal is to minimize the full
-augmented lagrangian where the constraint is that \(\Omega - Z\) is
-equal to zero:
-
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]
-
-The ADMM algorithm for estimating the penalized precision matrix in this
-problem is
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align}
-
-\vspace{1cm}
-
-\hypertarget{scaled-form-admm}{%
-\section{Scaled-Form ADMM}\label{scaled-form-admm}}
-
-An alternate form of the ADMM algorithm can constructed by scaling the
-dual variable (\(\Lambda^{k}\)). Let us define
-\(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).
-
-\begin{align*}
-  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-\end{align*}
-
-Therefore, the condensed-form ADMM algorithm can now be written as
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
-\end{align}
-
-And more generally (in vector form),
-
-\begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
-\end{align}
-
-Note that there are limitations to using this method. Because the dual
-variable is scaled by \(\rho\) (the step size), this form limits one to
-using a constant step size without making further adjustments to
-\(U^{k}\). It has been shown in the literature that a dynamic step size
-can significantly reduce the number of iterations required for
-convergence.
-
-\vspace{1cm}
-
 \hypertarget{algorithm}{%
-\section{Algorithm}\label{algorithm}}
-
-\begin{align*}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align*}
-
-\vspace{1cm}
-
-Initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Iterate the following
-three steps until convergence:
+\subsection{Algorithm}\label{algorithm}}
+
+Set \(k = 0\) and initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Repeat steps 1-3 until convergence:
 
@@
 \item
-  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) via spectral
-  decomposition.
+  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV'\) via spectral decomposition\footnote{Proof of \eqref{eq:omegaalgo} in section \ref{proofomegaalgo}.}. Then
 \end{enumerate}
 
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V'
+\label{eq:omegaalgo}
+\end{equation}
 
@@
 \item
-  Elementwise soft-thresholding for all \(i = 1,..., p\) and
-  \(j = 1,..., p\).
+  Elementwise soft-thresholding for all \(i = 1,..., p\) and \(j = 1,..., p\)\footnote{Proof of \eqref{eq:ZZalgo} in section \ref{proofZZalgo}.}.
 \end{enumerate}
 
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\label{eq:ZZalgo}
+\end{split}
+\end{equation}
 
@@
 
-\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-1}{%
-\subsection{Proof of (1):}\label{proof-of-1}}
-
-\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
-\end{align*}
-
-Set the gradient equal to zero and decompose \(\Omega = VDV^{T}\) where
-\(D\) is a diagonal matrix with diagonal elements equal to the eigen
-values of \(\Omega\) and \(V\) is the matrix with corresponding eigen
-vectors as columns.
-
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
-
-This equivalence implies that
-
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
-
-where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
-
-\begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
-\end{align*}
-
-In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\)
-then
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-2}{%
-\subsection{Proof of (2)}\label{proof-of-2}}
-
-\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
-\end{align*}
-
-where \(Sign(Z)\) is the elementwise Sign operator. By setting the
-gradient/sub-differential equal to zero, we arrive at the following
-equivalence:
-
-\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]
-
-for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
-
-\begin{itemize}
+\begin{equation}
+\Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+\label{eq:lamalgo}\notag
+\end{equation}
+
+where \(\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}\).
+
+\hypertarget{scaled-form-admm}{%
+\subsection{Scaled-Form ADMM}\label{scaled-form-admm}}
+
+There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable (\(\Lambda^{k}\)). Let us define \(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).
+
+\begin{equation}
+\begin{split}
+  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
+  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
+  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
+\label{eq:scaled}\notag
+\end{split}
+\end{equation}
+
+Therefore, a scaled-form can now be written as
+
+\begin{align}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \label{eq:omegascaled}\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \label{eq:ZZscaled}\notag \\
+  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} \label{eq:Uscaled}\notag
+\end{align}
+
+And more generally (in vector form),
+
+\begin{align}
+  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \label{eq:xscaled}\notag \\
+  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \label{eq:zscaled}\notag \\
+  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c \label{eq:uscaled}\notag
+\end{align}
+
+Note that there are limitations to using this method.
+Because the dual variable is scaled by \(\rho\) (the step size), this form limits one to using a constant step size without making further adjustments to \(U^{k}\).
+It has been shown in the literature that a dynamic step size (like the one used in \texttt{ADMMsigma}) can significantly reduce the number of iterations required for convergence.
+
+\hypertarget{stopping-criterion}{%
+\subsection{Stopping Criterion}\label{stopping-criterion}}
+
+In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in \citet{boyd2011distributed} and cater them to precision matrix estimation.
+
+Below we have three optimality conditions:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
 \tightlist
 \item
-  If \(Z_{ij} > 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]
-
-\begin{itemize}
+  Primal:
+\end{enumerate}
+
+\begin{equation}
+\Omega^{k + 1} - Z^{k + 1} = 0
+\label{eq:admmprimal}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
 \tightlist
 \item
-  If \(Z_{ij} < 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]
-
-This implies that
-\(Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\).
-Putting all the pieces together, we arrive at
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-where \(Soft\) is the soft-thresholding function.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
+  Dual:
+\end{enumerate}
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \\
+  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
+\label{eq:admmdual}\notag
+\end{split}
+\end{equation}
+
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to \(\Omega^{k + 1}\) (note that we must honor the symmetric constraint of \(\Omega^{k + 1}\)) and the second is a result of taking the sub-differential of the lagrangian with respect to \(Z^{k + 1}\) (no symmetric constraint).
+
+We will define the left-hand side of the first condition as the primal residual \(r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}\).
+At convergence, optimality conditions require that \(r^{k + 1} \approx 0\).
+The second residual we will define is the dual residual \(s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)\).
+This residual is derived from the following:
+
+Because \(\Omega^{k + 1}\) is the minimizer of the augmented lagragian\footnote{Proof of \eqref{eq:dualresidual} in section \ref{proofdualresidual}.}, this implies that \(0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)\) which further implies that
+
+\begin{equation}
+0 \in \rho\left( Z^{k + 1} - Z^{k} \right)
+\label{eq:dualresidual}
+\end{equation}
+
+Like the primal residual, at convergence optimality conditions require that \(s^{k + 1} \approx 0\).
+Note that the second dual optimality condition is always satisfied\footnote{Proof of \eqref{eq:dualopt} in section \ref{proofdualopt}.}:
+
+\begin{equation}
+\begin{split}
+  0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\label{eq:dualopt}
+\end{split}
+\end{equation}
+
+One possible stopping criterion is to set \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and stop the algorithm when \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where
+
+\begin{equation}
+\begin{split}
+  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
+  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
+\label{eq:admmstopping}\notag
+\end{split}
+\end{equation}
 
 \hypertarget{simulations}{%
-\chapter{Simulations}\label{simulations}}
-
-In the simulations below we generated data from a number of oracle
-precision matrices with various structures. For each data-generating
-procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross
-validation. After 20 replications, the cross validation errors were
-totalled and the optimal tuning parameters were selected (results in the
-top figure). These results are compared with the Kullback Leibler (KL)
-losses between the estimates and the oracle precision matrix (bottom
-figure). We can see below that our cross validation procedure choosing
-tuning parameters close to the optimal parameters.
-
-\newpage
+\section{Simulations}\label{simulations}}
+
+In the simulations below, we generate data from a number of different oracle precision matrices with various structures.
+For each data-generating procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross validation.
+After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results below the top figure).
+These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure).
+
+We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.
+
+HOW DID WE GENERATE THE DATA?
+
+\hypertarget{plots}{%
+\subsection{Plots}\label{plots}}
 
 \hypertarget{compound-symmetric-p-100-n-50}{%
-\subsection{Compound Symmetric: P = 100, N =
-50}\label{compound-symmetric-p-100-n-50}}
-
-\includegraphics{images/compound_N50_P100.png}
-
-\vspace{0.5cm}
+\subsubsection{Compound Symmetric: P = 100, N = 50}\label{compound-symmetric-p-100-n-50}}
 
@@
 
-\newpage
+\vspace{0.5cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{images/compound_N50_P100}
+
+}
+
+\caption{Figure caption here.}\label{fig:admmsim1}
+\end{figure}
 
 \hypertarget{compound-symmetric-p-10-n-1000}{%
-\subsection{Compound Symmetric: P = 10, N =
-1000}\label{compound-symmetric-p-10-n-1000}}
-
-\includegraphics{images/compound_N1000_P10.png}
-
-\vspace{0.5cm}
+\subsubsection{Compound Symmetric: P = 10, N = 1000}\label{compound-symmetric-p-10-n-1000}}
 
@@
 
-\newpage
-
-\hypertarget{dense-p-100-n-50}{%
-\subsection{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
-
-\includegraphics{images/repsKLdenseQR_N50_P100.png}
-
 \vspace{0.5cm}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{100} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
-
-\hypertarget{dense-p-10-n-50}{%
-\subsection{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
-
-\includegraphics{images/repsKLdense_N50_P10.png}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{10}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-\end{Highlighting}
-\end{Shaded}
-
-\newpage
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{images/compound_N1000_P10}
+
+}
+
+\caption{Figure caption here.}\label{fig:admmsim2}
+\end{figure}
+
+--\textgreater{}
+ --\textgreater{}
+ --\textgreater{}
+ --\textgreater{}
+ --\textgreater{}
+
+--\textgreater{}
+ --\textgreater{}
+ --\textgreater{}
+ --\textgreater{}
 
 \hypertarget{tridiagonal-p-100-n-50}{%
-\subsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
-
-\includegraphics{images/repsKLtridiag_N50_P100.png}
-
-\vspace{0.5cm}
+\subsubsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
 
@@
 
-\hypertarget{benchmark}{%
-\chapter{Benchmark}\label{benchmark}}
-
-Below we benchmark the various functions contained in
-\texttt{ADMMsigma}. We can see that \texttt{ADMMsigma} (at the default
-tolerance) offers comparable computation time to the popular
-\texttt{glasso} R package.
-
-\hypertarget{computer-specs}{%
-\subsection{Computer Specs:}\label{computer-specs}}
-
+\vspace{0.5cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{images/repsKLtridiag_N50_P100}
+
+}
+
+\caption{Figure caption here.}\label{fig:admmsim5}
+\end{figure}
+
+\hypertarget{scpme}{%
+\chapter{SCPME}\label{scpme}}
+
+\hypertarget{literature-review-1}{%
+\subsection{literature review?}\label{literature-review-1}}
+
+\begin{itemize}
+\item
+  A similar estimator was proposed by \citet{dalal2017sparse} when \(C = 0\).
+\item
   \begin{itemize}
@@
   \item
-  MacBook Pro (Late 2016)
-\item
-  Processor: 2.9 GHz Intel Core i5
-\item
-  Memory: 8GB 2133 MHz
-\item
-  Graphics: Intel Iris Graphics 550
+    Quadratic equation with ridge is solve in closed form using a similar approach to \citet{witten2009covariance}; \citet{price2015ridge}.
   \end{itemize}
-
-\vspace{0.5cm}
+\end{itemize}
+
+\hypertarget{other-stuff}{%
+\subsection{other stuff}\label{other-stuff}}
+
+The penalty proposed by \citet{molstad2017shrinking} is one of the following form:
+
+\begin{equation}
+P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
+\label{eq:pen2}
+\end{equation}
+
+where \(A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}\) are matrices assumed to be known and specified by the user.
+Solving the full penalized log-likelihood for \(\Omega\) results in solving
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+\label{eq:omegaloglik2}
+\end{equation}
+
+This form of penalty is particularly useful because matrices \(A, B, \mbox{ and } C\) can be constructed so that we penalize the sum, absolute value of a \emph{characteristic} of the precision matrix \(\Omega\).
+This type of penalty leads to many new, interesting, and novel estimators for \(\Omega\).
+An example of one such estimator (suppose we observe \(n\) samples of \(Y_{i} \in \mathbb{R}^{r}\)) would be one where we set \(A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0\) where \(\Sigma_{xy}\) is the covariance matrix of \(X\) and \(Y\).
+This penalty has the effect of assuming sparsity in the forward regression coefficient \(\beta \equiv \Omega\Sigma_{xy}\).
+Of course, in practice we do not know the true covariance matrix \(\Sigma_{xy}\) but we might consider using the sample estimate \(\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n\)
+
+We will explore how to solve for \(\hat{\Omega}\) in the next section.
+
+\hypertarget{augmented-admm-algorithm}{%
+\section{Augmented ADMM Algorithm}\label{augmented-admm-algorithm}}
+
+\emph{This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm.
+I would recommend reading this overview I have written \href{https://mgallow.github.io/ADMMsigma/articles/Details.html\#admm-algorithm}{here} before proceeding.}
+
+The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.
+Within the context of \citet{molstad2017shrinking}, this algorithm would consist of iterating over the following three steps:
+
+\begin{align}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \label{eq:omegaauglagrange2}\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \label{eq:ZZauglagrange2}\notag \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \label{eq:lamauglagrange2}\notag
+\end{align}
+
+where \(L_{p}(\cdot)\) is the \emph{augmented lagrangian} defined as
+
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
+\label{eq:auglagrange2}
+\end{equation}
+
+with \(f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|\) and \(g\left(Z\right) = \lambda\left\|Z\right\|_{1}\).
+However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function (\(\tilde{L}\)) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.
+
+The approximating function is defined as
+
+\begin{equation}
+\begin{split}
+  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)\notag
+\label{eq:approx}
+\end{split}
+\end{equation}
+
+where \(Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)\), \(\otimes\) is the Kronecker product, and \(\tau\) is chosen such that \(Q\) is positive definite.
+Note that if \(Q\) is positive definite (p.d.), then
+
+\begin{equation}
+\frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0
+\label{eq:pd}\notag
+\end{equation}
+
+since \(\rho > 0\) and \(vec\left(\Omega - \Omega^{k}\right)\) is always nonzero whenever \(\Omega \neq \Omega^{k}\).
+Thus \(L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)\) for all \(\Omega\) and \(\tilde{L}\) is a majorizing function\footnote{Proof of BLAH in section BLAHHH}.
+
+The \emph{augmented ADMM} algorithm is the following:
+
+\begin{align}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \label{eq:omegaaugadmm}\notag \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \label{eq:ZZaugadmm}\notag \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \label{eq:lamaugadmm}\notag
+\end{align}
+
+\hypertarget{algorithm-1}{%
+\subsection{Algorithm}\label{algorithm-1}}
+
+Set \(k = 0\) and repeat steps 1-6 until convergence.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Compute \(G^{k}\).
+\end{enumerate}
+
+\begin{equation}
+G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}
+\label{eq:Gk}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Via spectral decomposition, decompose
+\end{enumerate}
+
+\begin{equation}
+S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}
+\label{eq:VQV}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Update \(\Omega^{k + 1}\).\footnote{Proof of \eqref{eq:Omegak} in section \ref{proofOmegak}}
+\end{enumerate}
+
+\begin{equation}
+\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)
+\label{eq:Omegak}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Update \(Z^{k + 1}\).\footnote{Proof of \eqref{eq:Zk} in section \ref{proofZk}}
+\end{enumerate}
+
+\begin{equation}
+Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)
+\label{eq:Zk}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  Update \(Y^{k + 1}\).
+\end{enumerate}
+
+\begin{equation}
+Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+\label{eq:Yk}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{5}
+\tightlist
+\item
+  Replace \(k\) with \(k + 1\).
+\end{enumerate}
+
+The soft-thresholding function is defined as \(\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}\).
+
+\hypertarget{stopping-criterion-1}{%
+\subsection{Stopping Criterion}\label{stopping-criterion-1}}
+
+In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in \citet{boyd2011distributed} and cater them to the SCPME method.
+
+Below we have three optimality conditions:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Primal:
+\end{enumerate}
+
+\begin{equation}
+A\Omega^{k + 1}B - Z^{k + 1} - C = 0
+\label{eq:scpmeprimal}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Dual:
+\end{enumerate}
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial f\left(\Omega^{k + 1}\right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) \\
+  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
+\label{eq:scpmedual}\notag
+\end{split}
+\end{equation}
+
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to \(\Omega^{k + 1}\) (note that we must honor the symmetric constraint of \(\Omega^{k + 1}\)) and the second is a result of taking the sub-differential of the lagrangian with respect to \(Z^{k + 1}\) (no symmetric constraint).
+
+We will define the left-hand side of the primal optimality condition as the primal residual \(r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C\).
+At convergence, the optimality conditions require that \(r^{k + 1} \approx 0\).
+The second residual we will define is the dual residual\footnote{Proof of \eqref{eq:stopproof} in section \ref{proofstopproof}.}:
+
+\begin{equation}
+s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
+\label{eq:stopproof}\notag
+\end{equation}
+
+Like the primal residual, at convergence the optimality conditions require that \(s^{k + 1} \approx 0\).
+Note that the second dual optimality condition is always satisfied\footnote{Proof of \eqref{eq:dualopt2} in section \ref{proofdualopt2}}.
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
+\label{eq:dualopt2}\notag
+\end{split}
+\end{equation}
+
+One possible stopping criterion is to set \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and stop the algorithm when \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where
+
+\begin{equation}
+\begin{split}
+  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
+  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
+\label{eq:scpmestopping}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{regression-illustration}{%
+\chapter{Regression Illustration}\label{regression-illustration}}
+
+Talk about regression problem\ldots{}
+
+\hypertarget{simulations-1}{%
+\section{Simulations}\label{simulations-1}}
+
+We compare the performance of various shrinkage estimators under different data realizations. Each data scenario was replicated a total of 20 times.
+
+\hypertarget{models}{%
+\subsection{Models}\label{models}}
+
+In the following estimators, let the superscript * denote the oracle estimator:
+
+\begin{itemize}
+\item
+  \texttt{OLS} = ordinary least squares estimator in \emph{low} dimensional setting and Moore-Penrose estimator in a \emph{high} (\(p >> n\)) dimensional setting
+\item
+  \texttt{ridge} = ridge regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV
+\item
+  \texttt{lasso} = lasso regression estimator where the optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV
+\item
+  \texttt{oracleB} = oracle estimator with the true \(\beta^{*}\) known (\(\left\| Y - X\beta^{*} \right\|_{F}^{2}\))
+\item
+  \texttt{oracleO} = oracle estimator with the true \(\Omega^{*}\) known (\(\left\| Y - X\Omega^{*}\hat{\Sigma}_{xy} \right\|_{F}^{2}\))
+\item
+  \texttt{oracleS} = oracle estimator with the true \(\Sigma_{xy}^{*}\) known and sample estimator for \(\Omega\) (\(\left\| Y - X\hat{\Omega}\Sigma_{xy}^{*} \right\|_{F}^{2}\))
+\item
+  \texttt{shrinkB} = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: \(\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}\))
+\item
+  \texttt{shrinkBS} = shrinking characteristics regression estimator with oracle cross-covariance where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: \(\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}\))
+\item
+  \texttt{shrinkBO} = shrinking characteristics estimator that penalizes the sum of the absolute values of \(\beta = \Omega\Sigma_{xy}\) \emph{and} \(\Omega\) (penalty: \(\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}\))
+\item
+  \texttt{glasso} = lasso penalized precision matrix where optimal tuning parameter is chosen to maximize log-likelihood via 3-fold CV.
+\end{itemize}
+
+\hypertarget{data-generation}{%
+\subsection{Data Generation}\label{data-generation}}
+
+Let \(\mathbb{X} \in \mathbb{R}^{n \times p}\), \(\mathbb{Y} \in \mathbb{R}^{n \times r}\), and \(\beta \in \mathbb{R}^{p \times r}\) so that
+
+\begin{equation}
+\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
+\label{eq:datalinregression}\notag
+\end{equation}
+
+These values are generated in the following way:
+
+Let \(\beta = \mathbb{B} \circ \mathbb{V}\) where \(vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)\) and \(\mathbb{V} \in \mathbb{R}^{p \times r}\) is a matrix containing \(pr\) random bernoulli draws with \texttt{sparse} probability being equal to 1.
+In effect, each \(\beta\) entry is turned off with equal probability.
+
+Now, if \texttt{sigma\ =\ "tridiag"} then \(\Sigma_{xx}\) and \(\Sigma_{y | x}\) is constructed so that \(\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}\) and \(\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}\), respectively.
+This ensures that the inverses will be tridiagonal (sparse).
+
+Then for \(n\) independent, identically distributed samples, we have that \(X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)\) and \(E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)\).
+
+If \texttt{sigma\ =\ "compound"} then the data is generated similarly but \(\Omega_{xx} \equiv \Sigma_{xx}^{-1}\) and \(\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}\) both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.
+
+An additional 1000 samples will be generated for the testing set -- regardless of the training set size (\(n\)).
+For instance, in the 3-fold cross validation procedure where \texttt{n\ =\ 100} and \texttt{p\ =\ 100}, 1000 samples would be set aside for later testing and \(100*(2/3)\) samples would be used for training in each fold (ie: high dimensional setting).
+
+Possible parameters in simulation:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{reps} = 20
+\item
+  \texttt{n} = (100, 1000)
+\item
+  \texttt{p} = (10, 50, 100, 150)
+\item
+  \texttt{r} = c(1, 5, 10)
+\item
+  \texttt{sparse} = c(0.5)
+\item
+  \texttt{sigma} = c(``tridiag'')
+\end{itemize}
+
+Note that prior to estimation, the intercept is removed by centering the data.
+
+\hypertarget{plots-1}{%
+\subsection{Plots}\label{plots-1}}
+
+\hypertarget{high-dimension}{%
+\subsubsection{High Dimension}\label{high-dimension}}
+
+Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE).
+Also, \texttt{OLS} and \texttt{oracleS} will not be show in the high dimensional setting plots because of poor performance.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim1-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim1}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim2-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim2}
+\end{figure}
+
+\vspace{1cm}
+
+\textbf{Notable: N = 100, P = 150, R = 10, sparse = 0.5, sigma = ``tridiag''}
+
+\begin{longtable}[]{@{}ccc@{}}
+\caption{Table caption here.}\tabularnewline
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+mean\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+mean\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.5056\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.5122\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.341\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.014\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.419\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.083\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+ridge\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.479\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.128\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+lasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.627\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.27\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+5.932\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+4.001\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+glasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+7.57\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+5.412\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+13.18\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+10.11\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+OLS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+14.41\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+11.24\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+52.07\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+44.62\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\vspace{1cm}
+
+\hypertarget{low-dimension}{%
+\subsubsection{Low Dimension}\label{low-dimension}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim4-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim4}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim5-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim5}
+\end{figure}
+
+\vspace{1cm}
+
+\textbf{Notable: N = 1000, P = 150, R = 5, sparse = 0.5, sigma = ``tridiag''}
+
+\begin{longtable}[]{@{}ccc@{}}
+\caption{Table caption here.}\tabularnewline
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+mean\strut
+\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+mean\strut
+\end{minipage} & \begin{minipage}[b]{0.13\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.5021\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.5088\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+ridge\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.7821\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.3177\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+lasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.7866\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.3137\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.8772\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.2536\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.9173\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.2396\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+glasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.9924\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.1793\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+OLS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.026\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.1593\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.175\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.08156\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.769\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.3867\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.994\strut
+\end{minipage} & \begin{minipage}[t]{0.13\columnwidth}\centering
+0.5292\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{takeaways}{%
+\subsection{Takeaways}\label{takeaways}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  In high dimensional settings, \texttt{shrinkBO} (penalty: \(\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}\)) and \texttt{shrinkB} (penalty: \(\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}\)) perform increasingly well relative (and superior) to the others when \(p >> n\).
+It's not surprising that \texttt{shrinkBO} performs the best because the embedded assumptions most closely match the data generating model.
+\item
+  In the high dimension setting, the oracle estimators \texttt{oracleO} (penalty: \(\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}\)) and \texttt{oracleS} (penalty: \(\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}\)) performed worse or comparable to OLS.
+The poor performance of \texttt{oracleS} is likely due to the fact that the sample estimate of \(\Omega\) is not identifiable when \(p > n\).
+\item
+  When \(n > p\) we see that \texttt{shrinkB} performs terribly.
+Interestingly, \texttt{shrinkBO} is still one of the better performing estimators -- though worse than both \texttt{lasso} and \texttt{ridge}.
+\item
+  It is interesting that \texttt{oracleO} performed worse than \texttt{oracleS} in the final table.
+It appears that estimating the covariance matrix \(\Sigma_{xy}\) well is \emph{more} important than estimating \(\Omega\) well.
+\end{enumerate}
+
+\hypertarget{shrinking-covariance-models}{%
+\subsection{Shrinking Covariance Models}\label{shrinking-covariance-models}}
+
+In the following estimators, let the superscript * denote the oracle estimator:
+
+\begin{itemize}
+\item
+  \texttt{shrinkB} = shrinking characteristics regression estimator where optimal tuning parameter is chosen to minimize in-sample MSPE via 3-fold CV (penalty: \(\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}\))
+\item
+  \texttt{shrinkBO} = shrinking characteristics estimator that penalizes the sum of the absolute values of \(\beta = \Omega\Sigma_{xy}\) \emph{and} \(\Omega\) (penalty: \(\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}\))
+\end{itemize}
+
+For each of the estimators, \(\Sigma_{xy}\) is estimated by the sample covariance matrix \(\hat{\Sigma}_{xy}\) times some constant factor \(k \in (0.1, 0.2, ..., 0.9, 1)\).
+We are shrinking \(\hat{\Sigma}_{xy}\) by a constant to determine if there are any benefits to doing so.
+
+\hypertarget{data-generation-1}{%
+\subsection{Data Generation}\label{data-generation-1}}
+
+Let \(\mathbb{X} \in \mathbb{R}^{n \times p}\), \(\mathbb{Y} \in \mathbb{R}^{n \times r}\), and \(\beta \in \mathbb{R}^{p \times r}\) so that
+
+\begin{equation}
+\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}
+\label{eq:datalinregression2}\notag
+\end{equation}
+
+These values are generated in the following way:
+
+Let \(\beta = \mathbb{B} \circ \mathbb{V}\) where \(vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)\) and \(\mathbb{V} \in \mathbb{R}^{p \times r}\) is a matrix containing \(pr\) random bernoulli draws with \texttt{sparse} probability being equal to 1.
+In effect, each \(\beta\) entry is turned off with equal probability.
+
+Now, if \texttt{sigma\ =\ "tridiag"} then \(\Sigma_{xx}\) and \(\Sigma_{y | x}\) is constructed so that \(\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}\) and \(\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}\), respectively.
+This ensures that the inverses will be tridiagonal (sparse).
+
+Then for \(n\) independent, identically distributed samples, we have that \(X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)\) and \(E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)\).
+
+If \texttt{sigma\ =\ "compound"} then the data is generated similarly but \(\Omega_{xx} \equiv \Sigma_{xx}^{-1}\) and \(\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}\) both have entries equal to 1 on the diagonal and 0.9 on the off-diagonal.
+
+An additional 1000 samples will be generated for the testing set -- regardless of the training set size (\(n\)).
+For instance, in the 3-fold cross validation procedure where \texttt{n\ =\ 100} and \texttt{p\ =\ 100}, 1000 samples would be set aside for later testing and \(100*(2/3)\) samples would be used for training in each fold (ie: high dimensional setting).
+
+Possible parameters in simulation:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{reps} = 20
+\item
+  \texttt{n} = (100, 1000)
+\item
+  \texttt{p} = (10, 50, 100, 150, 200)
+\item
+  \texttt{r} = c(1, 5, 10)
+\item
+  \texttt{sparse} = c(0.5)
+\item
+  \texttt{sigma} = c(``tridiag'', ``compound'')
+\end{itemize}
+
+Note that prior to estimation, the intercept is removed by centering the data.
+
+\hypertarget{plots-2}{%
+\subsection{Plots}\label{plots-2}}
+
+\hypertarget{high-dimension-1}{%
+\subsubsection{High Dimension}\label{high-dimension-1}}
+
+\hypertarget{shrinkb}{%
+\paragraph{\texorpdfstring{\texttt{shrinkB}}{shrinkB}}\label{shrinkb}}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim7-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim7}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim8-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim8}
+\end{figure}
+
+\hypertarget{shrinkbo}{%
+\paragraph{\texorpdfstring{\texttt{shrinkBO}}{shrinkBO}}\label{shrinkbo}}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim9-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim9}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim10-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim10}
+\end{figure}
+
+\vspace{1cm}
+
+\hypertarget{low-dimension-1}{%
+\subsubsection{Low Dimension}\label{low-dimension-1}}
+
+\hypertarget{shrinkb-1}{%
+\paragraph{\texorpdfstring{\texttt{shrinkB}}{shrinkB}}\label{shrinkb-1}}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim11-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim11}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim12-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim12}
+\end{figure}
+
+\hypertarget{shrinkbo-1}{%
+\subsubsection{\texorpdfstring{\texttt{shrinkBO}}{shrinkBO}}\label{shrinkbo-1}}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim13-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim13}
+\end{figure}
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth,]{Manuscript_files/figure-latex/scpmesim14-1}
+
+}
+
+\caption{Figure caption here.}\label{fig:scpmesim14}
+\end{figure}
+
+\vspace{1cm}
+
+\hypertarget{takeaways-1}{%
+\subsection{Takeaways}\label{takeaways-1}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  In the high dimensional settings, it does appear that shrinking the sample covariance matrix \(\hat{\Sigma}_{xy}\) by a constant factor helps in reducing MSPE.
+This is indicated by the fact that the optimal \texttt{const} hovers around 0.5 for each of the estimators \texttt{shrinkB} and \texttt{shrinkBO}.
+\item
+  In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.
+\item
+  The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.
+\item
+  The larger the dimension of \(Y\), the more beneficial shrinkage will likely be (not that surprising)
+\end{enumerate}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+The general optimization problem outlined in \citet{molstad2017shrinking} is to estimate \(\hat{\Omega}\) such that
+
+\begin{equation}
+  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+\label{eq:penloglik3}\notag
+\end{equation}
+
+where \(S\) is the sample covariance of \(X \in \mathbb{R}^{p}\) (denominator \(n\)) and \(\left\| \cdot \right\|_{1}\) denotes the \(L_{1}\)-norm.
+In addition, \(A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}\) are matrices assumed to be known and specified by the user.
+This objective function is a penalized log-likelihood for the marginal precision matrix of \(X\), which we denote here as \(\Omega \equiv \Sigma_{xx}^{-1}\).
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ -l\left( \Omega \right) + P_{\lambda}\left( \Omega \right) \right\}
+\label{eq:penloglik4}\notag
+\end{equation}
+
+where \(P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1}\).
+Under this particular likelihood, it is assumed that each observation of \(X_{i}\) in a sample size of size \(n\) follows a \(p\)-variate normal distribution (ie: \(X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)\)) -- however, Dennis Cook and others have shown this objective function to work well as a generic loss even when these assumptions are not met.
+
+This particular formulation for the penalty leads to many new, interesting, and novel estimators for \(\Omega\).
+For instance, if in addition to \(X\) we also observe \(n\) copies of the random variable \(Y\), we might set \(A = I_{p}, B = \Sigma_{xy}\) where \(\Sigma_{xy}\) is the covariance matrix of \(X\) and \(Y\), and \(C = 0\).
+In which case
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1}
+\label{eq:pen3}\notag
+\end{equation}
+
+This objective function estimates an \(\Omega\) via the marginal log-likelihood of \(X\) under the assumption that the forward regression coefficient \(\beta\) is sparse (recall that \(\beta \equiv \Omega\Sigma_{xy}\)).
+We could also take \(B = \left[ \Sigma_{xy}, I_{p} \right]\) so that the identity matrix (dimension \(p\)) is appended to the covariance matrix of \(X\) and \(Y\).
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
+\label{eq:pen4}\notag
+\end{equation}
+
+In this case, not only are we assuming that \(\beta\) is sparse, but we are also assuming sparsity in \(\Omega\).
+Furthermore, if we let \(\mathbb{X} \in \mathbb{R}^{n \times p}\) be a matrix with rows \(X_{i} - \bar{X}\) and \(\mathbb{Y} \in \mathbb{R}^{n \times r}\) be a matrix with rows \(Y_{i} - \bar{Y}\), we might also take \(A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}\) so that
+
+\begin{equation}
+\begin{split}
+\hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{1} \right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| \mathbb{Y} - \mathbb{X}\beta \right\|_{1} \right\}
+\label{eq:penloglik5}\notag
+\end{split}
+\end{equation}
+
+This estimator encourages the predicted values \(\hat{\mathbb{Y}} = \mathbb{X}\hat{\beta} = \mathbb{X}\hat{\Omega}\Sigma_{xy}\) to be exactly equal to the observed responses \(\mathbb{Y}\).
+We will name this estimator the \emph{lasso SCPME estimator}.
+Note that in practice - for any of these estimators - we do not know the true covariance matrix \(\Sigma_{xy}\) but we could provide the sample estimate \(\hat{\Sigma}_{xy} = \mathbb{X}^{T}\mathbb{Y}/n\) in its place.
+
+All of these estimators fall into the SCPME (shrinking characteristics of precision matrix estimators) algorithmic framework outlined in the paper.
+The augmented ADMM algorithm (details \href{https://mgallow.github.io/SCPME/articles/Details.html\#augmented-admm-algorithm}{here}) is the following:
+
+Set \(k = 0\) and repeat steps 1-6 until convergence.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Compute \(G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \Lambda^{k}/\rho \right)B^{T}\)
+\item
+  Decompose \(S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}\) (via the spectral decomposition).
+\item
+  Set \(\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)\)
+\item
+  Set \(Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda_{k}, \rho^{-1}\lambda \right)\)
+\item
+  Set \(\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)\)
+\item
+  Replace \(k\) with \(k + 1\).
+\end{enumerate}
+
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{appendix}{%
+\chapter{Appendix}\label{appendix}}
+
+\hypertarget{proofs}{%
+\section{Proofs}\label{proofs}}
+
+\hypertarget{proofomegaalgo}{%
+\subsection{Proof of \eqref{eq:omegaalgo}}\label{proofomegaalgo}}
+
+\begin{equation}
+\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\}
+\label{eq:appendixomegaloglik}\notag
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
+  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
+\label{eq:appendixomegagradient}\notag
+\end{split}
+\end{equation}
+
+Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
+First set the gradient equal to zero and decompose \(\Omega^{k + 1} = VDV^{T}\) where \(D\) is a diagonal matrix with diagonal elements equal to the eigen values of \(\Omega^{k + 1}\) and \(V\) is the matrix with corresponding eigen vectors as columns:
+
+\begin{equation}
+S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T}\notag
+\end{equation}
+
+This equivalence implies that
+
+\begin{equation}
+\phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1})\notag
+\end{equation}
+
+where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
+
+\begin{equation}
+\begin{split}
+  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
+  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
+\end{split}
+\notag
+\end{equation}
+
+In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) then
+
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
+\label{eq:appendixomegaproof}\notag
+\end{equation}
+
+\hypertarget{proofZZalgo}{%
+\subsection{Proof of \eqref{eq:ZZalgo}}\label{proofZZalgo}}
+
+\begin{equation}
+Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\}
+\label{eq:appendixZZloglik}\notag
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
+\label{eq:appendixZZgradient}\notag
+\end{split}
+\end{equation}
+
+where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+
+\begin{equation}
+Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right)
+\label{eq:ZZsoftproof}\notag
+\end{equation}
+
+for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} > 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \notag
+\end{equation}
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} < 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \notag
+\end{equation}
+
+This implies that \(\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\). Putting all the pieces together, we arrive at
+
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\label{eq:appendixZZproof}\notag
+\end{split}
+\end{equation}
+
+where soft is the soft-thresholding function.
+
+\hypertarget{proofdualresidual}{%
+\subsection{Proof of \eqref{eq:dualresidual}}\label{proofdualresidual}}
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
+  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
+\label{eq:appendixdualresidual}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{proofdualopt}{%
+\subsection{Proof of \eqref{eq:dualopt}}\label{proofdualopt}}
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\label{eq:appendixdualopt}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{proof-of-blahhhh}{%
+\subsection{Proof of BLAHHHH}\label{proof-of-blahhhh}}
+
+To see why this particular function was used, consider the Taylor's expansion of \(\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2\):
+
+\begin{equation}
+\begin{split}
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
+\label{eq:taylors}\notag
+\end{split}
+\end{equation}
+
+\textbf{Note:}
+
+\begin{equation}
+  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
+\label{eq:gradient}\notag
+\end{equation}
+
+\begin{equation}
+\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
+\label{eq:hessian}\notag
+\end{equation}
+
+This implies that
+
+\begin{equation}
+\begin{split}
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
+  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
+  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
+  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
+\label{eq:penapprox}\notag
+\end{split}
+\end{equation}
+
+Let us now plug in this equality into our optimization problem in step one:
+
+\begin{equation}
+\begin{split}
+  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
+  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
+ tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+\label{eq:omegaapprox}\notag
+\end{split}
+\end{equation}
+
+where \(G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}\).
+
+\hypertarget{proofOmegak}{%
+\subsection{Proof of \eqref{eq:Omegak}}\label{proofOmegak}}
+
+\begin{equation}
+\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}
+\label{eq:appendixomegaloglik2}\notag
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
+  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
+\label{eq:appendixomegagradient2}\notag
+\end{split}
+\end{equation}
+
+Note that we need to honor the symmetric constraint given by \(\Omega\). By setting the gradient equal to zero and multiplying all off-diagonal elements by \(1/2\), this simplifies to
+
+\begin{equation}
+S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
+\end{equation}
+
+We can then decompose \(\Omega^{k + 1} = VDV^{T}\) where \(D\) is a diagonal matrix with diagonal elements equal to the eigen values of \(\Omega^{k + 1}\) and \(V\) is the matrix with corresponding eigen vectors as columns.
+
+\begin{equation}
+S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \notag
+\end{equation}
+
+This equivalence implies that
+
+\begin{equation}
+\phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \notag
+\end{equation}
+
+where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value and \(D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}\). Therefore
+
+\begin{equation}
+\begin{split}
+  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
+  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
+\end{split}
+\notag
+\end{equation}
+
+In summary, if we decompose \(S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}\) then
+
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T}
+\label{eq:appendixomegaproof2}\notag
+\end{equation}
+
+\hypertarget{proofZk}{%
+\subsection{Proof of \eqref{eq:Zk}}\label{proofZk}}
+
+\begin{equation}
+Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
+\label{eq:appendixZZloglik2}\notag
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
+\label{eq:appendixZZgradient2}\notag
+\end{split}
+\end{equation}
+
+where \(\mbox{sign(Z)}\) is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+
+\begin{equation}
+Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right)
+\label{eq:ZZsoftproof2}\notag
+\end{equation}
+
+for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} > 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \notag
+\end{equation}
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} < 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \notag
+\end{equation}
+
+This implies that \(\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\). Putting all the pieces together, we arrive at
+
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
+&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
+\label{eq:appendixZZproof2}\notag
+\end{split}
+\end{equation}
+
+where soft is the soft-thresholding function.
+
+\hypertarget{proofstopproof}{%
+\subsection{Proof of \eqref{eq:stopproof}}\label{proofstopproof}}
+
+This residual is derived from the fact. Because \(\Omega^{k + 1}\) is the argument that minimizes \(L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)\),
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
+  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
+  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
+  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
+  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
+  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
+\label{eq:appendixstopproof}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{proofdualopt2}{%
+\subsection{Proof of \eqref{eq:dualopt2}}\label{proofdualopt2}}
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\label{eq:appendixdualopt2}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{connection-to-joint-log-likelihood}{%
+\subsection{Connection to joint log-likelihood}\label{connection-to-joint-log-likelihood}}
+
+The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of \(X\) and \(Y\) (under a few assumptions) when we consider its analogous \emph{ridge} version - the \emph{ridge SCPME estimator}:
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\label{eq:penregression}\notag
+\end{equation}
+
+To see this, let us suppose that we have \(n\) independent copies of the random pair \((Y_{i}, X_{i})\) and we assume a linear relationship of the following form:
+
+\begin{equation}
+Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
+\label{eq:linregression}\notag
+\end{equation}
+
+where \(E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)\) and \(X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)\).
+These two assumptions imply that the conditional distribution of \(Y_{i}|X_{i}\) is of the form
+
+\begin{equation}
+Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
+\label{eq:linnormal}\notag
+\end{equation}
+
+We can use this conditional distribution along with the marginal distribution of \(X\) to derive the joint likelihood of \(X\) and \(Y\).
+Similar to before, we will take \(\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}\) for convenience.
+We will also let \(f\) denote the probability distribution function for each respective variable.
+
+\begin{equation}
+\begin{split}
+  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
+  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
+  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
+  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
+  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
+\label{eq:jointlik}\notag
+\end{split}
+\end{equation}
+
+where \(\mbox{etr}\left( \cdot \right)\) denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:
+
+\begin{equation}
+\begin{split}
+  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const.
++ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
+  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
+\label{eq:jointloglik}\notag
+\end{split}
+\end{equation}
+
+\textbf{Note:} this form simplifies significantly if we solve for \(\mu_{x}\) and \(\mu_{y}\) and make a few additional assumptions about our data.
+
+\begin{equation}
+\begin{split}
+ \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
+ &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
+ \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
+ \label{eq:gradient2}\notag
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
+ &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
+ &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
+ &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
+ \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
+ \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
+ \Rightarrow \hat{\mu}_{x} &= \bar{X}
+\label{eq:gradient3}\notag
+\end{split}
+\end{equation}
+
+Therefore, by plugging in \(\hat{\mu}_{x}\) into \(\hat{\mu}_{y}\), we find that \(\hat{\mu}_{y} = \bar{Y}\) and \(\hat{\mu}_{x} = \bar{X}\).
+
+Without loss of generality, let us assume that \(\bar{X} = \bar{Y} = 0\).
+This can be achieved by simply centering the data by the sample averages.
+Putting all of this together and recalling that \(\beta \equiv \Omega\Sigma_{xy}\), we have that the partially maximized joint log-likelihood is the following:
+
+\begin{equation}
+\begin{split}
+  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const.
++ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
+  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
+  &= const.
++ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
+  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
+  &= const.
++ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
+  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
+\label{eq:partialjointloglik}\notag
+\end{split}
+\end{equation}
+
+where \(S = \mathbb{X}^{T}\mathbb{X}/n\). Now suppose we are interested in solving for \(\Omega\):
+
+\begin{equation}
+\begin{split}
+  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
+\label{eq:omegajointloglik}\notag
+\end{split}
+\end{equation}
+
+where \(\left\|\cdot\right\|_{F}\) denotes the Frobenius norm.
+Further, let us assume that, given \(X\), each of the \(r\) responses are pairwise independent with equal variance so that \(\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}\) and let \(\lambda = 2/(n\sigma_{y | x}^{2})\).
+Therefore, we have that
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\label{eq:omegajointmle}\notag
+\end{equation}
+
+Notice that this is exactly the ridge SCPME estimator!
+
+\hypertarget{takeaways-from-connection-to-joint-log-likelihood}{%
+\subsection{Takeaways from connection to joint log-likelihood}\label{takeaways-from-connection-to-joint-log-likelihood}}
+
+We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for \(\Omega \equiv \Sigma_{xx}^{-1}\) when the following assumptions hold:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Each observation \((Y_{i}, X_{i})\) is independent and linearly distributed such that
+\end{enumerate}
+
+\begin{equation}
+Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
+\label{eq:linregression2}\notag
+\end{equation}
+
+where \(E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)\) and \(X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)\).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\item
+  Given \(X\), each of the \(r\) responses in \(Y \in \mathbb{R}^{r}\) is independent of one another with equal variance such that \(\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}\).
+\item
+  Let the tuning parameter \(\lambda = 2/(n\sigma_{y | x}^{2})\).
+\end{enumerate}
+
+In addition, only a very slight modification of the augmented ADMM algorithm in \citet{molstad2017shrinking} is required to compute this estimate:
+
+Set \(k = 0\) and repeat steps 1-6 until convergence.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Compute \(G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}\)
+\item
+  Decompose \(S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}\) (via the spectral decomposition).
+\item
+  Set \(\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)\)
+\item
+  Set \(Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)\)
+\item
+  Set \(\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)\)
+\item
+  Replace \(k\) with \(k + 1\).
+\end{enumerate}
+
+Note that the only difference is in step 4.
+
+There are a few takeaways we can make after revealing this connection.
+The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to \(\Omega\).
+The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator.
+No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it.
+We show this below:
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
+\label{eq:penregression2}\notag
+\end{equation}
+
+\begin{equation}
+\begin{split}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
+  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
+  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
+  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
+\label{eq:penregressionproof}\notag
+\end{split}
+\end{equation}
+
+by multiplying all of the off-diagonal elements by \(1/2\). Note that we cannot isolate \(\hat{\Omega}\).
+
+\hypertarget{admmsigma-r-package}{%
+\chapter{\texorpdfstring{\texttt{ADMMsigma} R Package}{ADMMsigma R Package}}\label{admmsigma-r-package}}
+
+\texttt{ADMMsigma} is an R package that estimates a penalized precision matrix, often denoted \(\Omega\), via the alternating direction method of multipliers (ADMM) algorithm.
+Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user, which is the primary goal of this package.
+
+The package currently supports a general elastic-net penalty that allows for both ridge and lasso-type penalties as special cases.
+In particular, the algorithm solves the following optimization problem:
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{tr(S\Omega) - \log\det\left(\Omega\right) + \lambda\left[\frac{1 - \alpha}{2}\left\|\Omega\right\|_{F}^{2} + \alpha\left\|\Omega\right\|_{1} \right] \right\} \]
+
+where \(\lambda > 0\), \(0 \leq \alpha \leq 1\) are tuning parameters, \(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm, and we define \(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\).
+
+A list of functions contained in the package can be found below:
+
+\begin{itemize}
+\item
+  \texttt{ADMMsigma()} computes the estimated precision matrix via the ADMM algorithm (ridge, lasso, and elastic-net regularization optional)
+\item
+  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision matrix via closed-form solution
+\item
+  \texttt{plot.ADMMsigma()} produces a heat map or optional line graph for cross validation errors
+\item
+  \texttt{plot.RIDGEsigma()} produces a heat map or optional line graph for cross validation errors
+\end{itemize}
+
+\hypertarget{installation}{%
+\section{Installation}\label{installation}}
 
@@
 \begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-\KeywordTok{library}\NormalTok{(microbenchmark)}
-
-\CommentTok{# generate data from tri-diagonal (sparse) matrix compute covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\NormalTok{(}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j))}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{1000} \OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# glasso (for comparison)}
-\KeywordTok{microbenchmark}\NormalTok{(glasso}\OperatorTok{::}\KeywordTok{glasso}\NormalTok{(}\DataTypeTok{s =}\NormalTok{ S, }\DataTypeTok{rho =} \FloatTok{0.1}\NormalTok{))}
+\CommentTok{# The easiest way to install is from CRAN}
+\KeywordTok{install.packages}\NormalTok{(}\StringTok{"ADMMsigma"}\NormalTok{)}
+
+\CommentTok{# You can also install the development version from GitHub:}
+\CommentTok{# install.packages('devtools')}
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/ADMMsigma"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: milliseconds
-##                              expr      min       lq     mean   median
-##  glasso::glasso(s = S, rho = 0.1) 49.46673 53.37757 58.35196 55.90935
-##        uq      max neval
-##  60.77517 92.68082   100
-\end{verbatim}
+\vspace{0.5cm}
+
+This package is hosted on Github at \href{https://github.com/MGallow/ADMMsigma}{github.com/MGallow/ADMMsigma}.
+The project website is located at \href{http://mattxgalloway.com/ADMMsigma/}{mattxgalloway.com/ADMMsigma}.
+
+\hypertarget{tutorial}{%
+\section{Tutorial}\label{tutorial}}
+
+By default, \texttt{ADMMsigma} will estimate a penalized precision matrix, \(\Omega\), using the elastic-net penalty and choose the optimal \(\lambda\) and \(\alpha\) tuning parameters.
+The primary function is simply \texttt{ADMMsigma()}.
+The input value \(X\) is an \(n \times p\) data matrix so that there are \(n\) rows each representing an observation and \(p\) columns each representing a unique feauture or variable.
+
+Here, we will use a \(100 \times 5\) data matrix that is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix \(S\).
+A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal, which is useful for illustration purposes because the object is sparse (many zero entries) and the shrinkage penalty should prove useful.
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - default tolerance}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-04}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
+\CommentTok{# elastic-net type penalty (set tolerance to 1e-8)}
+\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-04, tol.rel = 1e-04,      trace = "none")
-##      min       lq     mean   median       uq      max neval
-##  77.2134 83.51351 89.71565 85.37738 94.37814 126.0049   100
+## 
+## Call: ADMMsigma(X = X, tol.abs = 1e-08, tol.rel = 1e-08)
+## 
+## Iterations: 48
+## 
+## Tuning parameters:
+##       log10(lam)  alpha
+## [1,]      -1.599      1
+## 
+## Log-likelihood: -108.41003
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.15283 -1.26902  0.00000  0.00000  0.19765
+## [2,] -1.26902  2.79032 -1.32206 -0.08056  0.00925
+## [3,]  0.00000 -1.32206  2.85470 -1.17072 -0.00865
+## [4,]  0.00000 -0.08056 -1.17072  2.49554 -1.18959
+## [5,]  0.19765  0.00925 -0.00865 -1.18959  1.88121
 \end{verbatim}
+
+\vspace{0.5cm}
+
+We can see that the optimal \(\alpha\) value selected is one. This selection corresponds with a lasso penalty -- a special case of the elastic-net penalty.
+
+We can also explicitly assume sparsity in our estimate rather than let the package decide by restricting the class of penalties to the lasso.
+We do this by simply setting \texttt{alpha\ =\ 1} in our function:
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - tolerance 1e-8}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
+\CommentTok{# lasso penalty (default tolerance)}
+\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{)}
 \end{Highlighting}
@@
 \begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-08, tol.rel = 1e-08,      trace = "none")
-##       min       lq     mean   median       uq      max neval
-##  258.5389 261.5402 272.3741 267.8829 274.7276 353.4726   100
+## 
+## Call: ADMMsigma(X = X, alpha = 1)
+## 
+## Iterations: 24
+## 
+## Tuning parameters:
+##       log10(lam)  alpha
+## [1,]      -1.599      1
+## 
+## Log-likelihood: -108.41193
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.15308 -1.26962  0.00000  0.00000  0.19733
+## [2,] -1.26962  2.79103 -1.32199 -0.08135  0.00978
+## [3,]  0.00000 -1.32199  2.85361 -1.16953 -0.00921
+## [4,]  0.00000 -0.08135 -1.16953  2.49459 -1.18914
+## [5,]  0.19733  0.00978 -0.00921 -1.18914  1.88096
 \end{verbatim}
+
+\vspace{0.5cm}
+
+\texttt{ADMMsigma} also has the capability to provide plots for the cross validation errors.
+This allows the user to analyze and manually select the appropriate tuning parameters.
+In the heatmap plot below, the bright, white areas of the heat map correspond to a better tuning parameter selection (low validation error).
+In the line graph, each line corresponds to a different \(\alpha\) tuning parameter.
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - default parameter grid}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
+\CommentTok{# produce CV heat map for ADMMsigma}
+\NormalTok{ADMM =}\StringTok{ }\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{)}
+\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: seconds
-##                          expr      min       lq     mean   median       uq
-##  ADMMsigma(X, trace = "none") 8.338241 8.341611 8.536446 8.472933 8.515822
-##       max neval
-##  9.013621     5
-\end{verbatim}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/ADMMsigmapackage1-1}
+
+}
+
+\caption{CV heatmap for ADMMsigma tutorial.}\label{fig:ADMMsigmapackage1}
+\end{figure}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma parallel CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{cores =} \DecValTok{3}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
+\CommentTok{# produce line graph for CV errors for ADMMsigma}
+\KeywordTok{plot}\NormalTok{(ADMM, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: seconds
-##                                     expr      min       lq     mean
-##  ADMMsigma(X, cores = 3, trace = "none") 9.285137 9.315978 9.470666
-##   median       uq      max neval
-##  9.40943 9.426579 9.916207     5
-\end{verbatim}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/ADMMsigmapackage2-1}
+
+}
+
+\caption{CV line graph for ADMMsigma tutorial.}\label{fig:ADMMsigmapackage2}
+\end{figure}
+
+\vspace{0.5cm}
+
+\texttt{ADMMsigma} has a number of more advanced options such as cross validation criteria, regularization path, and parallel CV that are explained in more detail on the project website at \href{http://mattxgalloway.com/ADMMsigma/}{mattxgalloway.com/ADMMsigma}.
+
+\hypertarget{scpme-r-package}{%
+\chapter{\texorpdfstring{\texttt{SCPME} R Package}{SCPME R Package}}\label{scpme-r-package}}
+
+\texttt{SCPME} is an R package that estimates a penalized precision matrix via a modified alternating direction method of multipliers (ADMM) algorithm as described in \citet{molstad2017shrinking}.
+Specifically, the modified ADMM algorithm solves the following optimization problem:
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S \Omega\right) - \log\det\left(\Omega\right) + \lambda\left\| A\Omega B - C \right\|_{1} \right\} \]
+
+where \(\lambda > 0\) is a tuning parameter, \(A, B, \mbox{ and } C\) are known, user-specified matrices, and we define \(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\).
+
+This form of penalty leads to many new, interesting, and novel estimators for the precision matrix \(\Omega\).
+Users can construct matrices \(A, B, \mbox{ and } C\) so that emphasis is placed on the sum, absolute value of a \emph{characteristic} of \(\Omega\).
+We will explore a few of these estimators in the tutorial section.
+
+A list of functions contained in the package can be found below:
+
+\begin{itemize}
+\item
+  \texttt{shrink()} computes the estimated precision matrix
+\item
+  \texttt{data\_gen()} data generation function (for convenience)
+\item
+  \texttt{plot.shrink()} produces a heat map or optional line graph for the cross validation errors
+\end{itemize}
+
+\hypertarget{installation-1}{%
+\section{Installation}\label{installation-1}}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - likelihood convergence criteria}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{crit =} \StringTok{"loglik"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
+\CommentTok{# The easiest way to install is from CRAN}
+\KeywordTok{install.packages}\NormalTok{(}\StringTok{"SCPME"}\NormalTok{)}
+
+\CommentTok{# You can also install the development version from GitHub:}
+\CommentTok{# install.packages('devtools')}
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/SCPME"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: seconds
-##                                           expr      min       lq     mean
-##  ADMMsigma(X, crit = "loglik", trace = "none") 7.028816 7.121599 7.185927
-##    median       uq      max neval
-##  7.181803 7.277249 7.320166     5
-\end{verbatim}
+\vspace{0.5cm}
+
+This package is hosted on Github at \href{https://github.com/MGallow/SCPME}{github.com/MGallow/SCPME}.
+The project website is located at \href{http://mattxgalloway.com/SCPME/}{mattxgalloway.com/SCPME}.
+
+\hypertarget{tutorial-1}{%
+\section{Tutorial}\label{tutorial-1}}
+
+The primary function in the \texttt{SCPME} package is \texttt{shrink()}.
+The input values \(X\) is an \(n \times p\) data matrix so that there are \(n\) rows each representing an observation and \(p\) columns each representing a unique variable and \(Y\) is an \(n \times r\) response matrix where \(r\) is the dimension of the response vector.
+By default, \texttt{SCPME} will estimate \(\Omega\) using a lasso penalty (\(A = I_{p}, B = I_{p}, \mbox{ and } C = 0\)) and choose the optimal \(\lambda\) tuning parameter that minimizes the mean squared prediction error for the regression of the variable \(Y\) on \(X\) (here \(I_{p}\) denotes a \(p\)-dimension identity matrix).
+If \(Y\) is not provided, then tuning parameter selection will be based on the validation likelihood.
+Note that \(\Omega\) (perhaps better denoted here as \(\Omega_{x}\)) will only have meaningful shrinkage unless the data vector \(X \in \mathbb{R^{p}}\) is multi-dimensional (\(p > 1\)).
+
+In this example, the data matrix is \(100 \times 5\) and the response is generated according to the following model:
+
+\[ Y_{i} = \beta^{T}X_{i} + E_{i} \]
+
+where \(E_{i} \sim N\left( 0, 1 \right)\) and \(X_{i}\) is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix \(S\).
+A tapered covariance matrix has the property that its inverse - the precision matrix - is tri-diagonal.
+Estimating this oracle precision matrix well and efficiently will be our primary interest.
+In addition, \(\beta\) is randomly generated and sparse.
+The data will be generated using the \texttt{data\_gen()} function contained in the package.
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark RIDGEsigma CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{), }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
+\KeywordTok{library}\NormalTok{(SCPME)}
+\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+
+\CommentTok{# generate 100 x 5 X data matrix and 100 x 1 Y data matrix}
+\NormalTok{data =}\StringTok{ }\KeywordTok{data_gen}\NormalTok{(}\DataTypeTok{p =} \DecValTok{5}\NormalTok{, }\DataTypeTok{n =} \DecValTok{100}\NormalTok{, }\DataTypeTok{r =} \DecValTok{1}\NormalTok{)}
+
+\CommentTok{# the oracle regression coefficients are sparse}
+\NormalTok{data}\OperatorTok{$}\NormalTok{betas}
 \end{Highlighting}
@@
 \begin{verbatim}
-## Unit: seconds
-##                                                      expr      min
-##  RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none") 12.22374
-##        lq     mean   median       uq      max neval
-##  12.37326 12.93705 13.01892 13.04356 14.02577     5
+##             [,1]
+## [1,] -0.25065233
+## [2,]  0.00000000
+## [3,]  0.69707555
+## [4,]  0.03153231
+## [5,]  0.00000000
 \end{verbatim}
 
-\bibliography{lib.bib}
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# shrink sum absolute entries in omega}
+\KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y)
+## 
+## Iterations: 37
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -1.163  0.069
+## 
+## Log-likelihood: -178.20154
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  1.60847 -0.73553 -0.14094 -0.04329 -0.11730
+## [2,] -0.73553  1.66045 -0.52579 -0.03576 -0.03342
+## [3,] -0.14094 -0.52579  1.73410 -0.85121 -0.07332
+## [4,] -0.04329 -0.03576 -0.85121  2.02541 -0.93612
+## [5,] -0.11730 -0.03342 -0.07332 -0.93612  1.62397
+\end{verbatim}
+
+\vspace{0.5cm}
+
+Notice here that the estimated precision matrix is \emph{not} sparse.
+This is due to the fact that our cross validation criteria is the mean-squared prediction error.
+We can estimate a new precision matrix using the validation likelihood as the cross validation criteria with the following command:
+
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# shrink sum absolute entries in omega}
+\KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{crit.cv =} \StringTok{"loglik"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, crit.cv = "loglik")
+## 
+## Iterations: 51
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -2.163  0.007
+## 
+## Log-likelihood: -120.02858
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.11926 -1.17294 -0.13784 -0.00678 -0.20014
+## [2,] -1.17294  2.28420 -0.81629  0.00009 -0.00001
+## [3,] -0.13784 -0.81629  2.45520 -1.42117  0.01650
+## [4,] -0.00678  0.00009 -1.42117  3.09526 -1.56839
+## [5,] -0.20014 -0.00001  0.01650 -1.56839  2.24703
+\end{verbatim}
+
+\vspace{0.5cm}
+
+All of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in \(\Omega\) (\(A = I_{p}, B = I_{p}, \mbox{ and } C = 0\)).
+In effect, this penalty embeds an assumption in our estimate that the true population precision matrix, \(\Omega\), is sparse.
+The flexibility of the penalty described in \citet{molstad2017shrinking} allows us to make other assumptions as well.
+For instance, in the penalty we could set \(A = I_{p}, B = \Sigma_{xy}\) where \(\Sigma_{xy}\) is the covariance matrix of \(X\) and \(Y\), and \(C = 0\).
+In which case our penalty function
+
+\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]
+
+This objective function estimates an \(\Omega\) via the marginal log-likelihood of \(X\) under the assumption that the forward regression coefficient \(\beta\) is sparse (recall that \(\beta \equiv \Omega\Sigma_{xy}\)).
+Of course, in practice, we do not know the true covariance matrix \(\Sigma_{xy}\) but we might consider using the sample estimate \(\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n\).
+
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# assume sparsity in beta}
+\NormalTok{lam_max =}\StringTok{ }\KeywordTok{max}\NormalTok{(}\KeywordTok{abs}\NormalTok{(}\KeywordTok{crossprod}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y)))}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\DataTypeTok{lam.max =}\NormalTok{ lam_max, }
+    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, B = cov(data$X, data$Y), nlam = 20, 
+##     lam.max = lam_max)
+## 
+## Iterations: 84
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -0.167  0.681
+## 
+## Log-likelihood: -133.98097
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.12467 -1.20016 -0.01149  0.01660 -0.20424
+## [2,] -1.20016  2.28202 -0.70370  0.03047 -0.01211
+## [3,] -0.01149 -0.70370  2.09284 -1.47505  0.01020
+## [4,]  0.01660  0.03047 -1.47505  2.86829 -1.45784
+## [5,] -0.20424 -0.01211  0.01020 -1.45784  2.18752
+\end{verbatim}
+
+Note that we specified the maximum \texttt{lam} value in the previous function to expand the tuning parameter grid.
+With these settings, the augmented ADMM algorithm also solves for the estimated \(\beta\) coefficient matrix simultaneously:
+
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# print estimated beta matrix}
+\NormalTok{shrink}\OperatorTok{$}\NormalTok{Z}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##            [,1]
+## [1,] 0.00000000
+## [2,] 0.00000000
+## [3,] 0.42221120
+## [4,] 0.04782093
+## [5,] 0.00000000
+\end{verbatim}
+
+\vspace{0.5cm}
+
+Another possible penalty is to set \(B = \left[ \Sigma_{xy}, I_{p} \right]\) so that the identity matrix is appended to the covariance matrix of \(X\) and \(Y\).
+That is, the penalty \(P\), is constructed as
+
+\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]
+
+In this case, we are equally penalizing the sum, absolute values of entries in \(\beta\) \emph{and} \(\Omega\) which embeds an assumption that \(\beta\) and \(\Omega\) are both sparse.
+
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# assume sparsity in beta AND omega}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }
+    \DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, B = cbind(cov(data$X, data$Y), 
+##     diag(ncol(data$X))), nlam = 20, lam.max = 10, lam.min.ratio = 1e-04)
+## 
+## Iterations: 46
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]       0.368  2.336
+## 
+## Log-likelihood: -624.54758
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  0.26376 -0.00003 -0.00015 -0.00010 -0.00005
+## [2,] -0.00003  0.24002 -0.00017 -0.00012 -0.00006
+## [3,] -0.00015 -0.00017  0.19066 -0.00516 -0.00020
+## [4,] -0.00010 -0.00012 -0.00516  0.20362 -0.00014
+## [5,] -0.00005 -0.00006 -0.00020 -0.00014  0.22750
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# print estimated beta}
+\NormalTok{shrink}\OperatorTok{$}\NormalTok{Z[, }\DecValTok{1}\NormalTok{, drop =}\StringTok{ }\OtherTok{FALSE}\NormalTok{]}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+##            [,1]
+## [1,] 0.06389361
+## [2,] 0.08542992
+## [3,] 0.14200713
+## [4,] 0.12357129
+## [5,] 0.09958374
+\end{verbatim}
+
+\vspace{0.5cm}
+
+\texttt{SCPME} also has the capability to provide plots (heatmaps and line graphs) for the cross validation errors.
+In the heatmap plot below, the more bright, white areas correspond to a better tuning parameter selection (lower cross validation error).
+
+\vspace{0.5cm}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# produce CV heat map}
+\KeywordTok{plot}\NormalTok{(shrink, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/SCPMEpackage1-1}
+
+}
+
+\caption{CV heatmap for SCPME tutorial}\label{fig:SCPMEpackage1}
+\end{figure}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# produce line graph}
+\KeywordTok{plot}\NormalTok{(shrink, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/SCPMEpackage2-1}
+
+}
+
+\caption{CV line graph for SCPME tutorial}\label{fig:SCPMEpackage2}
+\end{figure}
+
+\vspace{0.5cm}
+
+\texttt{SCPME} has a number of more advanced options including alternative convergence criteria and parallel CV that are explained in detail on the project website at \href{http://mattxgalloway.com/SCPME/}{mattxgalloway.com/SCPME}.
+
+\bibliography{lib.bib,packages.bib}
 

### 2019-03-10 index.Rmd
added notations and restructured

@@
 link-citations: yes
-#url: 'https://mgallow.github.io/oral_manuscript/'
+url: 'http://mattxgalloway.com/oral_manuscript/'
 github-repo: MGallow/oral_manuscript
-description: "This is a working manuscript in preparation for Matt Galloway's master's thesis defense."
+description: "Matt Galloway's Master's thesis."
 ---

### 2019-03-10 02-PME.Rmd
fixed bugs in tags

@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} (#eq:omegaauglagrange) \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} (\#eq:ZZauglagrange) \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) (\#eq:lamauglagrange)
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
 \end{align}
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} (\#eq:omegascaled)\notag \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} (\#eq:ZZscaled)\notag \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1} (\#eq:Uscaled)\notag
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
+  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
 \end{align}
@@
 \begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:xscaled)\notag \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} (\#eq:zscaled)\notag \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c (\#eq:uscaled)\notag
+  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
+  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
+  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
 \end{align}

### 2019-03-10 03-SCPME.Rmd
fixed bugs in tags

@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) (\#eq:omegaauglagrange2)\notag \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) (\#eq:ZZauglagrange2)\notag \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamauglagrange2)\notag
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
 \end{align}
@@
 L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
-(\#eq:auglagrange2)
+(\#eq:auglagrange3)
 \end{equation}
@@
 \begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} (\#eq:omegaaugadmm)\notag \\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} (\#eq:ZZaugadmm)\notag \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) (\#eq:lamaugadmm)\notag
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
 \end{align}

### 2019-03-10 01-intro.Rmd
largely completed chapters 1 and chapters 2

@@
 
-In many statistical applications, estimating the covariance matrix, $\Sigma$, for a set of random variables is a critical task.
-The covariance matrix is useful because it characterizes the *relationship* between variables.
-For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form
+In the simplest terms, inferential statistics boils down to two primary components: estimation and prediction.
+Estimation tends to refer to the process by which we infer properties and behavior about individual parameters.
+For instance, decision theory tell us that the method by which we estimate parameters should be one that incurs low risk or variance.
+Prediction, on the other hand, tends to refer to the process of determining the likelihood of an unknown or unforseeable event.
+Right now, prediction is king.
+The demand for good, predictive models has sparked huge investments in research and given rise to communities - like the machine learning community - whose primary goal is establishing good predictive models.
 
-\begin{equation}
-\Sigma_{xyz} = \begin{pmatrix}
-1 & 0 & 0.5 \\ 
-0 & 1 & 0 \\ 
-0.5 & 0 & 1
-\end{pmatrix}
-(\#eq:ex)\notag
-\end{equation}
+However, though prediction is getting a lot of attention, these two components are not entirely distinct and often go hand-in-hand.
+In fact, the success of many predictive models is largely contingent upon the ability to be efficient and proficient in estimation.
+That is, the succces and reliability of prediction is often a product of good estimation.
 
-We can gather valuable information from this matrix.
-First of all, we know that each of the variables has an equal variance of 1.
-Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0.
-This implies that any information in $X$ is useless in trying to gather information about $Y$.
-Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.
+For instance, many statistical models require the estimation of the co-variability and interaction between variables.
+This statistical object often comes in the form of a precision matrix ($\Omega$) - or the inverse of the covariance matrix.
+For this reason, in the last decade there has been an ever-expanding community devoted to matrix precision estimation.
+Like the covariance matrix, the precision matrix offers a powerful way of presenting the covariance - or pairwise variability between any two random variables.
 
-Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging.
-For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.
+Fisher's linear discriminant analysis (LDA) is one of these statistical models. Under the assumption of normal data, the model aims to classify observations into two or more populations of data.
 
-### references
+The central theme of this thesis is on precision matrix estimation but also expanding on a paper written by Aaron Molstad and Adam Rothman in 2017.
+In this paper, @molstad2017shrinking focused on the fact that only a "characteristic" of a precision matrix is required to fit these models.
 
-The reference we need here is @molstad2017shrinking!
-
-1.
-From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
+- From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
 For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.
@@
 
-3.
-Discuss linear regression application....
-where $\beta = \Omega_{*}\Sigma_{*XY}$.
-Like @witten2009covariance, this approach estimates the regression coefficients "using shrinkage estimators of the marginal precision matrix for the predictors".
+With the goal of improving performance..
 
-- Guide
+They offer a framework to do other things...
 
-- Model and notation
+Their approach/methodoloy was published in BLAH. Shrinking Characteristic of precision matrix estimators.
 
-## Outline
+The purpose of this work began with the desire to expand on the work in @molstad2017shrinking and to explore avenues that were mentioned but were not further investigated.
+One of these research directions was the application of their shrinking characteristics approach to regression.
+However, in order to get to that point and to build up the knowledge to understand and contribute new material, there were a number of concepts that needed to be understood along the way.
+This document will follow that journey.
 
-- Why do we care about covariance matrices? Covariance matrices are an object that summarizes the relationship between variables.
-
-- What is a precision matrix? Precision matrix is the inverse of a covariance matrix.
-
-- Precision matrices are powerful, essential in representing relationships in variables
-
-- In fact, required to be estimated to fit many statistical models.
-
-- That is, we must provide an object that accurately summarizes the relationship and interaction between variables in our model.
-
-- Many proposed shrinkage estimators when p is particularly large. Shrinkage.
-
-- However, to fit these models, Molstad and Rothman focused on the fact that onnly a "characteristic" of a precision matrix is required to fit these models.
-"We propose a framework to shrink a user-specified characteristic of a precision matrix estimator."
-
-- For instance, LDA, linear regression, ...
-
-- Their approach/methodology was published in BLAH. Shrinking characteristic of precision matrix estimators.
-
-- BREAK
-
-- We wanted to explore the regression application that was mentioned but not pursued/investigated
-
-- This document will outline the research and work leading up to that
-
-- The document is outlined as follows...
-
-- We will begin chapter 2 with a brief introduction to precision matrix estimation.
-This will include mentions of estimation methods/approaches and we will spend a particular amount of time elaborating on one approach which is estimation via the ADMM algorithm.
-This dicussion will be useful when we circle back to SCPME, the regression application, and the augmented ADMM algorithm developed in BLAH.
-
-- Lastly, the document will end with two brief tutorials for the R packages ADMMsigma and SCPME.
-These packages, developed by myself, will be mentioned throughout the document and were instrumental in this pursued line of research and facilitated many simulations and research direction explored throughout.
-Both packages have since been published on CRAN
+We will begin chapter 2 with a brief introduction to the area of precision matrix estimation and the gaussian log-likelihood function.
+This section will include mentions of other estimation methods and algorithms but most discussion we will spent on the ADMM algorithm.
+This discussion will be useful when we begin elaborating on the shrinking characteristics approach (sometimes referred to as SCPME), the augmented ADMM algorithm, and later the application to regression.
+Lastly, the document will end with two brief tutorials for the R packages `ADMMsigma` and `SCPME`.
+These packages were developed by myself to aid in simulation experiments and make it easier to branch into related research directions.
+Both packages have since been published on CRAN.
 
@@
 The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$.
-The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$.
+The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$ and the element-wise product will be denoted as $\mathbf{A} \circ \mathbf{B}$.
 Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

### 2019-03-10 02-PME.Rmd
largely completed chapters 1 and chapters 2

@@
 # Precision Matrix Estimation
-
-### Literature Review?
-
-- Articles that review covariance and precision matrix estimation in high dimensional settings are @pourahmadi2013high and @fan2016overview.
-
-- The person who initially proposed the lasso-penalized gaussian likelihood precision matrix estimation is @yuan2007model.
-
-- Other authors who have proposed methods with non-lasso penalizations are (Frobenius norms) @witten2009covariance, @rothman2014existence, (non-convex penalties) @lam2009sparsistency, and @fan2009network.
-
-- Standard alternating direction method of multipliers approaches are found in @boyd11distributed.
-
-- ADMM with modification based on majorize-minimize principle is found in @lange2016mm.
-
-- Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.
-
-- L1-penalized gaussian likelihood precision matrix estimator (@yuan2007model; @rothman2008sparse; @friedman2008sparse).
 
@@
 
-Consider the case where we observe $n$ independent, identically distributed copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$.
-That is, $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.
+The foundation of much of the precision matrix estimation literature is the gaussian negative log-likelihood.
+We consider the case where we observe $n$ independent, identically distributed (iid) copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$.
+That is, $X_{i}$ follows a $p$-dimensional normal distribution $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.
+Note that this formulation implies that $\mu \in \mathbb{R}^{p}$, $\Omega^{-1} \in \mathbb{S}_{+}^{p}$, and the probability of observing a single $X_{i}$ is
 
-Because we assume independence, we know that the probability of observing these specific observations $X_{1}, ..., X_{n}$ is equal to
+\begin{equation} 
+  f\left(X_{i}; \mu, \Omega^{-1}\right) = (2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] 
+(\#eq:normallikone)\notag
+\end{equation}
+
+Furthermore, because we assume pairwise independence between each observation, we know that for a sample of size $n$, the probability of observing all $X_{1}, ..., X_{n}$ is equal to
 
@@
 
-where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. It follows that the log-likelihood for $\mu$ and $\Omega$ is equal to the following:
+where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. Therefore, the gaussian log-likelihood for $\mu$ and $\Omega$ can be written as
 
@@
 
-If we are interested in estimating $\mu$, it is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n$ which we typically denote as $\bar{X}$.
-However, in addition to $\mu$, many applications require the estimation of $\Sigma$ as well.
-We can also find a maximum likelihood estimator:
+It is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$, so that the partially maximized gaussian log-likelihood for $\Omega$ can be written as
 
@@
 \begin{split}
-\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ const.
-+ \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right] \right\} \\
-  &= \left[ \frac{1}{n}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)' \right]^{-1}
+  l(\Omega | X) &= \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)'\Omega \right] \\
+  &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
+(\#eq:partialmaxloglik)\notag
+\end{split}
+\end{equation}
+
+where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the covariance matrix.
+
+In addition to $\mu$, we could also find the maximum likelihood estimator for $\Omega$ and use that as our estimator.
+By setting the gradient of the partially maximized log-likelihood equal to zero, we find that
+
+\begin{equation}
+\begin{split}
+\hat{\Omega}^{MLE} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left(S\Omega \right) \right\} \\
+  &= \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \\
+  &= S^{-1}
 \end{split}
@@
 
-By setting the gradient equal to zero and plugging in the MLE for $\mu$, we find that the MLE for $\Omega$ is the inverse our usual sample estimator for the covariance matrix, denoted here as $S^{-1}$.
-It turns out that we could have just as easily computed the maximum likelihood estimator for the precision matrix $\Omega \equiv \Sigma^{-1}$ and taken its inverse:
+so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{MLE} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]$.
+The reality, however, is that this object does *not* always exist.
+In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix, $S$, is rank deficient and no longer invertible.
 
-\begin{equation}
-\hat{\Omega}^{mle} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\}
-(\#eq:omegamlesimple)
-\end{equation}
-
-so that $\hat{\Omega}^{MLE} = S^{-1}$.
-Beyond the formatting convenience, computing estimates for $\Omega$ as opposed to $\Sigma$ often poses less computational challenges -- and accordingly, the literature has placed more emphasis on efficiently solving for $\Omega$ instead of $\Sigma$^[Notice that here we are *minimizing* the negative log-likelihood as opposed to maximizing the log-likelihood.
-Both procedures will result in the same estimate.].
-
-As in regression settings, we can construct a *penalized* log-likelihood estimator by adding a penalty term, $P\left(\Omega\right)$, to the log-likelihood so that
+For this reason, many papers in the last decade have proposed shrinkage estimators of the precision matrix similar to the shrinkage estimators in regression settings.
+That is, instead of minimizing solely the negative log-likelihood function, authors have proposed minimizing the gaussian log-likelihood *plus* a penalty - often a function of the precision matrix.
+These methods effectively force the eigen values of the precision matrix, $\Omega$, to be strictly greater than zero.
 
@@
 
-$P\left( \Omega \right)$ is often of the form $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or $P\left(\Omega \right) = \|\Omega\|_{1}$ where $\lambda > 0$, $\left\|\cdot \right\|_{F}^{2}$ is the Frobenius norm and we define $\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|$.
-These penalties are the ridge and lasso, respectively.
+This penalty, which we will denote as $P\left(\Omega\right)$, is typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$.
+The authors, @yuan2007model, were the ones who initially proposed precision matrix estimation by the lasso-penalized gaussian likelihood which they originally defined as
 
-## ADMM algorithm
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\sum_{i \neq j}\left|\Omega_{ij}\right| \right\}
+(\#eq:omegapenlasso)
+\end{equation}
 
-Many efficient methods have been proposed to solve for $\hat{\Omega}$ when $\alpha = 1$.
-The most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse.
-However, no methods (to the best of my knowledge) have estimated $\Omega$ when $\alpha \in (0, 1)$.
-We will use the alternating direction method of multipliers (ADMM) algorithm to do so.
+so as not to penalize the diagonal elements of the precision matrix estimate.
+Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include @rothman2008sparse and @friedman2008sparse and many efficient algorithms have been proposed to solve for $\hat{\Omega}$ in this setting.
+However, the most popular method is still the graphical lasso algorithm (sometimes referred to as glasso) introduced by @friedman2008sparse.
+Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm use in lasso regression.
 
-As the authors state in @boyd2011distributed, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers." For our purposes, we will only focus on the ADMM algorithm but it is encouraged to read the original text from Boyd and others for a complete introduction to the other two methods.
+Other papers published that propose methods with non-lasso penalizations like the Frobenius norms include @rothman2014existence, @witten2009covariance, and @price2015ridge.
+In fact, the latter two papers show that the estimation procedure can be solved in closed-form.
+Non-convex penalties were considered in @lam2009sparsistency and @fan2009network.
+
+The penalty we will explore here and in the next section is one that is a convex combination of the lasso and the ridge penalties:
+
+\begin{equation}
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+(\#eq:penelastic)\notag
+\end{equation}
+
+where $0 \leq \alpha \leq 1$ is an additional tuning parameter (similar to $\lambda$).
+Clearly, when $\alpha = 0$ this penalty reduces to a ridge penalty and when $\alpha = 1$ it reduces to a lasso penalty.
+This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] in the context of regression and is the penalty used in the popular penalized regression package `glmnet`.
+However, no published work has explored the elastic-net penalty in the context of precision matrix estimation.
+This penalty allows for increased flexibility and we will show how to solve the following optimization problem in the next section using the ADMM algorithm.
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
+(\#eq:optimelastic)
+\end{equation}
+
+## ADMM Algorithm
+
+ADMM stands for the alternating direction method of multipliers and this algorithm was largely popularized by Stephen Boyd and his fellow authors in the book *Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers* [@boyd2011distributed].
+As the authors state in the text, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers."
+
+The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.
 
@@
 
-\vspace{3cm}
-
-In the `ADMMsigma` package, we instead take
-
-\begin{equation}
-P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
-(\#eq:penelastic)\notag
-\end{equation}
-
-so that solving the full penalized log-likelihood for $\Omega$ results in solving
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
-(\#eq:optimelastic)
-\end{equation}
-
-where $0 \leq \alpha \leq 1$.
-This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] and is identical to the penalty used in the popular penalized regression package `glmnet`.
-Clearly, when $\alpha = 0$ the elastic-net reduces to a ridge-type penalty and when $\alpha = 1$ it reduces to a lasso-type penalty.
-Having this flexibility and generalization allows us to perform cross validation across proposed $\alpha$ values in addition to proposed $\lambda$ values.
-
 The ADMM algorithm is now the following:
@@
 where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
+
+@witten2009covariance; @price2015ridge
 

### 2019-03-10 03-SCPME.Rmd
largely completed chapters 1 and chapters 2

@@
 # SCPME
-
-### literature review?
-
-- A similar estimator was proposed by @dalal2017sparse when $C = 0$.
-
-- - Quadratic equation with ridge is solve in closed form using a similar approach to @witten2009covariance; @price2015ridge.
-
-###  other stuff
 
@@
 
+- A similar estimator was proposed by @dalal2017sparse when $C = 0$.
+
 This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$.
@@
 
-*This section requires general knowledge of the alternating direction method of multipliers (ADMM) algorithm.
-I would recommend reading this overview I have written [here](https://mgallow.github.io/ADMMsigma/articles/Details.html#admm-algorithm) before proceeding.*
-
-The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.
 Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:
@@
 However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.
+The ADMM algorithm with modification based on majorize-minimize principle is also found in @lange2016mm.
 
@@
   \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)\notag
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
 (\#eq:approx)
@@
 since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.
-Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Proof of BLAH in section BLAHHH].
+Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Further explanation of majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
 
@@
 
-\begin{align}
+\begin{equation}
+\begin{split}
   \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
-\end{align}
+(\#eq:augADMM)\notag
+\end{split}
+\end{equation}
 

### 2019-04-07 01-intro.Rmd
only SCPME sims and discussion left

@@
 
-In the simplest terms, inferential statistics boils down to two primary components: estimation and prediction.
-Estimation tends to refer to the process by which we infer properties and behavior about individual parameters.
-For instance, decision theory tell us that the method by which we estimate parameters should be one that incurs low risk or variance.
-Prediction, on the other hand, tends to refer to the process of determining the likelihood of an unknown or unforseeable event.
-Right now, prediction is king.
-The demand for good, predictive models has sparked huge investments in research and given rise to communities - like the machine learning community - whose primary goal is establishing good predictive models.
+Inferential statistics consists of two primary components: estimation and prediction.
+Estimation refers to the process by which we infer values, properties and behavior about individual parameters in our model.
+Prediction, on the other hand, refers to the process by which we draw inference about an event that has not-yet occurred.
+This component is prevalent in industry where the demand to predict stock prices, to predict which movie individuals will prefer, and even new friend connections in a network has sparked huge investments in research and given rise to groups whose primary goal is pushing the bounds and developing new predictive models.
 
-However, though prediction is getting a lot of attention, these two components are not entirely distinct and often go hand-in-hand.
-In fact, the success of many predictive models is largely contingent upon the ability to be efficient and proficient in estimation.
-That is, the succces and reliability of prediction is often a product of good estimation.
+However, though most attention is directed towards prediction, these two components are not distinct.
+In fact, the success and reliability of many predictive models is contingent upon good, efficient parameter estimation.
+Many of these models require the estimation of a precision matrix - the inverse of the covariance matrix (frequently denotes as $\Omega$) - that establishes the interaction and covariance between random variables.
 
-For instance, many statistical models require the estimation of the co-variability and interaction between variables.
-This statistical object often comes in the form of a precision matrix ($\Omega$) - or the inverse of the covariance matrix.
-For this reason, in the last decade there has been an ever-expanding community devoted to matrix precision estimation.
-Like the covariance matrix, the precision matrix offers a powerful way of presenting the covariance - or pairwise variability between any two random variables.
+For this reason, in the last decade there has been an ever-expanding community devoted to precision matrix estimation and among this community is Professor Adam Rothman and Aaron Molstad, Ph.D.
+whose research will be a focal point of this manuscript.
+The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this work is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking).
+In it, they outline a framework to estimate *characteristics* of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
+They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
+For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors." The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
 
-Fisher's linear discriminant analysis (LDA) is one of these statistical models. Under the assumption of normal data, the model aims to classify observations into two or more populations of data.
+One of the research directions mentioned in the original paper was the application of their framework to regression.
+Utilizing the fact that the population regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$ (where $\Sigma_{xy}$ is the cross-covariance matrix between the predictors, $X$, and the responses, $Y$, and $\Omega_{x}$ is the precision matrix for $X$), their framework allows for the simultaneous estimation of $\beta$ and $\Omega_{x}$ with an embedded assumption potentially useful for superior prediction performance.
+In close communication and collaboration with Professor Rothman, we wanted to explore this direction further.
+However, in order to build upon their work and contribute new material, there were a number of concepts that needed to be learned along the way and this document will follow that journey.
 
-The central theme of this thesis is on precision matrix estimation but also expanding on a paper written by Aaron Molstad and Adam Rothman in 2017.
-In this paper, @molstad2017shrinking focused on the fact that only a "characteristic" of a precision matrix is required to fit these models.
-
-- From @molstad2017shrinking: "To fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
-For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.
-Many authors have proposed methods that directly estimate this characteristic @cai2011direct; @fan2012road; @mai2012direct."
-
-2.
-From @molstad2017shrinking: "@chen2016regularized proposed a method for estimating the characteristic $\Omega_{*}\mu_{*}$ directly, but like the direct linear discriminant methods, this apporach does not lead to an estimate of $\Omega_{*}$."
-
-With the goal of improving performance..
-
-They offer a framework to do other things...
-
-Their approach/methodoloy was published in BLAH. Shrinking Characteristic of precision matrix estimators.
-
-The purpose of this work began with the desire to expand on the work in @molstad2017shrinking and to explore avenues that were mentioned but were not further investigated.
-One of these research directions was the application of their shrinking characteristics approach to regression.
-However, in order to get to that point and to build up the knowledge to understand and contribute new material, there were a number of concepts that needed to be understood along the way.
-This document will follow that journey.
-
-We will begin chapter 2 with a brief introduction to the area of precision matrix estimation and the gaussian log-likelihood function.
-This section will include mentions of other estimation methods and algorithms but most discussion we will spent on the ADMM algorithm.
-This discussion will be useful when we begin elaborating on the shrinking characteristics approach (sometimes referred to as SCPME), the augmented ADMM algorithm, and later the application to regression.
+We will begin chapter two with a brief introduction to precision matrix estimation and the gaussian log-likelihood function.
+This section will mention popular estimation methods and algorithms but most discussion will be directed towards the ADMM algorithm.
+This discussion will be useful as we begin detailing the shrinking characteristics of precision matrix estimators framework (which may be referred to as SCPME), the so-called augmented ADMM algorithm, and later the framework's application to regression.
 Lastly, the document will end with two brief tutorials for the R packages `ADMMsigma` and `SCPME`.
@@
 The class of real, symmetric matrices with dimension $p \times p$ will be denoted as $\mathbb{S}^{p}$ and $\mathbb{S}^{p}_{+}$ if we further require the object to be positive definite.
-The sample size in a given data set will most often correspond with $n$ and $p$ will correspond with the dimension of the prediction vector.
+The sample size and dimension of the predictor vector in a given data set will most often be denoted as $n$ and $p$, respectively.
 If the dimension of the response vector exceeds one, we will denote it as $r$.
 
-Most matrices will take the form of either $\Sigma$, which should be taken to represent the population covariance matrix, or $\Omega$, which should be taken to represent the population *precision* matrix.
-Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$).
-We will sometimes add a subscript star if the object is oracle - or known- a priori ($\Omega_{*}$) and the population object's estimator that minimizes/maximizes a pre-specified objective function will have a hat attached to it ($\hat{\Omega}$).
+Most matrices will take the form of either $\Sigma$, the population covariance matrix, or $\Omega$, the population precision matrix.
+Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$) and a subscript may be added to each if more than two random variables are considered in a problem.
+A subscript star may also be added if the object is oracle - or known - a priori ($\Omega_{*}$).
+The oracle's estimator that minimizes/maximizes a pre-specified objective function will be denoted with a hat ($\hat{\Omega}$).
 
-There will be significant matrix algebra notation throughout the document.
-The trace operator which sums the diagonal elements of a matrix will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$.
-The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form as simply $det\left(\mathbf{A}\right)$.
+There will be significant matrix algebra notation throughout the manuscript.
+The trace operator sums the diagonal elements of a matrix and will take the form $tr\left(\cdot\right)$ and the *exponential* trace operator will be denoted similarly as $etr\left(\cdot\right)$.
+The vector operator, $vec\left(\cdot\right)$, stacks the columns of a matrix into a column vector.
+The determinant of a matrix $\mathbf{A}$ will be denoted as $\left|\mathbf{A}\right|$ but may also take the form $det\left(\mathbf{A}\right)$.
 The kronecker product of two matrices $\mathbf{A}$ and $\mathbf{B}$ will be denoted as $\mathbf{A} \otimes \mathbf{B}$ and the element-wise product will be denoted as $\mathbf{A} \circ \mathbf{B}$.
-Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.
+Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as $\left\|\mathbf{A}\right\|_{F}$ and we will define $\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|$ where the $i$-$j$th element in matrix $\mathbf{A}$ is typically denoted as $\left(\mathbf{A}\right)_{ij}$ or simply $\mathbf{A}_{ij}$.

### 2019-04-07 02-PME.Rmd
only SCPME sims and discussion left

@@
 The foundation of much of the precision matrix estimation literature is the gaussian negative log-likelihood.
-We consider the case where we observe $n$ independent, identically distributed (iid) copies of the random variable ($X_{i}$) where $X_{i} \in \mathbb{R}^{p}$ is normally distributed with some mean, $\mu$, and some variance, $\Omega^{-1}$.
-That is, $X_{i}$ follows a $p$-dimensional normal distribution $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.
-Note that this formulation implies that $\mu \in \mathbb{R}^{p}$, $\Omega^{-1} \in \mathbb{S}_{+}^{p}$, and the probability of observing a single $X_{i}$ is
+Consider the case where we observe $n$ independent, identically distributed (iid) copies of the random variable $X$, where the $i$th observation $X_{i} \in \mathbb{R}^{p}$ is normally distributed with mean, $\mu$, and variance, $\Omega^{-1}$.
+That is, $X_{i}$ follows a $p$-dimensional normal distribution which is typically denoted as $X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)$.
+By definition, this multivariate formulation implies the probability distribution function, $f$, is of the form
 
 \begin{equation} 
-  f\left(X_{i}; \mu, \Omega^{-1}\right) = (2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] 
+  f\left(X_{i}; \mu, \Omega\right) = (2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] 
 (\#eq:normallikone)\notag
@@
 
-Furthermore, because we assume pairwise independence between each observation, we know that for a sample of size $n$, the probability of observing all $X_{1}, ..., X_{n}$ is equal to
+Furthermore, because we assume that each observation is independent, the probability distribution function for all $n$ observations $X_{1}, ..., X_{n}$ is equal to
 
@@
 \begin{split}
-  f(X_{1}, ..., X_{n}; \mu, \Omega^{-1}) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
+  f\left(X_{1}, ..., X_{n}; \mu, \Omega\right) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
   &= (2\pi)^{-np/2}\left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Omega \right]
@@
 
-where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. Therefore, the gaussian log-likelihood for $\mu$ and $\Omega$ can be written as
+Therefore, the gaussian log-likelihood, $l$, for $\mu$ and $\Omega$ given $X = (X_{1}, .., X_{n})$ can be written as
 
 \begin{equation}
-  l(\mu, \Omega | X) = const. + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
+  l(\mu, \Omega | X) = constant + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
 (\#eq:normalloglik)\notag
@@
 
-It is relatively straight forward to show that the maximum likelihood estimator (MLE) for $\mu$ is $\hat{\mu}^{MLE} = \sum_{i = 1}^{n}X_{i}/n \equiv \bar{X}$, so that the partially maximized gaussian log-likelihood for $\Omega$ can be written as
+The estimator for $\mu$ that maximizes the log-likelihood is $\hat{\mu}^{MLE} = \bar{X} \equiv \sum_{i = 1}^{n}X_{i}/n$, so that the partially maximized gaussian log-likelihood for $\Omega$ is
 
@@
 
-where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the covariance matrix.
-
-In addition to $\mu$, we could also find the maximum likelihood estimator for $\Omega$ and use that as our estimator.
-By setting the gradient of the partially maximized log-likelihood equal to zero, we find that
+where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the covariance matrix, $\Sigma$.
+In addition to $\mu$, we could also derive the maximum likelihood estimator for $\Omega$.
+By setting the gradient of the partially maximized log-likelihood equal to zero, we can show that
 
@@
 
-so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{MLE} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]$.
+so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{MLE} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]^{-1}$.
 The reality, however, is that this object does *not* always exist.
-In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix, $S$, is rank deficient and no longer invertible.
-
+In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix is rank deficient and no longer invertible.
 For this reason, many papers in the last decade have proposed shrinkage estimators of the precision matrix similar to the shrinkage estimators in regression settings.
-That is, instead of minimizing solely the negative log-likelihood function, authors have proposed minimizing the gaussian log-likelihood *plus* a penalty - often a function of the precision matrix.
-These methods effectively force the eigen values of the precision matrix, $\Omega$, to be strictly greater than zero.
+That is, instead of minimizing solely the negative log-likelihood function, authors have proposed minimizing the gaussian log-likelihood *plus* a penalty term, $P$, which is often a function of the precision matrix.
 
@@
 
-This penalty, which we will denote as $P\left(\Omega\right)$, is typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$.
-The authors, @yuan2007model, were the ones who initially proposed precision matrix estimation by the lasso-penalized gaussian likelihood which they originally defined as
+The penalties that have been proposed for precision matrix estimation are typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$.
+The authors, @yuan2007model, initially proposed the lasso-penalized gaussian log-likelihood defined as
 
@@
 so as not to penalize the diagonal elements of the precision matrix estimate.
-Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include @rothman2008sparse and @friedman2008sparse and many efficient algorithms have been proposed to solve for $\hat{\Omega}$ in this setting.
-However, the most popular method is still the graphical lasso algorithm (sometimes referred to as glasso) introduced by @friedman2008sparse.
-Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm use in lasso regression.
+Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include @rothman2008sparse and @friedman2008sparse.
+In addition, many efficient algorithms have been proposed to solve for $\hat{\Omega}$ in this setting but the most popular method is the graphical lasso algorithm (often referred to as glasso) introduced by @friedman2008sparse.
+Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm used in lasso-penalized regression.
 
-Other papers published that propose methods with non-lasso penalizations like the Frobenius norms include @rothman2014existence, @witten2009covariance, and @price2015ridge.
-In fact, the latter two papers show that the estimation procedure can be solved in closed-form.
-Non-convex penalties were considered in @lam2009sparsistency and @fan2009network.
-
-The penalty we will explore here and in the next section is one that is a convex combination of the lasso and the ridge penalties:
+Non-lasso, non-convex penalties were considered in @lam2009sparsistency and @fan2009network and other papers considered penalizations like the Frobenius norm (@rothman2014existence; @witten2009covariance; @price2015ridge).
+In fact, the latter two papers show that the resulting minimizer can be solved in closed-form - which will be discussed later in this manuscript.
+However, the penalty explored in the remainder of this chapter is not a lasso penality nor a ridge penalty but, in fact, a convex combination of the two known as the *elastic-net* penalty:
 
 \begin{equation}
-P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right\|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
 (\#eq:penelastic)\notag
@@
 
-where $0 \leq \alpha \leq 1$ is an additional tuning parameter (similar to $\lambda$).
+with tuning parameter $0 \leq \alpha \leq 1$.
 Clearly, when $\alpha = 0$ this penalty reduces to a ridge penalty and when $\alpha = 1$ it reduces to a lasso penalty.
-This penalty, know as the *elastic-net* penalty, was explored by Hui Zou and Trevor Hastie [@zou2005regularization] in the context of regression and is the penalty used in the popular penalized regression package `glmnet`.
-However, no published work has explored the elastic-net penalty in the context of precision matrix estimation.
-This penalty allows for increased flexibility and we will show how to solve the following optimization problem in the next section using the ADMM algorithm.
+Originally proposed in @zou2005regularization in the context of regression, this penalty has since been popularized and is used in the penalized regression R package `glmnet`.
+This penalty allows for additional flexibility but, despite this, no published work (to our knowledge) has explored the elastic-net penalty in the context of precision matrix estimation.
+We will show how to solve the following optimization problem in the next section using the ADMM algorithm.
 
@@
 
-ADMM stands for the alternating direction method of multipliers and this algorithm was largely popularized by Stephen Boyd and his fellow authors in the book *Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers* [@boyd2011distributed].
-As the authors state in the text, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers."
+ADMM stands for alternating direction method of multipliers.
+The algorithm was largely popularized by Stephen Boyd and his fellow authors in the book *Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers* [@boyd2011distributed].
+As the authors state in the text, the "ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers." By closely following Boyd's descriptions and guidance in the published text, we will show in this section that the ADMM algorithm is particularly well-suited to solve the penalized log-likelihood optimization problem we are interested in here.
 
-The ADMM algorithm - thanks to it's flexibility - is particularly well-suited to solve penalized-likelihood optimization problems that arise naturally in several statistics and machine learning applications.
-
-In general, suppose we want to solve an optimization problem of the following form:
+In general, suppose that we want to solve an optimization problem of the form
 
@@
 
-where $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are assumed to be convex functions (following @boyd2011distributed, the estimation procedure will be introduced in vector form though we could just as easily take $x$ and $z$ to be matrices).
-In addition to penalized precision matrix estimation, optimization problems like this arise naturally in several statistics and machine learning applications -- particularly regularization methods.
-For instance, we could take $f$ to be the squared error loss, $g$ to be the $l_{2}$-norm, $c$ to be equal to zero and $A$ and $B$ to be identity matrices to solve the ridge regression optimization problem.
-In all cases, our goal is to find $x^{*} \in \mathbb{R}^{n}$ and $z^{*} \in \mathbb{R}^{m}$ that achieves the infimum $p^{*}$:
-
-\begin{equation}
-p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\}
-(\#eq:infimum)\notag
-\end{equation}
-
-To do so, the ADMM algorithm uses the *augmented lagrangian*
+where we can assume here that $x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}$, $c \in \mathbb{R}^{p}$, and $f$ and $g$ are convex functions.
+In order to find the pair $(x^{*}, z^{*})$ that achieves the infimum, the ADMM algorithm uses an *augmented lagrangian*, $L$, which @boyd2011distributed define as
 
@@
 
-where $y \in \mathbb{R}^{p}$ is the lagrange multiplier and $\rho > 0$ is a scalar.
-Clearly any minimizer, $p^{*}$, under the augmented lagrangian is equivalent to that of the lagrangian since any feasible point $(x, z)$ satisfies the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.
-
-The algorithm consists of the following repeated iterations:
+In this formulation, $y \in \mathbb{R}^{p}$ is called the lagrange multiplier and $\rho > 0$ is some scalar that acts as the step size for the algorithm.
+Note that any infimum under the augmented lagrangian is equivalent to the infimum of the traditional lagrangian since any feasible point $(x, z)$ must satisfy the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.
+@boyd2011distributed show that the infimum will be approached under the following repeated iterations:
 
@@
 
-In the context of precision matrix estimation, we can let $f$ be equal to the non-penalized likelihood, $g$ be equal to $P\left( \Omega \right)$, and use the constraint $\Omega$ equal to some $Z$ so that the lagrangian is
-
-\begin{equation}
-L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right]
-(\#eq:lagrange2)\notag
-\end{equation}
-
-and the augmented lagrangian is
+where the superscript, $k$, denotes the number of iterations.
+Conveniently, this general algorithm can be coerced into a format useful in precision matrix estimation.
+Suppose we let $f$ be equal to the non-penalized log-likelihood, $g$ equal to the elastic-net penalty, $P\left( \Omega \right)$, and we use the constraint that $\Omega$ must be equal to $Z$, then the augmented lagrangian in the context of precision matrix estimation is of the form
 
@@
 
-The ADMM algorithm is now the following:
+where $\Lambda$ is taking the role of $y$ and the ADMM algorithm now consists of the repeated iterations
 
-\begin{align}
+\begin{equation}
+\begin{split}
   \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align}
+(\#eq:ADMMorig)
+\end{split}
+\end{equation}
 
-### Algorithm
+It turns out that each step in this algorithm can be solved in closed-form.
+The full details of each can be found in the appendix \@ref(proofomegaalgo) but the following theorem provides the simplified steps in the algorithm.
 
-Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}$, and $\rho$. Repeat steps 1-3 until convergence:
+```{theorem, name = "ADMM Algorithm for Elastic-Net Penalized Precision Matrix Estimation"}
+
+Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
+Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}$, and $\rho$.
+Repeat steps 1-3 until convergence:
 
@@
 
-where $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
-
-@witten2009covariance; @price2015ridge
+```
 
@@
 
-There is another popular, alternate form of the ADMM algorithm used by scaling the dual variable ($\Lambda^{k}$). Let us define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$.
+Another popular, alternative form of the ADMM algorithm can be used when scaling the dual variable ($\Lambda^{k}$). We derive this scaled-form in the context of precision matrix estimation here.
+
+Define $R^{k} = \Omega - Z^{k}$ and $U^{k} = \Lambda^{k}/\rho$ then
 
@@
 
-\begin{align}
+\begin{equation}
+\begin{split}
   \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
@@
   U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
-\end{align}
-
-And more generally (in vector form),
-
-\begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
-\end{align}
-
-Note that there are limitations to using this method.
-Because the dual variable is scaled by $\rho$ (the step size), this form limits one to using a constant step size without making further adjustments to $U^{k}$.
-It has been shown in the literature that a dynamic step size (like the one used in `ADMMsigma`) can significantly reduce the number of iterations required for convergence.
-
-### Stopping Criterion
-
-In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to precision matrix estimation.
-
-Below we have three optimality conditions:
-
-1. Primal:
-
-\begin{equation}
-\Omega^{k + 1} - Z^{k + 1} = 0
-(\#eq:admmprimal)\notag
-\end{equation}
-
-2. Dual:
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} \\
-  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:admmdual)\notag
+(\#eq:ADMMscaled)
 \end{split}
@@
 
-The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).
+Note that there are limitations to using this method.
+Because the dual variable is scaled by $\rho$ (the step size), this form limits one to using a constant step size for all $k$ steps if no further adjustments are made to $U^{k}$.
 
-We will define the left-hand side of the first condition as the primal residual $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$.
-At convergence, optimality conditions require that $r^{k + 1} \approx 0$.
-The second residual we will define is the dual residual $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$.
-This residual is derived from the following:
+### Stopping Criterion {#ADMMstop}
 
-Because $\Omega^{k + 1}$ is the minimizer of the augmented lagragian^[Proof of \@ref(eq:dualresidual) in section \@ref(proofdualresidual).], this implies that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ which further implies that
+There are three optimality conditions for the ADMM algorithm that we can use to inform the convergence and stopping criterion.
+These general conditions were outlined in @boyd2011distributed but here we cater them to precision matrix estimation.
+The first condition is the primal optimality condition $\Omega^{k + 1} - Z^{k + 1} = 0$ and the other two conditions are the dual conditions $0 \in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1}$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$.
+Note that in the first condition we must honor the symmetric constraint in $\Omega$ but the second condition does not require it.
 
-\begin{equation}
-0 \in \rho\left( Z^{k + 1} - Z^{k} \right)
-(\#eq:dualresidual)
-\end{equation}
+If we define the left-hand side of the primal optimality condition as the *primal residual* $r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}$, then at convergence we must require that $r^{k + 1} \approx 0$.
+Likewise, if we define the *dual residual* $s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)$, we must also require that $s^{k + 1} \approx 0$ for proper convergence.
+This dual residual is the direct result of the fact that $\Omega^{k + 1}$ is the minimizer of the augmented lagragian^[Proof in section \@ref(proofdualresidual).] so that $0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$ and consequently $0 \in \rho\left( Z^{k + 1} - Z^{k} \right)$^[Note that the second dual optimality condition $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$ is always satisfied.
+More details can be found in section \@ref(proofdualopt).].
 
-Like the primal residual, at convergence optimality conditions require that $s^{k + 1} \approx 0$.
-Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt) in section \@ref(proofdualopt).]:
-
-\begin{equation}
-\begin{split}
-  0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
-(\#eq:dualopt)
-\end{split}
-\end{equation}
-
-One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where
-
+Combining these three optimality conditions, Boyd suggests a stopping criterion similar to $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and
 \begin{equation}
@@
 
-In the simulations below, we generate data from a number of different oracle precision matrices with various structures.
-For each data-generating procedure, the `ADMMsigma()` function was run using 5-fold cross validation.
-After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results below the top figure).
-These results are compared with the Kullback Leibler (KL) losses between the estimates and the oracle precision matrix (bottom figure).
+As a proof-of-concept that the elastic-net penalty in the context of precision matrix estimation can provide useful results and that the ADMM algorithm used in this process works, the section offers a short simulation.
+For the simulation, we generated data from multiple, unique precision matrices with various oracle structures.
+For each data-generating procedure, the algorithm was run with a 5-fold cross validation.
+After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results are in the top half of the figures).
+These results were then compared with the Kullback Leibler (KL) losses between the estimated matrices and the oracle matrices (results are in the bottom half of the figures).
 
-We can see below that our cross validation procedure consistently chooses tuning parameters that are close to the optimal parameters with respsect to the oracle.
+The first figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a tri-diagonal oracle precision matrix.
+This oracle matrix was first generated as $\left(S_{ij}\right) = 0.7^{\left|i - j \right|}$ for $i,j = 1,..., p$ and then inverted.
+The results show that because the oracle precision matrix is sparse, the algorithm correctly chooses a sparse solution with $\alpha = 1$ - indicating a lasso penalty.
 
-HOW DID WE GENERATE THE DATA?
+The second figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a *dense* oracle precision matrix.
+Here, we randomly generated an orthogonal basis, set all eigen values equal to 1000, and then combined the matrices using QR decomposition.
+Interestingly, we find that the optimal $\alpha$ in this case is 0.6 which closely matches the optimal result based on the KL loss.
+This shows that there are cases where an elastic-net penalty can provide useful results and that using only a lasso penalty may unnecessarily restrict our penalized estimation.
 
-### Plots
+\vspace{1cm}
 
-#### Compound Symmetric: P = 100, N = 50
+<!-- #### Compound Symmetric: P = 100, N = 50 -->
 
-```{r, message = FALSE, echo = TRUE, eval = FALSE}
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE} -->
 
-# oracle precision matrix
-Omega = matrix(0.9, ncol = 100, nrow = 100)
-diag(Omega = 1)
+<!-- # oracle precision matrix -->
+<!-- Omega = matrix(0.9, ncol = 100, nrow = 100) -->
+<!-- diag(Omega = 1) -->
 
-# generate covariance matrix
-S = qr.solve(Omega)
+<!-- # generate covariance matrix -->
+<!-- S = qr.solve(Omega) -->
 
-# generate data
-Z = matrix(rnorm(100*50), nrow = 50, ncol = 100)
-out = eigen(S, symmetric = TRUE)
-S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
-X = Z %*% S.sqrt
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(100*50), nrow = 50, ncol = 100) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
 
-```
-<br>\vspace{0.5cm}
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
+
+<!-- ```{r admmsim1, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- knitr::include_graphics("images/compound_N50_P100.png") -->
+
+<!-- ``` -->
+
+<!-- #### Compound Symmetric: P = 10, N = 1000 -->
+
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE} -->
+
+<!-- # oracle precision matrix -->
+<!-- Omega = matrix(0.9, ncol = 10, nrow = 10) -->
+<!-- diag(Omega = 1) -->
+
+<!-- # generate covariance matrix -->
+<!-- S = qr.solve(Omega) -->
+
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(10*1000), nrow = 1000, ncol = 10) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
+
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
+
+<!-- ```{r admmsim2, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- knitr::include_graphics("images/compound_N1000_P10.png") -->
+
+<!-- ``` -->
+
+<!-- #### Dense: P = 10, N = 50 -->
+
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->
+
+<!-- # generate eigen values -->
+<!-- eigen = c(rep(1000, 5, rep(1, 10 - 5))) -->
+
+<!-- # randomly generate orthogonal basis (via QR) -->
+<!-- Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q -->
+
+<!-- # generate covariance matrix -->
+<!-- S = Q %*% diag(eigen) %*% t(Q) -->
+
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(10*50), nrow = 50, ncol = 10) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
+
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
+
+<!-- ```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- knitr::include_graphics("images/repsKLdense_N50_P10.png") -->
+
+<!-- ``` -->
+
+<!-- #### Tridiagonal: P = 100, N = 50 -->
+
+<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->
+
+<!-- # generate covariance matrix -->
+<!-- # (can confirm inverse is tri-diagonal) -->
+<!-- S = matrix(0, nrow = 100, ncol = 100) -->
+<!-- for (i in 1:100){ -->
+<!--    for (j in 1:100){ -->
+<!--      S[i, j] = 0.7^abs(i - j) -->
+<!--  } -->
+<!-- } -->
+
+<!-- # generate data -->
+<!-- Z = matrix(rnorm(10*50), nrow = 50, ncol = 10) -->
+<!-- out = eigen(S, symmetric = TRUE) -->
+<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
+<!-- X = Z %*% S.sqrt -->
+
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
 
 <!-- <center> -->
-<!-- ![Figure caption here.](images/compound_N50_P100.png){ -->
+<!-- ![Figure caption here.](images/repsKLtridiag_N50_P100.png){ -->
 <!-- width=90% } -->
@@
 
-```{r admmsim1, eval = T, echo = F, fig.cap = "Figure caption here."}
+```{r admmsim5, eval = T, echo = F, fig.cap = "The oracle precision matrices were tri-diagonal with dimension p = 100 and the data was generated with a sample size of n = 50.
+The cross validation errors are in the top figure and the KL losses between the estimated matrices and the oracle matrices are shown in the bottom figure.
+The optimal tuning parameter pair for each heatmap was found to be log10(lam) = -0.9 and alpha = 1.
+Note that brighter areas signify smaller losses."}
 
-knitr::include_graphics("images/compound_N50_P100.png")
-
-```
-
-#### Compound Symmetric: P = 10, N = 1000
-
-```{r, message = FALSE, echo = TRUE, eval = FALSE}
-
-# oracle precision matrix
-Omega = matrix(0.9, ncol = 10, nrow = 10)
-diag(Omega = 1)
-
-# generate covariance matrix
-S = qr.solve(Omega)
-
-# generate data
-Z = matrix(rnorm(10*1000), nrow = 1000, ncol = 10)
-out = eigen(S, symmetric = TRUE)
-S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
-X = Z %*% S.sqrt
-
-```
-<br>\vspace{0.5cm}
-
-<!-- <center> -->
-<!-- ![Figure caption here.](images/compound_N1000_P10.png){ -->
-<!-- width=90% } -->
-<!-- </center> -->
-
-```{r admmsim2, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-knitr::include_graphics("images/compound_N1000_P10.png")
+knitr::include_graphics("images/repsKLtridiag_N50_P100.png")
 
@@
 
-<!-- <!-- <center> --> -->
-<!-- <!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ --> -->
-<!-- <!-- width=90% } --> -->
-<!-- <!-- </center> --> -->
-<!-- <!-- } --> -->
+<!-- <center> -->
+<!-- <!-- ![Figure caption here.](images/repsKLdenseQR_N50_P100.png){ -->
+<!-- width=90% } -->
+<!-- </center> -->
+<!-- } -->
 
-<!-- ```{r admmsim3, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+```{r admmsim3, eval = T, echo = F, fig.cap = "The oracle precision matrices were dense with dimension p = 100 and the data was generated with a sample size of n = 50.
+The cross validation errors are in the top figure and the KL losses between the estimated matrices and the oracle matrices are shown in the bottom figure.
+The optimal tuning parameter pair for the cross validation errors was found to be log10(lam) = -0.4 and alpha = 0.6 and log10(lam) = -0.5 and alpha = 0.7 for the KL losses.
+Note that brighter areas signify smaller losses."}
 
-<!-- knitr::include_graphics("images/repsKLdenseQR_N50_P100.png") -->
-
-<!-- ``` -->
-
-<!-- #### Dense: P = 10, N = 50 -->
-
-<!-- ```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE} -->
-
-<!-- # generate eigen values -->
-<!-- eigen = c(rep(1000, 5, rep(1, 10 - 5))) -->
-
-<!-- # randomly generate orthogonal basis (via QR) -->
-<!-- Q = matrix(rnorm(10*10), nrow = 10, ncol = 10) %>% qr %>% qr.Q -->
-
-<!-- # generate covariance matrix -->
-<!-- S = Q %*% diag(eigen) %*% t(Q) -->
-
-<!-- # generate data -->
-<!-- Z = matrix(rnorm(10*50), nrow = 50, ncol = 10) -->
-<!-- out = eigen(S, symmetric = TRUE) -->
-<!-- S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors) -->
-<!-- X = Z %*% S.sqrt -->
-
-<!-- ``` -->
-<!-- <br>\vspace{0.5cm} -->
-
-<!-- <!-- <center> --> -->
-<!-- <!-- ![Figure caption here.](images/repsKLdense_N50_P10.png){ --> -->
-<!-- <!-- width=90% } --> -->
-<!-- <!-- </center> --> -->
-
-<!-- ```{r admmsim4, eval = T, echo = F, fig.cap = "Figure caption here."} -->
-
-<!-- knitr::include_graphics("images/repsKLdense_N50_P10.png") -->
-
-<!-- ``` -->
-
-#### Tridiagonal: P = 100, N = 50
-
-```{r, message = FALSE, echo = TRUE, eval = FALSE, tidy = FALSE}
-
-# generate covariance matrix
-# (can confirm inverse is tri-diagonal)
-S = matrix(0, nrow = 100, ncol = 100)
-for (i in 1:100){
-  for (j in 1:100){
-    S[i, j] = 0.7^abs(i - j)
-  }
-}
-
-# generate data
-Z = matrix(rnorm(10*50), nrow = 50, ncol = 10)
-out = eigen(S, symmetric = TRUE)
-S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
-X = Z %*% S.sqrt
+knitr::include_graphics("images/repsKLdenseQR_N50_P100.png")
 
 ```
-<br>\vspace{0.5cm}
-
-<!-- <center> -->
-<!-- ![Figure caption here.](images/repsKLtridiag_N50_P100.png){ -->
-<!-- width=90% } -->
-<!-- </center> -->
-
-```{r admmsim5, eval = T, echo = F, fig.cap = "Figure caption here."}
-
-knitr::include_graphics("images/repsKLtridiag_N50_P100.png")
-
-```

### 2019-04-07 03-SCPME.Rmd
only SCPME sims and discussion left

@@
 
-The penalty proposed by @molstad2017shrinking is one of the following form:
+In their 2017 paper, titled *Shrinking Characteristics of Precision Matrix Estimators*, Aaron Molstad, Ph.D.
+and Professor Adam Rothman outline a framework to estimate *characteristics* of precision matrices.
+This concept, inspired by others like @cai2011direct, @fan2012road, and @mai2012direct, exploits the fact that in many predictive models, estimation of the precision matrix is only necessary through its product with another feature such as a mean vector.
+
+The example they offer in @molstad2017shrinking is in the context of Fisher's linear discriminant analysis model.
+If a response vector $Y$ is categorical such that $Y$ can take values in $\left\{1, ..., J\right\}$, then the linear discrimnant analysis model assumes that the design matrix $X$, conditional on the response vector $Y$, is normally distributed:
+
+\begin{equation}
+X | Y = j \sim N_{p}\left(\mu_{j}, \Omega^{-1}\right)
+(\#eq:lda)
+\end{equation}
+
+for each $j = 1, ..., J$.
+We can see from this formulation that clearly an estimation of both $\mu$ and $\Omega$ are required for this model.
+However, they note that if prediction is the primary concern, then for a given observation $X_{i}$ only the *characteristic* $\Omega\left(\mu_{l} - \mu_{m}\right)$ is needed to discern between response categories $l$ and $m$.
+In other words, prediction only requires the characteristic $\Omega\left(\mu_{l} - \mu_{m}\right)$ for each $l, m \in \left\{1, ..., J\right\}$ and does *not* require estimation of the full precision matrix $\Omega$.
+@cai2011direct were among the first authors to propose estimating this characteristic directly but the interesting facet that distinguishes Molstad and Rothman's approach is that their framework simultaneously fits the model in \@ref(eq:lda) and performs variable selection.
+
+The general framework has applications outside of linear discriminant analysis and we will be exploring a regression application in later sections, but first we will outline their approach.
+The penalty proposed by @molstad2017shrinking is of the form
 
@@
 
-where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices assumed to be known and specified by the user.
-Solving the full penalized log-likelihood for $\Omega$ results in solving
+where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices that are assumed to be known and specified so that solving the full penalized gaussian log-likelihood for $\Omega$ results in solving
 
@@
 
-- A similar estimator was proposed by @dalal2017sparse when $C = 0$.
-
-This form of penalty is particularly useful because matrices $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of a *characteristic* of the precision matrix $\Omega$.
-This type of penalty leads to many new, interesting, and novel estimators for $\Omega$.
-An example of one such estimator (suppose we observe $n$ samples of $Y_{i} \in \mathbb{R}^{r}$) would be one where we set $A = I_{p}, B = \Sigma_{xy}, \mbox{ and } C = 0$ where $\Sigma_{xy}$ is the covariance matrix of $X$ and $Y$.
-This penalty has the effect of assuming sparsity in the forward regression coefficient $\beta \equiv \Omega\Sigma_{xy}$.
-Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$
-
+A similar estimator was proposed by @dalal2017sparse when $C = 0$ but here we do not require it.
+This form of penalty is particularly useful because it's extremely general.
+Note that by letting matrices $A = I_{p}, B = I_{p}, \mbox{ and } C = 0$, this penalty reduces to a lasso penalty - but clearly this form allows for much more creative penalties and $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of *many* characteristics of the precision matrix $\Omega$.
 We will explore how to solve for $\hat{\Omega}$ in the next section.
@@
 
-Within the context of @molstad2017shrinking, this algorithm would consist of iterating over the following three steps:
+Solving for $\hat{\Omega}$ in \@ref(eq:omegaloglik2) uses what we are going to call an *augmented ADMM* algorithm.
+Molstad and Rothman do not offer a name for this specific algorithm but it leverages the majorize-minimize principle in one of the steps in the algorithm - augmenting the ADMM algorithm discussed in the previous chapter.
+Within the context of the proposed penalty, the traditional ADMM algorithm for precision matrix estimation would consist of iterating over the following three steps:
 
@@
 
-where $L_{p}(\cdot)$ is the *augmented lagrangian* defined as
+where $L$, still the *augmented lagrangian*, is defined as
 
@@
 
-with $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$.
-However, instead of solving the first step exactly, the authors propose an alternative, approximating objective function ($\tilde{L}$) based on the majorize-minimize principle -- the purpose of which is to find a solution that can be solved in closed form.
-The ADMM algorithm with modification based on majorize-minimize principle is also found in @lange2016mm.
+Similar to the previous chapter, $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$.
+In fact, the details of the algorithm thus far are identical to the previous approach except that we are replacing $\Omega - Z$ with $A\Omega B - C - Z$ (or equivalently, $A\Omega B - Z - C$) in the augmented lagrangian and the dual update $\Lambda^{k + 1}$.
 
-The approximating function is defined as
+Instead of solving the first step exactly as we did in the previous section, the authors propose an alternative, approximating objective function, which we will call $\tilde{L}$, that is based on the majorize-minimize principle^[Further explanation of the majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
+The purpose of this approximating function is the desire to solve this first step in closed-form.
+The ADMM algorithm with this modification based on majorize-minimize principle is also found in @lange2016mm but here the approximating function is defined as
 
@@
 
-where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$, $\otimes$ is the Kronecker product, and $\tau$ is chosen such that $Q$ is positive definite.
-Note that if $Q$ is positive definite (p.d.), then
+where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite and thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ (therefore $\tilde{L}$ is a majorizing function^[Note that if $Q$ is positive definite, then $vec\left(\Omega - \Omega^{k} \right)^{T}\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0$ since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.]).
 
-\begin{equation}
-\frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) > 0
-(\#eq:pd)\notag
-\end{equation}
-
-since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.
-Thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[Further explanation of majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
-
-The *augmented ADMM* algorithm is the following:
+The *augmented ADMM* algorithm developed by Molstad and Rothman, which now includes the majorize-minimize principle, consists of the following repeated iterations:
 
@@
 
-### Algorithm
+where $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}$.
+Each step in this algorithm can now conveniently be solved in closed-form and the full details of each can be found in the appendix \@ref(proofOmegak).
+The following theorem provides the simplified steps in the algorithm.
 
-Set $k = 0$ and repeat steps 1-6 until convergence.
+```{theorem, name = "Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators."}
+
+Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$. Set $k = 0$ and repeat steps 1-6 until convergence.
 
@@
 
-The soft-thresholding function is defined as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
+```
 
@@
 
-In discussing the optimality conditions and stopping criterion, we will follow the steps outlined in @boyd2011distributed and cater them to the SCPME method.
-
-Below we have three optimality conditions:
-
-1. Primal:
-
-\begin{equation}
-A\Omega^{k + 1}B - Z^{k + 1} - C = 0
-(\#eq:scpmeprimal)\notag
-\end{equation}
-
-2. Dual:
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial f\left(\Omega^{k + 1}\right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) \\
-  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:scpmedual)\notag
-\end{split}
-\end{equation}
-
-The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to $\Omega^{k + 1}$ (note that we must honor the symmetric constraint of $\Omega^{k + 1}$) and the second is a result of taking the sub-differential of the lagrangian with respect to $Z^{k + 1}$ (no symmetric constraint).
-
-We will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$.
-At convergence, the optimality conditions require that $r^{k + 1} \approx 0$.
-The second residual we will define is the dual residual^[Proof of \@ref(eq:stopproof) in section \@ref(proofstopproof).]:
+A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous section \@ref(ADMMstop).
+The primal optimality condition here is that $A\Omega^{k + 1}B - Z^{k + 1} - C = 0$ and the two dual optimality conditions are $0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
+Similarly, we will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$ and the dual residual^[Proof of \@ref(eq:stopproof) in section \@ref(proofstopproof).] as
 
@@
 
-Like the primal residual, at convergence the optimality conditions require that $s^{k + 1} \approx 0$.
-Note that the second dual optimality condition is always satisfied^[Proof of \@ref(eq:dualopt2) in section \@ref(proofdualopt2)].
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}
-(\#eq:dualopt2)\notag
-\end{split}
-\end{equation}
-
-One possible stopping criterion is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where
+For proper convergence, we will require that both residuals are approximately equal to zero.
+Similar to the stopping criterion discussed previously, one possibility is to set $\epsilon^{rel} = \epsilon^{abs} = 10^{-3}$ and stop the algorithm when $\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}$ and $\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}$ where
 
@@
 \end{equation}
+
+## Regression Illustration
+
+One of the research directions mentioned in @molstad2017shrinking that was not further explored was the application of the SCPME framework to regression.
+Utilizing the fact that the population regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$ for predictors, $X$, and the responses, $Y$, they point out that their framework could allow for the simultaneous estimation of $\beta$ and $\Omega_{x}$.
+For example, recall that the general optimization problem outlined in the SCPME framework is to estimate $\hat{\Omega}$ such that
+
+\begin{equation}
+  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+(\#eq:penloglik3)\notag
+\end{equation}
+
+If the user specifies that $A = I_{p}, B = \Sigma_{xy}, C = 0, \mbox{ and } \Omega_{x}$ is the precision matrix for the predictors, then the optimization problem of interest is now
+
+\begin{equation}
+  \hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr(S_{x}\Omega_{x}) - \log\left| \Omega_{x} \right| + \lambda\left\| \Omega_{x} \Sigma_{xy} \right\|_{1} \right\} \\
+(\#eq:penloglik4)\notag
+\end{equation}
+
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ and then using our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+Like @witten2009covariance, this approach estimates the forward regression coefficient matrix while using shrinkage estimators of the marginal precision matrix for the predictors.
+Specifically, this optimization problem has the effect of deriving an estimate of $\Omega_{x} \mbox { and } \beta$ while assuming sparsity in the forward regression coefficient $\beta$.
+
+The penality outline in the SCPME framekwork is flexible that many novel estimators can be constructed.
+For instance, we might also consider taking $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the sample cross-covariance matrix of $X$ and $Y$.
+In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
+(\#eq:pen4)\notag
+\end{equation}
+
+In the next section we offer a short simulation comparing these estimators to related and competing prediction methods.
+
+## Simulations
+
+In this simulation, we compare the performance of several competing prediction methods, including the so-called SCPME regression estimators discussed in the previous section, under various data realizations.
+In total, we consider the following estimators:
+
+ - `OLS` = ordinary least squares estimator. In *high* dimensional setting ($p >> n$), the Moore-Penrose estimator is used.
+
+ - `ridge` = ridge regression estimator.
+
+ - `lasso` = lasso regression estimator.
+
+ - `oracleB` = oracle estimator for $\beta$.
+
+ - `oracleO` = regression estimator with oracle $\Omega^{*}$ (let $\beta = \Omega^{*}\hat{\Sigma}_{xy}$).
+
+ - `oracleS` = regression estimator with oracle $\Sigma_{xy}^{*}$ (let $\beta = \hat{\Omega}\Sigma_{xy}^{*}$).
+
+ - `shrinkB` = SCPME regression estimator with penalty $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$.
+
+ - `shrinkBS` = SCPME regression estimator with oracle $\Sigma_{xy}^{*}$ so that the penalty is $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$.
+
+ - `shrinkBO` = SCPME regression estimator with penalty $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$.
+
+ - `glasso` = graphical lasso estimator.
+
+Each tuning parameter was selected to minimize the mean squared prediction error (MSPE) over 3-fold cross validation.
+
+For each data generation procedures, let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that $\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}$.
+Here we let the script notation denote the fact that the columns have been centered so as to remove the intercept in our prediction models.
+The regression coefficient matrix $\beta$ is constructed so that $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $p$ times $r$ random bernoulli draws with 50\% probability being equal to one.
+The residual covariance matrix $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
+This ensures that its corresponding precision matrix will be tridiagonal and sparse.
+Then for 100 independent, identically distributed samples, we have that $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$.
+An additional 1000 samples will be generated for the testing set and the methods were evaluated on both model error and mean squared prediction error.
+Each data generating procedure for each $p$ in $(10, 50, 100, 150)$ was replicated a total of 20 times.
+
+Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE).
+Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.
+
+In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$.
+It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.
+
+In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS.
+The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.
+
+When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.
+
+It is interesting that `oracleO` performed worse than `oracleS` in the final table.
+It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
+
+<!-- <br>\vspace{0.5cm} -->
+<!-- ```{r scpmesim1, eval = T, echo = F, fig.cap = "ME by P and R (N = 100, spase = 0.5, sigma = tridiag. High dimension."} -->
+
+<!-- # load data -->
+<!-- load("images/sim6.Rdata") -->
+
+<!-- # set P to numeric  -->
+<!-- sim6$P %<>% as.character %>% as.numeric -->
+
+<!-- # ME by P and R (N = 100, sparse = 0.5, sigma = "tridiag") -->
+<!-- sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS"), metric == "ME") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 100, sparse = 0.5, sigma = tridiag)") -->
+
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
+
+\vspace{0.5cm}
+```{r scpmesim2, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag).
+The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
+The model errors (ME) for each estimator are plotted.
+shrinkBO and shrinkB were the two best-performing estimators closely follow by the ridge and lasso regression estimators."}
+
+# load  data
+load("images/sim6.Rdata")
+
+# set P to numeric
+sim6$P %<>% as.character %>% as.numeric
+
+# ME by P (N = 100, R = 10, sparse = 0.5, sigma = "tridiag")
+sim6 %>% filter(N == 100, R == 10, sparse == 0.5, sigma == "tridiag", !model %in% c("OLS", "oracleS")) %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("Model Error by Dimension")
+
+```
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+```{r, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)"}
+
+# ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
+sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
+
+```
+\vspace{0.5cm}
+
+<!-- <br>\vspace{0.5cm} -->
+<!-- ```{r scpmesim4, eval = T, echo = F, fig.cap = "ME by P and R (N = 1000, spase = 0.5, sigma = tridiag. Low dimension."} -->
+
+<!-- # ME by P and R (N = 1000, sparse = 0.5, sigma = "tridiag") -->
+<!-- sim6 %>% filter(N == 1000, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + facet_wrap(~ R, scales = "free") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P and R (N = 1000, sparse = 0.5, sigma = tridiag)") -->
+
+<!-- ``` -->
+<!-- <br>\vspace{0.5cm} -->
+
+<!-- \vspace{0.5cm} -->
+<!-- ```{r scpmesim5, eval = T, echo = F, fig.cap = "ME by P (N = 1000, R = 5, spase = 0.5, sigma = tridiag. Low dimension."} -->
+
+<!-- # ME by P (N = 1000, R = 5, sparse = 0.5, sigma = "tridiag") -->
+<!-- sim6 %>% filter(N == 1000, R == 5, sparse == 0.5, model != "OLS") %>% group_by(N, P, R, sparse, sigma, model) %>% summarise(mean = mean(Error)) %>% ggplot(aes(P, mean, color = model, linetype = model)) + geom_line() + scale_colour_discrete("") + scale_linetype_manual("", values = rep(c(5,6), 5)) + theme_minimal() + theme(legend.position = "bottom") + xlab("P") + labs(color = "Model") + scale_x_continuous(breaks = c(10, 50, 100, 150)) + ylab("ME") + ggtitle("ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)") -->
+
+<!-- ``` -->
+<!-- \vspace{0.5cm} -->
+
+<!-- \vspace{0.5cm} -->
+<!-- ```{r scpmesim6, eval = T, echo = F, fig.cap = "ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag)."} -->
+
+<!-- # ME table (N = 1000, sparse = 0.5, sigma = "tridiag", P = 150, R = 5) -->
+<!-- sim6 %>% filter(N == 1000, sparse == 0.5, sigma == "tridiag", P == 150, R == 5) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "ME by P (N = 1000, R = 5, sparse = 0.5, sigma = tridiag).") -->
+
+<!-- ``` -->
+<!-- \vspace{0.5cm} -->
+
+### Regression Simulations with Covariance Shrinkage
+
+Here we compare the `shrinkB` and the `shrinkBO` estimators.
+
+(same data generation except the parameters are different this time...)
+
+We consider the response dimension as 10.
+
+For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$.
+We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.
+
+In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE.
+This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.
+
+In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.
+
+The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.
+
+The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)
+
+```{r, eval = T, echo = F}
+
+# load  data
+load("images/sigma.Rdata")
+
+# design color palette
+bluetowhite <- c("#000E29", "white")
+
+# change to numeric
+sigma$lam %<>% as.character %>% as.numeric
+sigma$const %<>% as.character %>% as.numeric
+
+```
+
+\vspace{0.5cm}
+```{r scpmesim7, eval = T, echo = F, fig.cap = "The oracle precision matrices were tri-diagonal with dimension p = 200 and the data was generated with a sample size n = 100 and response vector dimension r = 10.
+The cross validation MSPE are plotted for each lambda and constant tuning parameter pair.
+The optimal tuning parameter pair was found to be log10(lam) = -1 and const = 0.6.
+Note that brighter areas signify smaller losses."}
+
+# shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB Covariance Shrinkage", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+\vspace{0.5cm}
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim8, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- # shrinkB MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound") -->
+<!-- d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- ##### `shrinkBO` -->
+
+<!-- <br>\vspace{1cm} -->
+
+\vspace{0.5cm}
+```{r scpmesim9, eval = T, echo = F, fig.cap = "The oracle precision matrices were tri-diagonal with dimension p = 200 and the data was generated with a sample size n = 100 and response vector dimension r = 10.
+The cross validation MSPE are plotted for each lambda and constant tuning parameter pair.
+The optimal tuning parameter pair was found to be log10(lam) = -0.5 and const = 0.3.
+Note that brighter areas signify smaller losses."}
+
+# shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
+d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))
+
+min = d[d$mean == min(d$mean),]
+
+d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO Covariance Shrinkage", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = ""))
+
+```
+\vspace{0.5cm}
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim10, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- # shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "compound") -->
+<!-- d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 100, P = 200, R = 10, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- #### Low Dimension -->
+
+<!-- ##### `shrinkB` -->
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim11, eval = T, echo = F, fig.cap = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag). Low dimension."} -->
+
+<!-- # shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "tridiag") -->
+<!-- d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim12, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- # shrinkB MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound") -->
+<!-- d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkB") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkB MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- #### `shrinkBO` -->
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim13, eval = T, echo = F, fig.cap = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag). Low dimension."} -->
+
+<!-- # shrinkBO MSPE by lam and const (N = 1000, P = 10, R = 1, sigma = "tridiag") -->
+<!-- d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = tridiag)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- <br>\vspace{1cm} -->
+
+<!-- ```{r scpmesim14, eval = T, echo = F, fig.cap = "Figure caption here."} -->
+
+<!-- # shrinkBO MSPE by lam and const (N = 1000, P = 50, R = 1, sigma = "compound") -->
+<!-- d = sigma %>% filter(N == 1000, P == 50, R == 1, sparse == 0.5, sigma == "compound", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean))) -->
+
+<!-- min = d[d$mean == min(d$mean),] -->
+
+<!-- d %>% ggplot(aes(const, log10(lam))) + geom_raster(aes(fill = augmean)) + scale_fill_gradientn(colours = colorRampPalette(bluetowhite)(2), guide = "none") + theme_minimal() + labs(title = "shrinkBO MSPE (N = 1000, P = 50, R = 1, sigma = compound)", caption = paste("**Optimal: log10(lam) = ", round(log10(min$lam), 3), ", const = ", round(min$const, 3), sep = "")) -->
+
+<!-- ``` -->
+
+<!-- <br>\vspace{1cm} -->
+
+## Discussion
+
+The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+(\#eq:penregression)\notag
+\end{equation}
+
+To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:
+
+\begin{equation}
+Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
+(\#eq:linregression)\notag
+\end{equation}
+
+where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
+These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form
+
+\begin{equation}
+Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
+(\#eq:linnormal)\notag
+\end{equation}
+
+We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$.
+Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience.
+We will also let $f$ denote the probability distribution function for each respective variable.
+
+(Talk about regression estimator minimizing frobenius norm of predictions)
+
+(REMEMBER INFORMATION IN APPENDIX)

### 2019-04-07 05-appendix.Rmd
largely completed chapters 1 and chapters 2
only SCPME sims and discussion left

@@
 
-## Proofs
+### Proof of \@ref(eq:omegaalgo) {#proofomegaalgo}
 
-### Proof of \@ref(eq:omegaalgo) {#proofomegaalgo}
+@witten2009covariance and @price2015ridge showed that the following optimization problem can be solved in closed-form. We outline their steps below.
 
@@
 \end{equation}
+
+First start by taking the gradient with respect to $\Omega$:
 
@@
 Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
-First set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns:
+Next set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ using spectral decomposition so that $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns so that
 
@@
 \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
-(\#eq:appendixomegaproof)\notag
+(\#eq:appendixomegaproof)
 \end{equation}
@@
 ### Proof of \@ref(eq:ZZalgo) {#proofZZalgo}
+
+Solve the optimization problem
 
@@
 \end{equation}
+
+Start by taking the subgradient with respect to $Z$:
 
@@
 
-where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we have that
 
@@
 
-### Proof of \@ref(eq:dualresidual) {#proofdualresidual}
+### Proof of the dual residual {#proofdualresidual}
+
+Here we want to show that $0 \in \rho\left(Z^{k + 1} - Z^{k}\right)$ which is a direct result of the fact that $\Omega^{k + 1}$ is the minimizer of the augmented lagrangian and $0 \in f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1}$.
 
@@
 
-### Proof of \@ref(eq:dualopt) {#proofdualopt}
+### Proof of second dual optimality condition {#proofdualopt}
+
+Here we use the primal optimality condition $\Omega^{k + 1} - Z^{k + 1} = 0$ to show that the second dual optimality condition $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$ is always satisfied.
 
@@
 
-### Proof of BLAHHHH
+### Explanation of majorizing function \@ref(eq:approx) {#taylorsexp}
 
@@
 
-**Note:**
+Note that the gradient and hessian, respectively, are
 
@@
 
-Let us now plug in this equality into our optimization problem in step one:
+Let us now plug in this equality into our optimization problem that includes the augmented lagrangian:
 
@@
 \begin{split}
-  \Omega^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  \hat{Omega}^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
-  &+ \left.\begin{matrix} \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right) \end{matrix}\right\} \\
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} vec\left(\Omega - \Omega^{k}\right)^{T}\rho Q\left(\Omega - \Omega^{k}\right)/2 \end{matrix}\right\} \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \end{matrix}\right. \\
-  &+ \left.\begin{matrix} \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} + \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 + tr\left[\rho\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
  tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
-  &- \left.\begin{matrix} \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \end{matrix}\right\} \\
+  &- \left.\begin{matrix} \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \end{matrix}\right\} \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
- tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+ tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \right\} \\
 (\#eq:omegaapprox)\notag
@@
 
+We show that the following optimization problem can be solved in closed-form similar to \@ref(eq:appendixomegaproof).
+
 \begin{equation}
@@
 
-We can then decompose $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
+We can then decompose using spectral decomposition $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
 
@@
 
+Solve the optimization problem
+
 \begin{equation}
@@
 
-This residual is derived from the fact. Because $\Omega^{k + 1}$ is the argument that minimizes $L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)$,
+Here we want to show that $0 \in \rho\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2$ which is a direct result of the fact that $0 \in \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$.
 
@@
 \begin{split}
-  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2} \right\} \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right) \\
-  &- \frac{\rho}{2}\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) \\
-  &+ \frac{\rho}{2}\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right) + \frac{\rho}{2}\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right) \\
-  &+ \frac{\rho}{2}\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right] \\
-  &+ \frac{1}{2}\left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right] + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \frac{1}{2}\left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right) + \frac{\rho}{2}\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right) \\
-  \Rightarrow 0 &\in \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
+  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2}/2 \right\} \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 + \rho\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right)/2 \\
+  &- \rho\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 \\
+  &+ \rho\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 + \rho\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right)/2 \\
+  &+ \rho\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right]/2 \\
+  &+ \left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right]/2 + \rho\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 + \rho\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2 \\
+  \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2
 (\#eq:appendixstopproof)\notag
-\end{split}
-\end{equation}
-
-### Proof of \@ref(eq:dualopt2) {#proofdualopt2}
-
-\begin{equation}
-\begin{split}
-  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k + 1} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k + 1} - C \right\|_{F}^{2} \right\} \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right) \\
-  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
-(\#eq:appendixdualopt2)\notag
 \end{split}
@@
 \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
-(\#eq:penregression)\notag
 \end{equation}
@@
 Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-(\#eq:linregression)\notag
 \end{equation}
@@
 Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
-(\#eq:linnormal)\notag
 \end{equation}

### 2019-04-07 03-SCPME.Rmd
adjustment to travis

@@
 and Professor Adam Rothman outline a framework to estimate *characteristics* of precision matrices.
-This concept, inspired by others like @cai2011direct, @fan2012road, and @mai2012direct, exploits the fact that in many predictive models, estimation of the precision matrix is only necessary through its product with another feature such as a mean vector.
+This concept, inspired by others like @cai2011direct, @fan2012road, and @mai2012direct, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector.
 
 The example they offer in @molstad2017shrinking is in the context of Fisher's linear discriminant analysis model.
-If a response vector $Y$ is categorical such that $Y$ can take values in $\left\{1, ..., J\right\}$, then the linear discrimnant analysis model assumes that the design matrix $X$, conditional on the response vector $Y$, is normally distributed:
+If a response vector $Y$ is categorical such that $Y$ can take values in $\left\{1, ..., J\right\}$, then the linear discrimnant analysis model assumes that the design matrix $X$ conditional on the response vector $Y$ is normally distributed:
 
@@
 
-where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices that are assumed to be known and specified so that solving the full penalized gaussian log-likelihood for $\Omega$ results in solving
+where $A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}$ are matrices that are assumed to be known and specified so that solving the full penalized gaussian negative log-likelihood for $\Omega$ results in solving
 
@@
 
-where $L$, still the *augmented lagrangian*, is defined as
+where $L$, the *augmented lagrangian*, is defined as
 
@@
 
-Instead of solving the first step exactly as we did in the previous section, the authors propose an alternative, approximating objective function, which we will call $\tilde{L}$, that is based on the majorize-minimize principle^[Further explanation of the majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
-The purpose of this approximating function is the desire to solve this first step in closed-form.
-The ADMM algorithm with this modification based on majorize-minimize principle is also found in @lange2016mm but here the approximating function is defined as
+Instead of solving the first step exactly as we did in the previous section, the authors propose an alternative, approximating objective function, which we will denote as $\tilde{L}$, that is based on the majorize-minimize principle^[Further explanation of the majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
+The purpose of this approximating function is the desire to solve the first step of the algorithm in closed-form.
+The ADMM algorithm with this modification based on majorize-minimize principle is also found in @lange2016mm but here we define the approximating function as
 
@@
 
-where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite and thus $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ (therefore $\tilde{L}$ is a majorizing function^[Note that if $Q$ is positive definite, then $vec\left(\Omega - \Omega^{k} \right)^{T}\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0$ since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.]).
-
+where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite.
+Note that if $Q$ is positive definite, then $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[If $Q$ is positive definite, then $vec\left(\Omega - \Omega^{k} \right)^{T}\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0$ since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.].
 The *augmented ADMM* algorithm developed by Molstad and Rothman, which now includes the majorize-minimize principle, consists of the following repeated iterations:
@@
 
-A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous section \@ref(ADMMstop).
+A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous chapter \@ref(ADMMstop).
 The primal optimality condition here is that $A\Omega^{k + 1}B - Z^{k + 1} - C = 0$ and the two dual optimality conditions are $0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
@@
 Utilizing the fact that the population regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$ for predictors, $X$, and the responses, $Y$, they point out that their framework could allow for the simultaneous estimation of $\beta$ and $\Omega_{x}$.
+Like @witten2009covariance, this approach would estimate the forward regression coefficient matrix while using shrinkage estimators of the marginal precision matrix for the predictors.
 For example, recall that the general optimization problem outlined in the SCPME framework is to estimate $\hat{\Omega}$ such that
@@
 
-Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ and then using our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
-Like @witten2009covariance, this approach estimates the forward regression coefficient matrix while using shrinkage estimators of the marginal precision matrix for the predictors.
 Specifically, this optimization problem has the effect of deriving an estimate of $\Omega_{x} \mbox { and } \beta$ while assuming sparsity in the forward regression coefficient $\beta$.
-
-The penality outline in the SCPME framekwork is flexible that many novel estimators can be constructed.
-For instance, we might also consider taking $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the sample cross-covariance matrix of $X$ and $Y$.
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ and then use our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+Estimators such as this are truly novel an can conveniently be estimated by the SCPME framework.
+Another such estimator that is a product of this framework is one where we leave $A \mbox{ and } C$ unchanged but take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the sample cross-covariance matrix of $X$ and $Y$.
 In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
@@
 \end{equation}
+
+Like before, we would take our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+The embedded assumptions here are that not all predictors are useful in predicting the response, $Y$, *and* a number of the predictors are conditionally independent of one another - assumptions that would be quite reasonable in practice.
 

### 2019-04-07 03-SCPME.Rmd
update to travis - bug

@@
 
-In this simulation, we compare the performance of several competing prediction methods, including the so-called SCPME regression estimators discussed in the previous section, under various data realizations.
+In this simulation, we compare the performance of several competing regression prediction methods under various data realizations, including the so-called SCPME regression estimators discussed in the previous section.
 In total, we consider the following estimators:
 
- - `OLS` = ordinary least squares estimator. In *high* dimensional setting ($p >> n$), the Moore-Penrose estimator is used.
+ - `OLS` = ordinary least squares estimatior. In high dimensional settings ($p >> n$), the Moore-Penrose estimator is used.
 
@@
 
- - `oracleO` = regression estimator with oracle $\Omega^{*}$ (let $\beta = \Omega^{*}\hat{\Sigma}_{xy}$).
+ - `oracleO` = regression estimator with oracle $\Omega_{x}^{*}$ (let $\beta = \Omega_{x}^{*}\hat{\Sigma}_{xy}$).
 
- - `oracleS` = regression estimator with oracle $\Sigma_{xy}^{*}$ (let $\beta = \hat{\Omega}\Sigma_{xy}^{*}$).
+ - `oracleS` = regression estimator with oracle $\Sigma_{xy}^{*}$ (let $\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$).
 
- - `shrinkB` = SCPME regression estimator with penalty $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$.
+ - `shrinkB` = SCPME regression estimator with penalty $\lambda\left\| \Omega_{x}\hat{\Sigma}_{xy} \right\|_{1}$ so that $\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
 
- - `shrinkBS` = SCPME regression estimator with oracle $\Sigma_{xy}^{*}$ so that the penalty is $\lambda\left\| \Omega\hat{\Sigma}_{xy}^{*} \right\|_{1}$.
+ - `shrinkBS` = SCPME regression estimator with oracle $\Sigma_{xy}^{*}$ so that the penalty is $\lambda\left\| \Omega_{x}\Sigma_{xy}^{*} \right\|_{1}$ and we let $\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$.
 
- - `shrinkBO` = SCPME regression estimator with penalty $\lambda\left\| \Omega[\Sigma_{xy}, I_{p}] \right\|_{1}$.
+ - `shrinkBO` = SCPME regression estimator with penalty $\lambda\left\| \Omega_{x}[\Sigma_{xy}, I_{p}] \right\|_{1}$ so that $\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
 
- - `glasso` = graphical lasso estimator.
+ - `glasso` = graphical lasso estimator with penalty $\lambda\left\| \Omega_{x} \right\|_{1}$ so that $\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
 
-Each tuning parameter was selected to minimize the mean squared prediction error (MSPE) over 3-fold cross validation.
+For each estimator, if selection of a tuning parameter is required, then the tuning parameter was chosen so that the mean squared prediction error (MSPE) was minimized over 3-fold cross validation.
 
-For each data generation procedures, let $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$, and $\beta \in \mathbb{R}^{p \times r}$ so that $\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}$.
-Here we let the script notation denote the fact that the columns have been centered so as to remove the intercept in our prediction models.
-The regression coefficient matrix $\beta$ is constructed so that $\beta = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $p$ times $r$ random bernoulli draws with 50\% probability being equal to one.
-The residual covariance matrix $\Sigma_{y | x}$ is constructed so that $\left( \Sigma_{xx} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
-This ensures that its corresponding precision matrix will be tridiagonal and sparse.
-Then for 100 independent, identically distributed samples, we have that $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$.
-An additional 1000 samples will be generated for the testing set and the methods were evaluated on both model error and mean squared prediction error.
-Each data generating procedure for each $p$ in $(10, 50, 100, 150)$ was replicated a total of 20 times.
+The data generating procedures for the simulations are as follows.
+The oracle regression coefficient matrix $\beta^{*}$ was constructed so that $\beta^{*} = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $p$ times $r$ random bernoulli draws with 50\% probability being equal to one.
+The covariance matrices $\Sigma_{y | x}$ and $\Sigma_{x}$ were constructed so that $\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}$ and $\left( \Sigma_{x} \right)_{ij} = 0.7^{\left| i - j \right|}$, respectively.
+This ensures that their corresponding precision matrices will be tridiagonal and sparse.
+Then for 100 independent, identically distributed samples, we had $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$ so that $\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}$ where $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$ and the script notation denotes the fact that the columns have been centered so as to remove the intercept in our prediction models.
+An additional 1000 samples were generated similarly for the testing set and each prediction method was evaluated on both model error and mean squared prediction error.
 
-Note that we are now displaying model error (ME) as opposed to mean squared prediction error (MSPE).
-Also, `OLS` and `oracleS` will not be show in the high dimensional setting plots because of poor performance.
+Figure \@ref(fig:scpmesim2) displays the model error for each method by dimension of the design matrix.
+Here we took the sample size equal to $n = 100$ and the response matrix dimension $r = 10$ with each data generating procedure replicated a total of 20 times.
+Note `OLS` and `oracleS` are not shown due to extremely poor performance.
+
+We find that...
 

### 2019-04-09 03-SCPME.Rmd
only discussion left

@@
 Note `OLS` and `oracleS` are not shown due to extremely poor performance.
-
-We find that...
-
-In high dimensional settings, `shrinkBO` (penalty: $\lambda\left\| \Omega[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$) and `shrinkB` (penalty: $\lambda\left\| \Omega\hat{\Sigma}_{xy} \right\|_{1}$) perform increasingly well relative (and superior) to the others when $p >> n$.
-It's not surprising that `shrinkBO` performs the best because the embedded assumptions most closely match the data generating model.
+We find that in high dimensional settings, `shrinkBO` and `shrinkB` perform increasingly well relative to the others as the predictor dimension increases with `shrinkBO` performing the best.
+Interestingly, when $n > p$ is still one of the best-performing estimators - though worse than both `lasso` and `ridge` - but the performance of `shrinkB` decreases drastically (plot not shown).
 
@@
 
-When $n > p$ we see that `shrinkB` performs terribly. Interestingly, `shrinkBO` is still one of the better performing estimators -- though worse than both `lasso` and `ridge`.
-
-It is interesting that `oracleO` performed worse than `oracleS` in the final table.
-It appears that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
+The table below shows the average model error for each estimator when $n = 100$, $p = 150$, and $r = 10$.
 
@@
 ```
-\vspace{0.5cm}
 
-\vspace{0.5cm}
+\newpage
 ```{r, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)"}
@@
 # ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
-sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(mean = mean(Error), sd = sd(Error)) %>% arrange(mean) %>% pander(caption = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(error = mean(Error), sd = sd(Error)) %>% arrange(error) %>% pander(caption = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
 
@@
 
-Here we compare the `shrinkB` and the `shrinkBO` estimators.
+This final simulation was run and explored due to the fact each of the SCPME regression estimators require an estimation of the cross-covariance matrix.
+In the previous simulations, we used the maximum likelihood estimator.
+However, because the data-generating procedures construct settings that are inherently sparse, we were interested to determine if additional shrinkage of the *cross-covariance* matrix would also prove beneficial.
+For instance, in a number of settings, we were finding that the estimator `oracleO` ($\beta = \Omega_{x}^{*}\hat{\Sigma}_{xy}$) was performing worse than `oracleS` ($\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$) which perhaps suggests that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
+This simulation explores that theory a bit further.
 
-(same data generation except the parameters are different this time...)
+The data-generating procedure for this simulation is similar to previous one but here we take $n = 100$, $p = 200$, $r = 10$, *and* we additionally multiple the cross-covariance sample estimator by a factor of $k$ where $k \in (0.1, 0.2, ..., 0.9, 1)$.
+Figure \@ref(fig:scpmesim7) plots the MSPE for `shrinkB` for each tuning parameter, $\lambda$, and constant, $k$, pair.
+Figure \@ref(fig:scpmesim9) plots the MSPE similarly for `shrinkBO`.
 
-We consider the response dimension as 10.
-
-For each of the estimators, $\Sigma_{xy}$ is estimated by the sample covariance matrix $\hat{\Sigma}_{xy}$ times some constant factor $k \in (0.1, 0.2, ..., 0.9, 1)$.
-We are shrinking $\hat{\Sigma}_{xy}$ by a constant to determine if there are any benefits to doing so.
-
-In the high dimensional settings, it does appear that shrinking the sample covariance matrix $\hat{\Sigma}_{xy}$ by a constant factor helps in reducing MSPE.
-This is indicated by the fact that the optimal `const` hovers around 0.5 for each of the estimators `shrinkB` and `shrinkBO`.
-
-In the low dimension settings, it appears that shrinking the covariance matrix is not beneficial.
-
-The type of oracle precision matrix (tridiagonal or compound symmetric) does not appear to be too influential with regards to the affect of shrinking the covariance matrix.
-
-The larger the dimension of $Y$, the more beneficial shrinkage will likely be (not that surprising)
+Interestingly, we find that in this high dimension setting, it does appear that shrinking the sample covariance matrix by a constant factor helps the overall prediction performance of the SCPME estimators.
+This is indicated by the fact that the optimal constant, $k$, hovers between 0.3 and 0.6 for each of the estimators.
+We also performed a simulation in low dimensions (not shown) but we did not see the same benefit.
 
@@
 
+\newpage
+
 ## Discussion

### 2019-04-20 01-intro.Rmd
intro, PME final

@@
 Prediction, on the other hand, refers to the process by which we draw inference about an event that has not-yet occurred.
-This component is prevalent in industry where the demand to predict stock prices, to predict which movie individuals will prefer, and even new friend connections in a network has sparked huge investments in research and given rise to groups whose primary goal is pushing the bounds and developing new predictive models.
+The latter component is abundant in industry where the demand to predict stock prices, movies individuals prefer, and even to predict new friend connections in a network has sparked huge investments in research and given rise to research groups whose primary goal is pushing the bounds and developing new predictive models.
 
@@
 In fact, the success and reliability of many predictive models is contingent upon good, efficient parameter estimation.
-Many of these models require the estimation of a precision matrix - the inverse of the covariance matrix (frequently denotes as $\Omega$) - that establishes the interaction and covariance between random variables.
+Many of these models require the estimation of a precision matrix - the inverse of the covariance matrix (frequently denoted as $\Omega$) - that establishes the interaction and covariance between random variables.
+For this reason, the last decade has seen an ever-expanding community devoted to precision matrix estimation.
 
-For this reason, in the last decade there has been an ever-expanding community devoted to precision matrix estimation and among this community is Professor Adam Rothman and Aaron Molstad, Ph.D.
+Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D.
 whose research will be a focal point of this manuscript.
-The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this work is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking).
+The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this manuscript is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking).
 In it, they outline a framework to estimate *characteristics* of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
-They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated.
-For example, in binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors." The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
+They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated...
+In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors." The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
 
@@
 Utilizing the fact that the population regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$ (where $\Sigma_{xy}$ is the cross-covariance matrix between the predictors, $X$, and the responses, $Y$, and $\Omega_{x}$ is the precision matrix for $X$), their framework allows for the simultaneous estimation of $\beta$ and $\Omega_{x}$ with an embedded assumption potentially useful for superior prediction performance.
-In close communication and collaboration with Professor Rothman, we wanted to explore this direction further.
+In close communication and collaboration with Professor Rothman, we wanted to explore this research direction further.
 However, in order to build upon their work and contribute new material, there were a number of concepts that needed to be learned along the way and this document will follow that journey.
@@
 This section will mention popular estimation methods and algorithms but most discussion will be directed towards the ADMM algorithm.
-This discussion will be useful as we begin detailing the shrinking characteristics of precision matrix estimators framework (which may be referred to as SCPME), the so-called augmented ADMM algorithm, and later the framework's application to regression.
+Discussion of the ADMM algorithm will be useful as we begin detailing the shrinking characteristics of precision matrix estimators framework (which may be referred to as SCPME), the so-called augmented ADMM algorithm, and later the framework's application to regression.
 Lastly, the document will end with two brief tutorials for the R packages `ADMMsigma` and `SCPME`.
@@
 Most matrices will take the form of either $\Sigma$, the population covariance matrix, or $\Omega$, the population precision matrix.
-Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$) and a subscript may be added to each if more than two random variables are considered in a problem.
+Note that the precision matrix is simply the inverse of the covariance matrix ($\Omega \equiv \Sigma^{-1}$) and a subscript may be added to each if more than two random variables are considered in a problem ($\Omega_{x}$).
 A subscript star may also be added if the object is oracle - or known - a priori ($\Omega_{*}$).
-The oracle's estimator that minimizes/maximizes a pre-specified objective function will be denoted with a hat ($\hat{\Omega}$).
+The oracle's estimator that optimizes a pre-specified objective function will be denoted with a hat ($\hat{\Omega}$).
 

### 2019-04-20 02-PME.Rmd
intro, PME final

@@
 
-The estimator for $\mu$ that maximizes the log-likelihood is $\hat{\mu}^{MLE} = \bar{X} \equiv \sum_{i = 1}^{n}X_{i}/n$, so that the partially maximized gaussian log-likelihood for $\Omega$ is
+The estimator for $\mu$ that maximizes the log-likelihood is $\hat{\mu}^{mle} = \bar{X} \equiv \sum_{i = 1}^{n}X_{i}/n$, so that the partially maximized gaussian log-likelihood function for $\Omega$ is
 
@@
 
-where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the covariance matrix, $\Sigma$.
-In addition to $\mu$, we could also derive the maximum likelihood estimator for $\Omega$.
-By setting the gradient of the partially maximized log-likelihood equal to zero, we can show that
+where $S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n$ is the usual sample estimator for the population covariance matrix, $\Sigma$.
+In addition to $\mu$, one could also derive the maximum likelihood estimator for $\Omega$.
+By setting the gradient of the partially maximized log-likelihood equal to zero, one could show that
 
@@
 \begin{split}
-\hat{\Omega}^{MLE} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left(S\Omega \right) \right\} \\
+\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left(S\Omega \right) \right\} \\
   &= \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \\
@@
 
-so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{MLE} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]^{-1}$.
+so that the MLE for $\Omega$, when it exists, is $\hat{\Omega}^{mle} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]^{-1}$.
 The reality, however, is that this object does *not* always exist.
 In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix is rank deficient and no longer invertible.
-For this reason, many papers in the last decade have proposed shrinkage estimators of the precision matrix similar to the shrinkage estimators in regression settings.
-That is, instead of minimizing solely the negative log-likelihood function, authors have proposed minimizing the gaussian log-likelihood *plus* a penalty term, $P$, which is often a function of the precision matrix.
+For this reason, many papers in the last decade have proposed *shrinkage estimators* of the population precision matrix similar to the shrinkage estimators in regression settings.
+That is, instead of minimizing solely the negative log-likelihood function, researchers have proposed minimizing the gaussian log-likelihood *plus* a penalty term, $P$, where $P$ is often a function of the precision matrix.
 
@@
 
-The penalties that have been proposed for precision matrix estimation are typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$.
+The penalties that have been proposed for precision matrix estimation are typically a variation of the ridge penalty $P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2$ or the lasso penalty $P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}$ (here $\lambda$ is a tuning parameter).
 The authors, @yuan2007model, initially proposed the lasso-penalized gaussian log-likelihood defined as
@@
 Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include @rothman2008sparse and @friedman2008sparse.
-In addition, many efficient algorithms have been proposed to solve for $\hat{\Omega}$ in this setting but the most popular method is the graphical lasso algorithm (often referred to as glasso) introduced by @friedman2008sparse.
+In addition, many efficient algorithms have been proposed to solve for $\hat{\Omega}$, however, the most popular method is the graphical lasso algorithm (glasso) introduced by @friedman2008sparse.
 Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm used in lasso-penalized regression.
@@
 In fact, the latter two papers show that the resulting minimizer can be solved in closed-form - which will be discussed later in this manuscript.
-However, the penalty explored in the remainder of this chapter is not a lasso penality nor a ridge penalty but, in fact, a convex combination of the two known as the *elastic-net* penalty:
+However, the penalty explored through the remainder of this chapter is not a lasso penality nor a ridge penalty but, in fact, a convex combination of the two known as the *elastic-net* penalty:
 
@@
 
-with tuning parameter $0 \leq \alpha \leq 1$.
+with additional tuning parameter $0 \leq \alpha \leq 1$.
 Clearly, when $\alpha = 0$ this penalty reduces to a ridge penalty and when $\alpha = 1$ it reduces to a lasso penalty.
 Originally proposed in @zou2005regularization in the context of regression, this penalty has since been popularized and is used in the penalized regression R package `glmnet`.
-This penalty allows for additional flexibility but, despite this, no published work (to our knowledge) has explored the elastic-net penalty in the context of precision matrix estimation.
+This penalty allows for additional flexibility but, despite this, no published work to our knowledge has explored the elastic-net penalty in the context of precision matrix estimation.
 We will show how to solve the following optimization problem in the next section using the ADMM algorithm.
@@
 
-In general, suppose that we want to solve an optimization problem of the form
+In general, the ADMM algorithm supposes that we want to solve an optimization problem of the form
 
@@
 Note that any infimum under the augmented lagrangian is equivalent to the infimum of the traditional lagrangian since any feasible point $(x, z)$ must satisfy the constraint $\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0$.
-@boyd2011distributed show that the infimum will be approached under the following repeated iterations:
+@boyd2011distributed show that using the ADMM algorithm the infimum will be approached under the following repeated iterations:
 
@@
 Conveniently, this general algorithm can be coerced into a format useful in precision matrix estimation.
-Suppose we let $f$ be equal to the non-penalized log-likelihood, $g$ equal to the elastic-net penalty, $P\left( \Omega \right)$, and we use the constraint that $\Omega$ must be equal to $Z$, then the augmented lagrangian in the context of precision matrix estimation is of the form
+Suppose we let $f$ be equal to the non-penalized gaussian log-likelihood, $g$ equal to the elastic-net penalty, $P\left( \Omega \right)$, and we use the constraint that $\Omega \in \mathbb{S}_{+}^{p}$ must be equal to some matrix $Z \in \mathbb{R}^{p \times p}$, then the augmented lagrangian in the context of precision matrix estimation is of the form
 
@@
 
-where $\Lambda$ is taking the role of $y$ and the ADMM algorithm now consists of the repeated iterations
+where $\Lambda$ takes the role of $y$ as the lagrange multiplier. The ADMM algorithm now consists of the following repeated iterations:
 
@@
 
-It turns out that each step in this algorithm can be solved in closed-form.
+Furthermore, it turns out that each step in this algorithm can be solved efficiently in closed-form.
 The full details of each can be found in the appendix \@ref(proofomegaalgo) but the following theorem provides the simplified steps in the algorithm.
@@
 
-Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$.
+Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$ and $S$ as the sample covariance matrix.
 Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}$, and $\rho$.
@@
 
-Another popular, alternative form of the ADMM algorithm can be used when scaling the dual variable ($\Lambda^{k}$). We derive this scaled-form in the context of precision matrix estimation here.
+Another popular, alternative form of the ADMM algorithm can be used when scaling the dual variable ($\Lambda^{k}$) which we will briefly mention in the context of precision matrix estimation here.
 
@@
 
-Therefore, a scaled-form can now be written as
+Therefore, a scaled-form ADMM algorithm can now be written as
 
@@
 \begin{split}
-  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{R}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
   Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
@@
 
-As a proof-of-concept that the elastic-net penalty in the context of precision matrix estimation can provide useful results and that the ADMM algorithm used in this process works, the section offers a short simulation.
+As a proof-of-concept that the elastic-net penalty in the context of precision matrix estimation can provide useful results and that the ADMM algorithm used in this process works, this section offers a short simulation.
 For the simulation, we generated data from multiple, unique precision matrices with various oracle structures.
-For each data-generating procedure, the algorithm was run with a 5-fold cross validation.
+For each data-generating procedure, the algorithm was run with a 5-fold cross validation to tune parameters $\lambda$ and $\alpha$.
 After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results are in the top half of the figures).
@@
 
-The second figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a *dense* oracle precision matrix.
+The second figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a *dense* oracle precision matrix (non-sparse).
 Here, we randomly generated an orthogonal basis, set all eigen values equal to 1000, and then combined the matrices using QR decomposition.

### 2019-04-20 03-SCPME.Rmd
completed SCPME final

@@
 This concept, inspired by others like @cai2011direct, @fan2012road, and @mai2012direct, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector.
-
 The example they offer in @molstad2017shrinking is in the context of Fisher's linear discriminant analysis model.
@@
 for each $j = 1, ..., J$.
-We can see from this formulation that clearly an estimation of both $\mu$ and $\Omega$ are required for this model.
+One can see from this formulation that clearly an estimation of both $\mu$ and $\Omega$ are required for this model.
 However, they note that if prediction is the primary concern, then for a given observation $X_{i}$ only the *characteristic* $\Omega\left(\mu_{l} - \mu_{m}\right)$ is needed to discern between response categories $l$ and $m$.
@@
 A similar estimator was proposed by @dalal2017sparse when $C = 0$ but here we do not require it.
-This form of penalty is particularly useful because it's extremely general.
+This form of penalty is particularly useful because it is extremely general.
 Note that by letting matrices $A = I_{p}, B = I_{p}, \mbox{ and } C = 0$, this penalty reduces to a lasso penalty - but clearly this form allows for much more creative penalties and $A, B, \mbox{ and } C$ can be constructed so that we penalize the sum, absolute value of *many* characteristics of the precision matrix $\Omega$.
-We will explore how to solve for $\hat{\Omega}$ in the next section.
+We will explore how to solve for $\hat{\Omega}$ in \@ref(eq:omegaloglik2) in the next section.
 
@@
 
-Solving for $\hat{\Omega}$ in \@ref(eq:omegaloglik2) uses what we are going to call an *augmented ADMM* algorithm.
-Molstad and Rothman do not offer a name for this specific algorithm but it leverages the majorize-minimize principle in one of the steps in the algorithm - augmenting the ADMM algorithm discussed in the previous chapter.
-Within the context of the proposed penalty, the traditional ADMM algorithm for precision matrix estimation would consist of iterating over the following three steps:
+Solving for $\hat{\Omega}$ in \@ref(eq:omegaloglik2) uses what we are going to call an *augmented ADMM algorithm*.
+Molstad and Rothman do not offer a name for this specific algorithm but it leverages the majorize-minimize principle in one of the steps in the algorithm - augmenting the original ADMM algorithm discussed in the previous chapter.
+Within the context of the proposed penalty, the original ADMM algorithm for precision matrix estimation would consist of iterating over the following three steps:
 
@@
 
-where $L$, the *augmented lagrangian*, is defined as
+where $L$, the augmented lagrangian, is defined as
 
@@
 Similar to the previous chapter, $f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|$ and $g\left(Z\right) = \lambda\left\|Z\right\|_{1}$.
-In fact, the details of the algorithm thus far are identical to the previous approach except that we are replacing $\Omega - Z$ with $A\Omega B - C - Z$ (or equivalently, $A\Omega B - Z - C$) in the augmented lagrangian and the dual update $\Lambda^{k + 1}$.
+In fact, the details of the algorithm thus far are identical to the previous approach except that we are replacing $\Omega - Z$ with $A\Omega B - Z - C$ in the augmented lagrangian and the dual update $\Lambda^{k + 1}$.
 
-Instead of solving the first step exactly as we did in the previous section, the authors propose an alternative, approximating objective function, which we will denote as $\tilde{L}$, that is based on the majorize-minimize principle^[Further explanation of the majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
+Instead of solving the first step directly, the authors propose an alternative, approximating objective function, which we will denote as $\tilde{L}$, that is based on the majorize-minimize principle^[Further explanation of the majorizing function \@ref(eq:approx) in section \@ref(taylorsexp)].
 The purpose of this approximating function is the desire to solve the first step of the algorithm in closed-form.
@@
 \begin{split}
-  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
+  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
   &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
@@
 
-where $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}$.
+where $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$.
 Each step in this algorithm can now conveniently be solved in closed-form and the full details of each can be found in the appendix \@ref(proofOmegak).
@@
 
-Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$. Set $k = 0$ and repeat steps 1-6 until convergence.
+Define the soft-thresholding function as $\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}$ and $S$ as the sample covariance matrix.
+Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}, \Omega^{0}$, and $\rho$ and repeat steps 1-5 until convergence.
 
@@
 \begin{equation}
-G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}Y^{k} \right)B^{T}
+G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}
 (\#eq:Gk)\notag
@@
 
-4. Update $Z^{k + 1}$.^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)]
+4. Update $Z^{k + 1}$ with element-wise soft-thresholding for the resulting matrix.^[Proof of \@ref(eq:Zk) in section \@ref(proofZk)]
 
 \begin{equation}
-Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}Y^{k}, \rho^{-1}\lambda \right)
+Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda^{k}, \rho^{-1}\lambda \right)
 (\#eq:Zk)
@@
 
-5. Update $Y^{k + 1}$.
+5. Update $\Lambda^{k + 1}$.
 
 \begin{equation}
-Y^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
 (\#eq:Yk)\notag
 \end{equation}
-
-6. Replace $k$ with $k + 1$.
 
@@
 
-A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous chapter \@ref(ADMMstop).
+A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous chapter in section \@ref(ADMMstop).
 The primal optimality condition here is that $A\Omega^{k + 1}B - Z^{k + 1} - C = 0$ and the two dual optimality conditions are $0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
@@
 Utilizing the fact that the population regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$ for predictors, $X$, and the responses, $Y$, they point out that their framework could allow for the simultaneous estimation of $\beta$ and $\Omega_{x}$.
-Like @witten2009covariance, this approach would estimate the forward regression coefficient matrix while using shrinkage estimators of the marginal precision matrix for the predictors.
+Like @witten2009covariance, this approach would estimate the forward regression coefficient matrix while using shrinkage estimators for the marginal population precision matrix for the predictors.
 For example, recall that the general optimization problem outlined in the SCPME framework is to estimate $\hat{\Omega}$ such that
@@
 
-Specifically, this optimization problem has the effect of deriving an estimate of $\Omega_{x} \mbox { and } \beta$ while assuming sparsity in the forward regression coefficient $\beta$.
-Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ and then use our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
-Estimators such as this are truly novel an can conveniently be estimated by the SCPME framework.
-Another such estimator that is a product of this framework is one where we leave $A \mbox{ and } C$ unchanged but take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the sample cross-covariance matrix of $X$ and $Y$.
+Specifically, this optimization problem has the effect of deriving an estimate of $\Omega_{x}$ while assuming sparsity in the forward regression coefficient $\beta$.
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ in place of $\Sigma_{xy}$.
+We could then use our estimator, $\hat{\Omega}_{x}$, to construct the estimated forward regression coefficient matrix $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+Estimators such as these are truly novel an can conveniently be estimated by the SCPME framework.
+Another such estimator that is a product of this new framework is one where we construct $A \mbox{ and } C$ similarly but take $B = \left[ \Sigma_{xy}, I_{p} \right]$ so that the identity matrix is appended to the cross-covariance matrix of $X$ and $Y$.
 In this case, not only are we assuming that $\beta$ is sparse, but we are also assuming sparsity in $\Omega$.
@@
 
-Like before, we would take our estimator, $\hat{\Omega}_{x}$, to construct the forward regression coefficient matrix estimator $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
-The embedded assumptions here are that not all predictors are useful in predicting the response, $Y$, *and* a number of the predictors are conditionally independent of one another - assumptions that would be quite reasonable in practice.
-
-In the next section we offer a short simulation comparing these estimators to related and competing prediction methods.
+Like before, we could use $\hat{\Sigma}_{xy}$ as a replacement and take our resulting estimator, $\hat{\Omega}_{x}$, to construct the estimated forward regression coefficient matrix $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+The embedded assumptions here are that not all predictors in $X$ are useful in predicting the response, $Y$, *and* that a number of the predictors are conditionally independent of one another.
+These are assumptions that are quite reasonable in practice and in the next section we offer a short simulation comparing these new estimators to related and competing prediction methods.
 
@@
 
-In this simulation, we compare the performance of several competing regression prediction methods under various data realizations, including the so-called SCPME regression estimators discussed in the previous section.
-In total, we consider the following estimators:
+In this simulation, we compare, under various data realizations, the performance of several competing regression prediction methods including the new so-called SCPME regression estimators discussed in the previous section.
+In total, we consider the following:
 
- - `OLS` = ordinary least squares estimatior. In high dimensional settings ($p >> n$), the Moore-Penrose estimator is used.
+ - `OLS` = ordinary least squares estimatior. In high dimensional settings ($p >> n$), the Moore-Penrose estimator is used as a replacement.
 
@@
 
- - `oracleS` = regression estimator with oracle $\Sigma_{xy}^{*}$ (let $\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$).
+ - `oracleS` = regression estimator with oracle $\Sigma_{xy}^{*}$ (let $\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$) and $\Omega_{x}$ is estimated using an elastic-net penalty.
 
@@
 
- - `shrinkBO` = SCPME regression estimator with penalty $\lambda\left\| \Omega_{x}[\Sigma_{xy}, I_{p}] \right\|_{1}$ so that $\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
+ - `shrinkBO` = SCPME regression estimator with penalty $\lambda\left\| \Omega_{x}[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}$ so that $\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
 
@@
 
-For each estimator, if selection of a tuning parameter is required, then the tuning parameter was chosen so that the mean squared prediction error (MSPE) was minimized over 3-fold cross validation.
+For each estimator, if selection of a tuning parameter is required, the tuning parameter was chosen so that the mean squared prediction error (MSPE) was minimized over 3-fold cross validation.
 
-The data generating procedures for the simulations are as follows.
+The data generating procedure for the simulations is the following.
 The oracle regression coefficient matrix $\beta^{*}$ was constructed so that $\beta^{*} = \mathbb{B} \circ \mathbb{V}$ where $vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)$ and $\mathbb{V} \in \mathbb{R}^{p \times r}$ is a matrix containing $p$ times $r$ random bernoulli draws with 50\% probability being equal to one.
@@
 This ensures that their corresponding precision matrices will be tridiagonal and sparse.
-Then for 100 independent, identically distributed samples, we had $X_{i} \sim N_{p}\left( 0, \Sigma_{xx} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$ so that $\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}$ where $\mathbb{X} \in \mathbb{R}^{n \times p}$, $\mathbb{Y} \in \mathbb{R}^{n \times r}$ and the script notation denotes the fact that the columns have been centered so as to remove the intercept in our prediction models.
-An additional 1000 samples were generated similarly for the testing set and each prediction method was evaluated on both model error and mean squared prediction error.
+Then for 100 independent, identically distributed samples, we had $X_{i} \sim N_{p}\left( 0, \Sigma_{x} \right)$ and $E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)$ so that $\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}$ where $\mathbb{X} \in \mathbb{R}^{n \times p}$ and $\mathbb{Y} \in \mathbb{R}^{n \times r}$ are the matrices with stacked rows $X_{i}$ and $E_{i}$, respectively, for $i = 1, ..., n$ and the script notation denotes the fact that the columns have been centered so as to remove the intercept in our prediction models.
+A sample of an additional 1000 observations was generated similarly for the testing set.
+Each prediction method was evaluated on both model error and mean squared prediction error.
 
@@
 Note `OLS` and `oracleS` are not shown due to extremely poor performance.
-We find that in high dimensional settings, `shrinkBO` and `shrinkB` perform increasingly well relative to the others as the predictor dimension increases with `shrinkBO` performing the best.
-Interestingly, when $n > p$ is still one of the best-performing estimators - though worse than both `lasso` and `ridge` - but the performance of `shrinkB` decreases drastically (plot not shown).
+We find that in high dimensional settings, `shrinkBO` and `shrinkB` perform increasingly well relative to the others as the predictor dimension increases.
+`shrinkBO` performed the best.
+Interestingly, when $n > p$ `shrinkBO` is still one of the best-performing estimators - though worse than both `lasso` and `ridge` - but the performance of `shrinkB` decreases drastically (plot not shown).
 
-In the high dimension setting, the oracle estimators `oracleO` (penalty: $\lambda\left\| \Omega^{*}\hat{\Sigma}_{xy} \right\|_{1}$) and `oracleS` (penalty: $\lambda\left\| \hat{\Omega}\Sigma_{xy}^{*} \right\|_{1}$) performed worse or comparable to OLS.
-The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega$ is not identifiable when $p > n$.
+In the high dimension setting, the oracle estimators `oracleO` and `oracleS` performed worse or comparable to the `OLS` estimator.
+The poor performance of `oracleS` is likely due to the fact that the sample estimate of $\Omega_{x}$ is not identifiable when $p > n$.
 
-The table below shows the average model error for each estimator when $n = 100$, $p = 150$, and $r = 10$.
+The following table shows the average model error for each estimator when $n = 100$, $p = 150$, and $r = 10$.
 
@@
 \vspace{0.5cm}
-```{r scpmesim2, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag).
-The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
-The model errors (ME) for each estimator are plotted.
+```{r scpmesim2, eval = T, echo = F, fig.cap = "The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
+The model errors (ME) for each estimator with variable dimension of the design matrix are plotted.
 shrinkBO and shrinkB were the two best-performing estimators closely follow by the ridge and lasso regression estimators."}
@@
 
-This final simulation was run and explored due to the fact each of the SCPME regression estimators require an estimation of the cross-covariance matrix.
-In the previous simulations, we used the maximum likelihood estimator.
-However, because the data-generating procedures construct settings that are inherently sparse, we were interested to determine if additional shrinkage of the *cross-covariance* matrix would also prove beneficial.
-For instance, in a number of settings, we were finding that the estimator `oracleO` ($\beta = \Omega_{x}^{*}\hat{\Sigma}_{xy}$) was performing worse than `oracleS` ($\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}$) which perhaps suggests that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
+This final simulation was explored due to the fact that each of the SCPME regression estimators require an estimation of the cross-covariance matrix.
+In the previous simulations, we naively used the maximum likelihood estimate.
+However, because the data-generating procedure constructs settings that are inherently sparse, we were interested to determine if additional shrinkage of the maximum likelihood estimate for the *cross-covariance* matrix would also prove beneficial.
+For instance, in a number of settings, we were finding that the estimator `oracleO` was performing worse than `oracleS`.
+This perhaps suggests that estimating the covariance matrix $\Sigma_{xy}$ well is *more* important than estimating $\Omega$ well.
 This simulation explores that theory a bit further.
 
-The data-generating procedure for this simulation is similar to previous one but here we take $n = 100$, $p = 200$, $r = 10$, *and* we additionally multiple the cross-covariance sample estimator by a factor of $k$ where $k \in (0.1, 0.2, ..., 0.9, 1)$.
+The data-generating procedure for this simulation is similar to previous one but here we take $n = 100$, $p = 200$, $r = 10$, and, in addition, we multiply the population cross-covariance estimator by a factor of $k$ where $k \in (0.1, 0.2, ..., 0.9, 1)$.
 Figure \@ref(fig:scpmesim7) plots the MSPE for `shrinkB` for each tuning parameter, $\lambda$, and constant, $k$, pair.
@@
 
+\vspace{0.5cm}
 ```{r, eval = T, echo = F}

### 2019-04-20 05-appendix.Rmd
complete appendix near final

@@
 
-@witten2009covariance and @price2015ridge showed that the following optimization problem can be solved in closed-form. We outline their steps below.
+@witten2009covariance and @price2015ridge showed that the following optimization problem can be solved in closed-form. We outline their steps here.
 
@@
 \begin{split}
-  \hat{Omega}^{k + 1} &:= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  \hat{\Omega}^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
@@
 \begin{equation}
-Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} - Sign(Z_{ij}^{k + 1})\lambda \right)
+Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} - Sign\left(Z_{ij}^{k + 1}\right)\lambda \right)
 (\#eq:ZZsoftproof2)\notag
@@
 
-This implies that $\mbox{sign}(Z_{ij}^{k + 1}) = \mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at
+This implies that $\mbox{sign}\left(Z_{ij}^{k + 1}\right) = \mbox{sign}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}\right)$. Putting all the pieces together, we arrive at
 
@@
 \begin{split}
-Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}\right)\left( \left| \rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
-&= \frac{1}{\rho}\mbox{soft}\left(\rho(A\Omega_{ij}^{k + 1}B - C) + \Lambda_{ij}^{k}, \lambda\right)
+Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}\right)\left( \left| \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
+&= \frac{1}{\rho}\mbox{soft}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}, \lambda\right)
 (\#eq:appendixZZproof2)\notag

### 2019-04-20 03-SCPME.Rmd
completed appendix final

@@
 \begin{equation}
-L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda^{T}\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda '\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
 (\#eq:auglagrange3)
@@
 \begin{split}
-  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)^{T}Q\left(\Omega - \Omega^{k}\right)
+  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
 (\#eq:approx)
@@
 
-where $Q = \tau I_{p} - \left(A^{T}A \otimes BB^{T}\right)$ and $\tau$ is chosen such that $Q$ is positive definite.
-Note that if $Q$ is positive definite, then $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[If $Q$ is positive definite, then $vec\left(\Omega - \Omega^{k} \right)^{T}\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0$ since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.].
+where $Q = \tau I_{p} - \left(A'A \otimes BB'\right)$ and $\tau$ is chosen such that $Q$ is positive definite.
+Note that if $Q$ is positive definite, then $L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)$ for all $\Omega$ and $\tilde{L}$ is a majorizing function^[If $Q$ is positive definite, then $vec\left(\Omega - \Omega^{k} \right)'\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0$ since $\rho > 0$ and $vec\left(\Omega - \Omega^{k}\right)$ is always nonzero whenever $\Omega \neq \Omega^{k}$.].
 The *augmented ADMM* algorithm developed by Molstad and Rothman, which now includes the majorize-minimize principle, consists of the following repeated iterations:
@@
   \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
-  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
@@
 
-where $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$.
+where $G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'$.
 Each step in this algorithm can now conveniently be solved in closed-form and the full details of each can be found in the appendix \@ref(proofOmegak).
@@
 \begin{equation}
-G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}
+G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'
 (\#eq:Gk)\notag
@@
 \begin{equation}
-S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}
+S + \left( G^{k} + (G^{k})' \right)/2 - \rho\tau\Omega^{k} = VQV'
 (\#eq:VQV)\notag
@@
 \begin{equation}
-\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)
+\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V' /(2\rho\tau)
 (\#eq:Omegak)
@@
 A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous chapter in section \@ref(ADMMstop).
-The primal optimality condition here is that $A\Omega^{k + 1}B - Z^{k + 1} - C = 0$ and the two dual optimality conditions are $0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
+The primal optimality condition here is that $A\Omega^{k + 1}B - Z^{k + 1} - C = 0$ and the two dual optimality conditions are $0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2$ and $0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}$.
 Similarly, we will define the left-hand side of the primal optimality condition as the primal residual $r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C$ and the dual residual^[Proof of \@ref(eq:stopproof) in section \@ref(proofstopproof).] as
@@
 \begin{equation}
-s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)
+s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)
 (\#eq:stopproof)\notag
@@
   \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
-  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 \right\|_{F}
+  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
 (\#eq:scpmestopping)\notag
@@
 Specifically, this optimization problem has the effect of deriving an estimate of $\Omega_{x}$ while assuming sparsity in the forward regression coefficient $\beta$.
-Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$ in place of $\Sigma_{xy}$.
+Of course, in practice we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)'/n$ in place of $\Sigma_{xy}$.
 We could then use our estimator, $\hat{\Omega}_{x}$, to construct the estimated forward regression coefficient matrix $\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}$.
@@
 
-The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
+Apart from the two SCPME estimators discussed in the previous section, the generality of the SCPME framework allows for many previously unknown precision matrix estimators to be explored.
+One estimator that was concieved of in our work but deserves further attention in future research is of the form
 
 \begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr(S_{x}\Omega_{x}) - \log\left| \Omega_{x} \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega_{x} \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
 (\#eq:penregression)\notag
@@
 
-To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:
+Note that here we are using the Frobenius norm instead of the matrix $l_{1}$-norm in the SCPME framework but this requires only a slight modification of the augmented ADMM algorithm - which will be presented later.
+As before, the script notation denotes matrices that are column-centered.
+This optimization problem and objective function estimates a precision matrix that balances minimizing the gaussian negative log-likelihood for $\Omega_{x}$ with minimizing the MSPE for the forward regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$.
+In other words, this estimator estimates a precision matrix using the likelihood function but that does not otherwise hinder predictive performance of the forward regression model.
+
+This estimator also reveals an interesting connection to the joint log-likelihood of $X \in \mathbb{R}^{p}$ and $Y \in \mathbb{R}^{r}$ (assuming $X$ is now random).
+To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship.
 
 \begin{equation}
-Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-(\#eq:linregression)\notag
+Y_{i} = \mu_{y} + \beta'\left(X_{i} - \mu_{x}\right) + E_{i}
 \end{equation}
 
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form
+where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega_{x}^{-1} \right)$.
+This implies that the conditional distribution of $Y_{i}|X_{i}$ is of the form
 
 \begin{equation}
-Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
-(\#eq:linnormal)\notag
+Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta'\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
 \end{equation}
 
-We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$.
-Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience.
-We will also let $f$ denote the probability distribution function for each respective variable.
+We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint log-likelihood of $X$ and $Y$.
+Without loss of generality, we will assume that $\mu_{x} = \mu_{y} = 0$.
+This can similarly achieved by simply centering the data by the sample averages.
 
-(Talk about regression estimator minimizing frobenius norm of predictions)
+\begin{equation}
+\begin{split}
+  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
+  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
+  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
+  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
+(\#eq:partialjointloglik)\notag
+\end{split}
+\end{equation}
 
-(REMEMBER INFORMATION IN APPENDIX)
+Note that $\beta \equiv \Omega\Sigma_{xy}$ and $S_{x}$ still denotes the marginal sample covariance matrix of random variable $X$.
+Now suppose we are interested in optimizing this gaussian log-likelihood function with respect to $\Omega$:
+
+\begin{equation}
+\begin{split}
+  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
+  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
+(\#eq:omegajointloglik)\notag
+\end{split}
+\end{equation}
+
+If we assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$, then we have that
+
+\begin{equation}
+\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+(\#eq:omegajointmle)\notag
+\end{equation}
+
+There are a few takeaways we can make after revealing this connection.
+The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$.
+
+Note that the only difference is in step 4.
+
+```{theorem, name = "Modified Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators with Frobenius Norm"}
+
+Set $k = 0$ and initialize $Z^{0}, \Lambda^{0}, \Omega^{0}$, and $\rho$ and repeat steps 1-5 until convergence.
+
+1. Compute $G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'$
+
+2. Decompose $S + \left( G^{k} + (G^{k})' \right)/2 - \rho\tau\Omega^{k} = VQV'$ (via the spectral decomposition).
+
+3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V'/(2\rho\tau)$
+
+4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$
+
+5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
+
+```
+
+Note that no closed-form solution to this estimator exists and so we must resort to some iterative algorithm similar to the SCPME augmented ADMM algorithm in order to solve it^[Proof in section \@ref(proofpenregression).].

### 2019-04-20 05-appendix.Rmd
completed appendix final

@@
 Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
-Next set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV^{T}$ using spectral decomposition so that $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns so that
+Next set the gradient equal to zero and decompose $\Omega^{k + 1} = VDV'$ using spectral decomposition so that $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns so that
 
 \begin{equation}
-S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T}\notag
+S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V' - \rho VDV' =  V\left(D^{-1} - \rho D\right)V'\notag
 \end{equation}
@@
 
-In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV^{T}$ then
+In summary, if we decompose $S + \Lambda^{k} - \rho Z^{k} = VQV'$ then
 
 \begin{equation}
-\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V'
 (\#eq:appendixomegaproof)
@@
   \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
-  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
-  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
 (\#eq:taylors)\notag
@@
 \begin{equation}
-  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB^{T}\Omega A^{T}A - \rho BZ^{T}A - \rho BC^{T}A
+  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB'\Omega A'A - \rho BZ'A - \rho BC'A
 (\#eq:gradient)\notag
@@
 \begin{equation}
-\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A^{T}A \otimes BB^{T} \right)
+\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A'A \otimes BB' \right)
 (\#eq:hessian)\notag
@@
 \begin{split}
-  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
-  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)^{T}Q\left(\Omega - \Omega^{k} \right) \\
-  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)^{T}\left(A^{T}A \otimes BB^{T}\right)vec\left(\Omega - \Omega^{k}\right) \\
-  &+ \rho vec\left(\Omega - \Omega^{k}\right)^{T}vec\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right) \\
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)'Q\left(\Omega - \Omega^{k} \right) \\
+  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)'Q\left(\Omega - \Omega^{k} \right) \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)' vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right) \\
   &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
-  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right]
+  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right]
 (\#eq:penapprox)\notag
@@
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
-  &+ \left.\begin{matrix} vec\left(\Omega - \Omega^{k}\right)^{T}\rho Q\left(\Omega - \Omega^{k}\right)/2 \end{matrix}\right\} \\
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} vec\left(\Omega - \Omega^{k}\right)'\rho Q\left(\Omega - \Omega^{k}\right)/2 \end{matrix}\right\} \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})^{T}(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
-  &+ \left.\begin{matrix} \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 + tr\left[\rho\left(\Omega - \Omega^{k}\right)\left(BB^{T}\Omega^{k}A^{T}A - B(Z^{k})^{T}A - BC^{T}A \right)\right] \end{matrix}\right\} \\
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 + tr\left[\rho\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right] \end{matrix}\right\} \\
   &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
- tr\left[\left(S + \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T} \right)\Omega\right] \end{matrix}\right. \\
+ tr\left[\left(S + \rho A'(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B' \right)\Omega\right] \end{matrix}\right. \\
   &- \left.\begin{matrix} \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \end{matrix}\right\} \\
@@
 
-where $G^{k} = \rho A^{T}(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B^{T}$.
+where $G^{k} = \rho A'(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B'$.
 
@@
   &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
-  &= 2S - S\circ I_{p} + G^{k} + (G^{k})^{T} - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
-  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})^{T} + 2\Omega^{T} - 2\Omega^{k} - 2(\Omega - \Omega^{k})^{T}\circ I_{p} \right]
+  &= 2S - S\circ I_{p} + G^{k} + (G^{k})' - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
+  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
 (\#eq:appendixomegagradient2)\notag
@@
 \begin{equation}
-S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
+S + \frac{1}{2}\left(G^{k} + (G^{k})'\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
 \end{equation}
 
-We can then decompose using spectral decomposition $\Omega^{k + 1} = VDV^{T}$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
+We can then decompose using spectral decomposition $\Omega^{k + 1} = VDV'$ where $D$ is a diagonal matrix with diagonal elements equal to the eigen values of $\Omega^{k + 1}$ and $V$ is the matrix with corresponding eigen vectors as columns.
 
 \begin{equation}
-S + \frac{1}{2}\left(G^{k} + (G^{k})^{T}\right) - \rho\tau\Omega^{k} = VD^{-1}V^{T} - \rho\tau VDV^{T} = V\left(D^{-1} - \rho\tau D\right)V^{T} \notag
+S + \frac{1}{2}\left(G^{k} + (G^{k})'\right) - \rho\tau\Omega^{k} = VD^{-1}V' - \rho\tau VDV' = V\left(D^{-1} - \rho\tau D\right)V' \notag
 \end{equation}
@@
 
-where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k}$. Therefore
+where $\phi_{j}(\cdot)$ is the $j$th eigen value and $D^{k} = S + \left(G^{k} + (G^{k})'\right)/2 - \rho\tau\Omega^{k}$. Therefore
 
@@
 
-In summary, if we decompose $S + \left(G^{k} + (G^{k})^{T}\right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ then
+In summary, if we decompose $S + \left(G^{k} + (G^{k})'\right)/2 - \rho\tau\Omega^{k} = VQV'$ then
 
 \begin{equation}
-\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V^{T}
+\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V'
 (\#eq:appendixomegaproof2)\notag
@@
 \begin{equation}
-Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
+Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
 (\#eq:appendixZZloglik2)\notag
@@
 \begin{split}
-  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})^{T}\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
   &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
@@
 
-Here we want to show that $0 \in \rho\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2$ which is a direct result of the fact that $0 \in \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2$.
+Here we want to show that $0 \in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2$ which is a direct result of the fact that $0 \in \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2$.
 
@@
   0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2}/2 \right\} \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 + \rho\left( BB^{T}\Omega^{k + 1}A^{T}A + A^{T}A\Omega^{k + 1}BB^{T} \right)/2 \\
-  &- \rho\left( A^{T}(Z^{k} + C)B^{T} + B(Z^{k} + C)^{T}A \right)/2 \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 \\
-  &+ \rho\left( B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k})^{T} - C^{T})A + A^{T}(A\Omega^{k + 1}B - Z^{k} - C)B^{T} \right)/2 \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \left( B(\Lambda^{k})^{T}A + A^{T}\Lambda^{k}B^{T} \right)/2 + \rho\left(A^{T}(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B^{T} \right)/2 \\
-  &+ \rho\left(B(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} + (Z^{k + 1})^{T} - (Z^{k})^{T} - C^{T})A \right)/2 \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \left[ B\left((\Lambda^{k})^{T} + \rho(B^{T}\Omega^{k + 1}A^{T} - (Z^{k + 1})^{T} - C^{T}) \right)A \right]/2 \\
-  &+ \left[ A^{T}\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B^{T} \right]/2 + \rho\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2 \\
-  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})^{T}A + A^{T}\Lambda^{k + 1}B^{T} \right)/2 + \rho\left(B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2 \\
-  \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})^{T}A + A^{T}(Z^{k + 1} - Z^{k})B^{T} \right)/2
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 + \rho\left( BB'\Omega^{k + 1}A'A + A'A\Omega^{k + 1}BB' \right)/2 \\
+  &- \rho\left( A'(Z^{k} + C)B' + B(Z^{k} + C)'A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 \\
+  &+ \rho\left( B(B'\Omega^{k + 1}A' - (Z^{k})' - C')A + A'(A\Omega^{k + 1}B - Z^{k} - C)B' \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left( B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 + \rho\left(A'(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B' \right)/2 \\
+  &+ \rho\left(B(B'\Omega^{k + 1}A' - (Z^{k + 1})' + (Z^{k + 1})' - (Z^{k})' - C')A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left[ B\left((\Lambda^{k})' + \rho(B'\Omega^{k + 1}A' - (Z^{k + 1})' - C') \right)A \right]/2 \\
+  &+ \left[ A'\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B' \right]/2 + \rho\left(B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 + \rho\left(B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2 \\
+  \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2
 (\#eq:appendixstopproof)\notag
@@
 
-### Connection to joint log-likelihood
+### Proof of no closed-form solution {#proofpenregression}
 
-The last estimator in the previous section reveals an interesting connection to the joint log-likelihood of $X$ and $Y$ (under a few assumptions) when we consider its analogous *ridge* version - the *ridge SCPME estimator*:
+Here we want to show that the following optimization problem cannot be solved in closed-form.
 
 \begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
+(\#eq:penregression2)\notag
 \end{equation}
 
-To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship of the following form:
-
-\begin{equation}
-Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-\end{equation}
-
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-These two assumptions imply that the conditional distribution of $Y_{i}|X_{i}$ is of the form
-
-\begin{equation}
-Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
-\end{equation}
-
-We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint likelihood of $X$ and $Y$.
-Similar to before, we will take $\Omega_{y | x} \equiv \Sigma_{y | x}^{-1}, \Omega \equiv \Sigma_{xx}^{-1}, \mbox{ and } \beta \equiv \Omega\Sigma_{xy}$ for convenience.
-We will also let $f$ denote the probability distribution function for each respective variable.
+First start by taking the gradient with respect to $\Omega$:
 
@@
 \begin{split}
-  L&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) \propto f\left(Y | X; \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta \right) \times f\left(X; \Omega, \mu_{x} \right) \\
-  &= \prod_{i = 1}^{n} (2\pi)^{-r/2}\left| \Omega_{y | x} \right|^{1/2} \exp\left[ -\frac{1}{2}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right) \right] \\
-  &\times (2\pi)^{-p/2}\left| \Omega \right|^{1/2} \exp\left[ -\frac{1}{2}\left( X_{i} - \mu_{x} \right)^{T}\Omega\left( X_{i} - \mu_{x} \right) \right] \\
-  &\propto \left| \Omega_{y | x} \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right] \\
-  &\times \left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right]
-(\#eq:jointlik)\notag
-\end{split}
-\end{equation}
-
-where $\mbox{etr}\left( \cdot \right)$ denotes the exponential trace operator. This implies that the joint log-likelihood is of the following form:
-
-\begin{equation}
-\begin{split}
-  l&\left( \Omega_{y | x}, \Omega, \mu_{x}, \mu_{y}, \beta | Y, X \right) = const.
-+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left[ \left( X_{i} - \mu_{x} \right)\left( X_{i} - \mu_{x} \right)^{T}\Omega \right] \\
-  &+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)\left( Y_{i} - \mu_{y} - \beta^{T}\left(X_{i} - \mu_{x}\right) \right)^{T}\Omega_{y | x} \right]
-(\#eq:jointloglik)\notag
-\end{split}
-\end{equation}
-
-**Note:** this form simplifies significantly if we solve for $\mu_{x}$ and $\mu_{y}$ and make a few additional assumptions about our data.
-
-\begin{equation}
-\begin{split}
- \nabla_{\mu_{y}}l\left\{\cdot\right\} &= \nabla_{\mu_{y}}\left\{ -\frac{1}{2}tr\left[ -n\mu_{y}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)^{T}\Omega_{y | x} - n\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x})\right)\mu_{y}^{T}\Omega_{y | x} + n\mu_{y}\mu_{y}^{T}\Omega_{y | x} \right] \right\} \\
- &= -\frac{1}{2}\left[ -n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) - n\Omega_{y | x}\left(\bar{Y} - \beta^{T}(\bar{X} - \mu_{x}) \right) + 2n\Omega_{y | x}\mu_{y} \right] \\
- \Rightarrow \hat{\mu}_{y} &= \bar{Y} - \hat{\beta}^{T}\left(\bar{X} - \hat{\mu_{x}}\right)
- (\#eq:gradient2)\notag
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-  \nabla_{\mu_{x}}l\left\{\cdot\right\} &= \nabla_{\mu_{x}}\left\{ -\frac{1}{2}tr\left[n\beta^{T}\mu_{x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)^{T}\Omega_{y | x} + n\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right)\mu_{x}^{T}\beta\Omega_{y | x} + \beta^{T}\mu_{x}\mu_{x}^{T}\beta\Omega_{y | x} \right] \right\} \\
- &-\nabla_{\mu_{x}}\left\{\frac{1}{2}tr\left[ -n\mu_{x}\bar{X}^{T}\Omega - n\bar{X}\mu_{x}^{T}\Omega + n\mu_{x}\mu_{x}^{T}\Omega \right] \right\} \\
- &= -\frac{1}{2}\left[n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + n\beta\Omega_{y | x}\left(\bar{Y} - \mu_{y} - \beta^{T}\bar{X} \right) + 2\beta\Omega_{y | x}\beta^{T}\mu_{x} \right] \\
- &-\frac{1}{2}\left( -n\Omega\bar{X} - n\Omega\bar{X} + 2n\Omega\mu_{x} \right) \\
- \Rightarrow 0 &= -n\hat{\beta}\hat{\Omega}_{y | x}(\bar{Y} - \hat{\mu}_{y} - \hat{\beta}^{T}\bar{X}) - \hat{\beta}\hat{\Omega}_{y | x}\hat{\beta}^{T}\hat{\mu}_{x} + n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
- \Rightarrow 0 &= n\hat{\Omega}\bar{X} - n\hat{\Omega}\hat{\mu}_{x} \\
- \Rightarrow \hat{\mu}_{x} &= \bar{X}
-(\#eq:gradient3)\notag
-\end{split}
-\end{equation}
-
-Therefore, by plugging in $\hat{\mu}_{x}$ into $\hat{\mu}_{y}$, we find that $\hat{\mu}_{y} = \bar{Y}$ and $\hat{\mu}_{x} = \bar{X}$.
-
-Without loss of generality, let us assume that $\bar{X} = \bar{Y} = 0$.
-This can be achieved by simply centering the data by the sample averages.
-Putting all of this together and recalling that $\beta \equiv \Omega\Sigma_{xy}$, we have that the partially maximized joint log-likelihood is the following:
-
-\begin{equation}
-\begin{split}
-  l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)\left( Y_{i} - \Sigma_{xy}^{T}\Omega X_{i} \right)^{T}\Omega_{y | x} \right] \\
-  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}^{T}\Omega \right) \\
-  &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] \\
-  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}tr\left( \mathbb{X}^{T}\mathbb{X}\Omega \right) \\
-  &= const.
-+ \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
-  &+ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
-(\#eq:partialjointloglik)\notag
-\end{split}
-\end{equation}
-
-where $S = \mathbb{X}^{T}\mathbb{X}/n$. Now suppose we are interested in solving for $\Omega$:
-
-\begin{equation}
-\begin{split}
-  \hat{\Omega} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}-l\left( \Omega_{y | x}, \Omega, \Sigma_{xy} | Y, X \right) \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S\Omega \right) - \frac{n}{2}\log\left| \Omega \right| \right\} \\
-  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{1}{n}\left\| \left( \mathbb{Y} - \mathbb{X}\Omega\Sigma_{xy} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
-(\#eq:omegajointloglik)\notag
-\end{split}
-\end{equation}
-
-where $\left\|\cdot\right\|_{F}$ denotes the Frobenius norm.
-Further, let us assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$.
-Therefore, we have that
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S\Omega \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
-(\#eq:omegajointmle)\notag
-\end{equation}
-
-Notice that this is exactly the ridge SCPME estimator!
-
-### Takeaways from connection to joint log-likelihood
-
-We have shown that solving for the ridge SCPME estimator is equivalent to solving for the MLE for $\Omega \equiv \Sigma_{xx}^{-1}$ when the following assumptions hold:
-
-1. Each observation $(Y_{i}, X_{i})$ is independent and linearly distributed such that
-
-\begin{equation}
-Y_{i} = \mu_{y} + \beta^{T}\left(X_{i} - \mu_{x}\right) + E_{i}
-(\#eq:linregression2)\notag
-\end{equation}
-
-where $E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)$ and $X_{i} \sim N_{p}\left( \mu_{x}, \Omega^{-1} \right)$.
-
-2. Given $X$, each of the $r$ responses in $Y \in \mathbb{R}^{r}$ is independent of one another with equal variance such that $\Omega_{y | x}^{-1} \equiv \Sigma_{y | x} = I_{r}/\sigma_{y | x}^{2}$.
-
-3. Let the tuning parameter $\lambda = 2/(n\sigma_{y | x}^{2})$.
-
-In addition, only a very slight modification of the augmented ADMM algorithm in @molstad2017shrinking is required to compute this estimate:
-
-Set $k = 0$ and repeat steps 1-6 until convergence.
-
-1. Compute $G^{k} = \rho A^{T}\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B^{T}$
-
-2. Decompose $S + \left( G^{k} + (G^{k})^{T} \right)/2 - \rho\tau\Omega^{k} = VQV^{T}$ (via the spectral decomposition).
-
-3. Set $\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V^{T}/(2\rho\tau)$
-
-4. Set $Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)$
-
-5. Set $\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)$
-
-6. Replace $k$ with $k + 1$.
-
-Note that the only difference is in step 4.
-
-There are a few takeaways we can make after revealing this connection.
-The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$.
-The second takeaway is that the SCPME algorithmic framework offers a very efficient method of computing this joint likelihood estimator.
-No closed-form solution to this estimator exists (to the best of my knowledge) and so we must resort to some iterative algorithm like the SCPME agumented ADMM algorithm in order to solve it.
-We show this below:
-
-\begin{equation}
-\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
-(\#eq:penregression2)\notag
-\end{equation}
-
-\begin{equation}
-\begin{split}
-  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
-  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y})^{T}(\mathbb{X}\Omega\hat{\Sigma}_{xy} - \mathbb{Y}) \right] \right\} \\
-  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} - 2\Omega\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} \right) \right\} \\
-  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \lambda\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\Omega\mathbb{X}^{T}\mathbb{X} \\
-  &- \lambda\mathbb{X}^{T}\mathbb{X}\Omega\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\circ I_{p} - \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X} - \mathbb{X}^{T}\mathbb{Y}\hat{\Sigma}_{xy} + \hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}\circ I_{P} \\
-  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}^{T}\mathbb{X}\hat{\Omega}\hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T} + \hat{\Sigma}_{xy}\hat{\Sigma}_{xy}^{T}\hat{\Omega}\mathbb{X}^{T}\mathbb{X} \right) - \lambda\hat{\Sigma}_{xy}\mathbb{Y}^{T}\mathbb{X}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[\left(\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right)'\left(\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right) \right] \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}' - 2\Omega\Sigma_{xy}\mathbb{Y}'\mathbb{X} \right) \right\} \\
+  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}' + \lambda\Sigma_{xy}\Sigma_{xy}'\Omega\mathbb{X}'\mathbb{X} \\
+  &- \lambda\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}'\circ I_{p} - \Sigma_{xy}\mathbb{Y}'\mathbb{X} - \mathbb{X}'\mathbb{Y}\Sigma_{xy} + \Sigma_{xy}\mathbb{Y}'\mathbb{X}\circ I_{P} \\
+  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}'\mathbb{X}\hat{\Omega}\Sigma_{xy}\Sigma_{xy}' + \Sigma_{xy}\Sigma_{xy}'\hat{\Omega}\mathbb{X}'\mathbb{X} \right) - \lambda\Sigma_{xy}\mathbb{Y}'\mathbb{X}
 (\#eq:penregressionproof)\notag
@@
 
-by multiplying all of the off-diagonal elements by $1/2$. Note that we cannot isolate $\hat{\Omega}$.
+Note that we cannot isolate $\hat{\Omega}$.

### 2019-04-20 07-SCPME-Package.Rmd
completed appendix final

@@
 
-\[ Y_{i} = \beta^{T}X_{i} + E_{i} \]
+\[ Y_{i} = \beta'X_{i} + E_{i} \]
 
@@
 This objective function estimates an $\Omega$ via the marginal log-likelihood of $X$ under the assumption that the forward regression coefficient $\beta$ is sparse (recall that $\beta \equiv \Omega\Sigma_{xy}$).
-Of course, in practice, we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)^{T}/n$.
+Of course, in practice, we do not know the true covariance matrix $\Sigma_{xy}$ but we might consider using the sample estimate $\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)'/n$.
 

### 2019-04-21 03-SCPME.Rmd
completed manuscript final

@@
 
-Apart from the two SCPME estimators discussed in the previous section, the generality of the SCPME framework allows for many previously unknown precision matrix estimators to be explored.
+Apart from the two SCPME estimators discussed in the previous section, the generality of the SCPME framework allows for many previously unconceptualized precision matrix estimators to be explored.
 One estimator that was concieved of in our work but deserves further attention in future research is of the form
@@
 
-Note that here we are using the Frobenius norm instead of the matrix $l_{1}$-norm in the SCPME framework but this requires only a slight modification of the augmented ADMM algorithm - which will be presented later.
-As before, the script notation denotes matrices that are column-centered.
-This optimization problem and objective function estimates a precision matrix that balances minimizing the gaussian negative log-likelihood for $\Omega_{x}$ with minimizing the MSPE for the forward regression coefficient matrix $\beta \equiv \Omega_{x}\Sigma_{xy}$.
-In other words, this estimator estimates a precision matrix using the likelihood function but that does not otherwise hinder predictive performance of the forward regression model.
+For clarity in regards to the SCPME framework, $A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}$.
+As before, $\mathbb{X}$ is the $n \times p$ matrix with rows $X_{i} \in \mathbb{R}^{p}$ for $i = 1,..., n$ and the script notation denotes that the matrix has been column-centered.
+The matrix $\mathbb{Y}$ is a similar representation for the observed responses $Y_{i} \in \mathbb{R}^{r}$.
+Also note that here we are using the Frobenius norm instead of the matrix $l_{1}$-norm but this replacement requires only a slight modification of the augmented ADMM algorithm for optimization - details of which will be presented later.
 
-This estimator also reveals an interesting connection to the joint log-likelihood of $X \in \mathbb{R}^{p}$ and $Y \in \mathbb{R}^{r}$ (assuming $X$ is now random).
-To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship.
+This optimization problem estimates a precision matrix that balances minimizing the gaussian negative log-likelihood for $\Omega_{x}$ with minimizing the squared prediction error for the forward regression model.
+In other words, the objective function aims to penalize estimates, determined by $\lambda$, that too heavily favor maximizing the marginal likelihood for $X$ over the predictive performance of the conditional model $Y$ given $X$.
+This estimator also reveals an interesting connection to the joint log-likelihood of the two random variables.
+To see this, let us suppose that we have $n$ independent copies of the random pair $(Y_{i}, X_{i})$ and we assume a linear relationship such that
 
@@
 We can use this conditional distribution along with the marginal distribution of $X$ to derive the joint log-likelihood of $X$ and $Y$.
-Without loss of generality, we will assume that $\mu_{x} = \mu_{y} = 0$.
-This can similarly achieved by simply centering the data by the sample averages.
+Recall that $\beta \equiv \Omega_{x}\Sigma_{xy}$ and $S_{x}$ is the marginal sample covariance matrix of $X$.
+Without loss of generality, we will assume here that $\mu_{x} = \mu_{y} = 0$.
 
@@
 
-Note that $\beta \equiv \Omega\Sigma_{xy}$ and $S_{x}$ still denotes the marginal sample covariance matrix of random variable $X$.
-Now suppose we are interested in optimizing this gaussian log-likelihood function with respect to $\Omega$:
+Optimizing this joint log-likelihood with respect to $\Omega_{x}$ reveals strong similiarities to the estimator that was derived from the SCPME framework:
 
@@
 \begin{split}
-  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)^{T}\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
+  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
   &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
@@
 
-If we assume that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = I_{r}/\sigma_{y | x}$ and let $\lambda = 2/(n\sigma_{y | x}^{2})$, then we have that
+If it is the case that, given $X$, each of the $r$ responses are pairwise independent with equal variance so that $\Omega_{y | x}^{1/2} = \sigma_{y | x}I_{r}$ and we let $\lambda = 2\sigma_{y | x}^{2}/n$, then we have that
 
 \begin{equation}
-\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
 (\#eq:omegajointmle)\notag
@@
 
-There are a few takeaways we can make after revealing this connection.
-The first is that the estimator constructed in the previous section is, in fact, solving a very similar problem to that of optimizing the joint likelihood with respect to $\Omega$.
+This is exactly the estimator conceived of previously.
+Of course, throughout this derivation there were several assumptions that were made and in practice we do not know the true values of neither $\Omega_{y | x}$ nor $\Sigma_{xy}$.
+However, we can see that this estimator is solving a very similar problem to that of optimizing the joint log-likelihood with respect to $\Omega_{x}$.
+We think this estimator and related ones deserve attention in future work.
 
-Note that the only difference is in step 4.
+The algorithm for solving this optimization problem is below.
+Note that no closed-form solution exists and so we must resort to some iterative algorithm similar to the SCPME augmented ADMM algorithm^[Proof in section \@ref(proofpenregression).].
+The only difference here is that in step four we no longer require elementwise soft-thresholding.
 
@@
 ```
-
-Note that no closed-form solution to this estimator exists and so we must resort to some iterative algorithm similar to the SCPME augmented ADMM algorithm in order to solve it^[Proof in section \@ref(proofpenregression).].

### 2019-04-21 03-SCPME.Rmd
added libraries

@@
 # load  data
+library(magrittr)
 load("images/sim6.Rdata")
@@
 # shrinkBO MSPE by lam and const (N = 100, P = 200, R = 10, sigma = "tridiag")
+library(dplyr)
+library(ggplot2)
 d = sigma %>% filter(N == 100, P == 200, R == 10, sparse == 0.5, sigma == "tridiag", model == "shrinkBO") %>% group_by(lam, const) %>% summarise(mean = mean(Error)) %>% mutate(augmean = 1/(c(mean)))

### 2019-04-21 index.Rmd
only SCPME sims and discussion left
removed cache altogether
added graphics latex package dependency

@@
 documentclass: report
+header-includes:
+   - \usepackage{graphicx}
 bibliography: [lib.bib, packages.bib]
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, cache = TRUE, tidy = TRUE, out.width = "90%", fig.align = "center", out.extra = "")
+knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, out.width = "85%", fig.align = "center", out.extra = "")
+
+# load packages
+library(magrittr)
+library(dplyr)
+library(ggplot2)
+library(pander)
 

### 2019-04-21 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

--- 2018-06-07 Manuscript.tex
@@
 \usepackage{amsthm}
+\usepackage{fancyhdr} % Required for custom headers
+\usepackage{lastpage} % Required to determine the last page for the footer
+\usepackage{extramarks} % Required for headers and footers
+\usepackage{graphicx}
 \makeatletter
@@
 
-\title{Oral Manuscript}
+\title{Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression}
 \author{Matt Galloway}
-\date{2018-06-07}
+\date{2019-04-21}
 
@@
 \newtheorem{lemma}{Lemma}[chapter]
+\newtheorem{corollary}{Corollary}[chapter]
+\newtheorem{proposition}{Proposition}[chapter]
+\newtheorem{conjecture}{Conjecture}[chapter]
 \theoremstyle{definition}
 \newtheorem{definition}{Definition}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
-\newtheorem{proposition}{Proposition}[chapter]
 \theoremstyle{definition}
@@
 \newtheorem*{solution}{Solution}
+\let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
 \begin{document}
@@
 
-This is the introduction for Matt's oral manuscript. (UPDATED 8)
-
-\hypertarget{tutorial}{%
-\chapter{Tutorial}\label{tutorial}}
-
-\vspace{0.5cm}
+Inferential statistics consists of two primary components: estimation and prediction.
+Estimation refers to the process by which we infer values, properties and behavior about individual parameters in our model.
+Prediction, on the other hand, refers to the process by which we draw inference about an event that has not-yet occurred.
+The latter component is abundant in industry where the demand to predict stock prices, movies individuals prefer, and even to predict new friend connections in a network has sparked huge investments in research and given rise to research groups whose primary goal is pushing the bounds and developing new predictive models.
+
+However, though most attention is directed towards prediction, these two components are not distinct.
+In fact, the success and reliability of many predictive models is contingent upon good, efficient parameter estimation.
+Many of these models require the estimation of a precision matrix - the inverse of the covariance matrix (frequently denoted as \(\Omega\)) - that establishes the interaction and covariance between random variables.
+For this reason, the last decade has seen an ever-expanding community devoted to precision matrix estimation.
+
+Among this community of researchers is Professor Adam Rothman and Aaron Molstad, Ph.D.~whose research will be a focal point of this manuscript.
+The two have published work on indirect multivariate linear regression (\citet{molstad2016indirect}) and classification with matrix-valued predictors (\citet{molstad2018penalized}) but the focus of this manuscript is their 2017 paper titled \emph{Shrinking Characteristics of Precision Matrix Estimators} (\citet{molstad2017shrinking}).
+In it, they outline a framework to estimate \emph{characteristics} of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
+They write in their manuscript that ``to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated\ldots{} In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.'' The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
+
+One of the research directions mentioned in the original paper was the application of their framework to regression.
+Utilizing the fact that the population regression coefficient matrix \(\beta \equiv \Omega_{x}\Sigma_{xy}\) (where \(\Sigma_{xy}\) is the cross-covariance matrix between the predictors, \(X\), and the responses, \(Y\), and \(\Omega_{x}\) is the precision matrix for \(X\)), their framework allows for the simultaneous estimation of \(\beta\) and \(\Omega_{x}\) with an embedded assumption potentially useful for superior prediction performance.
+In close communication and collaboration with Professor Rothman, we wanted to explore this research direction further.
+However, in order to build upon their work and contribute new material, there were a number of concepts that needed to be learned along the way and this document will follow that journey.
+
+We will begin chapter two with a brief introduction to precision matrix estimation and the gaussian log-likelihood function.
+This section will mention popular estimation methods and algorithms but most discussion will be directed towards the ADMM algorithm.
+Discussion of the ADMM algorithm will be useful as we begin detailing the shrinking characteristics of precision matrix estimators framework (which may be referred to as SCPME), the so-called augmented ADMM algorithm, and later the framework's application to regression.
+Lastly, the document will end with two brief tutorials for the R packages \texttt{ADMMsigma} and \texttt{SCPME}.
+These packages were developed by myself to aid in simulation experiments and make it easier to branch into related research directions.
+Both packages have since been published on CRAN.
+
+\hypertarget{notation-and-definitions}{%
+\subsection{Notation and Definitions}\label{notation-and-definitions}}
+
+For strictly positive integers \(n\) and \(p\), we will denote \(\mathbb{R}^{n \times p}\) as the class of real matrices with dimenson \(n \times p\).
+The class of real, symmetric matrices with dimension \(p \times p\) will be denoted as \(\mathbb{S}^{p}\) and \(\mathbb{S}^{p}_{+}\) if we further require the object to be positive definite.
+The sample size and dimension of the predictor vector in a given data set will most often be denoted as \(n\) and \(p\), respectively.
+If the dimension of the response vector exceeds one, we will denote it as \(r\).
+
+Most matrices will take the form of either \(\Sigma\), the population covariance matrix, or \(\Omega\), the population precision matrix.
+Note that the precision matrix is simply the inverse of the covariance matrix (\(\Omega \equiv \Sigma^{-1}\)) and a subscript may be added to each if more than two random variables are considered in a problem (\(\Omega_{x}\)).
+A subscript star may also be added if the object is oracle - or known - a priori (\(\Omega_{*}\)).
+The oracle's estimator that optimizes a pre-specified objective function will be denoted with a hat (\(\hat{\Omega}\)).
+
+There will be significant matrix algebra notation throughout the manuscript.
+The trace operator sums the diagonal elements of a matrix and will take the form \(tr\left(\cdot\right)\) and the \emph{exponential} trace operator will be denoted similarly as \(etr\left(\cdot\right)\).
+The vector operator, \(vec\left(\cdot\right)\), stacks the columns of a matrix into a column vector.
+The determinant of a matrix \(\mathbf{A}\) will be denoted as \(\left|\mathbf{A}\right|\) but may also take the form \(det\left(\mathbf{A}\right)\).
+The kronecker product of two matrices \(\mathbf{A}\) and \(\mathbf{B}\) will be denoted as \(\mathbf{A} \otimes \mathbf{B}\) and the element-wise product will be denoted as \(\mathbf{A} \circ \mathbf{B}\).
+Lastly, the Frobenius norm which sums the square of all entries in a matrix will be denoted as \(\left\|\mathbf{A}\right\|_{F}\) and we will define \(\left\|\mathbf{A}\right\|_{1} := \sum_{i, j}\left|\mathbf{A}_{ij}\right|\) where the \(i\)-\(j\)th element in matrix \(\mathbf{A}\) is typically denoted as \(\left(\mathbf{A}\right)_{ij}\) or simply \(\mathbf{A}_{ij}\).
+
+\hypertarget{precision-matrix-estimation}{%
+\chapter{Precision Matrix Estimation}\label{precision-matrix-estimation}}
+
+\hypertarget{background}{%
+\section{Background}\label{background}}
+
+The foundation of much of the precision matrix estimation literature is the gaussian negative log-likelihood.
+Consider the case where we observe \(n\) independent, identically distributed (iid) copies of the random variable \(X\), where the \(i\)th observation \(X_{i} \in \mathbb{R}^{p}\) is normally distributed with mean, \(\mu\), and variance, \(\Omega^{-1}\).
+That is, \(X_{i}\) follows a \(p\)-dimensional normal distribution which is typically denoted as \(X_{i} \sim N_{p}\left( \mu, \Omega^{-1} \right)\).
+By definition, this multivariate formulation implies the probability distribution function, \(f\), is of the form
+
+\begin{equation} 
+  f\left(X_{i}; \mu, \Omega\right) = (2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] 
+\label{eq:normallikone}\notag
+\end{equation}
+
+Furthermore, because we assume that each observation is independent, the probability distribution function for all \(n\) observations \(X_{1}, ..., X_{n}\) is equal to
+
+\begin{equation} 
+\begin{split}
+  f\left(X_{1}, ..., X_{n}; \mu, \Omega\right) &= \prod_{i = 1}^{n}(2\pi)^{-p/2}\left| \Omega \right|^{1/2}\exp\left[ -\frac{1}{2}\left( X_{i} - \mu \right)'\Omega\left( X_{i} - \mu \right) \right] \\
+  &= (2\pi)^{-np/2}\left| \Omega \right|^{n/2}\mbox{etr}\left[ -\frac{1}{2}\sum_{i = 1}^{n}\left( X_{i} - \mu \right)\left( X_{i} - \mu \right)'\Omega \right]
+\end{split}
+\label{eq:normallik}\notag
+\end{equation}
+
+Therefore, the gaussian log-likelihood, \(l\), for \(\mu\) and \(\Omega\) given \(X = (X_{1}, .., X_{n})\) can be written as
+
+\begin{equation}
+  l(\mu, \Omega | X) = constant + \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \mu \right)\left(X_{i} - \mu \right)'\Omega \right]
+\label{eq:normalloglik}\notag
+\end{equation}
+
+The estimator for \(\mu\) that maximizes the log-likelihood is \(\hat{\mu}^{mle} = \bar{X} \equiv \sum_{i = 1}^{n}X_{i}/n\), so that the partially maximized gaussian log-likelihood function for \(\Omega\) is
+
+\begin{equation}
+\begin{split}
+  l(\Omega | X) &= \frac{n}{2}\log\left| \Omega \right| - tr\left[ \frac{1}{2}\sum_{i = 1}^{n}\left(X_{i} - \bar{X} \right)\left(X_{i} - \bar{X} \right)'\Omega \right] \\
+  &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
+\label{eq:partialmaxloglik}\notag
+\end{split}
+\end{equation}
+
+where \(S = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n\) is the usual sample estimator for the population covariance matrix, \(\Sigma\).
+In addition to \(\mu\), one could also derive the maximum likelihood estimator for \(\Omega\).
+By setting the gradient of the partially maximized log-likelihood equal to zero, one could show that
+
+\begin{equation}
+\begin{split}
+\hat{\Omega}^{mle} &= \arg\max_{\Omega \in S_{+}^{p}}\left\{ \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left(S\Omega \right) \right\} \\
+  &= \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| \right\} \\
+  &= S^{-1}
+\end{split}
+\label{eq:omegamle}\notag
+\end{equation}
+
+so that the MLE for \(\Omega\), when it exists, is \(\hat{\Omega}^{mle} = S^{-1} = \left[\sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(X_{i} - \bar{X}\right)'/n \right]^{-1}\).
+The reality, however, is that this object does \emph{not} always exist.
+In settings where the number of observations is exceeded by the number of features in a sample, the sample covariance matrix is rank deficient and no longer invertible.
+For this reason, many papers in the last decade have proposed \emph{shrinkage estimators} of the population precision matrix similar to the shrinkage estimators in regression settings.
+That is, instead of minimizing solely the negative log-likelihood function, researchers have proposed minimizing the gaussian log-likelihood \emph{plus} a penalty term, \(P\), where \(P\) is often a function of the precision matrix.
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + P\left( \Omega \right) \right\}
+\label{eq:omegapen}
+\end{equation}
+
+The penalties that have been proposed for precision matrix estimation are typically a variation of the ridge penalty \(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}/2\) or the lasso penalty \(P\left(\Omega \right) = \lambda\left\|\Omega\right\|_{1}\) (here \(\lambda\) is a tuning parameter).
+The authors, \citet{yuan2007model}, initially proposed the lasso-penalized gaussian log-likelihood defined as
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\sum_{i \neq j}\left|\Omega_{ij}\right| \right\}
+\label{eq:omegapenlasso}
+\end{equation}
+
+so as not to penalize the diagonal elements of the precision matrix estimate.
+Other papers published on the lasso-penalized gaussian likelihood precision matrix estimator include \citet{rothman2008sparse} and \citet{friedman2008sparse}.
+In addition, many efficient algorithms have been proposed to solve for \(\hat{\Omega}\), however, the most popular method is the graphical lasso algorithm (glasso) introduced by \citet{friedman2008sparse}.
+Their method utilizes an iterative block-wise coordinate descent algorithm that builds upon the coordinate descent algorithm used in lasso-penalized regression.
+
+Non-lasso, non-convex penalties were considered in \citet{lam2009sparsistency} and \citet{fan2009network} and other papers considered penalizations like the Frobenius norm (\citet{rothman2014existence}; \citet{witten2009covariance}; \citet{price2015ridge}).
+In fact, the latter two papers show that the resulting minimizer can be solved in closed-form - which will be discussed later in this manuscript.
+However, the penalty explored through the remainder of this chapter is not a lasso penality nor a ridge penalty but, in fact, a convex combination of the two known as the \emph{elastic-net} penalty:
+
+\begin{equation}
+P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right\|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]
+\label{eq:penelastic}\notag
+\end{equation}
+
+with additional tuning parameter \(0 \leq \alpha \leq 1\).
+Clearly, when \(\alpha = 0\) this penalty reduces to a ridge penalty and when \(\alpha = 1\) it reduces to a lasso penalty.
+Originally proposed in \citet{zou2005regularization} in the context of regression, this penalty has since been popularized and is used in the penalized regression R package \texttt{glmnet}.
+This penalty allows for additional flexibility but, despite this, no published work to our knowledge has explored the elastic-net penalty in the context of precision matrix estimation.
+We will show how to solve the following optimization problem in the next section using the ADMM algorithm.
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\}
+\label{eq:optimelastic}
+\end{equation}
+
+\hypertarget{admm-algorithm}{%
+\section{ADMM Algorithm}\label{admm-algorithm}}
+
+ADMM stands for alternating direction method of multipliers.
+The algorithm was largely popularized by Stephen Boyd and his fellow authors in the book \emph{Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers} \citep{boyd2011distributed}.
+As the authors state in the text, the ``ADMM is an algorithm that is intended to blend the decomposability of dual ascent with the superior convergence properties of the method of multipliers.'' By closely following Boyd's descriptions and guidance in the published text, we will show in this section that the ADMM algorithm is particularly well-suited to solve the penalized log-likelihood optimization problem we are interested in here.
+
+In general, the ADMM algorithm supposes that we want to solve an optimization problem of the form
+
+\begin{equation}
+\begin{split}
+  \mbox{minimize } f(x) + g(z) \\
+  \mbox{subject to } Ax + Bz = c
+\end{split}
+\label{eq:boyd}\notag
+\end{equation}
+
+where we can assume here that \(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\), \(c \in \mathbb{R}^{p}\), and \(f\) and \(g\) are convex functions.
+In order to find the pair \((x^{*}, z^{*})\) that achieves the infimum, the ADMM algorithm uses an \emph{augmented lagrangian}, \(L\), which \citet{boyd2011distributed} define as
+
+\begin{equation}
+L_{\rho}(x, z, y) = f(x) + g(z) + y'(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2}
+\label{eq:auglagrange}\notag
+\end{equation}
+
+In this formulation, \(y \in \mathbb{R}^{p}\) is called the lagrange multiplier and \(\rho > 0\) is some scalar that acts as the step size for the algorithm.
+Note that any infimum under the augmented lagrangian is equivalent to the infimum of the traditional lagrangian since any feasible point \((x, z)\) must satisfy the constraint \(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
+\citet{boyd2011distributed} show that using the ADMM algorithm the infimum will be approached under the following repeated iterations:
+
+\begin{equation}
+\begin{split}
+  x^{k + 1} &= \arg\min_{x \in \mathbb{R}^{n}}L_{\rho}(x, z^{k}, y^{k}) \\
+  z^{k + 1} &= \arg\min_{z \in \mathbb{R}^{m}}L_{\rho}(x^{k + 1}, z, y^{k}) \\
+  y^{k + 1} &= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
+\end{split}  
+\label{eq:admmalgo}\notag
+\end{equation}
+
+where the superscript, \(k\), denotes the number of iterations.
+Conveniently, this general algorithm can be coerced into a format useful in precision matrix estimation.
+Suppose we let \(f\) be equal to the non-penalized gaussian log-likelihood, \(g\) equal to the elastic-net penalty, \(P\left( \Omega \right)\), and we use the constraint that \(\Omega \in \mathbb{S}_{+}^{p}\) must be equal to some matrix \(Z \in \mathbb{R}^{p \times p}\), then the augmented lagrangian in the context of precision matrix estimation is of the form
+
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2}
+\label{eq:auglagrange2}\notag
+\end{equation}
+
+where \(\Lambda\) takes the role of \(y\) as the lagrange multiplier. The ADMM algorithm now consists of the following repeated iterations:
+
+\begin{equation}
+\begin{split}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+\label{eq:ADMMorig}
+\end{split}
+\end{equation}
+
+Furthermore, it turns out that each step in this algorithm can be solved efficiently in closed-form.
+The full details of each can be found in the appendix \ref{proofomegaalgo} but the following theorem provides the simplified steps in the algorithm.
+
+\BeginKnitrBlock{theorem}[ADMM Algorithm for Elastic-Net Penalized Precision Matrix Estimation]
+\protect\hypertarget{thm:unnamed-chunk-2}{}{\label{thm:unnamed-chunk-2} \iffalse (ADMM Algorithm for Elastic-Net Penalized Precision Matrix Estimation) \fi{} }
+Define the soft-thresholding function as \(\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}\) and \(S\) as the sample covariance matrix.
+Set \(k = 0\) and initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\).
+Repeat steps 1-3 until convergence:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV'\) via spectral decomposition\footnote{Proof of \eqref{eq:omegaalgo} in section \ref{proofomegaalgo}.}. Then
+\end{enumerate}
+
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V'
+\label{eq:omegaalgo}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Elementwise soft-thresholding for all \(i = 1,..., p\) and \(j = 1,..., p\)\footnote{Proof of \eqref{eq:ZZalgo} in section \ref{proofZZalgo}.}.
+\end{enumerate}
+
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\label{eq:ZZalgo}
+\end{split}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Update \(\Lambda^{k + 1}\).
+\end{enumerate}
+
+\begin{equation}
+\Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+\label{eq:lamalgo}\notag
+\end{equation}
+\EndKnitrBlock{theorem}
+
+\hypertarget{scaled-form-admm}{%
+\subsection{Scaled-Form ADMM}\label{scaled-form-admm}}
+
+Another popular, alternative form of the ADMM algorithm can be used when scaling the dual variable (\(\Lambda^{k}\)) which we will briefly mention in the context of precision matrix estimation here.
+
+Define \(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\) then
+
+\begin{equation}
+\begin{split}
+  tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
+  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
+  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
+\label{eq:scaled}\notag
+\end{split}
+\end{equation}
+
+Therefore, a scaled-form ADMM algorithm can now be written as
+
+\begin{equation}
+\begin{split}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
+  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
+\label{eq:ADMMscaled}
+\end{split}
+\end{equation}
+
+Note that there are limitations to using this method.
+Because the dual variable is scaled by \(\rho\) (the step size), this form limits one to using a constant step size for all \(k\) steps if no further adjustments are made to \(U^{k}\).
+
+\hypertarget{ADMMstop}{%
+\subsection{Stopping Criterion}\label{ADMMstop}}
+
+There are three optimality conditions for the ADMM algorithm that we can use to inform the convergence and stopping criterion.
+These general conditions were outlined in \citet{boyd2011distributed} but here we cater them to precision matrix estimation.
+The first condition is the primal optimality condition \(\Omega^{k + 1} - Z^{k + 1} = 0\) and the other two conditions are the dual conditions \(0 \in \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1}\) and \(0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}\).
+The first dual optimality condition is a result of taking the sub-differential of the lagrangian (non-augmented) with respect to \(\Omega^{k + 1}\) and the second is a result of taking the sub-differential of the lagrangian with respect to \(Z^{k + 1}\).
+Note that in the first condition we must honor the symmetric constraint in \(\Omega\) but the second condition does not require it.
+
+If we define the left-hand side of the primal optimality condition as the \emph{primal residual} \(r^{k + 1} = \Omega^{k + 1} - Z^{k + 1}\), then at convergence we must require that \(r^{k + 1} \approx 0\).
+Likewise, if we define the \emph{dual residual} \(s^{k + 1} = \rho\left( Z^{k + 1} - Z^{k} \right)\), we must also require that \(s^{k + 1} \approx 0\) for proper convergence.
+This dual residual is the direct result of the fact that \(\Omega^{k + 1}\) is the minimizer of the augmented lagragian\footnote{Proof in section \ref{proofdualresidual}.} so that \(0 \in \partial L_{p}\left( \Omega, Z^{k}, \Lambda^{k} \right)\) and consequently \(0 \in \rho\left( Z^{k + 1} - Z^{k} \right)\)\footnote{Note that the second dual optimality condition \(0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}\) is always satisfied.
+More details can be found in section \ref{proofdualopt}.}.
+
+Combining these three optimality conditions, Boyd suggests a stopping criterion similar to \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and
+\begin{equation}
+\begin{split}
+  \epsilon^{pri} &= p\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| \Omega^{k + 1} \right\|_{F}, \left\| Z^{k + 1} \right\|_{F} \right\} \\
+  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
+\label{eq:admmstopping}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{simulations}{%
+\section{Simulations}\label{simulations}}
+
+As a proof-of-concept that the elastic-net penalty in the context of precision matrix estimation can provide useful results and that the ADMM algorithm used in this process works, this section offers a short simulation.
+For the simulation, we generated data from multiple, unique precision matrices with various oracle structures.
+For each data-generating procedure, the algorithm was run with a 5-fold cross validation to tune parameters \(\lambda\) and \(\alpha\).
+After 20 replications, the cross validation errors were totalled and the optimal tuning parameters were selected (results are in the top half of the figures).
+These results were then compared with the Kullback Leibler (KL) losses between the estimated matrices and the oracle matrices (results are in the bottom half of the figures).
+
+The first figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a tri-diagonal oracle precision matrix.
+This oracle matrix was first generated as \(\left(S_{ij}\right) = 0.7^{\left|i - j \right|}\) for \(i,j = 1,..., p\) and then inverted.
+The results show that because the oracle precision matrix is sparse, the algorithm correctly chooses a sparse solution with \(\alpha = 1\) - indicating a lasso penalty.
+
+The second figure shows the results when the data was generated from a multivariate normal distribution with mean equal to zero and a \emph{dense} oracle precision matrix (non-sparse).
+Here, we randomly generated an orthogonal basis, set all eigen values equal to 1000, and then combined the matrices using QR decomposition.
+Interestingly, we find that the optimal \(\alpha\) in this case is 0.6 which closely matches the optimal result based on the KL loss.
+This shows that there are cases where an elastic-net penalty can provide useful results and that using only a lasso penalty may unnecessarily restrict our penalized estimation.
+
+\vspace{1cm}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth,]{images/repsKLtridiag_N50_P100}
+
+}
+
+\caption{The oracle precision matrices were tri-diagonal with dimension p = 100 and the data was generated with a sample size of n = 50.
+The cross validation errors are in the top figure and the KL losses between the estimated matrices and the oracle matrices are shown in the bottom figure.
+The optimal tuning parameter pair for each heatmap was found to be log10(lam) = -0.9 and alpha = 1.
+Note that brighter areas signify smaller losses.}\label{fig:admmsim5}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth,]{images/repsKLdenseQR_N50_P100}
+
+}
+
+\caption{The oracle precision matrices were dense with dimension p = 100 and the data was generated with a sample size of n = 50.
+The cross validation errors are in the top figure and the KL losses between the estimated matrices and the oracle matrices are shown in the bottom figure.
+The optimal tuning parameter pair for the cross validation errors was found to be log10(lam) = -0.4 and alpha = 0.6 and log10(lam) = -0.5 and alpha = 0.7 for the KL losses.
+Note that brighter areas signify smaller losses.}\label{fig:admmsim3}
+\end{figure}
+
+\hypertarget{scpme}{%
+\chapter{SCPME}\label{scpme}}
+
+In their 2017 paper, titled \emph{Shrinking Characteristics of Precision Matrix Estimators}, Aaron Molstad, Ph.D.~and Professor Adam Rothman outline a framework to estimate \emph{characteristics} of precision matrices.
+This concept, inspired by others like \citet{cai2011direct}, \citet{fan2012road}, and \citet{mai2012direct}, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector.
+The example they offer in \citet{molstad2017shrinking} is in the context of Fisher's linear discriminant analysis model.
+If a response vector \(Y\) is categorical such that \(Y\) can take values in \(\left\{1, ..., J\right\}\), then the linear discrimnant analysis model assumes that the design matrix \(X\) conditional on the response vector \(Y\) is normally distributed:
+
+\begin{equation}
+X | Y = j \sim N_{p}\left(\mu_{j}, \Omega^{-1}\right)
+\label{eq:lda}
+\end{equation}
+
+for each \(j = 1, ..., J\).
+One can see from this formulation that clearly an estimation of both \(\mu\) and \(\Omega\) are required for this model.
+However, they note that if prediction is the primary concern, then for a given observation \(X_{i}\) only the \emph{characteristic} \(\Omega\left(\mu_{l} - \mu_{m}\right)\) is needed to discern between response categories \(l\) and \(m\).
+In other words, prediction only requires the characteristic \(\Omega\left(\mu_{l} - \mu_{m}\right)\) for each \(l, m \in \left\{1, ..., J\right\}\) and does \emph{not} require estimation of the full precision matrix \(\Omega\).
+\citet{cai2011direct} were among the first authors to propose estimating this characteristic directly but the interesting facet that distinguishes Molstad and Rothman's approach is that their framework simultaneously fits the model in \eqref{eq:lda} and performs variable selection.
+
+The general framework has applications outside of linear discriminant analysis and we will be exploring a regression application in later sections, but first we will outline their approach.
+The penalty proposed by \citet{molstad2017shrinking} is of the form
+
+\begin{equation}
+P\left(\Omega\right) = \lambda\left\| A\Omega B - C \right\|_{1}
+\label{eq:pen2}
+\end{equation}
+
+where \(A \in \mathbb{R}^{m \times p}, B \in \mathbb{R}^{p \times q}, \mbox{ and } C \in \mathbb{R}^{m \times q}\) are matrices that are assumed to be known and specified so that solving the full penalized gaussian negative log-likelihood for \(\Omega\) results in solving
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+\label{eq:omegaloglik2}
+\end{equation}
+
+A similar estimator was proposed by \citet{dalal2017sparse} when \(C = 0\) but here we do not require it.
+This form of penalty is particularly useful because it is extremely general.
+Note that by letting matrices \(A = I_{p}, B = I_{p}, \mbox{ and } C = 0\), this penalty reduces to a lasso penalty - but clearly this form allows for much more creative penalties and \(A, B, \mbox{ and } C\) can be constructed so that we penalize the sum, absolute value of \emph{many} characteristics of the precision matrix \(\Omega\).
+We will explore how to solve for \(\hat{\Omega}\) in \eqref{eq:omegaloglik2} in the next section.
+
+\hypertarget{augmented-admm-algorithm}{%
+\section{Augmented ADMM Algorithm}\label{augmented-admm-algorithm}}
+
+Solving for \(\hat{\Omega}\) in \eqref{eq:omegaloglik2} uses what we are going to call an \emph{augmented ADMM algorithm}.
+Molstad and Rothman do not offer a name for this specific algorithm but it leverages the majorize-minimize principle in one of the steps in the algorithm - augmenting the original ADMM algorithm discussed in the previous chapter.
+Within the context of the proposed penalty, the original ADMM algorithm for precision matrix estimation would consist of iterating over the following three steps:
+
+\begin{align}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+\end{align}
+
+where \(L\), the augmented lagrangian, is defined as
+
+\begin{equation}
+L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + tr\left[\Lambda '\left(A\Omega B - Z - C\right)\right] + \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2}
+\label{eq:auglagrange3}
+\end{equation}
+
+Similar to the previous chapter, \(f\left(\Omega\right) = tr\left(S\Omega\right) - \log\left|\Omega\right|\) and \(g\left(Z\right) = \lambda\left\|Z\right\|_{1}\).
+In fact, the details of the algorithm thus far are identical to the previous approach except that we are replacing \(\Omega - Z\) with \(A\Omega B - Z - C\) in the augmented lagrangian and the dual update \(\Lambda^{k + 1}\).
+
+Instead of solving the first step directly, the authors propose an alternative, approximating objective function, which we will denote as \(\tilde{L}\), that is based on the majorize-minimize principle\footnote{Further explanation of the majorizing function \eqref{eq:approx} in section \ref{taylorsexp}}.
+The purpose of this approximating function is the desire to solve the first step of the algorithm in closed-form.
+The ADMM algorithm with this modification based on majorize-minimize principle is also found in \citet{lange2016mm} but here we define the approximating function as
+
+\begin{equation}
+\begin{split}
+  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
+\label{eq:approx}
+\end{split}
+\end{equation}
+
+where \(Q = \tau I_{p} - \left(A'A \otimes BB'\right)\) and \(\tau\) is chosen such that \(Q\) is positive definite.
+Note that if \(Q\) is positive definite, then \(L_{\rho}\left(\cdot\right) \leq \tilde{L}\left(\cdot\right)\) for all \(\Omega\) and \(\tilde{L}\) is a majorizing function\footnote{If \(Q\) is positive definite, then \(vec\left(\Omega - \Omega^{k} \right)'\rho Q\left(\Omega - \Omega^{k} \right)/2 > 0\) since \(\rho > 0\) and \(vec\left(\Omega - \Omega^{k}\right)\) is always nonzero whenever \(\Omega \neq \Omega^{k}\).}.
+The \emph{augmented ADMM} algorithm developed by Molstad and Rothman, which now includes the majorize-minimize principle, consists of the following repeated iterations:
+
+\begin{equation}
+\begin{split}
+  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
+  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
+  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+\label{eq:augADMM}\notag
+\end{split}
+\end{equation}
+
+where \(G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'\).
+Each step in this algorithm can now conveniently be solved in closed-form and the full details of each can be found in the appendix \ref{proofOmegak}.
+The following theorem provides the simplified steps in the algorithm.
+
+\BeginKnitrBlock{theorem}[Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators.]
+\protect\hypertarget{thm:unnamed-chunk-3}{}{\label{thm:unnamed-chunk-3} \iffalse (Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators.) \fi{} }
+Define the soft-thresholding function as \(\mbox{soft}(a, b) = \mbox{sign}(a)(\left| a \right| - b)_{+}\) and \(S\) as the sample covariance matrix.
+Set \(k = 0\) and initialize \(Z^{0}, \Lambda^{0}, \Omega^{0}\), and \(\rho\) and repeat steps 1-5 until convergence.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Compute \(G^{k}\).
+\end{enumerate}
+
+\begin{equation}
+G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'
+\label{eq:Gk}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Via spectral decomposition, decompose
+\end{enumerate}
+
+\begin{equation}
+S + \left( G^{k} + (G^{k})' \right)/2 - \rho\tau\Omega^{k} = VQV'
+\label{eq:VQV}\notag
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Update \(\Omega^{k + 1}\).\footnote{Proof of \eqref{eq:Omegak} in section \ref{proofOmegak}}
+\end{enumerate}
+
+\begin{equation}
+\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V' /(2\rho\tau)
+\label{eq:Omegak}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{3}
+\tightlist
+\item
+  Update \(Z^{k + 1}\) with element-wise soft-thresholding for the resulting matrix.\footnote{Proof of \eqref{eq:Zk} in section \ref{proofZk}}
+\end{enumerate}
+
+\begin{equation}
+Z^{k + 1} = \mbox{soft}\left( A\Omega^{k + 1}B - C + \rho^{-1}\Lambda^{k}, \rho^{-1}\lambda \right)
+\label{eq:Zk}
+\end{equation}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{4}
+\tightlist
+\item
+  Update \(\Lambda^{k + 1}\).
+\end{enumerate}
+
+\begin{equation}
+\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+\label{eq:Yk}\notag
+\end{equation}
+\EndKnitrBlock{theorem}
+
+\hypertarget{stopping-criterion}{%
+\subsection{Stopping Criterion}\label{stopping-criterion}}
+
+A possibe stopping criterion for this framework is one derived from similar optimality conditions used in the previous chapter in section \ref{ADMMstop}.
+The primal optimality condition here is that \(A\Omega^{k + 1}B - Z^{k + 1} - C = 0\) and the two dual optimality conditions are \(0 \in \partial f\left(\Omega^{k + 1}\right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2\) and \(0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}\).
+Similarly, we will define the left-hand side of the primal optimality condition as the primal residual \(r^{k + 1} = A\Omega^{k + 1}B - Z^{k + 1} - C\) and the dual residual\footnote{Proof of \eqref{eq:stopproof} in section \ref{proofstopproof}.} as
+
+\begin{equation}
+s^{k + 1} = \frac{\rho}{2}\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)
+\label{eq:stopproof}\notag
+\end{equation}
+
+For proper convergence, we will require that both residuals are approximately equal to zero.
+Similar to the stopping criterion discussed previously, one possibility is to set \(\epsilon^{rel} = \epsilon^{abs} = 10^{-3}\) and stop the algorithm when \(\epsilon^{pri} \leq \left\| r^{k + 1} \right\|_{F}\) and \(\epsilon^{dual} \leq \left\| s^{k + 1} \right\|_{F}\) where
+
+\begin{equation}
+\begin{split}
+  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
+  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
+\label{eq:scpmestopping}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{regression-illustration}{%
+\section{Regression Illustration}\label{regression-illustration}}
+
+One of the research directions mentioned in \citet{molstad2017shrinking} that was not further explored was the application of the SCPME framework to regression.
+Utilizing the fact that the population regression coefficient matrix \(\beta \equiv \Omega_{x}\Sigma_{xy}\) for predictors, \(X\), and the responses, \(Y\), they point out that their framework could allow for the simultaneous estimation of \(\beta\) and \(\Omega_{x}\).
+Like \citet{witten2009covariance}, this approach would estimate the forward regression coefficient matrix while using shrinkage estimators for the marginal population precision matrix for the predictors.
+For example, recall that the general optimization problem outlined in the SCPME framework is to estimate \(\hat{\Omega}\) such that
+
+\begin{equation}
+  \hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr(S\Omega) - \log\left| \Omega \right| + \lambda\left\| A\Omega B - C \right\|_{1} \right\}
+\label{eq:penloglik3}\notag
+\end{equation}
+
+If the user specifies that \(A = I_{p}, B = \Sigma_{xy}, C = 0, \mbox{ and } \Omega_{x}\) is the precision matrix for the predictors, then the optimization problem of interest is now
+
+\begin{equation}
+  \hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr(S_{x}\Omega_{x}) - \log\left| \Omega_{x} \right| + \lambda\left\| \Omega_{x} \Sigma_{xy} \right\|_{1} \right\} \\
+\label{eq:penloglik4}\notag
+\end{equation}
+
+Specifically, this optimization problem has the effect of deriving an estimate of \(\Omega_{x}\) while assuming sparsity in the forward regression coefficient \(\beta\).
+Of course, in practice we do not know the true covariance matrix \(\Sigma_{xy}\) but we might consider using the sample estimate \(\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)'/n\) in place of \(\Sigma_{xy}\).
+We could then use our estimator, \(\hat{\Omega}_{x}\), to construct the estimated forward regression coefficient matrix \(\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}\).
+Estimators such as these are truly novel an can conveniently be estimated by the SCPME framework.
+Another such estimator that is a product of this new framework is one where we construct \(A \mbox{ and } C\) similarly but take \(B = \left[ \Sigma_{xy}, I_{p} \right]\) so that the identity matrix is appended to the cross-covariance matrix of \(X\) and \(Y\).
+In this case, not only are we assuming that \(\beta\) is sparse, but we are also assuming sparsity in \(\Omega\).
+
+\begin{equation}
+P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1}
+\label{eq:pen4}\notag
+\end{equation}
+
+Like before, we could use \(\hat{\Sigma}_{xy}\) as a replacement and take our resulting estimator, \(\hat{\Omega}_{x}\), to construct the estimated forward regression coefficient matrix \(\hat{\beta} = \hat{\Omega}_{x}\hat{\Sigma}_{xy}\).
+The embedded assumptions here are that not all predictors in \(X\) are useful in predicting the response, \(Y\), \emph{and} that a number of the predictors are conditionally independent of one another.
+These are assumptions that are quite reasonable in practice and in the next section we offer a short simulation comparing these new estimators to related and competing prediction methods.
+
+\hypertarget{simulations-1}{%
+\section{Simulations}\label{simulations-1}}
+
+In this simulation, we compare, under various data realizations, the performance of several competing regression prediction methods including the new so-called SCPME regression estimators discussed in the previous section.
+In total, we consider the following:
+
+\begin{itemize}
+\item
+  \texttt{OLS} = ordinary least squares estimatior. In high dimensional settings (\(p >> n\)), the Moore-Penrose estimator is used as a replacement.
+\item
+  \texttt{ridge} = ridge regression estimator.
+\item
+  \texttt{lasso} = lasso regression estimator.
+\item
+  \texttt{oracleB} = oracle estimator for \(\beta\).
+\item
+  \texttt{oracleO} = regression estimator with oracle \(\Omega_{x}^{*}\) (let \(\beta = \Omega_{x}^{*}\hat{\Sigma}_{xy}\)).
+\item
+  \texttt{oracleS} = regression estimator with oracle \(\Sigma_{xy}^{*}\) (let \(\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}\)) and \(\Omega_{x}\) is estimated using an elastic-net penalty.
+\item
+  \texttt{shrinkB} = SCPME regression estimator with penalty \(\lambda\left\| \Omega_{x}\hat{\Sigma}_{xy} \right\|_{1}\) so that \(\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}\).
+\item
+  \texttt{shrinkBS} = SCPME regression estimator with oracle \(\Sigma_{xy}^{*}\) so that the penalty is \(\lambda\left\| \Omega_{x}\Sigma_{xy}^{*} \right\|_{1}\) and we let \(\beta = \hat{\Omega}_{x}\Sigma_{xy}^{*}\).
+\item
+  \texttt{shrinkBO} = SCPME regression estimator with penalty \(\lambda\left\| \Omega_{x}[\hat{\Sigma}_{xy}, I_{p}] \right\|_{1}\) so that \(\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}\).
+\item
+  \texttt{glasso} = graphical lasso estimator with penalty \(\lambda\left\| \Omega_{x} \right\|_{1}\) so that \(\beta = \hat{\Omega}_{x}\hat{\Sigma}_{xy}\).
+\end{itemize}
+
+For each estimator, if selection of a tuning parameter is required, the tuning parameter was chosen so that the mean squared prediction error (MSPE) was minimized over 3-fold cross validation.
+
+The data generating procedure for the simulations is the following.
+The oracle regression coefficient matrix \(\beta^{*}\) was constructed so that \(\beta^{*} = \mathbb{B} \circ \mathbb{V}\) where \(vec\left( \mathbb{B} \right) \sim N_{pr}\left( 0, I_{p} \otimes I_{r}/\sqrt{p} \right)\) and \(\mathbb{V} \in \mathbb{R}^{p \times r}\) is a matrix containing \(p\) times \(r\) random bernoulli draws with 50\% probability being equal to one.
+The covariance matrices \(\Sigma_{y | x}\) and \(\Sigma_{x}\) were constructed so that \(\left( \Sigma_{y | x} \right)_{ij} = 0.7^{\left| i - j \right|}\) and \(\left( \Sigma_{x} \right)_{ij} = 0.7^{\left| i - j \right|}\), respectively.
+This ensures that their corresponding precision matrices will be tridiagonal and sparse.
+Then for 100 independent, identically distributed samples, we had \(X_{i} \sim N_{p}\left( 0, \Sigma_{x} \right)\) and \(E_{i} \sim N_{r}\left( 0, \Sigma_{y | x} \right)\) so that \(\mathbb{Y} = \mathbb{X}\beta + \mathbb{E}\) where \(\mathbb{X} \in \mathbb{R}^{n \times p}\) and \(\mathbb{Y} \in \mathbb{R}^{n \times r}\) are the matrices with stacked rows \(X_{i}\) and \(E_{i}\), respectively, for \(i = 1, ..., n\) and the script notation denotes the fact that the columns have been centered so as to remove the intercept in our prediction models.
+A sample of an additional 1000 observations was generated similarly for the testing set.
+Each prediction method was evaluated on both model error and mean squared prediction error.
+
+Figure \ref{fig:scpmesim2} displays the model error for each method by dimension of the design matrix.
+Here we took the sample size equal to \(n = 100\) and the response matrix dimension \(r = 10\) with each data generating procedure replicated a total of 20 times.
+Note \texttt{OLS} and \texttt{oracleS} are not shown due to extremely poor performance.
+We find that in high dimensional settings, \texttt{shrinkBO} and \texttt{shrinkB} perform increasingly well relative to the others as the predictor dimension increases.
+\texttt{shrinkBO} performed the best.
+Interestingly, when \(n > p\) \texttt{shrinkBO} is still one of the best-performing estimators - though worse than both \texttt{lasso} and \texttt{ridge} - but the performance of \texttt{shrinkB} decreases drastically (plot not shown).
+
+In the high dimension setting, the oracle estimators \texttt{oracleO} and \texttt{oracleS} performed worse or comparable to the \texttt{OLS} estimator.
+The poor performance of \texttt{oracleS} is likely due to the fact that the sample estimate of \(\Omega_{x}\) is not identifiable when \(p > n\).
+
+The following table shows the average model error for each estimator when \(n = 100\), \(p = 150\), and \(r = 10\).
+
+\vspace{0.5cm}
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth,]{Manuscript_files/figure-latex/scpmesim2-1}
+
+}
+
+\caption{The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
+The model errors (ME) for each estimator with variable dimension of the design matrix are plotted.
+shrinkBO and shrinkB were the two best-performing estimators closely follow by the ridge and lasso regression estimators.}\label{fig:scpmesim2}
+\end{figure}
+
+\newpage
+
+\begin{longtable}[]{@{}ccc@{}}
+\caption{ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)
+\vspace{0.5cm}}\tabularnewline
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+error\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.14\columnwidth}\centering
+model\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+error\strut
+\end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
+sd\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.5056\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+0.5122\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.341\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.014\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkB\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.419\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.083\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+ridge\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.479\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.128\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+lasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+2.627\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+1.27\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+shrinkBS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+5.932\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+4.001\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+glasso\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+7.57\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+5.412\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleO\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+13.18\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+10.11\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+OLS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+14.41\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+11.24\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.14\columnwidth}\centering
+oracleS\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+52.07\strut
+\end{minipage} & \begin{minipage}[t]{0.11\columnwidth}\centering
+44.62\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{regression-simulations-with-covariance-shrinkage}{%
+\subsection{Regression Simulations with Covariance Shrinkage}\label{regression-simulations-with-covariance-shrinkage}}
+
+This final simulation was explored due to the fact that each of the SCPME regression estimators require an estimation of the cross-covariance matrix.
+In the previous simulations, we naively used the maximum likelihood estimate.
+However, because the data-generating procedure constructs settings that are inherently sparse, we were interested to determine if additional shrinkage of the maximum likelihood estimate for the \emph{cross-covariance} matrix would also prove beneficial.
+For instance, in a number of settings, we were finding that the estimator \texttt{oracleO} was performing worse than \texttt{oracleS}.
+This perhaps suggests that estimating the covariance matrix \(\Sigma_{xy}\) well is \emph{more} important than estimating \(\Omega\) well.
+This simulation explores that theory a bit further.
+
+The data-generating procedure for this simulation is similar to previous one but here we take \(n = 100\), \(p = 200\), \(r = 10\), and, in addition, we multiply the population cross-covariance estimator by a factor of \(k\) where \(k \in (0.1, 0.2, ..., 0.9, 1)\).
+Figure \ref{fig:scpmesim7} plots the MSPE for \texttt{shrinkB} for each tuning parameter, \(\lambda\), and constant, \(k\), pair.
+Figure \ref{fig:scpmesim9} plots the MSPE similarly for \texttt{shrinkBO}.
+
+Interestingly, we find that in this high dimension setting, it does appear that shrinking the sample covariance matrix by a constant factor helps the overall prediction performance of the SCPME estimators.
+This is indicated by the fact that the optimal constant, \(k\), hovers between 0.3 and 0.6 for each of the estimators.
+We also performed a simulation in low dimensions (not shown) but we did not see the same benefit.
+
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth,]{Manuscript_files/figure-latex/scpmesim7-1}
+
+}
+
+\caption{The oracle precision matrices were tri-diagonal with dimension p = 200 and the data was generated with a sample size n = 100 and response vector dimension r = 10.
+The cross validation MSPE are plotted for each lambda and constant tuning parameter pair.
+The optimal tuning parameter pair was found to be log10(lam) = -1 and const = 0.6.
+Note that brighter areas signify smaller losses.}\label{fig:scpmesim7}
+\end{figure}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\begin{figure}
+
+{\centering \includegraphics[width=0.85\linewidth,]{Manuscript_files/figure-latex/scpmesim9-1}
+
+}
+
+\caption{The oracle precision matrices were tri-diagonal with dimension p = 200 and the data was generated with a sample size n = 100 and response vector dimension r = 10.
+The cross validation MSPE are plotted for each lambda and constant tuning parameter pair.
+The optimal tuning parameter pair was found to be log10(lam) = -0.5 and const = 0.3.
+Note that brighter areas signify smaller losses.}\label{fig:scpmesim9}
+\end{figure}
+\vspace{0.5cm}
+
+\newpage
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Apart from the two SCPME estimators discussed in the previous section, the generality of the SCPME framework allows for many previously unconceptualized precision matrix estimators to be explored.
+One estimator that was concieved of in our work but deserves further attention in future research is of the form
+
+\begin{equation}
+\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr(S_{x}\Omega_{x}) - \log\left| \Omega_{x} \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega_{x} \Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\label{eq:penregression}\notag
+\end{equation}
+
+For clarity in regards to the SCPME framework, \(A = \mathbb{X}, B = \Sigma_{xy}, \mbox{ and } C = \mathbb{Y}\).
+As before, \(\mathbb{X}\) is the \(n \times p\) matrix with rows \(X_{i} \in \mathbb{R}^{p}\) for \(i = 1,..., n\) and the script notation denotes that the matrix has been column-centered.
+The matrix \(\mathbb{Y}\) is a similar representation for the observed responses \(Y_{i} \in \mathbb{R}^{r}\).
+Also note that here we are using the Frobenius norm instead of the matrix \(l_{1}\)-norm but this replacement requires only a slight modification of the augmented ADMM algorithm for optimization - details of which will be presented later.
+
+This optimization problem estimates a precision matrix that balances minimizing the gaussian negative log-likelihood for \(\Omega_{x}\) with minimizing the squared prediction error for the forward regression model.
+In other words, the objective function aims to penalize estimates, determined by \(\lambda\), that too heavily favor maximizing the marginal likelihood for \(X\) over the predictive performance of the conditional model \(Y\) given \(X\).
+This estimator also reveals an interesting connection to the joint log-likelihood of the two random variables.
+To see this, let us suppose that we have \(n\) independent copies of the random pair \((Y_{i}, X_{i})\) and we assume a linear relationship such that
+
+\begin{equation}
+Y_{i} = \mu_{y} + \beta'\left(X_{i} - \mu_{x}\right) + E_{i}
+\end{equation}
+
+where \(E_{i} \sim N_{r}\left( 0, \Omega_{y | x}^{-1} \right)\) and \(X_{i} \sim N_{p}\left( \mu_{x}, \Omega_{x}^{-1} \right)\).
+This implies that the conditional distribution of \(Y_{i}|X_{i}\) is of the form
+
+\begin{equation}
+Y_{i} | X_{i} \sim N_{r}\left( \mu_{y} + \beta'\left(X_{i} - \mu_{x}\right), \Omega_{y | x}^{-1} \right)
+\end{equation}
+
+We can use this conditional distribution along with the marginal distribution of \(X\) to derive the joint log-likelihood of \(X\) and \(Y\).
+Recall that \(\beta \equiv \Omega_{x}\Sigma_{xy}\) and \(S_{x}\) is the marginal sample covariance matrix of \(X\).
+Without loss of generality, we will assume here that \(\mu_{x} = \mu_{y} = 0\).
+
+\begin{equation}
+\begin{split}
+  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
+  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
+  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
+  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
+\label{eq:partialjointloglik}\notag
+\end{split}
+\end{equation}
+
+Optimizing this joint log-likelihood with respect to \(\Omega_{x}\) reveals strong similiarities to the estimator that was derived from the SCPME framework:
+
+\begin{equation}
+\begin{split}
+  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
+  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
+\label{eq:omegajointloglik}\notag
+\end{split}
+\end{equation}
+
+If it is the case that, given \(X\), each of the \(r\) responses are pairwise independent with equal variance so that \(\Omega_{y | x}^{1/2} = \sigma_{y | x}I_{r}\) and we let \(\lambda = 2\sigma_{y | x}^{2}/n\), then we have that
+
+\begin{equation}
+\hat{\Omega}_{x} = \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{\lambda}{2}\left\| \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right\|_{F}^{2} \right\}
+\label{eq:omegajointmle}\notag
+\end{equation}
+
+This is exactly the estimator conceived of previously.
+Of course, throughout this derivation there were several assumptions that were made and in practice we do not know the true values of neither \(\Omega_{y | x}\) nor \(\Sigma_{xy}\).
+However, we can see that this estimator is solving a very similar problem to that of optimizing the joint log-likelihood with respect to \(\Omega_{x}\).
+We think this estimator and related ones deserve attention in future work.
+
+The algorithm for solving this optimization problem is below.
+Note that no closed-form solution exists and so we must resort to some iterative algorithm similar to the SCPME augmented ADMM algorithm\footnote{Proof in section \ref{proofpenregression}.}.
+The only difference here is that in step four we no longer require elementwise soft-thresholding.
+
+\BeginKnitrBlock{theorem}[Modified Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators with Frobenius Norm]
+\protect\hypertarget{thm:unnamed-chunk-6}{}{\label{thm:unnamed-chunk-6} \iffalse (Modified Augmented ADMM Algorithm for Shrinking Characteristics of Precision Matrix Estimators with Frobenius Norm) \fi{} }
+Set \(k = 0\) and initialize \(Z^{0}, \Lambda^{0}, \Omega^{0}\), and \(\rho\) and repeat steps 1-5 until convergence.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  Compute \(G^{k} = \rho A'\left( A\Omega^{k} B - Z^{k} - C + \rho^{-1}\Lambda^{k} \right)B'\)
+\item
+  Decompose \(S + \left( G^{k} + (G^{k})' \right)/2 - \rho\tau\Omega^{k} = VQV'\) (via the spectral decomposition).
+\item
+  Set \(\Omega^{k + 1} = V\left( -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2} \right)V'/(2\rho\tau)\)
+\item
+  Set \(Z^{k + 1} = \left[ \rho\left( A\Omega^{k + 1} B - C \right) + \Lambda^{k} \right]/(\lambda + \rho)\)
+\item
+  Set \(\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)\)
+\end{enumerate}
+\EndKnitrBlock{theorem}
+
+\hypertarget{appendix-appendix}{%
+\appendix}
+
+\hypertarget{appendix}{%
+\chapter{Appendix}\label{appendix}}
+
+\hypertarget{proofomegaalgo}{%
+\subsection{Proof of \eqref{eq:omegaalgo}}\label{proofomegaalgo}}
+
+\citet{witten2009covariance} and \citet{price2015ridge} showed that the following optimization problem can be solved in closed-form. We outline their steps here.
+
+\begin{equation}
+\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\}
+\label{eq:appendixomegaloglik}\notag
+\end{equation}
+
+First start by taking the gradient with respect to \(\Omega\):
+
+\begin{equation}
+\begin{split}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
+  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
+\label{eq:appendixomegagradient}\notag
+\end{split}
+\end{equation}
+
+Note that because all of the variables are symmetric, we can ignore the symmetric constraint when deriving the gradient.
+Next set the gradient equal to zero and decompose \(\Omega^{k + 1} = VDV'\) using spectral decomposition so that \(D\) is a diagonal matrix with diagonal elements equal to the eigen values of \(\Omega^{k + 1}\) and \(V\) is the matrix with corresponding eigen vectors as columns so that
+
+\begin{equation}
+S + \Lambda^{k} - \rho Z^{k} = (\Omega^{k + 1})^{-1} - \rho \Omega^{k + 1} = VD^{-1}V' - \rho VDV' =  V\left(D^{-1} - \rho D\right)V'\notag
+\end{equation}
+
+This equivalence implies that
+
+\begin{equation}
+\phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1})\notag
+\end{equation}
+
+where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
+
+\begin{equation}
+\begin{split}
+  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
+  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
+\end{split}
+\notag
+\end{equation}
+
+In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV'\) then
+
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V'
+\label{eq:appendixomegaproof}
+\end{equation}
+
+\hypertarget{proofZZalgo}{%
+\subsection{Proof of \eqref{eq:ZZalgo}}\label{proofZZalgo}}
+
+Solve the optimization problem
+
+\begin{equation}
+Z^{k + 1} = \arg\min_{Z \in \mathbb{S}^{p}}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\}
+\label{eq:appendixZZloglik}\notag
+\end{equation}
+
+Start by taking the subgradient with respect to \(Z\):
+
+\begin{equation}
+\begin{split}
+  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] \right\} + \nabla_{\Omega}\left\{ tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
+  &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
+\label{eq:appendixZZgradient}\notag
+\end{split}
+\end{equation}
+
+where sign is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we have that
+
+\begin{equation}
+Z_{ij}^{k + 1} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - \mbox{sign}(Z_{ij}^{k + 1})\lambda\alpha \right)
+\label{eq:ZZsoftproof}\notag
+\end{equation}
+
+for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} > 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \notag
+\end{equation}
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} < 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \notag
+\end{equation}
+
+This implies that \(\mbox{sign}(Z_{ij}) = \mbox{sign}(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\). Putting all the pieces together, we arrive at
+
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{sign}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
+&= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\label{eq:appendixZZproof}\notag
+\end{split}
+\end{equation}
+
+where soft is the soft-thresholding function.
+
+\hypertarget{proofdualresidual}{%
+\subsection{Proof of the dual residual}\label{proofdualresidual}}
+
+Here we want to show that \(0 \in \rho\left(Z^{k + 1} - Z^{k}\right)\) which is a direct result of the fact that \(\Omega^{k + 1}\) is the minimizer of the augmented lagrangian and \(0 \in f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1}\).
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z^{k} \right\|_{F}^{2} \right\} \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} + Z^{k + 1} - Z^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k} + \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) + \rho\left(Z^{k + 1} - Z^{k}\right) \\
+  &= \partial f\left(\Omega^{k + 1}\right) + \Lambda^{k + 1} + \rho\left(Z^{k + 1} - Z^{k}\right) \\
+  \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
+\label{eq:appendixdualresidual}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{proofdualopt}{%
+\subsection{Proof of second dual optimality condition}\label{proofdualopt}}
+
+Here we use the primal optimality condition \(\Omega^{k + 1} - Z^{k + 1} = 0\) to show that the second dual optimality condition \(0 \in \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1}\) is always satisfied.
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ g\left(Z^{k + 1}\right) + tr\left[ \Lambda^{k}\left( \Omega^{k + 1} - Z^{k + 1} \right) \right] + \rho\left\| \Omega^{k + 1} - Z^{k + 1} \right\|_{F}^{2} \right\} \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k} - \rho\left(\Omega^{k + 1} - Z^{k + 1}\right) \\
+  &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\label{eq:appendixdualopt}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{taylorsexp}{%
+\subsection{Explanation of majorizing function \eqref{eq:approx}}\label{taylorsexp}}
+
+To see why this particular function was used, consider the Taylor's expansion of \(\rho\left\|A\Omega B - Z^{k} - C\right\|_{F}^{2}/2\):
+
+\begin{equation}
+\begin{split}
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
+\label{eq:taylors}\notag
+\end{split}
+\end{equation}
+
+Note that the gradient and hessian, respectively, are
+
+\begin{equation}
+  \nabla_{\Omega}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C\right\|_{F}^{2} \right\} = \rho BB'\Omega A'A - \rho BZ'A - \rho BC'A
+\label{eq:gradient}\notag
+\end{equation}
+
+\begin{equation}
+\nabla_{\Omega}^{2}\left\{ \frac{\rho}{2}\left\|A\Omega B - Z - C \right\|_{F}^{2} \right\} = \rho\left(A'A \otimes BB' \right)
+\label{eq:hessian}\notag
+\end{equation}
+
+This implies that
+
+\begin{equation}
+\begin{split}
+  \frac{\rho}{2}\left\| A\Omega B - Z^{k} - C \right\|_{F}^{2} &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)'Q\left(\Omega - \Omega^{k} \right) \\
+  &\approx \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho}{2}vec\left(\Omega - \Omega^{k} \right)'Q\left(\Omega - \Omega^{k} \right) \\
+  &+ \frac{\rho}{2}vec\left( \Omega - \Omega^{k}\right)'\left(A'A \otimes BB'\right)vec\left(\Omega - \Omega^{k}\right) \\
+  &+ \rho vec\left(\Omega - \Omega^{k}\right)' vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right) \\
+  &= \frac{\rho}{2}\left\| A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2} + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \\
+  &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right]
+\label{eq:penapprox}\notag
+\end{split}
+\end{equation}
+
+Let us now plug in this equality into our optimization problem that includes the augmented lagrangian:
+
+\begin{equation}
+\begin{split}
+  \hat{\Omega}^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\tilde{L}_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} vec\left(\Omega - \Omega^{k}\right)'\rho Q\left(\Omega - \Omega^{k}\right)/2 \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left(S\Omega\right) - \log\left|\Omega\right| + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \rho\left\|A\Omega^{k} B - Z^{k} - C \right\|_{F}^{2}/2 \end{matrix}\right. \\
+  &+ \left.\begin{matrix} \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 + tr\left[\rho\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right] \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{\begin{matrix}
+ tr\left[\left(S + \rho A'(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B' \right)\Omega\right] \end{matrix}\right. \\
+  &- \left.\begin{matrix} \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \end{matrix}\right\} \\
+  &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{
+ tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \right\} \\
+\label{eq:omegaapprox}\notag
+\end{split}
+\end{equation}
+
+where \(G^{k} = \rho A'(A\Omega^{k}B - Z^{k} - C + \Lambda^{k}/\rho)B'\).
+
+\hypertarget{proofOmegak}{%
+\subsection{Proof of \eqref{eq:Omegak}}\label{proofOmegak}}
+
+We show that the following optimization problem can be solved in closed-form similar to \eqref{eq:appendixomegaproof}.
+
+\begin{equation}
+\Omega^{k + 1} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}
+\label{eq:appendixomegaloglik2}\notag
+\end{equation}
+
+First start by taking the gradient with respect to \(\Omega\):
+
+\begin{equation}
+\begin{split}
+  &\nabla_{\Omega}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\} \\
+  &= 2S - S\circ I_{p} + G^{k} + (G^{k})' - G^{k}\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} \\
+  &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
+\label{eq:appendixomegagradient2}\notag
+\end{split}
+\end{equation}
+
+Note that we need to honor the symmetric constraint given by \(\Omega\). By setting the gradient equal to zero and multiplying all off-diagonal elements by \(1/2\), this simplifies to
+
+\begin{equation}
+S + \frac{1}{2}\left(G^{k} + (G^{k})'\right) - \rho\tau\Omega^{k} = (\Omega^{k + 1})^{-1} - \rho\tau\Omega^{k + 1} \notag
+\end{equation}
+
+We can then decompose using spectral decomposition \(\Omega^{k + 1} = VDV'\) where \(D\) is a diagonal matrix with diagonal elements equal to the eigen values of \(\Omega^{k + 1}\) and \(V\) is the matrix with corresponding eigen vectors as columns.
+
+\begin{equation}
+S + \frac{1}{2}\left(G^{k} + (G^{k})'\right) - \rho\tau\Omega^{k} = VD^{-1}V' - \rho\tau VDV' = V\left(D^{-1} - \rho\tau D\right)V' \notag
+\end{equation}
+
+This equivalence implies that
+
+\begin{equation}
+\phi_{j}\left( D^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\tau\phi_{j}(\Omega^{k + 1}) \notag
+\end{equation}
+
+where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value and \(D^{k} = S + \left(G^{k} + (G^{k})'\right)/2 - \rho\tau\Omega^{k}\). Therefore
+
+\begin{equation}
+\begin{split}
+  &\Rightarrow \rho\tau\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( D^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
+  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(D^{k}) \pm \sqrt{\phi_{j}^{2}(D^{k}) + 4\rho\tau}}{2\rho\tau}
+\end{split}
+\notag
+\end{equation}
+
+In summary, if we decompose \(S + \left(G^{k} + (G^{k})'\right)/2 - \rho\tau\Omega^{k} = VQV'\) then
+
+\begin{equation}
+\Omega^{k + 1} = \frac{1}{2\rho\tau}V\left[ -Q + (Q^{2} + 4\rho\tau I_{p})^{1/2}\right] V'
+\label{eq:appendixomegaproof2}\notag
+\end{equation}
+
+\hypertarget{proofZk}{%
+\subsection{Proof of \eqref{eq:Zk}}\label{proofZk}}
+
+Solve the optimization problem
+
+\begin{equation}
+Z^{k + 1} = \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\}
+\label{eq:appendixZZloglik2}\notag
+\end{equation}
+
+Start by taking the subgradient with respect to \(Z\):
+
+\begin{equation}
+\begin{split}
+  \partial&\left\{ \lambda\left\| Z \right\|_{1} + tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  &= \partial\left\{ \lambda\left\| Z \right\|_{1} \right\} + \nabla_{\Omega}\left\{ tr\left[(\Lambda^{k})'\left(A\Omega^{k + 1}B - Z - C\right)\right] + \frac{\rho}{2}\left\| A\Omega^{k + 1}B - Z - C \right\|_{F}^{2} \right\} \\
+  &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
+\label{eq:appendixZZgradient2}\notag
+\end{split}
+\end{equation}
+
+where \(\mbox{sign(Z)}\) is the elementwise sign operator. By setting the gradient/sub-differential equal to zero, we arrive at the following equivalence:
+
+\begin{equation}
+Z_{ij}^{k + 1} = \frac{1}{\rho}\left( \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} - Sign\left(Z_{ij}^{k + 1}\right)\lambda \right)
+\label{eq:ZZsoftproof2}\notag
+\end{equation}
+
+for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} > 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} > \lambda\alpha \notag
+\end{equation}
+
+\begin{itemize}
+\tightlist
+\item
+  If \(Z_{ij}^{k + 1} < 0\) then
+\end{itemize}
+
+\begin{equation}
+\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} < -\lambda\alpha \notag
+\end{equation}
+
+This implies that \(\mbox{sign}\left(Z_{ij}^{k + 1}\right) = \mbox{sign}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}\right)\). Putting all the pieces together, we arrive at
+
+\begin{equation}
+\begin{split}
+Z_{ij}^{k + 1} &= \frac{1}{\rho}\mbox{sign}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}\right)\left( \left| \rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k} \right| - \lambda \right)_{+} \\
+&= \frac{1}{\rho}\mbox{soft}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}, \lambda\right)
+\label{eq:appendixZZproof2}\notag
+\end{split}
+\end{equation}
+
+where soft is the soft-thresholding function.
+
+\hypertarget{proofstopproof}{%
+\subsection{Proof of \eqref{eq:stopproof}}\label{proofstopproof}}
+
+Here we want to show that \(0 \in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2\) which is a direct result of the fact that \(0 \in \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2\).
+
+\begin{equation}
+\begin{split}
+  0 &\in \partial \left\{ f\left(\Omega^{k + 1}\right) + tr\left[ \Lambda^{k}\left( A\Omega^{k + 1}B - Z^{k} - C \right) \right] + \rho\left\| A\Omega^{k + 1}B - Z^{k} - C \right\|_{F}^{2}/2 \right\} \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 + \rho\left( BB'\Omega^{k + 1}A'A + A'A\Omega^{k + 1}BB' \right)/2 \\
+  &- \rho\left( A'(Z^{k} + C)B' + B(Z^{k} + C)'A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 \\
+  &+ \rho\left( B(B'\Omega^{k + 1}A' - (Z^{k})' - C')A + A'(A\Omega^{k + 1}B - Z^{k} - C)B' \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left( B(\Lambda^{k})'A + A'\Lambda^{k}B' \right)/2 + \rho\left(A'(A\Omega^{k + 1}B - Z^{k + 1} + Z^{k + 1} - Z^{k} - C)B' \right)/2 \\
+  &+ \rho\left(B(B'\Omega^{k + 1}A' - (Z^{k + 1})' + (Z^{k + 1})' - (Z^{k})' - C')A \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left[ B\left((\Lambda^{k})' + \rho(B'\Omega^{k + 1}A' - (Z^{k + 1})' - C') \right)A \right]/2 \\
+  &+ \left[ A'\left(\Lambda^{k} + \rho(A\Omega^{k + 1}B - Z^{k + 1} - c)B \right)B' \right]/2 + \rho\left(B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2 \\
+  &= \partial f\left(\Omega^{k + 1} \right) + \left(B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 + \rho\left(B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2 \\
+  \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2
+\label{eq:appendixstopproof}\notag
+\end{split}
+\end{equation}
+
+\hypertarget{proofpenregression}{%
+\subsection{Proof of no closed-form solution}\label{proofpenregression}}
+
+Here we want to show that the following optimization problem cannot be solved in closed-form.
+
+\begin{equation}
+\hat{\Omega} = \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\}
+\label{eq:penregression2}\notag
+\end{equation}
+
+First start by taking the gradient with respect to \(\Omega\):
+
+\begin{equation}
+\begin{split}
+  \nabla_{\Omega}&\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}\left\|\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right\|_{F}^{2} \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left[\left(\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right)'\left(\mathbb{X}\Omega\Sigma_{xy} - \mathbb{Y}\right) \right] \right\} \\
+  &= \nabla_{\Omega}\left\{ tr\left(S\Omega\right) - \log\left|\Omega\right| + \frac{\lambda}{2}tr\left(\Omega\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}' - 2\Omega\Sigma_{xy}\mathbb{Y}'\mathbb{X} \right) \right\} \\
+  &= 2S - S\circ I_{p} - 2\Omega^{-1} + \Omega^{-1}\circ I_{p} + \lambda\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}' + \lambda\Sigma_{xy}\Sigma_{xy}'\Omega\mathbb{X}'\mathbb{X} \\
+  &- \lambda\mathbb{X}'\mathbb{X}\Omega\Sigma_{xy}\Sigma_{xy}'\circ I_{p} - \Sigma_{xy}\mathbb{Y}'\mathbb{X} - \mathbb{X}'\mathbb{Y}\Sigma_{xy} + \Sigma_{xy}\mathbb{Y}'\mathbb{X}\circ I_{P} \\
+  \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}'\mathbb{X}\hat{\Omega}\Sigma_{xy}\Sigma_{xy}' + \Sigma_{xy}\Sigma_{xy}'\hat{\Omega}\mathbb{X}'\mathbb{X} \right) - \lambda\Sigma_{xy}\mathbb{Y}'\mathbb{X}
+\label{eq:penregressionproof}\notag
+\end{split}
+\end{equation}
+
+Note that we cannot isolate \(\hat{\Omega}\).
+
+\hypertarget{admmsigma-r-package}{%
+\chapter{\texorpdfstring{\texttt{ADMMsigma} R Package}{ADMMsigma R Package}}\label{admmsigma-r-package}}
+
+\texttt{ADMMsigma} is an R package that estimates a penalized precision matrix, often denoted \(\Omega\), via the alternating direction method of multipliers (ADMM) algorithm.
+Though not the fastest estimation method, the ADMM algorithm is easily adaptable and allows for rapid experimentation by the user, which is the primary goal of this package.
+
+The package currently supports a general elastic-net penalty that allows for both ridge and lasso-type penalties as special cases.
+In particular, the algorithm solves the following optimization problem:
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{tr(S\Omega) - \log\det\left(\Omega\right) + \lambda\left[\frac{1 - \alpha}{2}\left\|\Omega\right\|_{F}^{2} + \alpha\left\|\Omega\right\|_{1} \right] \right\} \]
+
+where \(\lambda > 0\), \(0 \leq \alpha \leq 1\) are tuning parameters, \(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm, and we define \(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\).
+
+A list of functions contained in the package can be found below:
+
+\begin{itemize}
+\item
+  \texttt{ADMMsigma()} computes the estimated precision matrix via the ADMM algorithm (ridge, lasso, and elastic-net regularization optional)
+\item
+  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision matrix via closed-form solution
+\item
+  \texttt{plot.ADMMsigma()} produces a heat map or optional line graph for cross validation errors
+\item
+  \texttt{plot.RIDGEsigma()} produces a heat map or optional line graph for cross validation errors
+\end{itemize}
+
+\hypertarget{installation}{%
+\section{Installation}\label{installation}}
 
@@
 
-If there are any issues/bugs, please let me know:
-\href{https://github.com/MGallow/ADMMsigma/issues}{github}. You can also
-contact me via my \href{https://mgallow.github.io/}{website}. Pull
-requests are welcome!
-
-\vspace{0.5cm}
-
-A (possibly incomplete) list of functions contained in the package can
-be found below:
-
-\begin{itemize}
-\item
-  \texttt{ADMMsigma()} computes the estimated precision matrix (ridge,
-  lasso, and elastic-net type regularization optional)
-\item
-  \texttt{RIDGEsigma()} computes the estimated ridge penalized precision
-  matrix via closed-form solution
-\item
-  \texttt{plot.ADMMsigma()} produces a heat map or line graph for cross
-  validation errors
-\item
-  \texttt{plot.RIDGEsigma()} produces a heat map or line graph for cross
-  validation errors
-\end{itemize}
-
-\vspace{1cm}
-
-\hypertarget{usage}{%
-\section{Usage}\label{usage}}
-
-We will first generate data from a sparse, tri-diagonal precision matrix
-and denote it as Omega.
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-
-\CommentTok{# generate data from a sparse matrix first compute covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.7}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{5}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{5}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\NormalTok{S[i, j]}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# print oracle precision matrix (shrinkage might be useful)}
-\NormalTok{(}\DataTypeTok{Omega =} \KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(S), }\DecValTok{3}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##        [,1]   [,2]   [,3]   [,4]   [,5]
-## [1,]  1.961 -1.373  0.000  0.000  0.000
-## [2,] -1.373  2.922 -1.373  0.000  0.000
-## [3,]  0.000 -1.373  2.922 -1.373  0.000
-## [4,]  0.000  0.000 -1.373  2.922 -1.373
-## [5,]  0.000  0.000  0.000 -1.373  1.961
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{5}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{5}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# snap shot of data}
-\KeywordTok{head}\NormalTok{(X)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##            [,1]         [,2]         [,3]       [,4]        [,5]
-## [1,] -0.4311177 -0.217744186  1.276826576 -0.1061308 -0.02363953
-## [2,] -0.0418538  0.304253474  0.688201742 -0.5976510 -1.06758924
-## [3,]  1.1344174  0.004493877 -0.440059159 -0.9793198 -0.86953222
-## [4,] -0.0738241 -0.286438212  0.009577281 -0.7850619 -0.32351261
-## [5,] -0.2905499 -0.906939891 -0.656034183 -0.4324413  0.28516534
-## [6,]  1.3761967  0.276942730 -0.297518545 -0.2634814 -1.35944340
-\end{verbatim}
-
-\vspace{0.5cm}
-
-As described earlier in the report, the maximum likelihood estimator
-(MLE) for Omega is the inverse of the sample precision matrix
-\(S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}\):
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# print inverse of sample precision matrix (perhaps a bad estimate)}
-\KeywordTok{round}\NormalTok{(}\KeywordTok{qr.solve}\NormalTok{(}\KeywordTok{cov}\NormalTok{(X) }\OperatorTok{*}\StringTok{ }\NormalTok{(}\KeywordTok{nrow}\NormalTok{(X) }\OperatorTok{-}\StringTok{ }\DecValTok{1}\NormalTok{)}\OperatorTok{/}\KeywordTok{nrow}\NormalTok{(X)), }\DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.32976 -1.55033  0.22105 -0.08607  0.24309
-## [2,] -1.55033  3.27561 -1.68026 -0.14277  0.18949
-## [3,]  0.22105 -1.68026  3.19897 -1.25158 -0.11016
-## [4,] -0.08607 -0.14277 -1.25158  2.76790 -1.37226
-## [5,]  0.24309  0.18949 -0.11016 -1.37226  2.05377
-\end{verbatim}
-
-\vspace{0.5cm}
-
-However, because Omega (known as the \emph{oracle}) is sparse, a
-shrinkage estimator will perhaps perform better than the sample
-estimator. Below we construct various penalized estimators:
+This package is hosted on Github at \href{https://github.com/MGallow/ADMMsigma}{github.com/MGallow/ADMMsigma}.
+The project website is located at \href{http://mattxgalloway.com/ADMMsigma/}{mattxgalloway.com/ADMMsigma}.
+
+\hypertarget{tutorial}{%
+\section{Tutorial}\label{tutorial}}
+
+By default, \texttt{ADMMsigma} will estimate a penalized precision matrix, \(\Omega\), using the elastic-net penalty and choose the optimal \(\lambda\) and \(\alpha\) tuning parameters.
+The primary function is simply \texttt{ADMMsigma()}.
+The input value \(X\) is an \(n \times p\) data matrix so that there are \(n\) rows each representing an observation and \(p\) columns each representing a unique feauture or variable.
+
+Here, we will use a \(100 \times 5\) data matrix that is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix \(S\).
+A tapered covariance matrix has an inverse - or precision matrix - that is tri-diagonal, which is useful for illustration purposes because the object is sparse (many zero entries) and the shrinkage penalty should prove useful.
 
@@
 ## 
-## Iterations: 162
+## Iterations: 48
 ## 
@@
 
-\textbf{LASSO:}
+We can see that the optimal \(\alpha\) value selected is one. This selection corresponds with a lasso penalty -- a special case of the elastic-net penalty.
+
+We can also explicitly assume sparsity in our estimate rather than let the package decide by restricting the class of penalties to the lasso.
+We do this by simply setting \texttt{alpha\ =\ 1} in our function:
 
@@
 ## 
-## Iterations: 66
+## Iterations: 24
 ## 
@@
 ## 
-## Log-likelihood: -108.41022
+## Log-likelihood: -108.41193
 ## 
@@
 ##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15228 -1.26841  0.00000  0.00000  0.19744
-## [2,] -1.26841  2.78830 -1.31943 -0.08246  0.01018
-## [3,]  0.00000 -1.31943  2.84979 -1.16708 -0.01015
-## [4,]  0.00000 -0.08246 -1.16708  2.49277 -1.18844
-## [5,]  0.19744  0.01018 -0.01015 -1.18844  1.88069
+## [1,]  2.15308 -1.26962  0.00000  0.00000  0.19733
+## [2,] -1.26962  2.79103 -1.32199 -0.08135  0.00978
+## [3,]  0.00000 -1.32199  2.85361 -1.16953 -0.00921
+## [4,]  0.00000 -0.08135 -1.16953  2.49459 -1.18914
+## [5,]  0.19733  0.00978 -0.00921 -1.18914  1.88096
 \end{verbatim}
@@
 
-\textbf{ELASTIC-NET:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# elastic-net penalty (alpha = 0.5)}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \FloatTok{0.5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0.5)
-## 
-## Iterations: 67
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821    0.5
-## 
-## Log-likelihood: -101.13595
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.20031 -1.32471  0.01656 -0.00334  0.21798
-## [2,] -1.32471  2.90659 -1.37599 -0.19084  0.13651
-## [3,]  0.01656 -1.37599  2.92489 -1.12859 -0.12033
-## [4,] -0.00334 -0.19084 -1.12859  2.56559 -1.23472
-## [5,]  0.21798  0.13651 -0.12033 -1.23472  1.94528
-\end{verbatim}
-
-\newpage
-
-\textbf{RIDGE:}
-
-\vspace{0.5cm}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty}
-\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{alpha =} \DecValTok{0}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: ADMMsigma(X = X, alpha = 0)
-## 
-## Iterations: 65
-## 
-## Tuning parameters:
-##       log10(lam)  alpha
-## [1,]      -1.821      0
-## 
-## Log-likelihood: -99.19746
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.18979 -1.31533  0.04515 -0.04090  0.23511
-## [2,] -1.31533  2.90019 -1.37049 -0.22633  0.17808
-## [3,]  0.04515 -1.37049  2.89435 -1.07647 -0.17369
-## [4,] -0.04090 -0.22633 -1.07647  2.55026 -1.22786
-## [5,]  0.23511  0.17808 -0.17369 -1.22786  1.95495
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# ridge penalty no ADMM}
-\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-## Call: RIDGEsigma(X = X, lam = 10^seq(-8, 8, 0.01))
-## 
-## Tuning parameter:
-##       log10(lam)    lam
-## [1,]       -2.17  0.007
-## 
-## Log-likelihood: -109.18156
-## 
-## Omega:
-##          [,1]     [,2]     [,3]     [,4]     [,5]
-## [1,]  2.15416 -1.31185  0.08499 -0.05571  0.22862
-## [2,] -1.31185  2.85605 -1.36677 -0.19650  0.16880
-## [3,]  0.08499 -1.36677  2.82606 -1.06325 -0.14946
-## [4,] -0.05571 -0.19650 -1.06325  2.50721 -1.21935
-## [5,]  0.22862  0.16880 -0.14946 -1.21935  1.92871
-\end{verbatim}
-
-\newpage
-
-This package also has the capability to provide heat maps for the cross
-validation errors. The more bright (white) areas of the heat map pertain
-to more optimal tuning parameters.
+\texttt{ADMMsigma} also has the capability to provide plots for the cross validation errors.
+This allows the user to analyze and manually select the appropriate tuning parameters.
+In the heatmap plot below, the bright, white areas of the heat map correspond to a better tuning parameter selection (low validation error).
+In the line graph, each line corresponds to a different \(\alpha\) tuning parameter.
 
@@
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-8-1.pdf}
-\newpage
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/ADMMsigmapackage1-1}
+
+}
+
+\caption{CV heatmap for ADMMsigma tutorial.}\label{fig:ADMMsigmapackage1}
+\end{figure}
 
@@
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
-\newpage
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/ADMMsigmapackage2-1}
+
+}
+
+\caption{CV line graph for ADMMsigma tutorial.}\label{fig:ADMMsigmapackage2}
+\end{figure}
+
+\vspace{0.5cm}
+
+\texttt{ADMMsigma} has a number of more advanced options such as cross validation criteria, regularization path, and parallel CV that are explained in more detail on the project website at \href{http://mattxgalloway.com/ADMMsigma/}{mattxgalloway.com/ADMMsigma}.
+
+\hypertarget{scpme-r-package}{%
+\chapter{\texorpdfstring{\texttt{SCPME} R Package}{SCPME R Package}}\label{scpme-r-package}}
+
+\texttt{SCPME} is an R package that estimates a penalized precision matrix via a modified alternating direction method of multipliers (ADMM) algorithm as described in \citet{molstad2017shrinking}.
+Specifically, the modified ADMM algorithm solves the following optimization problem:
+
+\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ tr\left(S \Omega\right) - \log\det\left(\Omega\right) + \lambda\left\| A\Omega B - C \right\|_{1} \right\} \]
+
+where \(\lambda > 0\) is a tuning parameter, \(A, B, \mbox{ and } C\) are known, user-specified matrices, and we define \(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\).
+
+This form of penalty leads to many new, interesting, and novel estimators for the precision matrix \(\Omega\).
+Users can construct matrices \(A, B, \mbox{ and } C\) so that emphasis is placed on the sum, absolute value of a \emph{characteristic} of \(\Omega\).
+We will explore a few of these estimators in the tutorial section.
+
+A list of functions contained in the package can be found below:
+
+\begin{itemize}
+\item
+  \texttt{shrink()} computes the estimated precision matrix
+\item
+  \texttt{data\_gen()} data generation function (for convenience)
+\item
+  \texttt{plot.shrink()} produces a heat map or optional line graph for the cross validation errors
+\end{itemize}
+
+\hypertarget{installation-1}{%
+\section{Installation}\label{installation-1}}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# produce CV heat map for RIDGEsigma}
-\NormalTok{RIDGE =}\StringTok{ }\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{))}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
+\CommentTok{# The easiest way to install is from CRAN}
+\KeywordTok{install.packages}\NormalTok{(}\StringTok{"SCPME"}\NormalTok{)}
+
+\CommentTok{# You can also install the development version from GitHub:}
+\CommentTok{# install.packages('devtools')}
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"MGallow/SCPME"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
-
-\newpage
+\vspace{0.5cm}
+
+This package is hosted on Github at \href{https://github.com/MGallow/SCPME}{github.com/MGallow/SCPME}.
+The project website is located at \href{http://mattxgalloway.com/SCPME/}{mattxgalloway.com/SCPME}.
+
+\hypertarget{tutorial-1}{%
+\section{Tutorial}\label{tutorial-1}}
+
+The primary function in the \texttt{SCPME} package is \texttt{shrink()}.
+The input values \(X\) is an \(n \times p\) data matrix so that there are \(n\) rows each representing an observation and \(p\) columns each representing a unique variable and \(Y\) is an \(n \times r\) response matrix where \(r\) is the dimension of the response vector.
+By default, \texttt{SCPME} will estimate \(\Omega\) using a lasso penalty (\(A = I_{p}, B = I_{p}, \mbox{ and } C = 0\)) and choose the optimal \(\lambda\) tuning parameter that minimizes the mean squared prediction error for the regression of the variable \(Y\) on \(X\) (here \(I_{p}\) denotes a \(p\)-dimension identity matrix).
+If \(Y\) is not provided, then tuning parameter selection will be based on the validation likelihood.
+Note that \(\Omega\) (perhaps better denoted here as \(\Omega_{x}\)) will only have meaningful shrinkage unless the data vector \(X \in \mathbb{R^{p}}\) is multi-dimensional (\(p > 1\)).
+
+In this example, the data matrix is \(100 \times 5\) and the response is generated according to the following model:
+
+\[ Y_{i} = \beta'X_{i} + E_{i} \]
+
+where \(E_{i} \sim N\left( 0, 1 \right)\) and \(X_{i}\) is generated from a multivariate normal distribution with mean zero and tapered oracle covariance matrix \(S\).
+A tapered covariance matrix has the property that its inverse - the precision matrix - is tri-diagonal.
+Estimating this oracle precision matrix well and efficiently will be our primary interest.
+In addition, \(\beta\) is randomly generated and sparse.
+The data will be generated using the \texttt{data\_gen()} function contained in the package.
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# produce line graph for CV errors for RIDGEsigma}
-\KeywordTok{plot}\NormalTok{(RIDGE, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
+\KeywordTok{library}\NormalTok{(SCPME)}
+\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+
+\CommentTok{# generate 100 x 5 X data matrix and 100 x 1 Y data matrix}
+\NormalTok{data =}\StringTok{ }\KeywordTok{data_gen}\NormalTok{(}\DataTypeTok{p =} \DecValTok{5}\NormalTok{, }\DataTypeTok{n =} \DecValTok{100}\NormalTok{, }\DataTypeTok{r =} \DecValTok{1}\NormalTok{)}
+
+\CommentTok{# the oracle regression coefficients are sparse}
+\NormalTok{data}\OperatorTok{$}\NormalTok{betas}
 \end{Highlighting}
@@
 
-\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
-
-\hypertarget{details}{%
-\chapter{Details}\label{details}}
-
-Suppose we want to solve the following optimization problem:
-
-\begin{align*}
-  \mbox{minimize } f(x) + g(z) \\
-  \mbox{subject to } Ax + Bz = c
-\end{align*}
-
-where
-\(x \in \mathbb{R}^{n}, z \in \mathbb{R}^{m}, A \in \mathbb{R}^{p \times n}, B \in \mathbb{R}^{p \times m}\),
-and \(c \in \mathbb{R}^{p}\). Following \citet{boyd2011distributed}, the
-optimization problem will be introduced in vector form though we will
-later consider cases where \(x\) and \(z\) are matrices. We will also
-assume \(f\) and \(g\) are convex functions. Optimization problems like
-this arise naturally in several statistics and machine learning
-applications -- particularly regularization methods. For instance, we
-could take \(f\) to be the squared error loss, \(g\) to be the
-\(l_{2}\)-norm, \(c\) to be equal to zero and \(A\) and \(B\) to be
-identity matrices to solve the ridge regression optimization problem.
-
-The \emph{augmented lagrangian} is constructed as follows:
-
-\[ L_{\rho}(x, z, y) = f(x) + g(z) + y^{T}(Ax + Bz - c) + \frac{\rho}{2}\left\| Ax + Bz - c \right\|_{2}^{2} \]
-
-where \(y \in \mathbb{R}^{p}\) is the lagrange multiplier and
-\(\rho > 0\) is a scalar. Clearly any minimizer, \(p^{*}\), under the
-augmented lagrangian is equivalent to that of the lagrangian since any
-feasible point \((x, z)\) satisfies the constraint
-\(\rho\left\| Ax + Bz - c \right\|_{2}^{2}/2 = 0\).
-
-\[ p^{*} = inf\left\{ f(x) + g(z) | Ax + Bz = c \right\} \]
-
-The alternating direction method of multipliers (ADMM) algorithm
-consists of the following repeated iterations:
-
-\begin{align}
-  x^{k + 1} &:= \arg\min_{x}L_{\rho}(x, z^{k}, y^{k}) \\
-  z^{k + 1} &:= \arg\min_{z}L_{\rho}(x^{k + 1}, z, y^{k}) \\
-  y^{k + 1} &:= y^{k} + \rho(Ax^{k + 1} + Bz^{k + 1} - c)
-\end{align}
-
-A more complete introduction to the algorithm -- specifically how it
-arose out of \emph{dual ascent} and \emph{method of multipliers} -- can
-be found in \citet{boyd2011distributed}.
-
-\vspace{1cm}
-
-\hypertarget{admm-algorithm}{%
-\section{ADMM Algorithm}\label{admm-algorithm}}
-
-Now consider the case where \(X_{1}, ..., X_{n}\) are iid
-\(N_{p}(\mu, \Sigma)\) random variables and we are tasked with
-estimating the precision matrix, denoted \(\Omega \equiv \Sigma^{-1}\).
-The maximum likelihood estimator for \(\Omega\) is
-
-\[ \hat{\Omega}_{MLE} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) \right\} \]
-
-where \(S = \sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n\)
-and \(\bar{X}\) is the sample mean. By setting the gradient equal to
-zero, we can show that when the solution exists,
-\(\hat{\Omega}_{MLE} = S^{-1}\).
-
-As in regression settings, we can construct a \emph{penalized}
-likelihood estimator by adding a penalty term,
-\(P\left( \Omega \right)\), to the likelihood:
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + P\left( \Omega \right) \right\} \]
-
-\(P\left( \Omega \right)\) is often of the form
-\(P\left(\Omega \right) = \lambda\|\Omega \|_{F}^{2}\) or
-\(P\left(\Omega \right) = \|\Omega\|_{1}\) where \(\lambda > 0\),
-\(\left\|\cdot \right\|_{F}^{2}\) is the Frobenius norm and we define
-\(\left\|A \right\|_{1} = \sum_{i, j} \left| A_{ij} \right|\). These
-penalties are the ridge and lasso, respectively. We will, instead, take
-\(P\left( \Omega \right) = \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right]\)
-so that the full penalized likelihood is
-
-\[ \hat{\Omega} = \arg\min_{\Omega \in S_{+}^{p}}\left\{ Tr\left(S\Omega\right) - \log \det\left(\Omega \right) + \lambda\left[\frac{1 - \alpha}{2}\left\| \Omega \right|_{F}^{2} + \alpha\left\| \Omega \right\|_{1} \right] \right\} \]
-
-where \(0 \leq \alpha \leq 1\). This \emph{elastic-net} penalty was
-explored by Hui Zou and Trevor Hastie \citep{zou2005regularization} and
-is identical to the penalty used in the popular penalized regression
-package \texttt{glmnet}. Clearly, when \(\alpha = 0\) the elastic-net
-reduces to a ridge-type penalty and when \(\alpha = 1\) it reduces to a
-lasso-type penalty.
-
-By letting \(f\) be equal to the non-penalized likelihood and \(g\)
-equal to \(P\left( \Omega \right)\), our goal is to minimize the full
-augmented lagrangian where the constraint is that \(\Omega - Z\) is
-equal to zero:
-
-\[ L_{\rho}(\Omega, Z, \Lambda) = f\left(\Omega\right) + g\left(Z\right) + Tr\left[\Lambda\left(\Omega - Z\right)\right] + \frac{\rho}{2}\left\|\Omega - Z\right\|_{F}^{2} \]
-
-The ADMM algorithm for estimating the penalized precision matrix in this
-problem is
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align}
-
-\vspace{1cm}
-
-\hypertarget{scaled-form-admm}{%
-\section{Scaled-Form ADMM}\label{scaled-form-admm}}
-
-An alternate form of the ADMM algorithm can constructed by scaling the
-dual variable (\(\Lambda^{k}\)). Let us define
-\(R^{k} = \Omega - Z^{k}\) and \(U^{k} = \Lambda^{k}/\rho\).
-
-\begin{align*}
-  Tr\left[ \Lambda^{k}\left( \Omega - Z^{k} \right) \right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} &= Tr\left[ \Lambda^{k}R^{k} \right] + \frac{\rho}{2}\left\| R^{k} \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + \Lambda^{k}/\rho \right\|_{F}^{2} - \frac{\rho}{2}\left\| \Lambda^{k}/\rho \right\|_{F}^{2} \\
-  &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
-\end{align*}
-
-Therefore, the condensed-form ADMM algorithm can now be written as
-
-\begin{align}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + \frac{\rho}{2}\left\| \Omega - Z^{k} + U^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z + U^{k} \right\|_{F}^{2} \right\} \\
-  U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
-\end{align}
-
-And more generally (in vector form),
-
-\begin{align}
-  x^{k + 1} &= \arg\min_{x}\left\{ f(x) + \frac{\rho}{2}\left\| Ax + Bz^{k} - c + u^{k} \right\|_{2}^{2} \right\} \\
-  z^{k + 1} &= \arg\min_{z}\left\{ g(z) + \frac{\rho}{2}\left\| Ax^{k + 1} + Bz - c + u^{k} \right\|_{2}^{2} \right\} \\
-  u^{k + 1} &= u^{k} + Ax^{k + 1} + Bz^{k + 1} - c
-\end{align}
-
-Note that there are limitations to using this method. Because the dual
-variable is scaled by \(\rho\) (the step size), this form limits one to
-using a constant step size without making further adjustments to
-\(U^{k}\). It has been shown in the literature that a dynamic step size
-can significantly reduce the number of iterations required for
-convergence.
-
-\vspace{1cm}
-
-\hypertarget{algorithm}{%
-\section{Algorithm}\label{algorithm}}
-
-\begin{align*}
-  \Omega^{k + 1} &= \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  Z^{k + 1} &= \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
-\end{align*}
-
-\vspace{1cm}
-
-Initialize \(Z^{0}, \Lambda^{0}\), and \(\rho\). Iterate the following
-three steps until convergence:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\) via spectral
-  decomposition.
-\end{enumerate}
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + \left( Q^{2} + 4\rho I_{p} \right)^{1/2} \right]V^{T} \]
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Elementwise soft-thresholding for all \(i = 1,..., p\) and
-  \(j = 1,..., p\).
-\end{enumerate}
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Update \(\Lambda^{k + 1}\).
-\end{enumerate}
-
-\[ \Lambda^{k + 1} = \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right) \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-1}{%
-\subsection{Proof of (1):}\label{proof-of-1}}
-
-\[ \Omega^{k + 1} = \arg\min_{\Omega}\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \nabla_{\Omega}&\left\{ Tr\left(S\Omega\right) - \log\det\left(\Omega\right) + Tr\left[\Lambda^{k}\left(\Omega - Z^{k}\right)\right] + \frac{\rho}{2}\left\| \Omega - Z^{k} \right\|_{F}^{2} \right\} \\
-  &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
-\end{align*}
-
-Set the gradient equal to zero and decompose \(\Omega = VDV^{T}\) where
-\(D\) is a diagonal matrix with diagonal elements equal to the eigen
-values of \(\Omega\) and \(V\) is the matrix with corresponding eigen
-vectors as columns.
-
-\[ S + \Lambda^{k} - \rho Z^{k} = \Omega^{-1} - \rho \Omega = VD^{-1}V^{T} - \rho VDV^{T} =  V\left(D^{-1} - \rho D\right)V^{T} \]
-
-This equivalence implies that
-
-\[ \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right) = \frac{1}{\phi_{j}(\Omega^{k + 1})} - \rho\phi_{j}(\Omega^{k + 1}) \]
-
-where \(\phi_{j}(\cdot)\) is the \(j\)th eigen value.
-
-\begin{align*}
-  &\Rightarrow \rho\phi_{j}^{2}(\Omega^{k + 1}) + \phi_{j}\left( S + \Lambda^{k} - \rho Z^{k} \right)\phi_{j}(\Omega^{k + 1}) - 1 = 0 \\
-  &\Rightarrow \phi_{j}(\Omega^{k + 1}) = \frac{-\phi_{j}(S + \Lambda^{k} - \rho Z^{k}) \pm \sqrt{\phi_{j}^{2}(S + \Lambda^{k} - \rho Z^{k}) + 4\rho}}{2\rho}
-\end{align*}
-
-In summary, if we decompose \(S + \Lambda^{k} - \rho Z^{k} = VQV^{T}\)
-then
-
-\[ \Omega^{k + 1} = \frac{1}{2\rho}V\left[ -Q + (Q^{2} + 4\rho I_{p})^{1/2}\right] V^{T} \]
-
-\vspace{1cm}
-
-\hypertarget{proof-of-2}{%
-\subsection{Proof of (2)}\label{proof-of-2}}
-
-\[ Z^{k + 1} = \arg\min_{Z}\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \]
-
-\begin{align*}
-  \partial&\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right] + \frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \partial\left\{ \lambda\left[ \frac{1 - \alpha}{2}\left\| Z \right\|_{F}^{2} + \alpha\left\| Z \right\|_{1} \right] + Tr\left[\Lambda^{k}\left(\Omega^{k + 1} - Z\right)\right]\right\} + \nabla_{\Omega}\left\{\frac{\rho}{2}\left\| \Omega^{k + 1} - Z \right\|_{F}^{2} \right\} \\
-  &= \lambda(1 - \alpha)Z + Sign(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
-\end{align*}
-
-where \(Sign(Z)\) is the elementwise Sign operator. By setting the
-gradient/sub-differential equal to zero, we arrive at the following
-equivalence:
-
-\[ Z_{ij} = \frac{1}{\lambda(1 - \alpha) + \rho}\left( \rho \Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} - Sign(Z_{ij})\lambda\alpha \right) \]
-
-for all \(i = 1,..., p\) and \(j = 1,..., p\). We observe two scenarios:
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} > 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} > \lambda\alpha \]
-
-\begin{itemize}
-\tightlist
-\item
-  If \(Z_{ij} < 0\) then
-\end{itemize}
-
-\[ \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} < -\lambda\alpha \]
-
-This implies that
-\(Sign(Z_{ij}) = Sign(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k})\).
-Putting all the pieces together, we arrive at
-
-\begin{align*}
-Z_{ij}^{k + 1} &= \frac{1}{\lambda(1 - \alpha) + \rho}Sign\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}\right)\left( \left| \rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k} \right| - \lambda\alpha \right)_{+} \\
-&= \frac{1}{\lambda(1 - \alpha) + \rho}Soft\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
-\end{align*}
-
-where \(Soft\) is the soft-thresholding function.
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{simulations}{%
-\chapter{Simulations}\label{simulations}}
-
-In the simulations below we generated data from a number of oracle
-precision matrices with various structures. For each data-generating
-procedure, the \texttt{ADMMsigma()} function was run using 5-fold cross
-validation. After 20 replications, the cross validation errors were
-totalled and the optimal tuning parameters were selected (results in the
-top figure). These results are compared with the Kullback Leibler (KL)
-losses between the estimates and the oracle precision matrix (bottom
-figure). We can see below that our cross validation procedure choosing
-tuning parameters close to the optimal parameters.
-
-\newpage
-
-\hypertarget{compound-symmetric-p-100-n-50}{%
-\subsection{Compound Symmetric: P = 100, N =
-50}\label{compound-symmetric-p-100-n-50}}
-
-\includegraphics{images/compound_N50_P100.png}
+\begin{verbatim}
+##             [,1]
+## [1,] -0.25065233
+## [2,]  0.00000000
+## [3,]  0.69707555
+## [4,]  0.03153231
+## [5,]  0.00000000
+\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100} \OperatorTok{*}\StringTok{ }\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
+\CommentTok{# shrink sum absolute entries in omega}
+\KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y)}
 \end{Highlighting}
@@
 
-\newpage
-
-\hypertarget{compound-symmetric-p-10-n-1000}{%
-\subsection{Compound Symmetric: P = 10, N =
-1000}\label{compound-symmetric-p-10-n-1000}}
-
-\includegraphics{images/compound_N1000_P10.png}
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y)
+## 
+## Iterations: 37
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -1.163  0.069
+## 
+## Log-likelihood: -178.20154
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  1.60847 -0.73553 -0.14094 -0.04329 -0.11730
+## [2,] -0.73553  1.66045 -0.52579 -0.03576 -0.03342
+## [3,] -0.14094 -0.52579  1.73410 -0.85121 -0.07332
+## [4,] -0.04329 -0.03576 -0.85121  2.02541 -0.93612
+## [5,] -0.11730 -0.03342 -0.07332 -0.93612  1.62397
+\end{verbatim}
+
+\vspace{0.5cm}
+
+Notice here that the estimated precision matrix is \emph{not} sparse.
+This is due to the fact that our cross validation criteria is the mean-squared prediction error.
+We can estimate a new precision matrix using the validation likelihood as the cross validation criteria with the following command:
 
@@
 \begin{Highlighting}[]
-\CommentTok{# oracle precision matrix}
-\NormalTok{Omega =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\FloatTok{0.9}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{)}
-\KeywordTok{diag}\NormalTok{(}\DataTypeTok{Omega =} \DecValTok{1}\NormalTok{)}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\KeywordTok{qr.solve}\NormalTok{(Omega)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10} \OperatorTok{*}\StringTok{ }\DecValTok{1000}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
+\CommentTok{# shrink sum absolute entries in omega}
+\KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{crit.cv =} \StringTok{"loglik"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\newpage
-
-\hypertarget{dense-p-100-n-50}{%
-\subsection{Dense: P = 100, N = 50}\label{dense-p-100-n-50}}
-
-\includegraphics{images/repsKLdenseQR_N50_P100.png}
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, crit.cv = "loglik")
+## 
+## Iterations: 51
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -2.163  0.007
+## 
+## Log-likelihood: -120.02858
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.11926 -1.17294 -0.13784 -0.00678 -0.20014
+## [2,] -1.17294  2.28420 -0.81629  0.00009 -0.00001
+## [3,] -0.13784 -0.81629  2.45520 -1.42117  0.01650
+## [4,] -0.00678  0.00009 -1.42117  3.09526 -1.56839
+## [5,] -0.20014 -0.00001  0.01650 -1.56839  2.24703
+\end{verbatim}
+
+\vspace{0.5cm}
+
+All of the estimators so far have used a lasso penalty that penalizes the sum of the absolute value of all the entries in \(\Omega\) (\(A = I_{p}, B = I_{p}, \mbox{ and } C = 0\)).
+In effect, this penalty embeds an assumption in our estimate that the true population precision matrix, \(\Omega\), is sparse.
+The flexibility of the penalty described in \citet{molstad2017shrinking} allows us to make other assumptions as well.
+For instance, in the penalty we could set \(A = I_{p}, B = \Sigma_{xy}\) where \(\Sigma_{xy}\) is the covariance matrix of \(X\) and \(Y\), and \(C = 0\).
+In which case our penalty function
+
+\[P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\Sigma_{xy} \right\|_{1} = \lambda\left\| \beta \right\|_{1} \]
+
+This objective function estimates an \(\Omega\) via the marginal log-likelihood of \(X\) under the assumption that the forward regression coefficient \(\beta\) is sparse (recall that \(\beta \equiv \Omega\Sigma_{xy}\)).
+Of course, in practice, we do not know the true covariance matrix \(\Sigma_{xy}\) but we might consider using the sample estimate \(\hat{\Sigma}_{xy} = \sum_{i = 1}^{n}\left(X_{i} - \bar{X}\right)\left(Y_{i} - \bar{Y}\right)'/n\).
 
@@
 \begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{100} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{100}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
+\CommentTok{# assume sparsity in beta}
+\NormalTok{lam_max =}\StringTok{ }\KeywordTok{max}\NormalTok{(}\KeywordTok{abs}\NormalTok{(}\KeywordTok{crossprod}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y)))}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\DataTypeTok{lam.max =}\NormalTok{ lam_max, }
+    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
 \end{Highlighting}
@@
 
-\newpage
-
-\hypertarget{dense-p-10-n-50}{%
-\subsection{Dense: P = 10, N = 50}\label{dense-p-10-n-50}}
-
-\includegraphics{images/repsKLdense_N50_P10.png}
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, B = cov(data$X, data$Y), nlam = 20, 
+##     lam.max = lam_max)
+## 
+## Iterations: 84
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]      -0.167  0.681
+## 
+## Log-likelihood: -133.98097
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  2.12467 -1.20016 -0.01149  0.01660 -0.20424
+## [2,] -1.20016  2.28202 -0.70370  0.03047 -0.01211
+## [3,] -0.01149 -0.70370  2.09284 -1.47505  0.01020
+## [4,]  0.01660  0.03047 -1.47505  2.86829 -1.45784
+## [5,] -0.20424 -0.01211  0.01020 -1.45784  2.18752
+\end{verbatim}
+
+Note that we specified the maximum \texttt{lam} value in the previous function to expand the tuning parameter grid.
+With these settings, the augmented ADMM algorithm also solves for the estimated \(\beta\) coefficient matrix simultaneously:
 
@@
 \begin{Highlighting}[]
-\CommentTok{# generate eigen values}
-\NormalTok{eigen =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{1000}\NormalTok{, }\DecValTok{5}\NormalTok{, }\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{, }\DecValTok{10} \OperatorTok{-}\StringTok{ }\DecValTok{5}\NormalTok{)))}
-
-\CommentTok{# randomly generate orthogonal basis (via QR)}
-\NormalTok{Q =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{10}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{10}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr }\OperatorTok{%>%}\StringTok{ }\NormalTok{qr.Q}
-
-\CommentTok{# generate covariance matrix}
-\NormalTok{S =}\StringTok{ }\NormalTok{Q }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(eigen) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(Q)}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
+\CommentTok{# print estimated beta matrix}
+\NormalTok{shrink}\OperatorTok{$}\NormalTok{Z}
 \end{Highlighting}
@@
 
-\newpage
-
-\hypertarget{tridiagonal-p-100-n-50}{%
-\subsection{Tridiagonal: P = 100, N = 50}\label{tridiagonal-p-100-n-50}}
-
-\includegraphics{images/repsKLtridiag_N50_P100.png}
+\begin{verbatim}
+##            [,1]
+## [1,] 0.00000000
+## [2,] 0.00000000
+## [3,] 0.42221120
+## [4,] 0.04782093
+## [5,] 0.00000000
+\end{verbatim}
+
+\vspace{0.5cm}
+
+Another possible penalty is to set \(B = \left[ \Sigma_{xy}, I_{p} \right]\) so that the identity matrix is appended to the covariance matrix of \(X\) and \(Y\).
+That is, the penalty \(P\), is constructed as
+
+\[ P_{\lambda}\left(\Omega \right) = \lambda\left\| A\Omega B - C \right\|_{1} = \lambda\left\| \Omega\left[\Sigma_{xy}, I_{p}\right] \right\|_{1} = \lambda\left\| \beta \right\|_{1} + \lambda\left\| \Omega \right\|_{1} \]
+
+In this case, we are equally penalizing the sum, absolute values of entries in \(\beta\) \emph{and} \(\Omega\) which embeds an assumption that \(\beta\) and \(\Omega\) are both sparse.
 
@@
 \begin{Highlighting}[]
-\CommentTok{# generate covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{)\{}
-\NormalTok{    S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j)}
-\NormalTok{  \}}
-\NormalTok{\}}
-
-\CommentTok{# generate data}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{10}\OperatorTok{*}\DecValTok{50}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{50}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{10}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
+\CommentTok{# assume sparsity in beta AND omega}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }
+    \DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
 \end{Highlighting}
@@
 
-\hypertarget{benchmark}{%
-\chapter{Benchmark}\label{benchmark}}
-
-Below we benchmark the various functions contained in
-\texttt{ADMMsigma}. We can see that \texttt{ADMMsigma} (at the default
-tolerance) offers comparable computation time to the popular
-\texttt{glasso} R package.
-
-\hypertarget{computer-specs}{%
-\subsection{Computer Specs:}\label{computer-specs}}
-
-\begin{itemize}
-\tightlist
-\item
-  MacBook Pro (Late 2016)
-\item
-  Processor: 2.9 GHz Intel Core i5
-\item
-  Memory: 8GB 2133 MHz
-\item
-  Graphics: Intel Iris Graphics 550
-\end{itemize}
-
-\vspace{0.5cm}
+\begin{verbatim}
+## 
+## Call: shrink(X = data$X, Y = data$Y, B = cbind(cov(data$X, data$Y), 
+##     diag(ncol(data$X))), nlam = 20, lam.max = 10, lam.min.ratio = 1e-04)
+## 
+## Iterations: 46
+## 
+## Tuning parameters:
+##       log10(lam)    lam
+## [1,]       0.368  2.336
+## 
+## Log-likelihood: -624.54758
+## 
+## Omega:
+##          [,1]     [,2]     [,3]     [,4]     [,5]
+## [1,]  0.26376 -0.00003 -0.00015 -0.00010 -0.00005
+## [2,] -0.00003  0.24002 -0.00017 -0.00012 -0.00006
+## [3,] -0.00015 -0.00017  0.19066 -0.00516 -0.00020
+## [4,] -0.00010 -0.00012 -0.00516  0.20362 -0.00014
+## [5,] -0.00005 -0.00006 -0.00020 -0.00014  0.22750
+\end{verbatim}
 
@@
 \begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(ADMMsigma)}
-\KeywordTok{library}\NormalTok{(microbenchmark)}
-
-\CommentTok{# generate data from tri-diagonal (sparse) matrix compute covariance matrix}
-\CommentTok{# (can confirm inverse is tri-diagonal)}
-\NormalTok{S =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DataTypeTok{nrow =} \DecValTok{100}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-
-\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-    \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\DecValTok{100}\NormalTok{) \{}
-\NormalTok{        S[i, j] =}\StringTok{ }\FloatTok{0.7}\OperatorTok{^}\NormalTok{(}\KeywordTok{abs}\NormalTok{(i }\OperatorTok{-}\StringTok{ }\NormalTok{j))}
-\NormalTok{    \}}
-\NormalTok{\}}
-
-\CommentTok{# generate 1000 x 100 matrix with rows drawn from iid N_p(0, S)}
-\KeywordTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-\NormalTok{Z =}\StringTok{ }\KeywordTok{matrix}\NormalTok{(}\KeywordTok{rnorm}\NormalTok{(}\DecValTok{1000} \OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{), }\DataTypeTok{nrow =} \DecValTok{1000}\NormalTok{, }\DataTypeTok{ncol =} \DecValTok{100}\NormalTok{)}
-\NormalTok{out =}\StringTok{ }\KeywordTok{eigen}\NormalTok{(S, }\DataTypeTok{symmetric =} \OtherTok{TRUE}\NormalTok{)}
-\NormalTok{S.sqrt =}\StringTok{ }\NormalTok{out}\OperatorTok{$}\NormalTok{vectors }\OperatorTok{%*%}\StringTok{ }\KeywordTok{diag}\NormalTok{(out}\OperatorTok{$}\NormalTok{values}\OperatorTok{^}\FloatTok{0.5}\NormalTok{) }\OperatorTok{%*%}\StringTok{ }\KeywordTok{t}\NormalTok{(out}\OperatorTok{$}\NormalTok{vectors)}
-\NormalTok{X =}\StringTok{ }\NormalTok{Z }\OperatorTok{%*%}\StringTok{ }\NormalTok{S.sqrt}
-
-\CommentTok{# glasso (for comparison)}
-\KeywordTok{microbenchmark}\NormalTok{(glasso}\OperatorTok{::}\KeywordTok{glasso}\NormalTok{(}\DataTypeTok{s =}\NormalTok{ S, }\DataTypeTok{rho =} \FloatTok{0.1}\NormalTok{))}
+\CommentTok{# print estimated beta}
+\NormalTok{shrink}\OperatorTok{$}\NormalTok{Z[, }\DecValTok{1}\NormalTok{, drop =}\StringTok{ }\OtherTok{FALSE}\NormalTok{]}
 \end{Highlighting}
@@
 \begin{verbatim}
-## Unit: milliseconds
-##                              expr      min       lq     mean   median
-##  glasso::glasso(s = S, rho = 0.1) 49.46673 53.37757 58.35196 55.90935
-##        uq      max neval
-##  60.77517 92.68082   100
+##            [,1]
+## [1,] 0.06389361
+## [2,] 0.08542992
+## [3,] 0.14200713
+## [4,] 0.12357129
+## [5,] 0.09958374
 \end{verbatim}
+
+\vspace{0.5cm}
+
+\texttt{SCPME} also has the capability to provide plots (heatmaps and line graphs) for the cross validation errors.
+In the heatmap plot below, the more bright, white areas correspond to a better tuning parameter selection (lower cross validation error).
+
+\vspace{0.5cm}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - default tolerance}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-04}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
+\CommentTok{# produce CV heat map}
+\KeywordTok{plot}\NormalTok{(shrink, }\DataTypeTok{type =} \StringTok{"heatmap"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-04, tol.rel = 1e-04,      trace = "none")
-##      min       lq     mean   median       uq      max neval
-##  77.2134 83.51351 89.71565 85.37738 94.37814 126.0049   100
-\end{verbatim}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/SCPMEpackage1-1}
+
+}
+
+\caption{CV heatmap for SCPME tutorial}\label{fig:SCPMEpackage1}
+\end{figure}
 
@@
 \begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma - tolerance 1e-8}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(}\DataTypeTok{S =}\NormalTok{ S, }\DataTypeTok{lam =} \FloatTok{0.1}\NormalTok{, }\DataTypeTok{alpha =} \DecValTok{1}\NormalTok{, }\DataTypeTok{tol.abs =} \FloatTok{1e-08}\NormalTok{, }\DataTypeTok{tol.rel =} \FloatTok{1e-08}\NormalTok{, }
-    \DataTypeTok{trace =} \StringTok{"none"}\NormalTok{))}
+\CommentTok{# produce line graph}
+\KeywordTok{plot}\NormalTok{(shrink, }\DataTypeTok{type =} \StringTok{"line"}\NormalTok{)}
 \end{Highlighting}
@@
 
-\begin{verbatim}
-## Unit: milliseconds
-##                                                                                           expr
-##  ADMMsigma(S = S, lam = 0.1, alpha = 1, tol.abs = 1e-08, tol.rel = 1e-08,      trace = "none")
-##       min       lq     mean   median       uq      max neval
-##  258.5389 261.5402 272.3741 267.8829 274.7276 353.4726   100
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - default parameter grid}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                          expr      min       lq     mean   median       uq
-##  ADMMsigma(X, trace = "none") 8.338241 8.341611 8.536446 8.472933 8.515822
-##       max neval
-##  9.013621     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma parallel CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{cores =} \DecValTok{3}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                     expr      min       lq     mean
-##  ADMMsigma(X, cores = 3, trace = "none") 9.285137 9.315978 9.470666
-##   median       uq      max neval
-##  9.40943 9.426579 9.916207     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark ADMMsigma CV - likelihood convergence criteria}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{ADMMsigma}\NormalTok{(X, }\DataTypeTok{crit =} \StringTok{"loglik"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                           expr      min       lq     mean
-##  ADMMsigma(X, crit = "loglik", trace = "none") 7.028816 7.121599 7.185927
-##    median       uq      max neval
-##  7.181803 7.277249 7.320166     5
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# benchmark RIDGEsigma CV}
-\KeywordTok{microbenchmark}\NormalTok{(}\KeywordTok{RIDGEsigma}\NormalTok{(X, }\DataTypeTok{lam =} \DecValTok{10}\OperatorTok{^}\KeywordTok{seq}\NormalTok{(}\OperatorTok{-}\DecValTok{8}\NormalTok{, }\DecValTok{8}\NormalTok{, }\FloatTok{0.01}\NormalTok{), }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{), }\DataTypeTok{times =} \DecValTok{5}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Unit: seconds
-##                                                      expr      min
-##  RIDGEsigma(X, lam = 10^seq(-8, 8, 0.01), trace = "none") 12.22374
-##        lq     mean   median       uq      max neval
-##  12.37326 12.93705 13.01892 13.04356 14.02577     5
-\end{verbatim}
-
-\bibliography{lib.bib}
+\begin{figure}
+
+{\centering \includegraphics[width=0.8\linewidth,]{Manuscript_files/figure-latex/SCPMEpackage2-1}
+
+}
+
+\caption{CV line graph for SCPME tutorial}\label{fig:SCPMEpackage2}
+\end{figure}
+
+\vspace{0.5cm}
+
+\texttt{SCPME} has a number of more advanced options including alternative convergence criteria and parallel CV that are explained in detail on the project website at \href{http://mattxgalloway.com/SCPME/}{mattxgalloway.com/SCPME}.
+
+\bibliography{lib.bib,packages.bib}
 

### 2019-04-22 03-SCPME.Rmd
minor adjustments

--- 2019-04-21 03-SCPME.Rmd
@@
 \newpage
-```{r, eval = T, echo = F, fig.cap = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)"}
+```{r, eval = T, echo = F, fig.cap = "Average model error for dimension p = 150."}
 
 # ME table (N = 100, sparse = 0.5, sigma = "tridiag", P = 150, R = 10)
-sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% group_by(model) %>% summarise(error = mean(Error), sd = sd(Error)) %>% arrange(error) %>% pander(caption = "ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)")
+sim6 %>% filter(N == 100, sparse == 0.5, sigma == "tridiag", P == 150, R == 10) %>% rename(Model = model, error = Error) %>% group_by(Model) %>% summarise(Error = mean(error), SD = sd(error)) %>% arrange(Error) %>% pander(caption = "Average model error for dimension p = 150.")
 

### 2019-04-22 index.Rmd
minor adjustments

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, out.width = "85%", fig.align = "center", out.extra = "")
+knitr::opts_chunk$set(echo = TRUE, cache = FALSE, tidy = TRUE, tidy.opts = list(width.cutoff = 60), out.width = "85%", fig.align = "center", out.extra = "")
 
@@
 ```
+
+# Preface {-}
+
+I would like to thank my advisor Professor Adam Rothman for his guidance and support this past year.
+His enthusiasm towards this research area is ultimately what got me interested and I truly enjoyed having the opportunity to learn from him.
+
+My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.

### 2019-04-22 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

@@
 \usepackage{amsthm}
+\usepackage{amsmath}
 \usepackage{fancyhdr} % Required for custom headers
@@
 \usepackage{extramarks} % Required for headers and footers
-\usepackage{graphicx}
+\usepackage{graphicx} % Required for knitr::include_graphics
 \makeatletter
@@
 % \pagestyle{empty}
-\usepackage[left]{lineno} % line number package
-\linenumbers % line number command
+% \usepackage[left]{lineno} % line number package
+% \linenumbers % line number command
 \usepackage[]{natbib}
@@
 \author{Matt Galloway}
-\date{2019-04-21}
+\date{2019-04-22}
 
@@
 }
+\hypertarget{preface}{%
+\chapter*{Preface}\label{preface}}
+
+I would like to thank my advisor Professor Adam Rothman for his guidance and support this past year.
+His enthusiasm towards this research area is ultimately what got me interested and I truly enjoyed having the opportunity to learn from him.
+
+My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.
+
 \hypertarget{intro}{%
@@
 \begin{longtable}[]{@{}ccc@{}}
-\caption{ME by P (N = 100, R = 10, sparse = 0.5, sigma = tridiag)
+\caption{Average model error for dimension p = 150.
 \vspace{0.5cm}}\tabularnewline
@@
 \begin{minipage}[b]{0.14\columnwidth}\centering
-model\strut
+Model\strut
 \end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
-error\strut
+Error\strut
 \end{minipage} & \begin{minipage}[b]{0.11\columnwidth}\centering
-sd\strut
+SD\strut
 \end{minipage}\tabularnewline
@@
 \NormalTok{lam_max =}\StringTok{ }\KeywordTok{max}\NormalTok{(}\KeywordTok{abs}\NormalTok{(}\KeywordTok{crossprod}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y)))}
-\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\DataTypeTok{lam.max =}\NormalTok{ lam_max, }
-    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }
+    \DataTypeTok{lam.max =}\NormalTok{ lam_max, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
 \end{Highlighting}
@@
 \CommentTok{# assume sparsity in beta AND omega}
-\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }
-    \DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }\DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
+\NormalTok{(}\DataTypeTok{shrink =} \KeywordTok{shrink}\NormalTok{(}\DataTypeTok{X =}\NormalTok{ data}\OperatorTok{$}\NormalTok{X, }\DataTypeTok{Y =}\NormalTok{ data}\OperatorTok{$}\NormalTok{Y, }\DataTypeTok{B =} \KeywordTok{cbind}\NormalTok{(}\KeywordTok{cov}\NormalTok{(data}\OperatorTok{$}\NormalTok{X, }
+\NormalTok{    data}\OperatorTok{$}\NormalTok{Y), }\KeywordTok{diag}\NormalTok{(}\KeywordTok{ncol}\NormalTok{(data}\OperatorTok{$}\NormalTok{X))), }\DataTypeTok{lam.max =} \DecValTok{10}\NormalTok{, }\DataTypeTok{lam.min.ratio =} \FloatTok{1e-04}\NormalTok{, }
+    \DataTypeTok{nlam =} \DecValTok{20}\NormalTok{))}
 \end{Highlighting}

### 2019-04-28 03-SCPME.Rmd
fixed split rendering bug

@@
 
-\begin{align}
+\begin{equation}
+\begin{split}
   \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
-\end{align}
+\end{split}
+(#\eq:augmentedprecision)
+\end{equation}
 
@@
   &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
+\end{split}
 (\#eq:approx)
-\end{split}
 \end{equation}
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+\end{split}
 (\#eq:augADMM)\notag
-\end{split}
 \end{equation}
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
+\end{split}
 (\#eq:scpmestopping)\notag
-\end{split}
 \end{equation}
@@
   &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
+\end{split}
 (\#eq:partialjointloglik)\notag
-\end{split}
 \end{equation}
@@
   &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
+\end{split}
 (\#eq:omegajointloglik)\notag
-\end{split}
 \end{equation}

### 2019-04-28 05-appendix.Rmd
fixed split rendering bug

@@
   &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
+\end{split}
 (\#eq:appendixomegagradient)\notag
-\end{split}
 \end{equation}
@@
   &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
+\end{split}
 (\#eq:appendixZZgradient)\notag
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\end{split}
 (\#eq:appendixZZproof)\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
+\end{split}
 (\#eq:appendixdualresidual)\notag
-\end{split}
 \end{equation}
@@
   &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\end{split}
 (\#eq:appendixdualopt)\notag
-\end{split}
 \end{equation}
@@
   &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
+\end{split}
 (\#eq:taylors)\notag
-\end{split}
 \end{equation}
@@
   &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right]
+\end{split}
 (\#eq:penapprox)\notag
-\end{split}
 \end{equation}
@@
  tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \right\} \\
+\end{split}
 (\#eq:omegaapprox)\notag
-\end{split}
 \end{equation}
@@
   &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
+\end{split}
 (\#eq:appendixomegagradient2)\notag
-\end{split}
 \end{equation}
@@
   &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
+\end{split}
 (\#eq:appendixZZgradient2)\notag
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\rho}\mbox{soft}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}, \lambda\right)
+\end{split}
 (\#eq:appendixZZproof2)\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2
+\end{split}
 (\#eq:appendixstopproof)\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}'\mathbb{X}\hat{\Omega}\Sigma_{xy}\Sigma_{xy}' + \Sigma_{xy}\Sigma_{xy}'\hat{\Omega}\mathbb{X}'\mathbb{X} \right) - \lambda\Sigma_{xy}\mathbb{Y}'\mathbb{X}
+\end{split}
 (\#eq:penregressionproof)\notag
-\end{split}
 \end{equation}

### 2019-04-29 02-PME.Rmd
fixed split rendering bug
another rendering bug fix

@@
   &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
+\end{split}
 (\#eq:partialmaxloglik)\notag
-\end{split}
 \end{equation}
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+\end{split}
 (\#eq:ADMMorig)
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\end{split}
 (\#eq:ZZalgo)
-\end{split}
 \end{equation}
@@
   &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
+\end{split}
 (\#eq:scaled)\notag
-\end{split}
 \end{equation}
@@
   U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
+\end{split}
 (\#eq:ADMMscaled)
-\end{split}
 \end{equation}
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
+\end{split}
 (\#eq:admmstopping)\notag
-\end{split}
 \end{equation}

### 2019-05-01 01-intro.Rmd
bug fixes/typos

@@
 The two have published work on indirect multivariate linear regression (@molstad2016indirect) and classification with matrix-valued predictors (@molstad2018penalized) but the focus of this manuscript is their 2017 paper titled *Shrinking Characteristics of Precision Matrix Estimators* (@molstad2017shrinking).
-In it, they outline a framework to estimate *characteristics* of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
+In it, they outline a framework to shrink a *characteristic* of a precision matrix - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
 They write in their manuscript that "to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated...

### 2019-05-01 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

@@
 \author{Matt Galloway}
-\date{2019-04-22}
+\date{2019-05-01}
 
@@
 
-My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school's challenges extend far beyond the classroom and I'm so lucky to have you by my side.
+My parents also deserve a note of appreciation and thanks -- one probably much longer than this. Graduate school would not have been possible without their love and encouragement.
 
@@
 The two have published work on indirect multivariate linear regression (\citet{molstad2016indirect}) and classification with matrix-valued predictors (\citet{molstad2018penalized}) but the focus of this manuscript is their 2017 paper titled \emph{Shrinking Characteristics of Precision Matrix Estimators} (\citet{molstad2017shrinking}).
-In it, they outline a framework to estimate \emph{characteristics} of precision matrices - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
+In it, they outline a framework to shrink a \emph{characteristic} of a precision matrix - a concept that exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature.
 They write in their manuscript that ``to fit many predictive models, only a characteristic of the population precision matrix needs to be estimated\ldots{} In binary linear discriminant analysis, the population precision matrix is needed for prediction only through the product of the precision matrix and the difference between the two conditional distribution mean vectors.'' The purpose of the research detailed here began with the desire to expand on this concept and to explore avenues that were mentioned but were not further investigated.
@@
   &= \frac{n}{2}\log\left| \Omega \right| - \frac{n}{2}tr\left( S\Omega \right)
+\end{split}
 \label{eq:partialmaxloglik}\notag
-\end{split}
 \end{equation}
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left( \Omega^{k + 1} - Z^{k + 1} \right)
+\end{split}
 \label{eq:ADMMorig}
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\end{split}
 \label{eq:ZZalgo}
-\end{split}
 \end{equation}
@@
   &= \frac{\rho}{2}\left\| R^{k} + U^{k} \right\|_{F}^{2} - \frac{\rho}{2}\left\| U^{k} \right\|_{F}^{2}
+\end{split}
 \label{eq:scaled}\notag
-\end{split}
 \end{equation}
@@
   U^{k + 1} &= U^{k} + \Omega^{k + 1} - Z^{k + 1}
+\end{split}
 \label{eq:ADMMscaled}
-\end{split}
 \end{equation}
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \Lambda^{k + 1} \right\|_{F}
+\end{split}
 \label{eq:admmstopping}\notag
-\end{split}
 \end{equation}
@@
 
-In their 2017 paper, titled \emph{Shrinking Characteristics of Precision Matrix Estimators}, Aaron Molstad, Ph.D.~and Professor Adam Rothman outline a framework to estimate \emph{characteristics} of precision matrices.
+In their 2017 paper, titled \emph{Shrinking Characteristics of Precision Matrix Estimators}, Aaron Molstad, Ph.D.~and Professor Adam Rothman outline a framework to shrink a \emph{characteristic} of a precision matrix.
 This concept, inspired by others like \citet{cai2011direct}, \citet{fan2012road}, and \citet{mai2012direct}, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector.
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
-\end{align}
+\end{split}
+\label{eq:augmentedprecision}
+\end{equation}
 
@@
   &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
+\end{split}
 \label{eq:approx}
-\end{split}
 \end{equation}
@@
   \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
+\end{split}
 \label{eq:augADMM}\notag
-\end{split}
 \end{equation}
@@
 \begin{equation}
-\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+\Lambda^{k + 1} = \Lambda^{k} + \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
 \label{eq:Yk}\notag
@@
   \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
+\end{split}
 \label{eq:scpmestopping}\notag
-\end{split}
 \end{equation}
@@
   &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
+\end{split}
 \label{eq:partialjointloglik}\notag
-\end{split}
 \end{equation}
@@
   &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
+\end{split}
 \label{eq:omegajointloglik}\notag
-\end{split}
 \end{equation}
@@
   &= S - \Omega^{-1} + \Lambda^{k} + \rho\left( \Omega - Z^{k} \right)
+\end{split}
 \label{eq:appendixomegagradient}\notag
-\end{split}
 \end{equation}
@@
   &= \lambda(1 - \alpha)Z + \mbox{sign}(Z)\lambda\alpha - \Lambda^{k} - \rho\left( \Omega^{k + 1} - Z \right)
+\end{split}
 \label{eq:appendixZZgradient}\notag
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\lambda(1 - \alpha) + \rho}\mbox{soft}\left(\rho\Omega_{ij}^{k + 1} + \Lambda_{ij}^{k}, \lambda\alpha\right)
+\end{split}
 \label{eq:appendixZZproof}\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &\in \rho\left( Z^{k + 1} - Z^{k} \right)
+\end{split}
 \label{eq:appendixdualresidual}\notag
-\end{split}
 \end{equation}
@@
   &= \partial g\left(Z^{k + 1}\right) - \Lambda^{k + 1} \\
+\end{split}
 \label{eq:appendixdualopt}\notag
-\end{split}
 \end{equation}
@@
   &+ \rho vec\left(\Omega - \Omega^{k}\right)'vec\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)
+\end{split}
 \label{eq:taylors}\notag
-\end{split}
 \end{equation}
@@
   &+ \rho tr\left[\left(\Omega - \Omega^{k}\right)\left(BB'\Omega^{k}A'A - B(Z^{k})'A - BC'A \right)\right]
+\end{split}
 \label{eq:penapprox}\notag
-\end{split}
 \end{equation}
@@
  tr\left[\left(S + G^{k} \right)\Omega\right] - \log\left|\Omega\right| + \rho\tau\left\|\Omega - \Omega^{k}\right\|_{F}^{2}/2 \right\} \\
+\end{split}
 \label{eq:omegaapprox}\notag
-\end{split}
 \end{equation}
@@
   &+ \frac{\rho\tau}{2}\left[2\Omega - 2(\Omega^{k})' + 2\Omega' - 2\Omega^{k} - 2(\Omega - \Omega^{k})'\circ I_{p} \right]
+\end{split}
 \label{eq:appendixomegagradient2}\notag
-\end{split}
 \end{equation}
@@
   &= \mbox{sign}(Z)\lambda - \Lambda^{k} - \rho\left( A\Omega^{k + 1}B - Z - C \right)
+\end{split}
 \label{eq:appendixZZgradient2}\notag
-\end{split}
 \end{equation}
@@
 &= \frac{1}{\rho}\mbox{soft}\left(\rho\left(A\Omega_{ij}^{k + 1}B - C\right) + \Lambda_{ij}^{k}, \lambda\right)
+\end{split}
 \label{eq:appendixZZproof2}\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &\in \rho\left( B(Z^{k + 1} - Z^{k})'A + A'(Z^{k + 1} - Z^{k})B' \right)/2
+\end{split}
 \label{eq:appendixstopproof}\notag
-\end{split}
 \end{equation}
@@
   \Rightarrow 0 &= S - \hat{\Omega}^{-1} + \frac{\lambda}{2}\left(\mathbb{X}'\mathbb{X}\hat{\Omega}\Sigma_{xy}\Sigma_{xy}' + \Sigma_{xy}\Sigma_{xy}'\hat{\Omega}\mathbb{X}'\mathbb{X} \right) - \lambda\Sigma_{xy}\mathbb{Y}'\mathbb{X}
+\end{split}
 \label{eq:penregressionproof}\notag
-\end{split}
 \end{equation}

### 2019-05-18 03-SCPME.Rmd
bug fix
bug fixes/typos
final edits, fixed sigma_{y | x} typo and design typos

@@
 In their 2017 paper, titled *Shrinking Characteristics of Precision Matrix Estimators*, Aaron Molstad, Ph.D.
-and Professor Adam Rothman outline a framework to estimate *characteristics* of precision matrices.
+and Professor Adam Rothman outline a framework to shrink a *characteristic* of a precision matrix.
 This concept, inspired by others like @cai2011direct, @fan2012road, and @mai2012direct, exploits the fact that in many predictive models estimation of the precision matrix is only necessary through its product with another feature, such as a mean vector.
 The example they offer in @molstad2017shrinking is in the context of Fisher's linear discriminant analysis model.
-If a response vector $Y$ is categorical such that $Y$ can take values in $\left\{1, ..., J\right\}$, then the linear discrimnant analysis model assumes that the design matrix $X$ conditional on the response vector $Y$ is normally distributed:
+If a response vector $Y$ is categorical such that $Y$ can take values in $\left\{1, ..., J\right\}$, then the linear discrimnant analysis model assumes that the predictor matrix $X$ conditional on the response vector $Y$ is normally distributed:
 
@@
 \end{split}
-(#\eq:augmentedprecision)
+(\#eq:augmentedprecision)
 \end{equation}
@@
 \begin{equation}
-\Lambda^{k + 1} = \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
+\Lambda^{k + 1} = \Lambda^{k} + \rho\left( A\Omega^{k + 1} B - Z^{k + 1} - C \right)
 (\#eq:Yk)\notag
@@
 
-Figure \@ref(fig:scpmesim2) displays the model error for each method by dimension of the design matrix.
+Figure \@ref(fig:scpmesim2) displays the model error for each method by dimension of the predictor matrix.
 Here we took the sample size equal to $n = 100$ and the response matrix dimension $r = 10$ with each data generating procedure replicated a total of 20 times.
@@
 ```{r scpmesim2, eval = T, echo = F, fig.cap = "The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
-The model errors (ME) for each estimator with variable dimension of the design matrix are plotted.
+The model errors (ME) for each estimator with variable dimension of the predictor matrix are plotted.
 shrinkBO and shrinkB were the two best-performing estimators closely follow by the ridge and lasso regression estimators."}
@@
   &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
-  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
+  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] \\
   &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)

### 2019-05-18 Manuscript.tex
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:gh-pages

@@
 \author{Matt Galloway}
-\date{2019-05-01}
+\date{2019-05-18}
 
@@
 The example they offer in \citet{molstad2017shrinking} is in the context of Fisher's linear discriminant analysis model.
-If a response vector \(Y\) is categorical such that \(Y\) can take values in \(\left\{1, ..., J\right\}\), then the linear discrimnant analysis model assumes that the design matrix \(X\) conditional on the response vector \(Y\) is normally distributed:
+If a response vector \(Y\) is categorical such that \(Y\) can take values in \(\left\{1, ..., J\right\}\), then the linear discrimnant analysis model assumes that the predictor matrix \(X\) conditional on the response vector \(Y\) is normally distributed:
 
@@
 
-Figure \ref{fig:scpmesim2} displays the model error for each method by dimension of the design matrix.
+Figure \ref{fig:scpmesim2} displays the model error for each method by dimension of the predictor matrix.
 Here we took the sample size equal to \(n = 100\) and the response matrix dimension \(r = 10\) with each data generating procedure replicated a total of 20 times.
@@
 \caption{The oracle precision matrices were tri-diagonal with variable dimension (p) and the data was generated with sample size n = 100 and response vector dimension r = 10.
-The model errors (ME) for each estimator with variable dimension of the design matrix are plotted.
+The model errors (ME) for each estimator with variable dimension of the predictor matrix are plotted.
 shrinkBO and shrinkB were the two best-performing estimators closely follow by the ridge and lasso regression estimators.}\label{fig:scpmesim2}
